### 2019-12-20 mnras_template.tex
Initial Overleaf Import

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib,]{mnras}
\usepackage{lineno}
\linenumbers
% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{booktabs}   % Make tables directly in pandas
\usepackage{longtable}  % Add longer tables
\usepackage{rotating}
\usepackage{appendix}
\usepackage{float}
\usepackage[dvipsnames]{xcolor}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{wrapfig}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\captionsetup{compatibility=false}

\setlength{\rotFPtop}{0pt plus 1fil}% <- add this line after loading rotating
\setlength{\rotFPbot}{0pt plus 1fil}% <- maybe its better to add this line too
\usepackage{threeparttable}
\makeatletter
%\newlength{\abovecaptionskip}%
%\setlength{\abovecaptionskip}{10\p@}
\makeatother
\usepackage{booktabs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
%Co-authors:
\newcommand{\phil}[1]{\color{red}#1 \color{black}}
\newcommand{\mike}[1]{\color{green}#1 \color{black}}
\newcommand{\mat}[1]{\color{magenta}#1 \color{black}}
\newcommand{\lisa}[1]{\color{cyan}#1 \color{black}}
\newcommand{\replyanais}[1]{\color{purple}#1 \color{black}}
\newcommand{\replyravi}[1]{\color{cyan}#1 \color{black}}
\newcommand{\replydillon}[1]{\color{magenta}#1 \color{black}}
\newcommand{\comment}[1]{\textbf{[#1]}} %comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This if a fix from https://tex.stackexchange.com/questions/249579/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink-error-with/249743#249743 to sort hyperref breaking in pdfendlink when a reference spills over a page
\usepackage{etoolbox}
\makeatletter
\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
  \errmessage{\noexpand\@combinedblfloats could not be patched}%
}%
\makeatother

\defcitealias{Smith2019}{S19}
\defcitealias{Kelly2012}{KK12}
%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Supernova hosts in DES]{Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{
P. Wiseman$^1$\thanks{E-mail: p.s.wiseman@soton.ac.uk (PW)},
 M. Pursiainen$^1$,
 M. Smith$^1$,
 M. J. Childress$^1$, 
 L. Kelsey$^1$,
 and Other Authors$^{1,2}$,
\newauthor
(The DES Collaboration)
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK\\
$^{2}$Other Institutions\\
%$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2019}
% These dates will be filled out by the publisher

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Fournier1901},
and describes the problem the authors aim to solve \citep[e.g.][]{vanDijk1902}.
Multiple citations can be joined in a simple way like \citet{deLaguarde1903, delaGuarde1904}.

\section{Methods, Observations, Simulations etc.}

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2019-12-20 RET_Hosts.tex
Updates from Overleaf

--- 2019-12-20 mnras_template.tex
@@
 \newcommand{\phil}[1]{\color{red}#1 \color{black}}
-\newcommand{\mike}[1]{\color{green}#1 \color{black}}
-\newcommand{\mat}[1]{\color{magenta}#1 \color{black}}
-\newcommand{\lisa}[1]{\color{cyan}#1 \color{black}}
-\newcommand{\replyanais}[1]{\color{purple}#1 \color{black}}
-\newcommand{\replyravi}[1]{\color{cyan}#1 \color{black}}
-\newcommand{\replydillon}[1]{\color{magenta}#1 \color{black}}
+
 \newcommand{\comment}[1]{\textbf{[#1]}} %comments
@@
 %This if a fix from https://tex.stackexchange.com/questions/249579/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink-error-with/249743#249743 to sort hyperref breaking in pdfendlink when a reference spills over a page
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
-  \errmessage{\noexpand\@combinedblfloats could not be patched}%
-}%
-\makeatother
-
-\defcitealias{Smith2019}{S19}
-\defcitealias{Kelly2012}{KK12}
+%\usepackage{etoolbox}
+%\makeatletter
+%\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
+%  \errmessage{\noexpand\@combinedblfloats could not be patched}%
+%}%
+%\makeatother
+%
+%\defcitealias{Smith2019}{S19}
+%\defcitealias{Kelly2012}{KK12}
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
@@
  M. J. Childress$^1$,
- L. Kelsey$^1$,
  and Other Authors$^{1,2}$,
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+The advancement of large-area, deep astronomical sky surveys in the past decade has led to a step change in the study of
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Fournier1901},
-and describes the problem the authors aim to solve \citep[e.g.][]{vanDijk1902}.
-Multiple citations can be joined in a simple way like \citet{deLaguarde1903, delaGuarde1904}.
-
-\section{Methods, Observations, Simulations etc.}
+\section{Observations\label{sec:obs}}
 
@@
 
-\subsection{Maths}
-\label{sec:maths} % used for referring to this section from elsewhere
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/RET_MZR.png}
+\caption{The mass-metallicity relation (MZR) for RET host galaxies.
+\label{fig:mzr}}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/}
+\caption{Star-forming galaxy main sequence.
+\label{fig:sfms}}
+\end{figure*}
+\section{Analysis and results}
+\label{sec:analysis} % used for referring to this section from elsewhere
 
@@
 \bibliographystyle{mnras}
-\bibliography{example} % if your bibtex file is called example.bib
+\bibliography{PhilMendeley} % if your bibtex file is called example.bib
 

### 2019-12-23 RET_Hosts.tex
Updates from Overleaf

@@
 
-The advancement of large-area, deep astronomical sky surveys in the past decade has led to a step change in the study of
+In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe).
+Since the turn of the century, observations of CCSNe have been supplemented by two rarer, more exotic transient classes.
+Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
+Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley1996a,Woosley1996b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
+and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g.
+\citealt{Quimby2011; Gal-Yam2012})
 
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figs/}
-\caption{Star-forming galaxy main sequence.
+\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
+\caption{The sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
 \label{fig:sfms}}

### 2019-12-23 RET_Hosts.tex
Updates from Overleaf

@@
 
-\begin{figure*}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
+\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfms_sfr}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
+\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfr_cum}}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
 \caption{The sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfms}}
-\end{figure*}
+\label{fig:sfms_ssfr}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
+\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfr_cum}}
+\end{figure}
+
 \section{Analysis and results}

### 2020-01-02 RET_Hosts.tex

@@
 Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
-Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley1996a,Woosley1996b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
+Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
 and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g.
-\citealt{Quimby2011; Gal-Yam2012})
+\citealt{Quimby2011, Gal-Yam2012})
 
@@
 \label{sec:analysis} % used for referring to this section from elsewhere
-
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
-
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
-
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
-
-\subsection{Figures and tables}
-
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
-
-Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-e.g. Table~\ref{tab:example_table}.
-
-% Example figure
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
-\end{figure}
-
-% Example table
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
 

### 2020-01-09 RET_Hosts.tex

@@
 \newcommand{\comment}[1]{\textbf{[#1]}} %comments
-
+\defcitealias{Pursiainen2018}{P18}
+\defcitealias{Pursiainen2020}{P20}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2019}
+\pubyear{2020}
 % These dates will be filled out by the publisher
@@
 Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
-Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
-and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g.
+Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}, and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g.
 \citealt{Quimby2011, Gal-Yam2012})
 
-\section{Observations\label{sec:obs}}
+\section{Sample selection\label{sec:sample}}
 
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey.
+This number expands upon the 72 of \citetalias{Pursiainen2018} and is presented in a companion work \citetalias{Pursiainen2020}.
+We refer to the full sample as DES RETs.
+In order to calculate host galaxy properties Of the 106 objects in the sample, \textbf{n} have a host galaxy detected in deep host galaxy photometry (Section \ref{sec:obs}), of which 49 have a host galaxy spectroscopic redshift.
+A further two have redshifts
+
+\section{Host galaxy observations\label{sec:obs}}
 
@@
 
-\section{Analysis and results}
+\section{Host galaxy properties}
 \label{sec:analysis} % used for referring to this section from elsewhere
+\subsection{Stellar Mass \label{subsec:res_mass}}
+
+\subsection{Star formation rate \label{subsec:res_sfr}}
+
+\subsection{Metallicity \label{subsec:res_metallicity}}
+
+\section{Discussion \label{sec:disc}}
+
+\subsection{Transient - host galaxy correlations}
 

### 2020-01-15 RET_Hosts.tex

@@
 
+The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which was based upon deep coadds reaching $g$-band limiting magnitudes of 27.
+
 \begin{figure*}
@@
 \label{sec:analysis} % used for referring to this section from elsewhere
+
+To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
+
 \subsection{Stellar Mass \label{subsec:res_mass}}

### 2020-01-15 RET_Hosts.tex
Updates from Overleaf

@@
 
-The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which was based upon deep coadds reaching $g$-band limiting magnitudes of 27.
+The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which is based upon deep coadds reaching $g$-band limiting magnitudes of 27.
 

### 2020-01-16 RET_Hosts.tex

@@
 \newcommand{\comment}[1]{\textbf{[#1]}} %comments
+
+%define some nice astro shortcuts
+\newcommand{\halpha}[0]{H$\alpha$}
+\newcommand{\hbeta}[0]{H$\beta$}
+\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
+\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
+\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
+\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
+\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
+
 \defcitealias{Pursiainen2018}{P18}
@@
 
-\section{Host galaxy observations\label{sec:obs}}
+\section{Host galaxy observations \label{sec:obs}}
+\subsection{Photometry \label{subsec:phot}}
 
-The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which is based upon deep coadds reaching $g$-band limiting magnitudes of 27.
+The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which is based upon deep coadds reaching $r$-band limiting magnitudes of 26.5.
+The coadds were created using data from all five seasons of DES-SN, but by excluding one season at a time in order for that coadd not to include contamination from the transients in that season.
+For this sample, the limiting magnitude for obtaining a spectroscopic redshift (\ref{subsec:spec}) is $\sim 24.5$, meaning that all hosts in the sample are detected with a high S/N.
+
+\subsection{Spectroscopy \label{subsec:spec}}
+Accurate redshifts for DES-SN were obtained by OzDES\footnote{Australian (Oz) Dark Energy Survey}, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner.
+The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient.
+The spectra have a resolution of 1400-1700 and a wavelength range of 3700$\AA - 8800\AA$, and are reduced using a modified version of 2dfdr \citep{Croom2004} along with internal scripts.
+Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
+
+\section{Estimating host galaxy properties \label{sec:measure}}
+
+\subsection{SED fitting \label{subsec:sedfit}}
+
+To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
+
+\subsection{Spectral line fitting \label{subsec:linefit}}
+
+To estimate parameters from the OzDES host galaxy spectra requires several processing steps.
+We first apply a flux calibration using the method of \citet{Swann2020}, by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry.
+Rather than using global galaxy photometry (i.e.
+using a Kron aperture), we use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
+
+In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}.
+By subtracting the best-fitting stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines.
+We fit the emission lines using \texttt{PySpecKit} \citep{Ginsburg2011}.
+In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding a perturbation to the amplitude of the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in that part of the spectrum.
+We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
+
+\subsection{Estimating metallicities \label{subsec:calc_Z}}
+
+The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium.
+Due to the low S/N of the spectra in this sample, we are constrained to a subset of these diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959 and 5007, \NII 6548 and 6583, and \SII 6717 and 6731.
+Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII and \SII are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen lines available, mandating the use of the R23 diagnostic.
+For hosts at $z<0.3$ we are able to use the \OIII /\NII (O3N2) and \NII /\halpha (N2) line ratios.
+
+For the R23 indicator, we use the calibration of \citet{Pettini2004}, while for O3N2 and N2, we use the calibration of \citet{Kubulnicky2004}.
+In order to compare metallicities from our sample to those field galaxies from the Sloan Digital Sky Survey (SDSS), as well as to the sample of CCSNe from \citet{Kelly2012}, we scale the results to match the calibration of \citet{Tremonti2004} via the scaling factors outlined in \citet{Kewley2008}.
 
@@
 
-\section{Host galaxy properties}
+\section{Analysis and Discussion}
 \label{sec:analysis} % used for referring to this section from elsewhere
-
-To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
 

### 2020-01-17 RET_Hosts.tex
Updates from Overleaf

@@
 \newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
+\newcommand{\msun}[0]{M_{\odot}}
 
@@
 
+It is common also to consider metallicity as a factor driving the production of catastrophic stellar explosions.
+At the extreme end, both GRBs and SLSNe appear to require a low metallicity: for GRBs this threshold has been observed between 0.5 and 1 times the solar value \citep{Perley2016b,Japelj2016,Vergani2017}, while for SLSNe the value is somewhere around half-solar \citep{Lunnan2014,Chen2016a}.
+
 \section{Sample selection\label{sec:sample}}
@@
 A further two have redshifts
+
+\subsection{Comparison samples \label{subsec:comparison}}
 
@@
 \caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfr_cum}}
+\label{fig:ssfr_cum}}
 \end{figure}
@@
 \subsection{Star formation rate \label{subsec:res_sfr}}
+Fig.
+\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for CCSNe and for the field galaxies of SDSS.
+RETs and CCSNe both systematically avoid passive galaxies, suggesting that RETs may require the presence of star-formation and thus be linked to massive stars.
+
+In Fig.
+\ref{fig:sfr_cum} we show the cumulative distributions of the star-formation rate in RETs, CCSNe, and SDSS galaxies.
+With the exception of three objects, all RETs occured in galaxies with $\textrm{SFR}>0.1 \msun$yr$^{-1}$, and the curve is shifted towards higher SFRs than that for CCSNe.
+This would imply that a higher SFR is required for RETs to occur - or can be thought of as a higher SFR threshold for the formation of a RET progenitor.
+
+Fig.
+\ref{fig:sfms_ssfr} is similar to Fig.
+\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming nature of the galaxy itself.
+It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.
+Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts.
+
+As for SFR, we show the cumulative distribution of sSFR in Fig.
+\ref{fig:ssfr_cum}.
+The RET hosts are clearly shifted higher sSFRs than CCSNe.
+This result is significant as there are no obvious selection effects which could cause the shift.
 
 \subsection{Metallicity \label{subsec:res_metallicity}}
+
+In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars.
+A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity.
+Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we sIn Fig.
+\ref{fig:mzr}
 

### 2020-01-22 RET_Hosts.tex
Updates from Overleaf

@@
 
-\begin{figure*}
-\includegraphics[width=\textwidth]{figs/RET_MZR.png}
-\caption{The mass-metallicity relation (MZR) for RET host galaxies.
-\label{fig:mzr}}
-\end{figure*}
-
 \begin{figure}
@@
 \subsection{Star formation rate \label{subsec:res_sfr}}
-Fig.
-\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for CCSNe and for the field galaxies of SDSS.
+Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for CCSNe and for the field galaxies of SDSS.
 RETs and CCSNe both systematically avoid passive galaxies, suggesting that RETs may require the presence of star-formation and thus be linked to massive stars.
 
-In Fig.
-\ref{fig:sfr_cum} we show the cumulative distributions of the star-formation rate in RETs, CCSNe, and SDSS galaxies.
+In Fig.~\ref{fig:sfr_cum} we show the cumulative distributions of the star-formation rate in RETs, CCSNe, and SDSS galaxies.
 With the exception of three objects, all RETs occured in galaxies with $\textrm{SFR}>0.1 \msun$yr$^{-1}$, and the curve is shifted towards higher SFRs than that for CCSNe.
@@
 
-Fig.
-\ref{fig:sfms_ssfr} is similar to Fig.
-\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming nature of the galaxy itself.
+Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming nature of the galaxy itself.
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.
@@
 
-As for SFR, we show the cumulative distribution of sSFR in Fig.
-\ref{fig:ssfr_cum}.
+As for SFR, we show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}.
 The RET hosts are clearly shifted higher sSFRs than CCSNe.
@@
 \subsection{Metallicity \label{subsec:res_metallicity}}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
+\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:oh_cum}}
+\end{figure}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/RET_MZR.png}
+\caption{The mass-metallicity relation (MZR) for RET host galaxies.
+\label{fig:mzr}}
+\end{figure*}
 
@@
 A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity.
-Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we sIn Fig.
-\ref{fig:mzr}
+Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies.
+The cumulative distributions of metallicity are displayed in \ref{fig:oh_cum}, and show RET hosts to be consistent with CCSNe and field galaxies.
+While the RET curve lies at lower metallicity than CCSNe and field galaxies in the $8.4 < \log \left(12+\textrm{O/H}\right)<9.0$ range, this is entirely within the $1\sigma$ uncertainty region for the RET host CDF.
+In Fig.~\ref{fig:mzr} we show the mass-metallicity relation (MZR) for the RET and comparison samples.
 

### 2020-01-28 RET_Hosts.tex
Writing intro

@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+Rapidly evolving transients (RETs) are a mysterious class of astrophysical event.
+They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
 \end{abstract}
@@
 In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe).
-Since the turn of the century, observations of CCSNe have been supplemented by two rarer, more exotic transient classes.
+Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
+
  Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
-Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}, and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g.
-\citealt{Quimby2011, Gal-Yam2012})
+Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
+The second exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g.
+\citealt{Quimby2011, Gal-Yam2012}).
+Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2010,Grayling2020}.
+The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly-formed magnetar.
 
-It is common also to consider metallicity as a factor driving the production of catastrophic stellar explosions.
-At the extreme end, both GRBs and SLSNe appear to require a low metallicity: for GRBs this threshold has been observed between 0.5 and 1 times the solar value \citep{Perley2016b,Japelj2016,Vergani2017}, while for SLSNe the value is somewhere around half-solar \citep{Lunnan2014,Chen2016a}.
+ Along with observations of the transients themselves, host galaxies are frequently-used laboratories from which strong inferences about the progenitor stars and explosion mechanisms can be made.
+Core-collapse SNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars.
+There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
+On average, stripped envelope SNe (SESNe; types Ib, Ic and their sub-types) reside in galaxies with higher specific star-formation rate (sSFR) and younger stellar age \citep{Galbany2018}, indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II.
+
+ Metallicity is an important consideration when comparing host galaxy properties.
+While it does not appear to play a significant role in the relative production of CCSNe (although there are some trends, with SESNe typically found in slightly less metal-rich galaxies than SNe II), it appears to be vitally important in the production of LGRBs and SLSNe.
+Theory predicts that the production of a LGRB should only be possible in stars with a metallicity of $Z/Z_{\sun}\leq 0.3$ \citep{Woosley1993}  in order for the likely Wolf-Rayet or blue supergiants progenitors not to lose their outer atmospheres through metal-driven winds, thus conserving sufficient angular momentum to power the black-hole-driven jet or rapidly rotating magnetar.
+Many LGRB host galaxy studies have indeed revealed a metallicity threshold to be observed between 0.5 and 1 times the solar value \citep[e.g.][]{Stanek2006,Modjaz2008,Kruehler2015,Perley2016b,Japelj2016,Vergani2017}.
+SLSN host galaxies also appear to be lower in metallicity than would be expected for their stellar mass, with a suppression of SLSN production at a value around half-solar \citep{Lunnan2014,Chen2016a,Perley2016c}.
+They also require particularly high sSFR, suggesting that they are explosions of very young, rapidly rotating massive stars.
+
+Recently, inspection of high-cadence, all-sky survey data sets have revealed yet more exotic transients that are less easy to explain with conventional models.
+\citet{Drout2014} revealed a class of rapidly evolving transients (RETs) in the Pan-STARRS survey (PS1).
+\citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
+RETs typically rise to peak brightness within 7-10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
+The photometric measurements of the PS1 and DES RETs seem to be well described by simple expanding blackbodies, although a handful show declining photospheric radii from the outset.
+Due to the rapid nature of their lightcurves and location at high-redshift, spectral coverage is sparse and signal-to-noise ratio (SNR) is low, such that there has not yet been a conclusive detection of absorption or emission features from the transients.
+
+There are a limited number of local analogues to the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.]{Prentice2019,Lyman2019,Perley2019}.
+The transient declined from its discovery, with constraints on a ~1 day rise time, and did not resemble any known SN, GRB afterglow, or kilonova (KN).
+Other nearby rapid transients include the local fast-declining SN Ibn SN2018kzr \citep{McBrien2020}, and KSN-2015K \citep{Rest2018}. It is currently unclear whether these transients
+
+In this paper, we present the first comprehensive study of the host galaxies of rapidly evolving transients.
+We make use of the final DES sample, which builds on \citet{Pursiainen2018} using the final year of data as well as more refined discovery techniques.
+Using the deep DES photometry from \citet{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe.
+
+The order of the paper is as follows:
+Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$.
 
@@
 \subsection{Comparison samples \label{subsec:comparison}}
+
+In order to compare the host galaxies of DES RETs to those discovered in other surveys as well as other types of explosive transient, we draw upon samples in the literature.
+
+\subsubsection{RETs \label{subsubsec:compare_rets}}
+Since the DES sample of RETs is by far the largest discovered to date, there is no other large sample of RETs with which to compare host galaxy properties.
+\citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses and SFRs.
+To this we add the low-redshift transients AT2018cow \citep[e.g.][], with host galaxy measurements from \citet{Perley2019} (Metallicity??), and SN2018kzr (measurements??).
+
+\subsubsection{SNe and GRBs \label{subsubsec:compare_CCSNe}}
+
+To compare with CCSNe, we draw on the PMAS/PPak Integral-field Supernova hosts COmpilation (PISCO) sample presented in \citet{Galbany2018}.
+
+We use the sample of GRB host galaxies of \citet{Kruehler2015}, using only galaxies with $z<1$ in order to maintain completeness.
+
+To investigate similarities with CCSNe, we use the PTF sample of \citet{Perley2016c}
 
@@
 
-For the R23 indicator, we use the calibration of \citet{Pettini2004}, while for O3N2 and N2, we use the calibration of \citet{Kubulnicky2004}.
-In order to compare metallicities from our sample to those field galaxies from the Sloan Digital Sky Survey (SDSS), as well as to the sample of CCSNe from \citet{Kelly2012}, we scale the results to match the calibration of \citet{Tremonti2004} via the scaling factors outlined in \citet{Kewley2008}.
+For the R23 indicator, we use the calibration of \citet{Pettini2004} (PP04), while for O3N2 and N2, we use the calibration of \citet{Marino2013} (M13) in order to directly compare metallicity with the Pisco CCSN sample.
+We recalculate the metallicities given in \citet{Kruehler2015} using the M13 calibration.
 

### 2020-01-28 RET_Hosts.tex

@@
 
-There are a limited number of local analogues to the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.]{Prentice2019,Lyman2019,Perley2019}.
-The transient declined from its discovery, with constraints on a ~1 day rise time, and did not resemble any known SN, GRB afterglow, or kilonova (KN).
-Other nearby rapid transients include the local fast-declining SN Ibn SN2018kzr \citep{McBrien2020}, and KSN-2015K \citep{Rest2018}. It is currently unclear whether these transients
+There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}.
+The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN) \citep{Ho2019}.
+There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN) \citep{Soker2019}
+Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf in a non-standard scenario, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
+It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.
 
@@
 We make use of the final DES sample, which builds on \citet{Pursiainen2018} using the final year of data as well as more refined discovery techniques.
-Using the deep DES photometry from \citet{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe.
+Using the deep DES photometry from \citet{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
+For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.
 

### 2020-01-29 RET_Hosts.tex

@@
 \citealt{Quimby2011, Gal-Yam2012}).
-Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2010,Grayling2020}.
+Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2011,Grayling2020}.
 The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly-formed magnetar.
@@
 There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
-On average, stripped envelope SNe (SESNe; types Ib, Ic and their sub-types) reside in galaxies with higher specific star-formation rate (sSFR) and younger stellar age \citep{Galbany2018}, indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II.
+On average, stripped envelope SNe (SESNe; types Ib, Ic and their sub-types) reside in galaxies with higher specific star-formation rate (sSFR) and younger stellar age \citep{Galbany2018}, indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II.-
 

### 2020-02-07 RET_Hosts.tex

@@
 Due to the low S/N of the spectra in this sample, we are constrained to a subset of these diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959 and 5007, \NII 6548 and 6583, and \SII 6717 and 6731.
-Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII and \SII are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen lines available, mandating the use of the R23 diagnostic.
-For hosts at $z<0.3$ we are able to use the \OIII /\NII (O3N2) and \NII /\halpha (N2) line ratios.
+Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII and \SII are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta lines available, mandating the use of the R23 diagnostic.
+For hosts at $z<0.3$ we are able to use the \OIII /\NII (O3N2), \NII /\halpha (N2), and \SII /\NII (S2N2) line ratios.
 
-For the R23 indicator, we use the calibration of \citet{Pettini2004} (PP04), while for O3N2 and N2, we use the calibration of \citet{Marino2013} (M13) in order to directly compare metallicity with the Pisco CCSN sample.
+Due to the redshift rangeTo begin, we determine a set of indicators for which to calculate abundances for our DES RET sample.
+For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}.
+For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04).
+At abundances around $12 + \log mathrm{O/H} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio.
+In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII / \OII ratio \citep{Kewley2008}.
+In the cases where \NII is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy mass to derive a crude metallicity estimate from the MZR of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic.
+For $12 + \log mathrm{O/H}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.
+
+To
+
 We recalculate the metallicities given in \citet{Kruehler2015} using the M13 calibration.

### 2020-02-07 RET_Hosts.tex

@@
 To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
+We use \citet{Bruzual2003} models and a \citet{Chabrier2003} initial mass function (IMF).
+From the synthetic spectra we derive model magnitudes in the DES $griz$ bands and compare them to the observed magnitudes.
+For each set of model and observed magnitudes we calculate a $\chi^2$ value and adopt the $M/L$ and SFR from model with the lowest $\chi^2$ as our best estimates.
+To estimate uncertainties, we interpolate between the next best fitting models and take the values at the 16th and 84th percentiles to be our $1\sigma$ lower and upper bounds.
 
@@
 
-Due to the redshift rangeTo begin, we determine a set of indicators for which to calculate abundances for our DES RET sample.
+Due to the redshift range of our sample, and the limited wavelength coverage of the spectra ($3000-8000~\AA$), we are unable to use a single line ratio to estimate the oxygen abundances.
+We thus determine a set of indicators for which to calculate abundances.
 For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}.
@@
 
-To
-
-We recalculate the metallicities given in \citet{Kruehler2015} using the M13 calibration.
+The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised.
+Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the scale of PP04 (O3N2) using the conversion from \citet{Kewley2008}.
+This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide for DES RET hosts where available.
+For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we calculate a weighted average of the values after transforming them to the PP04 O3N2 scale.
 

### 2020-02-13 RET_Hosts.tex
Updates from Overleaf

@@
 For each set of model and observed magnitudes we calculate a $\chi^2$ value and adopt the $M/L$ and SFR from model with the lowest $\chi^2$ as our best estimates.
-To estimate uncertainties, we interpolate between the next best fitting models and take the values at the 16th and 84th percentiles to be our $1\sigma$ lower and upper bounds.
+To estimate uncertainties, we ??
+and take the values at the 16th and 84th percentiles to be our $1\sigma$ lower and upper bounds.
 
@@
 For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04).
-At abundances around $12 + \log mathrm{O/H} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio.
+At abundances around $12 + \log \mathrm{(O/H)} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio.
 In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII / \OII ratio \citep{Kewley2008}.
 In the cases where \NII is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy mass to derive a crude metallicity estimate from the MZR of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic.
-For $12 + \log mathrm{O/H}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.
+For $12 + \log \mathrm{(O/H)}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.
 
@@
 This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide for DES RET hosts where available.
-For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we calculate a weighted average of the values after transforming them to the PP04 O3N2 scale.
+For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we calculate a weighted mean of the values after transforming them to the PP04 O3N2 scale.
 
@@
 
+\subsection{Metallicity}
+
+The sample of DES RETs shows a preference for low metallicity host environments.
+The PDF displays a strong similarity to the hosts of SNe Ibc, as well as LGRBs.
+There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies.
+The aversion of high-metallicity systems is not as strong as for SLSNe.
+On first viewing, this is suggestive of a stripped-envelope, massive-star origin for RETs.
+There are however several selection biases that need to be considered.
+
 \section{Conclusions}

### 2020-02-14 RET_Hosts.tex
Adding to metallicity discussion

@@
 There are however several selection biases that need to be considered.
+Firstly, metallicity PDF is derived from a subset of the total sample of RETs.
+under half (49/106) have secure host galaxy redshifts, of which it was possible to derive a metallicity for 37 host galaxies.
+If the galaxies without redshifts and metallicities are systematically higher in metallicity than those for which measurements were possible,
 

### 2020-02-17 RET_Hosts.tex
Updates from Overleaf

--- 2020-02-13 RET_Hosts.tex
@@
 
+\subsection{Selection Biases \label{subsec:disc_bias}}
+The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs.
+Of 106 objects, under half (49/106) have secure host galaxy redshifts.
+Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and six were obtained by programmes for which we do not have access to the spectra.
+Of the remaining 42, it was possible to derive a metallicity for 37 host galaxies.
+The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible.
+This scenario is unlikely.
+For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g.
+\halpha, \hbeta, \OIII, and \OII), whose absolute luminosity is not strongly dependent on metallicity.
+It is likely that the redshifts were not obtained because of low SNR, caused by the galaxies being smaller and at higher redshift.
+We do not envisage a plausible scenario where those galaxies are systematically higher in metallicity.
+
+Another possibility is that the hosts without a redshift are mostly non-starforming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}.
+In order to test this possibility, we examined the RETs that do not have a host galaxy redshift.
+Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process.
+Of the 48 objects without a redshift, 40 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}.
+Of more significance is that only 34 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign.
+The other, `hostless', objects are either transients that are located remotely from a host that was detected, or are hosted by a galaxy that was not detected.
+Non-detected hosts are either intrinsically faint and thus low in mass, situated at high redshift, or both.
+Neither are expected to be systematically higher in metallicity than the detected hosts.
+Similarly, a further 16 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found.
+The resulting redshift completeness of targetted objects is 70\% (82\% for objects brighter than $m_r = 24$~mag, which is in line with the average for OzDES as a whole \citep{Lidman2020}.
+In Fig.
+\ref{fig:g-r} we show the observer-frame $i$-band magnitudes and $g-r$ colours for all RET hosts that were detected.
+The 40 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts.
+This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.
+
+\begin{table}
+    \centering
+    \begin{tabular}{l|l}
+         Cut &  Number of remaining objects \\
+        \toprule
+        All RETs & 106 \\
+        No redshift   & 48\\
+        Host in SN Deep & 40\\
+        Host in SVA1 & 34 \\
+        Targetted by OzDES & 18 \\
+        \bottomrule
+    \end{tabular}
+    \caption{Numbers of RETs passing various cuts relating to redshift targetting.}
+    \label{tab:z_cuts}
+\end{table}
+
 \subsection{Metallicity}
@@
 The PDF displays a strong similarity to the hosts of SNe Ibc, as well as LGRBs.
-There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies.
-The aversion of high-metallicity systems is not as strong as for SLSNe.
-On first viewing, this is suggestive of a stripped-envelope, massive-star origin for RETs.
-There are however several selection biases that need to be considered.
+There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies, while the aversion of high-metallicity systems is not as strong as for SLSNe.
+This result is suggestive of a stripped-envelope, massive-star origin for RETs.
 

### 2020-02-17 RET_Hosts.tex

@@
 Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
+\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES.
+The orange histogram represents the 97/106 DES RETs for which a host was detected.
+The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
+\label{fig:sfms_sfr}}
+\end{figure}
 

### 2020-02-17 RET_Hosts.tex
Updates from Overleaf

@@
 The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
-\label{fig:sfms_sfr}}
+\label{fig:mag_dist}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/z_dist.png}
+\caption{Redshift distribution for the host galaxies of RETs in DES for which a measurement was obtained.
+\label{fig:z_dist}}
 \end{figure}
@@
 We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey.
-This number expands upon the 72 of \citetalias{Pursiainen2018} and is presented in a companion work \citetalias{Pursiainen2020}.
+This number expands upon the 72 of \citetalias{Pursiainen2018}.
+and is presented in a companion work \citetalias{Pursiainen2020}.
 We refer to the full sample as DES RETs.
 In order to calculate host galaxy properties Of the 106 objects in the sample, \textbf{n} have a host galaxy detected in deep host galaxy photometry (Section \ref{sec:obs}), of which 49 have a host galaxy spectroscopic redshift.
-A further two have redshifts
+A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves.
+We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
 

### 2020-02-17 RET_Hosts.tex
Updates from Overleaf

@@
 In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe).
+CCSNe can be split into observationally-determinded subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
+Conversely, SNe Ib and Ic do not show signatures of hydrogen and are thus referred to collectively as stripped-envelope SNe (SESNe).
+The SN IIb subclass, which shows hydrogen only at early epochs, is also commonly grouped along with SESNe.
 Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
 
- Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
-Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
+ Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
+Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
 The second exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g.
 \citealt{Quimby2011, Gal-Yam2012}).
-Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2011,Grayling2020}.
-The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly-formed magnetar.
+Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2011,Grayling2020}.
+The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly formed, rapidly rotating magnetar.
 
  Along with observations of the transients themselves, host galaxies are frequently-used laboratories from which strong inferences about the progenitor stars and explosion mechanisms can be made.
-Core-collapse SNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars.
+CCSNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars.
 There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
-On average, stripped envelope SNe (SESNe; types Ib, Ic and their sub-types) reside in galaxies with higher specific star-formation rate (sSFR) and younger stellar age \citep{Galbany2018}, indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II.-
+On average, SESNe reside in galaxies with higher specific star-formation rate (sSFR) and younger stellar age indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II \citep{James2006,Kelly2008,Galbany2018}.
+More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
 
- Metallicity is an important consideration when comparing host galaxy properties.
-While it does not appear to play a significant role in the relative production of CCSNe (although there are some trends, with SESNe typically found in slightly less metal-rich galaxies than SNe II), it appears to be vitally important in the production of LGRBs and SLSNe.
+ The chemical composition of the interstellar medium (ISM) is an important consideration when comparing host galaxy properties.
+While it does not appear to play a significant role in the relative production of CCSNe (although there are some trends, with SESNe typically found in slightly less metal-rich galaxies than SNe II; \citealt{Galbany2018}), it appears to be vitally important in the production of LGRBs and SLSNe.
 Theory predicts that the production of a LGRB should only be possible in stars with a metallicity of $Z/Z_{\sun}\leq 0.3$ \citep{Woosley1993}  in order for the likely Wolf-Rayet or blue supergiants progenitors not to lose their outer atmospheres through metal-driven winds, thus conserving sufficient angular momentum to power the black-hole-driven jet or rapidly rotating magnetar.
@@
 Recently, inspection of high-cadence, all-sky survey data sets have revealed yet more exotic transients that are less easy to explain with conventional models.
-\citet{Drout2014} revealed a class of rapidly evolving transients (RETs) in the Pan-STARRS survey (PS1).
+\citet{Drout2014} revealed a class of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
 \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
@@
 The photometric measurements of the PS1 and DES RETs seem to be well described by simple expanding blackbodies, although a handful show declining photospheric radii from the outset.
-Due to the rapid nature of their lightcurves and location at high-redshift, spectral coverage is sparse and signal-to-noise ratio (SNR) is low, such that there has not yet been a conclusive detection of absorption or emission features from the transients.
+Due to the rapid nature of their lightcurves and location at high-redshift, spectral coverage is sparse and signal-to-noise ratio (SNR) is low, such that there has not yet been a conclusive detection of absorption or emission features from the transients and thus the physical mechanism responsible for their rapid evolution remains unexplained.
 
@@
 
-In this paper, we present the first comprehensive study of the host galaxies of rapidly evolving transients.
+In this paper, we present the first comprehensive study of the host galaxies of RETs.
 We make use of the final DES sample, which builds on \citet{Pursiainen2018} using the final year of data as well as more refined discovery techniques.
@@
 
-To compare with CCSNe, we draw on the PMAS/PPak Integral-field Supernova hosts COmpilation (PISCO) sample presented in \citet{Galbany2018}.
-
+To compare with CCSNe, we draw on the sample of SNe II from PTF \citep{Stoll2013} and the compilation of untargeted SESNe from \citet{Sanders2012}.
 We use the sample of GRB host galaxies of \citet{Kruehler2015}, using only galaxies with $z<1$ in order to maintain completeness.
-
-To investigate similarities with CCSNe, we use the PTF sample of \citet{Perley2016c}
+To investigate similarities with SLSNe, we use the PTF sample of \citet{Perley2016c}.
 

### 2020-02-18 RET_Hosts.tex
Updates from Overleaf

@@
 and is presented in a companion work \citetalias{Pursiainen2020}.
+
 We refer to the full sample as DES RETs.
-In order to calculate host galaxy properties Of the 106 objects in the sample, \textbf{n} have a host galaxy detected in deep host galaxy photometry (Section \ref{sec:obs}), of which 49 have a host galaxy spectroscopic redshift.
+Of the 106 objects in the sample, 97 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift.
 A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves.

### 2020-02-18 RET_Hosts.tex

@@
 
-Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming nature of the galaxy itself.
+Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming intensity compared to galaxies of the same mass.
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.

### 2020-02-19 RET_Hosts.tex

@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/mag_v_colour.png}
+\caption{The colour-magnitude distribution of RET hosts with (cyan) and without (orange) redshifts. There is an excess of objects with blue colours that do not have redshift measurements.
+\label{fig:g-i}}
+\end{figure}
+
 In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars.
@@
 In Fig.
-\ref{fig:g-r} we show the observer-frame $i$-band magnitudes and $g-r$ colours for all RET hosts that were detected.
+\ref{fig:g-i} we show the observer-frame $r$-band magnitudes and $g-i$ colours for all RET hosts that were detected.
 The 40 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts.

### 2020-02-21 RET_Hosts.tex
Updates from Overleaf

@@
  M. Pursiainen$^1$,
+ M. J. Childress$^1$,
  M. Smith$^1$,
- M. J. Childress$^1$,
  and Other Authors$^{1,2}$,
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
+\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfms_sfr}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
+\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfr_cum}}
+\end{figure}
+
 \section{Sample selection\label{sec:sample}}
@@
 This number expands upon the 72 of \citetalias{Pursiainen2018}.
-and is presented in a companion work \citetalias{Pursiainen2020}.
+The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years.
+The second reason is an update to the sample selection technique.
+In \citetalias{Pursiainen2018}, objects were highlighted based on various lightcurve criteria such as time of rise to peak brightness ($t_{\mathrm{rise}}$), time of decline ($t_{\mathrm{decl}}$), and lightcurve `full-width half-maximum' ($t_{\mathrm{FWHM}}$).
+Candidates fitting these criteria were then vetted manually in order to make the final sample.
+The manual vetting included a removing a large number of active galactic nuclei (AGN).
+In this work, we expand upon this procedure with the introduction of a machine learning technique
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
-\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfms_sfr}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
-\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfr_cum}}
-\end{figure}
-
-\begin{figure}
 \includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
@@
 As for SFR, we show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}.
-The RET hosts are clearly shifted higher sSFRs than CCSNe.
-This result is significant as there are no obvious selection effects which could cause the shift.
+The RET hosts are clearly shifted to higher sSFRs than CCSNe.
+To compare statistically the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}.
+For each pair of samples, we model the PDFs as skewed normal distributions.
+For both samples, we use identical normal priors for the `mean' and `scale'\footnote{See \citet{Wiseman2020} for a detailed description of the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
 
 \subsection{Metallicity \label{subsec:res_metallicity}}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
+\caption{The mass-metallicity relation (MZR) for RET host galaxies.
+\label{fig:mzr}}
+\end{figure}
+
 \begin{figure}
@@
 \end{figure}
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{figs/RET_MZR.png}
-\caption{The mass-metallicity relation (MZR) for RET host galaxies.
-\label{fig:mzr}}
-\end{figure*}
 
@@
 Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies.
-The cumulative distributions of metallicity are displayed in \ref{fig:oh_cum}, and show RET hosts to be consistent with CCSNe and field galaxies.
-While the RET curve lies at lower metallicity than CCSNe and field galaxies in the $8.4 < \log \left(12+\textrm{O/H}\right)<9.0$ range, this is entirely within the $1\sigma$ uncertainty region for the RET host CDF.
+The cumulative distributions of metallicity are displayed in \ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies.
+The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe.
+RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
+
+We compare the metallicity distributions in the same way as the sSFRs.
+The RET host metallicity distribution is significantly different to the SNe II and SDSS distributions, with no overlap in the posterior distributions for the skewed-normal distribution peak and skewness.
+On the other hand, simultaneous fits with SESNe show very similar distributions.
+
 In Fig.~\ref{fig:mzr} we show the mass-metallicity relation (MZR) for the RET and comparison samples.

### 2020-02-24 RET_Hosts.tex
Updates from Overleaf

@@
 They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
+Their evolution on fast timescales has hindered high quality follow-up observations, such that their origin and explosion/emission mechanism remains unexplained.
+In this paper, we investigate the host galaxies of the largest RET sample to date from the Dark Energy Survey (DES).
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar mass, star-formation rate (SFR), and metallicity for 42 hosts.
+We find that RETs explode almost exclusively in star-forming galaxies and are thus likely associated with massive stars.
+Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFR, indicating a link to young stellar populations stripped-envelope SNe.
+RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SNe host galaxies.
+
 \end{abstract}
@@
 
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/RET_Mosaic.png}
+\caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ bands. The locations of the transients are indicated with cyan crosses.
+\label{fig:mag_dist}}
+\end{figure*}
+
 \begin{figure}
@@
 
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
-\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfms_sfr}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
-\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfr_cum}}
-\end{figure}
-
 \section{Sample selection\label{sec:sample}}
@@
 The second reason is an update to the sample selection technique.
-In \citetalias{Pursiainen2018}, objects were highlighted based on various lightcurve criteria such as time of rise to peak brightness ($t_{\mathrm{rise}}$), time of decline ($t_{\mathrm{decl}}$), and lightcurve `full-width half-maximum' ($t_{\mathrm{FWHM}}$).
-Candidates fitting these criteria were then vetted manually in order to make the final sample.
-The manual vetting included a removing a large number of active galactic nuclei (AGN).
-In this work, we expand upon this procedure with the introduction of a machine learning technique
+By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 96 objects.
 
-We refer to the full sample as DES RETs.
+\subsection{Improvements to the search method}
+
+The original method of finding RETs in the DES-SN data (and presented in \citetalias{Pursiainen2018}) was designed to be simple and used light curve modelling with Gaussian and linear fits.
+The simplistic method made it possible to look for exotic transients without knowing their observed characteristics beforehand and resulted in a large sample of photometrically selected fast transients.
+However, as the search was simplistic and relied heavily on visual inspection of the available data (etc.
+images, light curves, host galaxy information), it is impossible to be sure how complete the sample is.
+For instance, due to the large redshift range within the sample it is entirely possible that distant events could have been missed due to time dilation.
+Here, a more sophisticated search method is presented.
+As only a fraction of transients in DES-SN have redshift information from host galaxy, the search must be done in the observer frame.
+The key features of RETs that distinguishes them from most traditional SNe types are the fast light curve evolution and blue colour at peak.
+Even though both of these quantities depend on the redshift of the transient, they still seem to distinguish the the fast events from traditional SN types.
+
+To assess the distinguishing photometric properties of RETs, we take the sample of 72 from the \citetalias{Pursiainen2018} method along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
+\begin{enumerate}
+\item The transient was only detected in one DES-SN observing season.
+\item Maximum observed brightness in both $g$- and $r$-bands was brighter than 24 mag (in the eight `shallow' DES-SN fields) or 25 mag (in the two `deep' fields).
+\item $g$- and $r$-band observations used for the colour had to be taken within 2 days in observer frame.
+\end{enumerate}
+
+Of objects passing these cuts, the RETs cluster at shorter timescales and bluer colours than other SNe, even in the observer frame.
+However, using photometric data points directly has several problems that can be improved.
+For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights, thus making it impossible to measure the peak colour in a number of cases.
+Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
+To negate this issue, we interpolate the light curves using the method of Gaussian processes (GP).
+The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
+Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space and are thus easier to separate.
+We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
+The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$.
+
+We process all $\sim 30,000$ DES-SN transient candidates with GP.
+In order to reduce the contamination from active galactic nuclei (AGN), we use a basic convolutional neural network (CNN) classifier which we train on spectrosopically confirmed objects, and use to separate the sample into two subtypes: AGN-like and SNe-like.
+The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are likely removed by the final manual vetting.
+The SNe passing the CNN classifier are subjected to the LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs.
+These objects are subject to a further set of cuts.
+We impose a cut based on a fit of the LC with the \texttt{PSNID} software (\citet{Sako2008}).
+We use thresholds of \texttt{FITPROB}$<0.91$ and \texttt{PBAYES}$<0.82$ to remove highly-probably SNe Ia, which removes 46 objects from the RET parameter space.
+In order to further remove longer-lived SNe, the decline time to half of the peak brightness must be $<24$ days.
+This removes 347 SNe, resulting in 546 objects remaining inside the parameter space.
+The final 564 transients have been visually inspected, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.
+
+Using the above method recovers N of the 96 rets found using the \citetalias{Pursiainen2018} technique, and adds a further M.
+We refer to the resulting sample as DES RETs.
 Of the 106 objects in the sample, 97 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift.
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
+\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfms_sfr}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
+\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfr_cum}}
+\end{figure}
 \subsection{Estimating metallicities \label{subsec:calc_Z}}
@@
 \subsection{Metallicity \label{subsec:res_metallicity}}
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
-\caption{The mass-metallicity relation (MZR) for RET host galaxies.
-\label{fig:mzr}}
-\end{figure}
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/mag_v_colour.png}
-\caption{The colour-magnitude distribution of RET hosts with (cyan) and without (orange) redshifts. There is an excess of objects with blue colours that do not have redshift measurements.
-\label{fig:g-i}}
+\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
+\caption{The mass-metallicity relation (MZR) for RET host galaxies.
+\label{fig:mzr}}
 \end{figure}
@@
 In Fig.~\ref{fig:mzr} we show the mass-metallicity relation (MZR) for the RET and comparison samples.
+The contours show the MZR for low-redshift ($\hat{z}=0.08$) star-forming galaixes from SDSS, adjusted to the PP04 O3N2 diagnostic.
+We use the MZR parameterisation \citet{Zahid2014} to show the best fit to the MZR for star-forming galaxies.
+The blue dashed line shows the fit to the low-z data, while the orange dashed line corresponds to the MZR at $z=0.45$, the mean redshift of the RET host sample.
+The RET hosts lie systematically below the galaxy MZR fits as well as the bulk of the SDSS galaxies, meaning that for a given stellar mass they have a lower metallicity.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/mag_v_colour.png}
+\caption{The colour-magnitude distribution of RET hosts with (cyan) and without (orange) redshifts. There is an excess of objects with blue colours that do not have redshift measurements.
+\label{fig:g-i}}
+\end{figure}
 
 \section{Discussion \label{sec:disc}}
-
-\subsection{Transient - host galaxy correlations}
 
@@
 
-\subsection{Metallicity}
+\subsection{Origin of RETs}
 
-The sample of DES RETs shows a preference for low metallicity host environments.
-The PDF displays a strong similarity to the hosts of SNe Ibc, as well as LGRBs.
-There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies, while the aversion of high-metallicity systems is not as strong as for SLSNe.
-This result is suggestive of a stripped-envelope, massive-star origin for RETs.
+The sample of DES RETs shows a preference for low-metallicity, strongly star-forming host environments.
+The PDF of their metallcities displays a strong similarity to the hosts of SNe Ibc, as well as LGRBs.
+There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies.
+The preference for low-metallicity systems is not as strong as for LGRBs or SLSNe, but the highest metallicities found in all three samples are very similar at around solar metallicity.
+This result is further suggestive of a stripped-envelope, massive-star origin for RETs.
+The population of RET hosts lies, on average, between CCSNe and LGRBs/SLSNe in terms of both star formation and metallicity.
+A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation.
+The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), (\citetalias{Pursiainen2018}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
+At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajz2016,Frohamier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
+These figures place the DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching their location in host galaxy parameter space.
+While stressing that these associations are lose - rates are uncertain and host galaxy parameters span wide ranges for all transients - they are both linked to the respective transients' progenitor channels.
+Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars that also require some extreme properties such as rapid rotation, albeit not as much as progenitors as SLSNe or LGRBs.
+It could therefore be possible that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to a shocked photosphere, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
+
+\subsection{Correlations with lightcurve properties}
 

### 2020-02-25 RET_Hosts.tex

@@
 \section{Discussion \label{sec:disc}}
-
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/RET_vs_host.png}
+\caption{RET lightcurve properties as a function of host galaxy measurements.
+\label{fig:ret_v_host}}
+\end{figure}
 \subsection{Selection Biases \label{subsec:disc_bias}}
@@
 
-\subsection{Correlations with lightcurve properties}
+\subsection{Correlations between lightcurve and host galaxy properties}
+Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies.
+For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFR \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
+In Fig.
+\ref{fig:ret_v_host} we show the RET peak magnitude (upper pannels) and decline rate parameterised as $t_{\mathrm{half}}$, the time taken for the LC to decline to half the peak brightness (lower panels) and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
 

### 2020-02-25 RET_Hosts.tex

@@
 \ref{fig:ret_v_host} we show the RET peak magnitude (upper pannels) and decline rate parameterised as $t_{\mathrm{half}}$, the time taken for the LC to decline to half the peak brightness (lower panels) and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
+The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a simple blackbody SED.
+There is no correlation between decline rate and either stellar mass or sSFR, while there are hints of a trend between peak magnitude and both mass and sSFR.
+These apparent trends are driven by the more extreme hosts (the three with $\log\left(M_*/M_{\odot}\right) < 9$ and one with very high mass/low sSFR).
+Assuming that these points are not outliers, the trends are still likely driven by selection effects.
+At higher redshifts, only the brighter objects are recovered by the survey and our selection method, while at those redshifts only the more massive galaxies are detected.
+This does not
 

### 2020-02-25 RET_Hosts.tex
Updates from Overleaf

@@
 Assuming that these points are not outliers, the trends are still likely driven by selection effects.
-At higher redshifts, only the brighter objects are recovered by the survey and our selection method, while at those redshifts only the more massive galaxies are detected.
-This does not
+At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those redshifts only the more massive galaxies are detected.
+This effect can be seen in the Fig.
+\ref{fig:ret_v_host} panel a, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in panel b.
+It is hoped that a complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) allowing the removal of these biases in order to reveal any underlying relationships.
 

### 2020-02-25 RET_Hosts.tex
Updates from Overleaf

@@
 % Keep the title short and informative.
-\title[Supernova hosts in DES]{Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients}
+\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
 % The list of authors, and the short list which is used in the headers.
@@
 RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SNe host galaxies.
+There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.
 
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/gr_trise_r.pdf}
+\caption{Observer-frame $g-r$ colour and $r$-band rise-time, derived from Gaussian Processed fits to DES-SN photometry for spectroscopically confirmed SNe and \citetalias{Pursiainen2018} RETs.
+The location of the red box is designed to maximise the completeness and purity of RETs,
+\label{fig:selection}}
+\end{figure}
+
 \begin{figure*}
@@
 The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
-Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space and are thus easier to separate.
+Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space (Fig.
+\ref{fig:selection}) and are thus easier to separate.
 We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
-The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$.
+The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig.
+\ref{fig:selection}.
 
@@
 Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/SFR_Mike.png}
+\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\label{fig:sfms_sfr}}
+\end{figure*}
 

### 2020-02-26 RET_Hosts.tex

@@
 P. Wiseman$^1$\thanks{E-mail: p.s.wiseman@soton.ac.uk (PW)},
- M. Pursiainen$^1$,
- M. J. Childress$^1$,
- M. Smith$^1$,
+ %M. Pursiainen$^1$,
+ %M. J. Childress$^1$,
+ %M. Smith$^1$,
  and Other Authors$^{1,2}$,
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figs/SFR_Mike.png}
-\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfms_sfr}}
+\includegraphics[width=\textwidth]{figs/DES16C2ggt.png}
+\caption{The spectrum of DES16C2ggt, decomposed into its constituent components according to the \texttt{pPXF} fit. 
+\label{fig:host_spec}}
 \end{figure*}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/RET_BPT.png}
+\caption{Baldwin-Phillips-Terlovich (BPT) diagram for RET hosts, showing that the emission lines are consistent with being generated by star-formation rather than AGN activity.
+\label{fig:bpt}}
+\end{figure}
 
@@
 In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}.
-By subtracting the best-fitting stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines.
+By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines.
+An example of this procedure is shown in Fig.
+\ref{fig:host_spec}.
 We fit the emission lines using \texttt{PySpecKit} \citep{Ginsburg2011}.
-In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding a perturbation to the amplitude of the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in that part of the spectrum.
+In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding a perturbation to the amplitude of the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a $100 \AA$ window around the central wavelength of the line.
 We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
@@
 The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium.
+Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation.
+Using the Baldwin-Phillips-Terlevich diagram (\ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
+
 Due to the low S/N of the spectra in this sample, we are constrained to a subset of these diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959 and 5007, \NII 6548 and 6583, and \SII 6717 and 6731.

### 2020-02-27 RET_Hosts.tex
Updates from Overleaf

@@
 \usepackage{wrapfig}
+\usepackage{ctable}
 \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
@@
 \newcommand{\phil}[1]{\color{red}#1 \color{black}}
+\newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
+\newcommand{\miika}[1]{\color{green}#1 \color{black}}
 
@@
 \includegraphics[width=\textwidth]{figs/RET_Mosaic.png}
-\caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ bands. The locations of the transients are indicated with cyan crosses.
+\caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ band deep coadds from \citet{Wiseman2020}.
+The locations of the transients are indicated with cyan crosses.
+\phil{Need to redo with more obvious scalebar and crosses}.
 \label{fig:mag_dist}}
@@
 
+\miika{Miika to verify!}
 The original method of finding RETs in the DES-SN data (and presented in \citetalias{Pursiainen2018}) was designed to be simple and used light curve modelling with Gaussian and linear fits.
@@
 We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
+The observational properties of the 49 hosts with redshift are displayed in Table \ref{tab:obs}.
 
@@
 Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
+Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the General Redshift Catalogue nontheless.
+Where the spectra from which those redshifts were derived are also public they are included in this analysis.
+These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}), the Sloan Digital Sky Survey Data Release 16 (SDSS DR16; \citealt{Ahumada2019}).
+In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56.
+We stress that the emission lines are detected with a higher SNR than this.
 
+\begin{table*}
+\begin{center}
+\caption{Host galaxy information for the 49 RETs with a host galaxy redshift. A full-length, machine-readable version of this table is available in the online version of the manuscript.}
+
+\begin{threeparttable}
+\begin{tabular}{llllllll}
+
+\toprule
+{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
+Transient name &          &           &          &         &         &            &               \\
+\midrule
+DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
+DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
+DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
+DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
+DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
+DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
+DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
+DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.6734 &       ACES &               \\
+DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.4750 &      OzDES &       4.50 \\
+DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.0521 &      OzDES &       0.75 \\
+DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.8298 &      OzDES &       3.50 \\
+DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.4473 &      OzDES &       2.33 \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}.
+\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\label{tab:obs}
+\end{table*}
 \begin{figure*}
-\includegraphics[width=\textwidth]{figs/DES16C2ggt.png}
+\includegraphics[width=\textwidth]{figs/gal_spec.png}
 \caption{The spectrum of DES16C2ggt, decomposed into its constituent components according to the \texttt{pPXF} fit. 
@@
 \subsection{SED fitting \label{subsec:sedfit}}
-
+\mike{Mike to read and add!}
 To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
@@
 
-\subsection{Origin of RETs}
+\subsection{Origin of RETs \label{subsec:disc_origin}}
 
@@
 
-\subsection{Correlations between lightcurve and host galaxy properties}
+\subsection{Correlations between lightcurve and host galaxy properties \label{subsec:disc_correlations}}
 Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies.
@@
 
+\subsection{The passive host of DES16C1cbd \label{subsec:disc_cbd}}
+In Figs. \ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr} there is one clear outlier with very low SFR. The host of DES16C1cbd appears to be a passive galaxy
 \section{Conclusions}
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of this as-yet unexplained phenomenon.
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+We acknowledge support from STFC grant ST/R000506/1.
+L.K.
+was supported by the Science and Technology Facilities Council (grant number ST/P006760/1) through the DISCnet Centre for Doctoral Training.
+M.S.
+and M.S.
+acknowledge support from EU/FP7-ERC grant 615929.
+L.G.
+was funded by the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l{}odowska-Curie grant agreement No.
+839090.
+
+This paper makes use of observations taken using the Anglo-Australian Telescope under programs ATAC A/2013B/12 and NOAO 2013B-0317.
+
+This research used resources of the National Energy Research Scientific Computing Center (NERSC), a U.S.
+Department of Energy Office of Science User Facility operated under Contract No.
+DE-AC02-05CH11231.
+
+Funding for the DES Projects has been provided by the U.S. Department of Energy, the U.S. National Science Foundation, the Ministry of Science and Education of Spain, 
+the Science and Technology Facilities Council of the United Kingdom, the Higher Education Funding Council for England, the National Center for Supercomputing 
+Applications at the University of Illinois at Urbana-Champaign, the Kavli Institute of Cosmological Physics at the University of Chicago, 
+the Center for Cosmology and Astro-Particle Physics at the Ohio State University,
+the Mitchell Institute for Fundamental Physics and Astronomy at Texas A\&M University, Financiadora de Estudos e Projetos, 
+Funda{\c c}{\~a}o Carlos Chagas Filho de Amparo {\`a} Pesquisa do Estado do Rio de Janeiro, Conselho Nacional de Desenvolvimento Cient{\'i}fico e Tecnol{\'o}gico and 
+the Minist{\'e}rio da Ci{\^e}ncia, Tecnologia e Inova{\c c}{\~a}o, the Deutsche Forschungsgemeinschaft and the Collaborating Institutions in the Dark Energy Survey.
+
+The Collaborating Institutions are Argonne National Laboratory, the University of California at Santa Cruz, the University of Cambridge, Centro de Investigaciones Energ{\'e}ticas, 
+Medioambientales y Tecnol{\'o}gicas-Madrid, the University of Chicago, University College London, the DES-Brazil Consortium, the University of Edinburgh, 
+the Eidgen{\"o}ssische Technische Hochschule (ETH) Z{\"u}rich, 
+Fermi National Accelerator Laboratory, the University of Illinois at Urbana-Champaign, the Institut de Ci{\`e}ncies de l'Espai (IEEC/CSIC), 
+the Institut de F{\'i}sica d'Altes Energies, Lawrence Berkeley National Laboratory, the Ludwig-Maximilians Universit{\"a}t M{\"u}nchen and the associated Excellence Cluster Universe, 
+the University of Michigan, the National Optical Astronomy Observatory, the University of Nottingham, The Ohio State University, the University of Pennsylvania, the University of Portsmouth, 
+SLAC National Accelerator Laboratory, Stanford University, the University of Sussex, Texas A\&M University, and the OzDES Membership Consortium.
+
+Based in part on observations at Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory, which is operated by the Association of 
+Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation.
+
+The DES data management system is supported by the National Science Foundation under Grant Numbers AST-1138766 and AST-1536171.
+The DES participants from Spanish institutions are partially supported by MINECO under grants AYA2015-71825, ESP2015-66861, FPA2015-68048, SEV-2016-0588, SEV-2016-0597, and MDM-2015-0509, 
+some of which include ERDF funds from the European Union. IFAE is partially funded by the CERCA program of the Generalitat de Catalunya.
+Research leading to these results has received funding from the European Research
+Council under the European Union's Seventh Framework Program (FP7/2007-2013) including ERC grant agreements 240672, 291329, and 306478.
+We  acknowledge support from the Brazilian Instituto Nacional de Ci\^encia
+e Tecnologia (INCT) e-Universe (CNPq grant 465376/2014-2).
+
+This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
 

### 2020-02-27 RET_Hosts.tex
Updates from Overleaf

@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/gr_trise_r.pdf}
+\includegraphics[width=0.5\textwidth]{figs/spec_gr_trise_r_GP5_new_colorscheme.pdf}
 \caption{Observer-frame $g-r$ colour and $r$-band rise-time, derived from Gaussian Processed fits to DES-SN photometry for spectroscopically confirmed SNe and \citetalias{Pursiainen2018} RETs.
@@
 \citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses and SFRs.
-To this we add the low-redshift transients AT2018cow \citep[e.g.][], with host galaxy measurements from \citet{Perley2019} (Metallicity??), and SN2018kzr (measurements??).
+To this we add the low-redshift transient AT2018cow with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui}.
 
@@
 
+\subsection{Comparison with AT2018cow \label{subsec:disc_cow}}
+\phil{To add!}
+
 \subsection{The passive host of DES16C1cbd \label{subsec:disc_cbd}}

### 2020-02-27 RET_Hosts.tex
Updates from Overleaf

@@
 \begin{tablenotes}
-\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}.
+\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
 \item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
@@
 We fit the emission lines using \texttt{PySpecKit} \citep{Ginsburg2011}.
-In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding a perturbation to the amplitude of the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a $100 \AA$ window around the central wavelength of the line.
+In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a 100~\AA~window around the central wavelength of the line.
 We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
@@
 
-\section{Analysis and Discussion}
+\section{Analysis}
 \label{sec:analysis} % used for referring to this section from elsewhere
-
-\subsection{Stellar Mass \label{subsec:res_mass}}
 
@@
 The RET hosts are clearly shifted to higher sSFRs than CCSNe.
-To compare statistically the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}.
+To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}.
 For each pair of samples, we model the PDFs as skewed normal distributions.
@@
 \subsection{Comparison with AT2018cow \label{subsec:disc_cow}}
-\phil{To add!}
+
+The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Mohan2020,Fox2020} due to its rapid evolution and blue colour.
 

### 2020-02-27 RET_Hosts.tex

@@
 \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
-RETs typically rise to peak brightness within 7-10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
+RETs typically rise to peak brightness within 7-10 days \textcolor{green}{(Would prefer "less than 10d" in DES at least we can't measure 7-10 with certainity)}, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
 The photometric measurements of the PS1 and DES RETs seem to be well described by simple expanding blackbodies, although a handful show declining photospheric radii from the outset.
@@
 The second reason is an update to the sample selection technique.
-By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 96 objects.
+By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.
 
@@
 
-To assess the distinguishing photometric properties of RETs, we take the sample of 72 from the \citetalias{Pursiainen2018} method along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
+To assess the distinguishing photometric properties of RETs, we take the sample of 72 \textcolor{green}{(92)} from the \citetalias{Pursiainen2018} method along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
 \begin{enumerate}
@@
 To negate this issue, we interpolate the light curves using the method of Gaussian processes (GP).
-The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
+\textcolor{green}{(To negate this issue, we use the interpolated GP LCs presented in Pursiainen et al.
+2019)} The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
 Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space (Fig.
@@
 The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are likely removed by the final manual vetting.
+\textcolor{green}{(I'll find the list of AGN and find out where they are from.)}
 The SNe passing the CNN classifier are subjected to the LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs.
@@
 
-Using the above method recovers N of the 96 rets found using the \citetalias{Pursiainen2018} technique, and adds a further M.
+Using the above method recovers 87 of the 92 RETs found using the \citetalias{Pursiainen2018} technique, and adds a further 14.
+\textcolor{green}{The five were not recovered as their GP lightcurves were fainter than the limits given above in either g or r band.}
 We refer to the resulting sample as DES RETs.
@@
 \citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses and SFRs.
-To this we add the low-redshift transient AT2018cow with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui}.
+To this we add the low-redshift transient AT2018cow with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui}, and SN2018gep with data from \citet{Ho2019}.
 
@@
 
-\subsection{Comparison with AT2018cow \label{subsec:disc_cow}}
+\subsection{Comparison with local RETs \label{subsec:disc_lowz}}
 
 The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Mohan2020,Fox2020} due to its rapid evolution and blue colour.
+AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018} , developing to something entirely different later on \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2020}.
+There have been several suggestions that AT2018cow is indeed an analogue of the high-z RETs.
+The host galaxy of AT2018cow appears to be moderately star forming and lies very close to the centre of the SFMS (Figs.
+\ref{fig:sfms_sfr},\ref{fig:sfms_ssfr}), along with many of the DES RET hosts.
+However, the host lies significantly above the fiducial MZR in Fig.
+\ref{fig:mzr}, suggesting that it has an abnormally high metallicity for its stellar mass.
+This is in contrast to the DES RET hosts, which are systematically less enriched for a given stellar mass.
+
+Other local rapid transients include SN2018gep \citep{Ho2019}, a spectroscopically classified SN Ic-bl with a rapid rise.
+The host of SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR.
+The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}.
+SN2018kzr \citep{McBrien2019} is one of the most rapidly declining transients ever discovered, with spectral signatures similar to SNe Ic.
+While host galaxy properties are not derived, the authors of that paper refer to narrow emission from the host galaxy, along with an apparently small, blue, star-forming host.
 

### 2020-02-28 RET_Hosts.tex

@@
 \newcommand{\hbeta}[0]{H$\beta$}
+\newcommand{\hgamma}[0]{H$\gamma$}
+\newcommand{\hdelta}[0]{H$\delta$}
 \newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
@@
  %M. Smith$^1$,
- and Other Authors$^{1,2}$,
+ %E. Swann$^2$,
+ and Other Authors$^{1,2,3}$,
 \newauthor
@@
 
+\begin{table*}
+\begin{center}
+\caption{Host galaxy information for the 49 RETs with a host galaxy redshift. A full-length, machine-readable version of this table is available in the online version of the manuscript.}
+
+\begin{threeparttable}
+\begin{tabular}{llllllll}
+
+\toprule
+{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
+Transient name &          &           &          &         &         &            &               \\
+\midrule
+DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
+DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
+DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
+DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    \tnote{d} &          - &             - \\
+DES13S2wxf\tnote{e}     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
+DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
+DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    \tnote{c} &      OzDES &             - \\
+DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
+DES13X3gmd\tnote{e}     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
+DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
+DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    \tnote{d} &          - &             - \\
+DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
+\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
+\item[c] Host targetted by OzDES but no redshift measurement possible.
+\item[d] Host not targetted by OzDES
+\item[e] Found by updated search method (Section \ref{subsec:new_method})
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\label{tab:obs}
+\end{table*}
+
 \begin{figure*}
@@
 
-\subsection{Improvements to the search method}
+\subsection{Improvements to the search method \label{subsec:new_method}}
 
@@
 As only a fraction of transients in DES-SN have redshift information from host galaxy, the search must be done in the observer frame.
-The key features of RETs that distinguishes them from most traditional SNe types are the fast light curve evolution and blue colour at peak.
+The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution and blue colour at peak.
 Even though both of these quantities depend on the redshift of the transient, they still seem to distinguish the the fast events from traditional SN types.
 
-To assess the distinguishing photometric properties of RETs, we take the sample of 72 \textcolor{green}{(92)} from the \citetalias{Pursiainen2018} method along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
+To assess the unique photometric properties of RETs, we take the sample of 72 from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES, along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
 \begin{enumerate}
@@
 Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
-To negate this issue, we interpolate the light curves using the method of Gaussian processes (GP).
-\textcolor{green}{(To negate this issue, we use the interpolated GP LCs presented in Pursiainen et al.
-2019)} The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
+To negate this issue, we use the interpolated GP LCs presented in \citet{Pursiainen2019}.
+The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
 Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space (Fig.
@@
 We process all $\sim 30,000$ DES-SN transient candidates with GP.
-In order to reduce the contamination from active galactic nuclei (AGN), we use a basic convolutional neural network (CNN) classifier which we train on spectrosopically confirmed objects, and use to separate the sample into two subtypes: AGN-like and SNe-like.
-The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are likely removed by the final manual vetting.
+In order to reduce the contamination from active galactic nuclei (AGN), we use a basic convolutional neural network (CNN) classifier.
+We train the CNN on spectrosopically confirmed SNe of all types and on spectroscopically typed AGN, and use it to separate the sample into two photometric subtypes: AGN-like and SNe-like.
+The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are removed by the final manual vetting.
 \textcolor{green}{(I'll find the list of AGN and find out where they are from.)}
@@
 Using the above method recovers 87 of the 92 RETs found using the \citetalias{Pursiainen2018} technique, and adds a further 14.
-\textcolor{green}{The five were not recovered as their GP lightcurves were fainter than the limits given above in either g or r band.}
+The five were not recovered as their GP lightcurves were fainter than the limits given above in either g or r band.
 We refer to the resulting sample as DES RETs.
@@
 
-\begin{table*}
-\begin{center}
-\caption{Host galaxy information for the 49 RETs with a host galaxy redshift. A full-length, machine-readable version of this table is available in the online version of the manuscript.}
-
-\begin{threeparttable}
-\begin{tabular}{llllllll}
-
-\toprule
-{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
-Transient name &          &           &          &         &         &            &               \\
-\midrule
-DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
-DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
-DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
-DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
-DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
-DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
-DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
-DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.6734 &       ACES &               \\
-DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.4750 &      OzDES &       4.50 \\
-DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.0521 &      OzDES &       0.75 \\
-DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.8298 &      OzDES &       3.50 \\
-DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.4473 &      OzDES &       2.33 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
-\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
-\end{tablenotes}
-\end{threeparttable}
-\end{center}
-\label{tab:obs}
-\end{table*}
 \begin{figure*}
@@
 
+\begin{table*}
+
+\caption{Host galaxy properties for the 49 DES RET host galaxies with redshifts and host galaxy spectra. The full table is available online in the online version in a machine readable format.}
+\begin{threeparttable}
+\begin{tabular}{lrrrllllll}
+\toprule
+Transient Name &$\log \left(M_*\right)$ &$\log \left(\mathrm{SFR}\right)$ &  $\log \left(\mathrm{sSFR}\right)$ &                                                           \multicolumn{6}{c}{$12+\log\left(\mathrm{O/H}\right)\tnote{a} $}\\
+%\midrule
+{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(M_{\odot}\ \mathrm{yr}^{-1} M_{\odot}^{-1}\right)$& Best &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\
+\midrule
+DES13X3gms &   $9.41 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.27}$ &  $-0.06 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.78}$ &   $-9.47 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.52}$ &  $8.55 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.37}$ &                                                             - &                                                             - &                                                             - &  $8.55 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.37}$ &   $8.22 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.35}$ \\
+DES13C1tgd &  $10.24 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &   $0.10 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.38}$ &  $-10.14 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &  $8.64 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.06}$ &  $8.59 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &  $8.68 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &   $8.75 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
+DES13S2wxf &   $9.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.06}$ &   $0.29 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.10}$ &   $-9.57 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.58 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &  $8.58 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.27}$ &   $8.25 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.25}$ \\
+DES13X1hav &   $9.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.38}$ &  $-0.44 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.93}$ &   $-9.60 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.55}$ &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &                                                             - &                                                             - &                                                             - &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &   $8.20 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.36}$ \\
+DES13E2lpk &  $10.66 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.10}$ &   $0.46 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.45}$ &  $-10.20 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.35}$ &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &                                                             - &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &   $8.58 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
+DES15C2eal &   $8.42 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.18}$ &  $-1.29 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.33}$ &   $-9.72 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.15}$ &  $8.29 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.25}$ &  $7.97 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.29}$ &  $8.29 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.15}$ &  $8.34 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.15}$ &  $8.52 _{\scriptscriptstyle 0.49} ^{\scriptscriptstyle 0.57}$ &   $8.28 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.30}$ \\
+DES16C2ggt &   $9.86 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.36}$ &   $0.13 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.94}$ &   $-9.73 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.59}$ &  $8.53 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.39}$ &  $8.37 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.51 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &  $8.54 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.93 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &   $8.56 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ \\
+DES17C2hno &   $9.56 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.16}$ &  $-0.02 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.33}$ &   $-9.58 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.17}$ &  $8.94 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.94 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.09}$ &   $8.60 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.11}$ \\
+
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item[a] Linear combination of the likelihoods for D16, PP04 N2, PP04 O3N2, KK04 R23.
+\item[b] Weighted average of PP04 N2, PP04 O3N2, and KK04 R23, where N2 and R23 were converted to PP04 O3N2 via \citet{Kewley2008}.
+
+\end{tablenotes}
+\end{threeparttable}
+\label{tab:derived}
+\end{table*}
+
 \begin{figure}
@@
 For $12 + \log \mathrm{(O/H)}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.
+
+Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the results from the probability density functions (PDFs) of the various different diagnostics, resulting in a final `best' PDF.
+We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and display the results in Table \ref{tab:derived}.
 
@@
 The host of SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR.
+While the SN2018gep host is lower in stellar mass than any DES RET ($\log \left(M/M_{\odot}\right) =8.11$, galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}.
 The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}.
@@
 In Figs. \ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr} there is one clear outlier with very low SFR. The host of DES16C1cbd appears to be a passive galaxy
+
+\phil{Adding more once I know about the SFR from [OII]}
 \section{Conclusions}
@@
 
-\section{Some extra material}
+\section{Spectral line fluxes}
+\begin{table*}
+\caption{Emission line fluxes for DES RET host galaxies.
+Values are given in units of erg/cm/s/\AA, and have been corrected for Milky Way reddening using \citet{Schlegel1998}, assuming a \citet{Cardelli1989} with $R_V = 3.1$, but not for intrinsic host galaxy reddening.}
+\setlength{\tabcolsep}{3pt}
+\begin{tabular}{llllllllllll}
+\toprule
+{} &              \OII 3727 &             \OIII 4960 &              \OIII 5007 &             \NII 6549 &             \NII 6585 &             \SII 6717 &             \SII 6731 &           \hdelta &            \hgamma &             \hbeta &            \halpha \\
+\midrule
+DES13X3gms &  $43.3 \pm 27.7$ &   $10.9 \pm 7.9$ &    $32.9 \pm 7.9$ &               - &               - &               - &               - &   $2.0 \pm 7.6$ &   $17.0 \pm 7.1$ &    $6.3 \pm 9.5$ &                - \\
+DES13C1tgd &    $1.9 \pm 0.7$ &    $0.0 \pm 0.1$ &     $0.0 \pm 0.1$ &   $0.5 \pm 0.1$ &   $1.6 \pm 0.1$ &   $1.1 \pm 0.0$ &   $0.8 \pm 0.0$ &   $0.9 \pm 0.2$ &    $1.3 \pm 0.1$ &    $0.2 \pm 0.1$ &    $4.5 \pm 0.2$ \\
+DES13S2wxf &   $22.1 \pm 5.3$ &    $3.2 \pm 2.0$ &     $9.8 \pm 2.0$ &               - &               - &               - &               - &   $2.4 \pm 1.0$ &    $4.3 \pm 0.8$ &    $4.5 \pm 2.1$ &                - \\
+DES13X1hav &  $31.4 \pm 49.1$ &  $10.5 \pm 12.0$ &   $31.9 \pm 12.0$ &               - &               - &               - &               - &   $0.0 \pm 6.2$ &   $5.2 \pm 11.5$ &   $10.6 \pm 4.8$ &                - \\
+DES13X3nyg &   $15.1 \pm 1.6$ &    $3.2 \pm 0.4$ &     $9.8 \pm 0.4$ &               - &               - &               - &               - &   $0.5 \pm 0.4$ &    $0.0 \pm 0.6$ &    $3.3 \pm 0.4$ &                - \\
+DES13X3gmd &   $18.8 \pm 5.3$ &                - &                 - &               - &               - &               - &               - &   $1.9 \pm 3.8$ &    $2.3 \pm 2.7$ &    $7.0 \pm 8.3$ &                - \\
+DES13X2wvv &  $61.5 \pm 14.4$ &    $7.4 \pm 3.6$ &    $22.6 \pm 3.6$ &               - &               - &               - &               - &   $2.7 \pm 4.9$ &    $1.1 \pm 3.3$ &   $10.3 \pm 2.8$ &                - \\
+DES14S2anq &  $486.0 \pm 0.4$ &   $74.9 \pm 1.1$ &   $227.1 \pm 1.1$ &  $10.3 \pm 5.1$ &  $31.1 \pm 5.1$ &  $43.1 \pm 4.0$ &  $31.1 \pm 4.5$ &  $31.5 \pm 1.4$ &   $58.9 \pm 1.4$ &  $114.0 \pm 1.4$ &  $240.0 \pm 0.9$ \\
+DES14X1bnh &   $23.1 \pm 1.2$ &                - &                 - &               - &               - &               - &               - &   $0.4 \pm 0.4$ &    $3.1 \pm 0.5$ &                - &                - \\
+DES15S1fli &   $33.3 \pm 3.3$ &    $3.4 \pm 1.5$ &    $10.5 \pm 1.5$ &               - &               - &               - &               - &   $3.0 \pm 1.5$ &    $4.2 \pm 0.8$ &    $8.7 \pm 0.4$ &                - \\
+DES15S1fll &  $75.2 \pm 78.8$ &  $13.6 \pm 10.8$ &   $41.3 \pm 10.8$ &   $1.4 \pm 3.9$ &   $4.4 \pm 3.9$ &   $2.7 \pm 2.6$ &   $4.9 \pm 2.8$ &  $0.6 \pm 19.2$ &  $14.3 \pm 16.6$ &  $13.4 \pm 10.2$ &   $40.9 \pm 5.2$ \\
+DES14X3pkl &   $13.5 \pm 9.5$ &    $2.6 \pm 0.8$ &     $7.9 \pm 0.8$ &   $0.7 \pm 0.4$ &   $2.2 \pm 0.4$ &   $3.5 \pm 0.5$ &   $1.9 \pm 0.3$ &   $1.7 \pm 2.7$ &    $2.6 \pm 2.8$ &    $0.0 \pm 2.1$ &   $10.4 \pm 0.7$ \\
+DES13X3npb &   $14.6 \pm 4.1$ &    $1.4 \pm 0.2$ &     $4.2 \pm 0.2$ &               - &               - &               - &               - &   $2.3 \pm 0.2$ &    $4.0 \pm 0.2$ &    $5.7 \pm 0.2$ &                - \\
+DES15X2ead &   $9.7 \pm 10.0$ &    $0.8 \pm 0.8$ &     $2.3 \pm 0.8$ &   $0.8 \pm 0.4$ &   $2.5 \pm 0.4$ &   $3.5 \pm 0.3$ &   $2.2 \pm 0.6$ &   $2.9 \pm 2.5$ &    $1.3 \pm 1.7$ &    $2.3 \pm 0.8$ &   $11.5 \pm 0.3$ \\
+DES14S2plb &   $14.1 \pm 0.7$ &    $1.0 \pm 0.1$ &     $3.0 \pm 0.1$ &   $1.2 \pm 0.0$ &   $3.6 \pm 0.0$ &   $2.3 \pm 0.0$ &   $1.8 \pm 0.0$ &   $2.0 \pm 0.1$ &    $2.3 \pm 0.1$ &    $4.8 \pm 0.1$ &   $12.2 \pm 0.0$ \\
+DES14S2pli &   $13.7 \pm 0.9$ &    $0.6 \pm 0.1$ &     $1.7 \pm 0.1$ &               - &               - &               - &               - &   $0.0 \pm 0.4$ &    $1.6 \pm 0.3$ &    $3.5 \pm 0.1$ &                - \\
+DES14C3tnz &   $23.1 \pm 4.5$ &    $3.0 \pm 1.0$ &     $9.2 \pm 1.0$ &               - &               - &               - &               - &   $1.1 \pm 0.9$ &    $4.5 \pm 1.5$ &    $4.4 \pm 3.8$ &                - \\
+DES15X3mxf &   $29.5 \pm 3.4$ &    $1.7 \pm 0.5$ &     $5.2 \pm 0.5$ &               - &               - &               - &               - &   $1.1 \pm 2.8$ &    $4.0 \pm 1.2$ &    $5.0 \pm 0.5$ &                - \\
+DES15C3lpq &   $37.0 \pm 9.8$ &    $8.6 \pm 3.3$ &    $26.2 \pm 3.3$ &               - &               - &               - &               - &   $4.2 \pm 2.6$ &    $2.3 \pm 2.6$ &    $9.1 \pm 4.5$ &                - \\
+DES15C3nat &   $21.6 \pm 1.5$ &                - &                 - &               - &               - &               - &               - &   $1.5 \pm 0.6$ &    $4.2 \pm 1.4$ &                - &                - \\
+DES15C3mgq &  $17.0 \pm 20.8$ &    $6.3 \pm 2.4$ &    $19.1 \pm 2.4$ &   $0.4 \pm 1.3$ &   $1.3 \pm 1.3$ &   $1.2 \pm 0.7$ &   $0.0 \pm 3.6$ &   $1.8 \pm 5.1$ &    $1.7 \pm 4.0$ &    $6.2 \pm 2.9$ &   $10.6 \pm 0.8$ \\
+DES15E2nqh &  $34.7 \pm 22.4$ &    $9.3 \pm 3.6$ &    $28.2 \pm 3.6$ &               - &               - &               - &               - &   $2.4 \pm 4.3$ &    $4.8 \pm 5.2$ &    $7.7 \pm 5.1$ &                - \\
+DES15C3opk &   $10.5 \pm 6.5$ &    $5.0 \pm 3.1$ &    $15.1 \pm 3.1$ &               - &               - &               - &               - &   $0.7 \pm 1.2$ &    $1.8 \pm 0.9$ &    $2.9 \pm 3.7$ &                - \\
+DES15C3opp &   $15.5 \pm 3.3$ &    $1.7 \pm 0.6$ &     $5.2 \pm 0.6$ &               - &               - &               - &               - &   $0.7 \pm 2.1$ &    $2.9 \pm 1.5$ &    $3.1 \pm 0.7$ &                - \\
+DES16E2pv  &  $39.7 \pm 12.2$ &    $6.0 \pm 9.5$ &    $18.0 \pm 9.5$ &               - &               - &               - &               - &   $0.3 \pm 4.9$ &    $5.9 \pm 5.1$ &    $6.9 \pm 4.9$ &                - \\
+DES16S1bbp &  $37.2 \pm 13.0$ &    $7.5 \pm 1.7$ &    $22.9 \pm 1.7$ &   $0.7 \pm 0.4$ &   $2.1 \pm 0.4$ &   $2.8 \pm 1.3$ &   $2.0 \pm 0.4$ &   $2.9 \pm 2.7$ &    $6.0 \pm 1.9$ &   $12.2 \pm 2.3$ &   $24.2 \pm 0.8$ \\
+DES16X3cxn &   $23.5 \pm 5.6$ &    $1.6 \pm 2.6$ &     $4.9 \pm 2.6$ &               - &               - &               - &               - &   $0.0 \pm 2.2$ &    $0.7 \pm 1.4$ &    $4.0 \pm 1.0$ &                - \\
+DES16C1cbd &    $9.3 \pm 1.8$ &    $0.6 \pm 0.3$ &     $1.8 \pm 0.3$ &               - &               - &               - &               - &   $0.8 \pm 0.1$ &    $1.0 \pm 0.1$ &    $1.9 \pm 0.1$ &                - \\
+DES16X3ega &   $28.2 \pm 2.1$ &    $0.9 \pm 1.0$ &     $2.8 \pm 1.0$ &   $1.0 \pm 0.8$ &   $3.0 \pm 0.8$ &   $2.8 \pm 0.4$ &   $1.5 \pm 0.9$ &   $2.0 \pm 0.8$ &    $4.4 \pm 0.7$ &    $5.8 \pm 0.5$ &   $14.5 \pm 0.4$ \\
+DES16X3erw &   $31.6 \pm 4.0$ &    $2.9 \pm 1.6$ &     $8.8 \pm 1.6$ &               - &               - &               - &               - &   $3.4 \pm 1.7$ &    $2.1 \pm 1.5$ &    $7.2 \pm 0.7$ &                - \\
+DES16C3gin &   $17.1 \pm 2.8$ &    $1.5 \pm 0.4$ &     $4.4 \pm 0.4$ &               - &               - &               - &               - &   $1.6 \pm 1.1$ &    $0.0 \pm 1.2$ &    $4.3 \pm 0.6$ &   $10.1 \pm 0.5$ \\
+DES16S1dxu &  $96.3 \pm 33.0$ &   $16.4 \pm 8.4$ &    $49.5 \pm 8.4$ &   $0.8 \pm 2.5$ &   $2.4 \pm 2.5$ &   $1.2 \pm 3.6$ &   $3.7 \pm 1.8$ &   $5.5 \pm 6.9$ &    $9.1 \pm 4.8$ &   $22.8 \pm 3.9$ &   $39.2 \pm 1.2$ \\
+DES16X1eho &    $6.6 \pm 0.9$ &                - &                 - &               - &               - &               - &               - &   $0.0 \pm 0.3$ &    $1.2 \pm 0.6$ &    $1.4 \pm 0.8$ &                - \\
+DES17C3gop &  $21.1 \pm 17.3$ &    $2.5 \pm 2.4$ &     $7.6 \pm 2.4$ &               - &               - &               - &               - &   $2.7 \pm 2.4$ &    $5.3 \pm 3.2$ &    $4.8 \pm 1.4$ &                - \\
+DES17S2fee &    $0.1 \pm 0.2$ &    $0.0 \pm 0.0$ &     $0.0 \pm 0.0$ &   $0.1 \pm 0.0$ &   $0.2 \pm 0.0$ &   $0.0 \pm 0.0$ &   $0.3 \pm 0.0$ &   $0.0 \pm 0.0$ &    $0.1 \pm 0.0$ &    $0.0 \pm 0.0$ &    $0.4 \pm 0.0$ \\
+DES17X3dxu &   $22.1 \pm 2.8$ &                - &                 - &               - &               - &               - &               - &   $3.8 \pm 6.1$ &    $4.7 \pm 1.3$ &                - &                - \\
+DES17X3cds &    $9.4 \pm 6.5$ &    $2.0 \pm 1.1$ &     $6.1 \pm 1.1$ &               - &               - &               - &               - &   $0.0 \pm 0.9$ &    $0.6 \pm 0.7$ &    $3.1 \pm 0.7$ &                - \\
+DES17X3hxi &  $56.6 \pm 78.6$ &  $35.7 \pm 26.0$ &  $108.3 \pm 26.0$ &               - &               - &               - &               - &  $8.9 \pm 22.2$ &  $16.1 \pm 22.9$ &  $22.7 \pm 18.0$ &                - \\
+DES13E2lpk &   $11.3 \pm 0.7$ &    $0.5 \pm 0.1$ &     $1.5 \pm 0.1$ &               - &               - &               - &               - &   $0.7 \pm 0.2$ &    $1.3 \pm 0.1$ &    $3.3 \pm 0.1$ &                - \\
+DES15C2eal &  $28.1 \pm 17.9$ &    $2.1 \pm 2.3$ &     $6.5 \pm 2.3$ &   $0.5 \pm 1.6$ &   $1.5 \pm 1.6$ &   $3.0 \pm 0.7$ &   $4.3 \pm 0.8$ &   $0.0 \pm 4.4$ &    $4.0 \pm 3.7$ &    $4.1 \pm 3.2$ &   $17.6 \pm 2.0$ \\
+DES16C2ggt &   $21.0 \pm 1.0$ &    $2.3 \pm 0.3$ &     $6.9 \pm 0.3$ &   $1.1 \pm 0.2$ &   $3.3 \pm 0.2$ &   $3.5 \pm 0.1$ &   $2.2 \pm 0.1$ &   $0.7 \pm 0.3$ &    $2.7 \pm 0.5$ &    $7.4 \pm 0.2$ &   $14.2 \pm 0.1$ \\
+DES17C2hno &   $19.1 \pm 6.2$ &    $2.1 \pm 1.5$ &     $6.2 \pm 1.5$ &               - &               - &               - &               - &   $2.4 \pm 2.5$ &    $2.7 \pm 1.6$ &    $7.0 \pm 1.8$ &                - \\
+\bottomrule
+\end{tabular}
 
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
+\end{table*}
 

### 2020-02-28 RET_Hosts.tex

@@
 \begin{table*}
-\begin{center}
 \caption{Host galaxy information for the 49 RETs with a host galaxy redshift. A full-length, machine-readable version of this table is available in the online version of the manuscript.}
@@
 \end{threeparttable}
-\end{center}
 \label{tab:obs}
@@
 \citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses and SFRs.
-To this we add the low-redshift transient AT2018cow with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui}, and SN2018gep with data from \citet{Ho2019}.
+To this we add the low-redshift transient AT2018cow with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, and SN2018gep with data from \citet{Ho2019}.
 
@@
 The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient.
-The spectra have a resolution of 1400-1700 and a wavelength range of 3700$\AA - 8800\AA$, and are reduced using a modified version of 2dfdr \citep{Croom2004} along with internal scripts.
+The spectra have a resolution of 1400-1700 and a wavelength range of 3700$\AA - 8800\AA$, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
 Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
@@
 Where the spectra from which those redshifts were derived are also public they are included in this analysis.
-These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}), the Sloan Digital Sky Survey Data Release 16 (SDSS DR16; \citealt{Ahumada2019}).
+These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}), the Sloan Digital Sky Survey Data Release 16 (SDSS DR16; \citealt{York2000,Ahumada2019}).
 In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56.
@@
 \includegraphics[width=0.5\textwidth]{figs/RET_BPT.png}
-\caption{Baldwin-Phillips-Terlovich (BPT) diagram for RET hosts, showing that the emission lines are consistent with being generated by star-formation rather than AGN activity.
+\caption{Baldwin-Phillips-Terlovich (BPT) diagram for RET hosts, showing that the emission lines are consistent with being generated by star formation rather than AGN activity.
+The three curves show the delimitation between star formation and AGN according to \citet{Kewley2013}.
 \label{fig:bpt}}
@@
 To estimate parameters from the OzDES host galaxy spectra requires several processing steps.
-We first apply a flux calibration using the method of \citet{Swann2020}, by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry.
+We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}).
 Rather than using global galaxy photometry (i.e.
@@
 Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation.
-Using the Baldwin-Phillips-Terlevich diagram (\ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
+Using the Baldwin-Phillips-Terlevich diagram (Fig.
+\ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
 
@@
 We thus determine a set of indicators for which to calculate abundances.
-For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}.
+For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII~is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}.
 For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04).
@@
 
-The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Mohan2020,Fox2020} due to its rapid evolution and blue colour.
-AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018} , developing to something entirely different later on \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2020}.
+The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Fox2019,Mohan2020} due to its rapid evolution and blue colour.
+AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018} , developing to something entirely different later on \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.
 There have been several suggestions that AT2018cow is indeed an analogue of the high-z RETs.
@@
 This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
+
+This work makes extensive use of Astropy,\footnote{http://www.astropy.org} a community-developed core Python package for Astronomy \citep{AstropyCollabor
 

### 2020-03-04 RET_Hosts.tex

@@
 \begin{abstract}
-Rapidly evolving transients (RETs) are a mysterious class of astrophysical event.
+Rapidly evolving transients (RETs), often also termed fast blue optical transients (FBOTs), are a mysterious class of astrophysical event.
 They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
@@
 In this paper, we investigate the host galaxies of the largest RET sample to date from the Dark Energy Survey (DES).
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar mass, star-formation rate (SFR), and metallicity for 42 hosts.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar mass star-formation rate (SFR) for 49 hosts, and metallicity for 42.
 We find that RETs explode almost exclusively in star-forming galaxies and are thus likely associated with massive stars.
-Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFR, indicating a link to young stellar populations stripped-envelope SNe.
+Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFR, indicating a link to young stellar populations, similar to stripped-envelope SNe.
 RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SNe host galaxies.
@@
 \citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses and SFRs.
-To this we add the low-redshift transient AT2018cow with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, and SN2018gep with data from \citet{Ho2019}.
+To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'') with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
 
@@
 \ref{fig:host_spec}.
-We fit the emission lines using \texttt{PySpecKit} \citep{Ginsburg2011}.
+We fit the emission lines with Gaussian profiles.
 In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a 100~\AA~window around the central wavelength of the line.
@@
 The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}.
+
+The rapidly evolving lightcurve of ZTF18abvkwla (``the Koala'') has been attributed to shock interaction, while radio emission can be explained by a collimated jet.
+The host of the Koala is a low metallicity starburst more typical of LGRBs and SLSNe, and places this transient at the very extreme end of the DES RET host population.
+While we note that the \citet{Ho2020} study made multiple non-detections of radio emission from the DES RETs, these were taken at very late epochs ($\geq 1\mathrm{year}$), so the presence of jets in the early evolution is not ruled out.
+Seen from the other point of view, we cannot rule out that the Koala comes from the same population of transients as the DES RETs.
+
 SN2018kzr \citep{McBrien2019} is one of the most rapidly declining transients ever discovered, with spectral signatures similar to SNe Ic.
@@
 
-This work makes extensive use of Astropy,\footnote{http://www.astropy.org} a community-developed core Python package for Astronomy \citep{AstropyCollabor
+This work makes extensive use of Astropy,\footnote{http://www.astropy.org} a community-developed core Python package for Astronomy \citep{AstropyCollaboration2013,AstropyCollaboration2018}, Pandas \citep{Mckinney2010}, and matplotlib \citep{Hunter2007}.
 

### 2020-03-06 RET_Hosts.tex
Updates from Overleaf

@@
 \mike{Mike to read and add!}
-To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
+To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
 We use \citet{Bruzual2003} models and a \citet{Chabrier2003} initial mass function (IMF).
@@
 For each set of model and observed magnitudes we calculate a $\chi^2$ value and adopt the $M/L$ and SFR from model with the lowest $\chi^2$ as our best estimates.
-To estimate uncertainties, we ??
-and take the values at the 16th and 84th percentiles to be our $1\sigma$ lower and upper bounds.
+To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds.
 

### 2020-03-09 RET_Hosts.tex
Updates from Overleaf

@@
 \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
-RETs typically rise to peak brightness within 7-10 days \textcolor{green}{(Would prefer "less than 10d" in DES at least we can't measure 7-10 with certainity)}, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
+A further sample of five objects has been discovered by the Hyper Suprime-Cam Subaru Strategic Program (SSP) Transient Survey \citep{Tampo2020}.
+RETs typically rise to peak brightness in less than 10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
 The photometric measurements of the PS1 and DES RETs seem to be well described by simple expanding blackbodies, although a handful show declining photospheric radii from the outset.
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figs/RET_Mosaic.png}
+\includegraphics[width=0.7\textwidth]{figs/RET_Mosaic.png}
 \caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ band deep coadds from \citet{Wiseman2020}.
 The locations of the transients are indicated with cyan crosses.
-\phil{Need to redo with more obvious scalebar and crosses}.
+The stamps have a size of 10\arcsec in each direction.
 \label{fig:mag_dist}}
@@
 For both samples, we use identical normal priors for the `mean' and `scale'\footnote{See \citet{Wiseman2020} for a detailed description of the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
+The results from the simultaneous fitting of the samples reveals:
 

### 2020-03-10 RET_Hosts.tex
Updates from Overleaf

@@
 \citealt{Quimby2011, Gal-Yam2012}).
-Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2011,Grayling2020}.
+Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2011}.
 The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly formed, rapidly rotating magnetar.
@@
 The stamps have a size of 10\arcsec in each direction.
-\label{fig:mag_dist}}
+\label{fig:mosaic}}
 \end{figure*}
@@
 
-\miika{Miika to verify!}
 The original method of finding RETs in the DES-SN data (and presented in \citetalias{Pursiainen2018}) was designed to be simple and used light curve modelling with Gaussian and linear fits.
@@
 
-To compare with CCSNe, we draw on the sample of SNe II from PTF \citep{Stoll2013} and the compilation of untargeted SESNe from \citet{Sanders2012}.
-We use the sample of GRB host galaxies of \citet{Kruehler2015}, using only galaxies with $z<1$ in order to maintain completeness.
-To investigate similarities with SLSNe, we use the PTF sample of \citet{Perley2016c}.
+In compiling a set of comparison samples, we aim for the least biased selections possible.
+This requires surveys to be untargetted (they were not monitoring certain galaxies in order to search for SNe), and ideally complete to a certain volume limit.
+While in practice the second of these criteria is difficult to achieve, we are able to choose comparison samples from untargetted surveys to mitigate initial selection biases.
+
+To compare with CCSNe, we draw on the untargetted sample of 47 SNe II from PTF \citep{Stoll2013}, which is likely complete in terms of hosts (all SNe have an associated host).
+While this sample lies at much lower redshift than the DES RETs (a maximum of 0.18 and mean of 0.05), redshift evolution is easier to account for than unknown incompleteness.
+We add to this the compilation of 56 untargeted SESNe from \citet{Sanders2012}, with a maximum redshift of 0.26 and a mean of 0.05.
+Since \citet{Sanders2012} do not report host galaxy magnitudes, stellar masses or SFRs, we cross-correlated the SN positions with the the Sloan Digital Sky Survey (SDSS; \citealt{York2000}) Data Release 16 (DR16; \citealt{Ahumada2019}) and perform our own SED fit using the method outlined in Section \ref{subsec:sedfit}.
+
+We use the sample of GRB host galaxies of \citet{Kruehler2015}, using only galaxies with $z<1$ in order to maintain completeness, resulting in a sample of 29 hosts with a mean redshift of 0.66.
+To investigate similarities with SLSNe, we use the PTF sample of \citet{Perley2016c} with a mean redshift of 0.24 and a maximum of 0.50.
+
+The host galaxy properties of the above samples are not all derived using the same methods.
+In terms of SED fitting, the largest systematic offsets in derived properties are due to differences in the assumed initial mass function (IMF).
+\citet{Stoll2013} and \citet{Drout2014} assume a \citet{Salpeter1955} IMF whereas all other samples considered (including those calculated in this work in Section \ref{subsec:sedfit}) are determined assuming a \citet{Chabrier2003} IMF.
+Stellar masses and star-formation rates derived using a Salpeter IMF are believed to be roughly $\sim 0.58$ \citep{Speagle2014}, and we convert by this factor in order to compare them.
 
@@
 For each pair of samples, we model the PDFs as skewed normal distributions.
-For both samples, we use identical normal priors for the `mean' and `scale'\footnote{See \citet{Wiseman2020} for a detailed description of the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
-The results from the simultaneous fitting of the samples reveals:
+For both samples, we use identical normal priors for the `loc' (location, i.e.
+central value, identical to mean for a skewness of 0) and `scale' (spread, identical to standard deviation for a skewness of 0)\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
+The results from the simultaneous fitting shows RET hosts to be shifted to higher sSFRs CCSNe.
+In 100\% of the posterior samples the RETs were located at higher average sSFRs than SNe II, while the same was true 76\% of the time for RETs when comparing with SESNe.
+
+RET host galaxies are significantly lower in sSFR than LGRBs.
+While the distributions are similar in shape, with a mean difference in scale of 0.28, the mean difference in loc is -1.64, with no overlap between the posterior distributions.
+The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{+1.8}_{-0.98}$ compared to $-0.18^{+0.75}_{-0.76}$ for RET hosts).
+The strong high-sSFR tail shows SLSNe to derive from a different population to RETs.
 
@@
 We compare the metallicity distributions in the same way as the sSFRs.
-The RET host metallicity distribution is significantly different to the SNe II and SDSS distributions, with no overlap in the posterior distributions for the skewed-normal distribution peak and skewness.
-On the other hand, simultaneous fits with SESNe show very similar distributions.
+The RET host metallicity distribution shows a broad peak, leading to two families of skewed-Gaussians that fit it well, one with a low-valued centre  ($12 + \log \mathrm{(O/H)} \sim 8.1$) and a positive skew, and the other with a higher-valued centre ($12 + \log \mathrm{(O/H)} \sim 8.6$).
+Comparing the DES RETs to the \citet{Stoll2013} SNe II shows the latter to be centred around 8.8, with the centre being greater than the RETs in 94\% of samples.
+We determine that the RET host metallicities are derived from a different population to the SNe II.
+On the other hand, simultaneous fits with SESNe show very similar distributions, including a smaller higher-metallicity peak, such that they are indistinguishable statistically.
+
+The median CDFs of LGRBs and SLSNe show divergence from the RETs, particularly at low metallicity.
+As a result, the central locations of their fits are shifted compared to the RETs.
+In 67\% of samples, the RET sample had a higher central metallicity than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
+While these effects are not as significant as with the RETs - SNe II comparison, there is mild evidence that RETs located in galaxies with higher metal content than LGRBs.
+The effect is more pronounced for SLSNe, where the RETs have a higher metallicity for the distribution peak 92\% of the time.
+The SLSN distribution is also more strongly skewed, with 89\% of the posterior distribution being more strongly skewed than the RETs.
+There is thus mild-to-strong evidence that RETs occur in more metal-rich environments than SLSNe.
 
@@
 A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation.
-The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), (\citetalias{Pursiainen2018}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
-At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajz2016,Frohamier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
+The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), (\citetalias{Drout2014,Pursiainen2018,Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
+At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohamier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
 These figures place the DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching their location in host galaxy parameter space.

### 2020-03-10 RET_Hosts_IR.tex

--- 2020-03-10 RET_Hosts.tex
@@
 The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are removed by the final manual vetting.
-\textcolor{green}{(I'll find the list of AGN and find out where they are from.)}
 The SNe passing the CNN classifier are subjected to the LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs.
@@
 \citet{Stoll2013} and \citet{Drout2014} assume a \citet{Salpeter1955} IMF whereas all other samples considered (including those calculated in this work in Section \ref{subsec:sedfit}) are determined assuming a \citet{Chabrier2003} IMF.
-Stellar masses and star-formation rates derived using a Salpeter IMF are believed to be roughly $\sim 0.58$ \citep{Speagle2014}, and we convert by this factor in order to compare them.
+Stellar masses and star-formation rates derived using a Salpeter IMF are believed to be roughly $\sim 1.72$ times higher than those using a Chabrier IMF \citep{Speagle2014}, and we convert by this factor in order to compare them.
 
@@
 The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), (\citetalias{Drout2014,Pursiainen2018,Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
-At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohamier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
+At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohmaier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
 These figures place the DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching their location in host galaxy parameter space.

### 2020-03-12 RET_Hosts_IR.tex

@@
 \begin{abstract}
-Rapidly evolving transients (RETs), often also termed fast blue optical transients (FBOTs), are a mysterious class of astrophysical event.
+Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a mysterious class of astrophysical event.
 They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
@@
 In this paper, we investigate the host galaxies of the largest RET sample to date from the Dark Energy Survey (DES).
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar mass star-formation rate (SFR) for 49 hosts, and metallicity for 42.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 hosts, and metallicity for 42.
 We find that RETs explode almost exclusively in star-forming galaxies and are thus likely associated with massive stars.
@@
 
- Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
+ Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973}, were only unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
 Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
@@
 \citealt{Quimby2011, Gal-Yam2012}).
-Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citet{Li2011}.
+Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citep{Li2011}.
 The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly formed, rapidly rotating magnetar.
@@
  The chemical composition of the interstellar medium (ISM) is an important consideration when comparing host galaxy properties.
-While it does not appear to play a significant role in the relative production of CCSNe (although there are some trends, with SESNe typically found in slightly less metal-rich galaxies than SNe II; \citealt{Galbany2018}), it appears to be vitally important in the production of LGRBs and SLSNe.
-Theory predicts that the production of a LGRB should only be possible in stars with a metallicity of $Z/Z_{\sun}\leq 0.3$ \citep{Woosley1993}  in order for the likely Wolf-Rayet or blue supergiants progenitors not to lose their outer atmospheres through metal-driven winds, thus conserving sufficient angular momentum to power the black-hole-driven jet or rapidly rotating magnetar.
-Many LGRB host galaxy studies have indeed revealed a metallicity threshold to be observed between 0.5 and 1 times the solar value \citep[e.g.][]{Stanek2006,Modjaz2008,Kruehler2015,Perley2016b,Japelj2016,Vergani2017}.
+While it does not appear to play a significant role in the relative production of CCSNe (although there are some trends, with SESNe typically found in slightly less metal-rich environments than SNe II; \citealt{Galbany2018}), it appears to be vitally important in the production of LGRBs and SLSNe.
+Theory predicts that the production of a LGRB should only be possible in stars with a metallicity of $Z/Z_{\sun}\leq 0.3$ \citep{Woosley1993}  in order for the likely Wolf-Rayet or blue supergiant progenitors not to lose their outer atmospheres through metal-driven winds, thus conserving sufficient angular momentum to power the black-hole-driven jet or rapidly rotating magnetar.
+Many LGRB host galaxy studies have indeed revealed a metallicity threshold to be observed between 0.5 and 1 times the solar value \citep[e.g.][]{Stanek2006,Modjaz2008,Kruehler2015,Perley2016b,Japelj2016,Vergani2017}, although this is not a rigid cut.
 SLSN host galaxies also appear to be lower in metallicity than would be expected for their stellar mass, with a suppression of SLSN production at a value around half-solar \citep{Lunnan2014,Chen2016a,Perley2016c}.
@@
 
-Recently, inspection of high-cadence, all-sky survey data sets have revealed yet more exotic transients that are less easy to explain with conventional models.
-\citet{Drout2014} revealed a class of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
+Recently, inspection of high-cadence, large-area survey data sets have revealed yet more exotic transients that are less easy to explain with conventional models.
+\citet{Drout2014} discovered a class of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
 \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
@@
 \toprule
-{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
-Transient name &          &           &          &         &         &            &               \\
+{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time \tnote{b} \\
+Transient name &  (J2000  & (J2000)  &  (AB)    &         &         &   (hours)         &               \\
 \midrule
@@
 \item[e] Found by updated search method (Section \ref{subsec:new_method})
+\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method 
 \end{tablenotes}
@@
 \item Maximum observed brightness in both $g$- and $r$-bands was brighter than 24 mag (in the eight `shallow' DES-SN fields) or 25 mag (in the two `deep' fields).
-\item $g$- and $r$-band observations used for the colour had to be taken within 2 days in observer frame.
+\item $g$- and $r$-band observations used for the colour had to be taken within 2 days of each other in the observer frame.
 \end{enumerate}
@@
 Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
-To negate this issue, we use the interpolated GP LCs presented in \citet{Pursiainen2019}.
+To negate this issue, we use lightcurves interpolated using Gaussian  (GP) as presented in \citet{Pursiainen2019}.
 The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
@@
 We refer to the resulting sample as DES RETs.
-Of the 106 objects in the sample, 97 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift.
+Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift.
 A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves.
 We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
-The observational properties of the 49 hosts with redshift are displayed in Table \ref{tab:obs}.
+
+The observed magnitude distribution of all DES RET hosts is displayed in Fig.
+\ref{fig:mag_dist}, while Fig.
+\ref{fig:z_dist} shows the distribution of redshifts amongst the 49 hosts for which such a measurement was possible.
+The effect that the redshift selection function has on the results is discussed in Section \ref{subsec:disc_bias}.
+The observational properties of the 97 detected hosts are displayed in Table \ref{tab:obs}.
+We highlight objects that were not presented in \citetalias{Pursiainen2018}.
+We also highlight a small subset of objects for which the redshift has taken on a new value than that presented in \citetalias{Pursiainen2018} due to further OzDES observations leading to a more accurate determination.
 
@@
 Since the DES sample of RETs is by far the largest discovered to date, there is no other large sample of RETs with which to compare host galaxy properties.
-\citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses and SFRs.
+\citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses, SFRs, and metallicities.
 To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'') with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
@@
 In compiling a set of comparison samples, we aim for the least biased selections possible.
-This requires surveys to be untargetted (they were not monitoring certain galaxies in order to search for SNe), and ideally complete to a certain volume limit.
-While in practice the second of these criteria is difficult to achieve, we are able to choose comparison samples from untargetted surveys to mitigate initial selection biases.
+This requires surveys to be untargetted (they were not monitoring certain galaxies in order to search for SNe), ideally complete, and also covering a similar redshift range to the RETs.
+While in practice the second and third of these criteria are difficult to achieve, particularly with the fainter CCSNe, we are able to choose comparison samples from untargetted surveys to mitigate initial selection biases.
 
-To compare with CCSNe, we draw on the untargetted sample of 47 SNe II from PTF \citep{Stoll2013}, which is likely complete in terms of hosts (all SNe have an associated host).
+To compare with CCSNe, we draw on the untargetted sample of 47 SNe II from the Palomar Transient Factory (PTF; \citealt{Stoll2013}), which is likely complete in terms of hosts (all SNe have an associated host).
 While this sample lies at much lower redshift than the DES RETs (a maximum of 0.18 and mean of 0.05), redshift evolution is easier to account for than unknown incompleteness.
 We add to this the compilation of 56 untargeted SESNe from \citet{Sanders2012}, with a maximum redshift of 0.26 and a mean of 0.05.
-Since \citet{Sanders2012} do not report host galaxy magnitudes, stellar masses or SFRs, we cross-correlated the SN positions with the the Sloan Digital Sky Survey (SDSS; \citealt{York2000}) Data Release 16 (DR16; \citealt{Ahumada2019}) and perform our own SED fit using the method outlined in Section \ref{subsec:sedfit}.
+Since \citet{Sanders2012} do not report host galaxy magnitudes, stellar masses or SFRs, we cross-match the SN positions with the the Sloan Digital Sky Survey (SDSS; \citealt{York2000}) Data Release 16 (DR16; \citealt{Ahumada2019}) and perform our own SED fit using the method outlined in Section \ref{subsec:sedfit}.
+We are able to do this for 38 objects, with the others lying outside of the SDSS footprint.
 
 We use the sample of GRB host galaxies of \citet{Kruehler2015}, using only galaxies with $z<1$ in order to maintain completeness, resulting in a sample of 29 hosts with a mean redshift of 0.66.
-To investigate similarities with SLSNe, we use the PTF sample of \citet{Perley2016c} with a mean redshift of 0.24 and a maximum of 0.50.
+To investigate similarities with SLSNe, we use the host galaxy sample from PTF presented in \citet{Perley2016c} with a mean redshift of 0.24 and a maximum of 0.50.
 
@@
 \citet{Stoll2013} and \citet{Drout2014} assume a \citet{Salpeter1955} IMF whereas all other samples considered (including those calculated in this work in Section \ref{subsec:sedfit}) are determined assuming a \citet{Chabrier2003} IMF.
-Stellar masses and star-formation rates derived using a Salpeter IMF are believed to be roughly $\sim 1.72$ times higher than those using a Chabrier IMF \citep{Speagle2014}, and we convert by this factor in order to compare them.
+Stellar masses and star-formation rates derived using a Salpeter IMF are believed to be roughly $\sim 1.72$ times higher than those using a Chabrier IMF \citep{Speagle2014}, and we convert the Salpeter-derived values by this factor in order to compare them.
 
@@
 The coadds were created using data from all five seasons of DES-SN, but by excluding one season at a time in order for that coadd not to include contamination from the transients in that season.
-For this sample, the limiting magnitude for obtaining a spectroscopic redshift (\ref{subsec:spec}) is $\sim 24.5$, meaning that all hosts in the sample are detected with a high S/N.
+For this sample, the limiting magnitude for obtaining a spectroscopic redshift (Section \ref{subsec:spec}) is $\sim 24.5$, meaning that all hosts in the sample are detected with a high S/N.
 
 \subsection{Spectroscopy \label{subsec:spec}}
-Accurate redshifts for DES-SN were obtained by OzDES\footnote{Australian (Oz) Dark Energy Survey}, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner.
+Accurate redshifts for DES-SN were obtained by OzDES, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner.
 The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient.
-The spectra have a resolution of 1400-1700 and a wavelength range of 3700$\AA - 8800\AA$, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
+The spectra have a resolution of 1400-1700 and a wavelength range of 3700~\AA~-~8800~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
 Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
@@
 Where the spectra from which those redshifts were derived are also public they are included in this analysis.
-These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}), the Sloan Digital Sky Survey Data Release 16 (SDSS DR16; \citealt{York2000,Ahumada2019}).
-In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56.
+These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS.
+In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel.
 We stress that the emission lines are detected with a higher SNR than this.
@@
 \subsection{SED fitting \label{subsec:sedfit}}
-\mike{Mike to read and add!}
 To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
-We use \citet{Bruzual2003} models and a \citet{Chabrier2003} initial mass function (IMF).
-From the synthetic spectra we derive model magnitudes in the DES $griz$ bands and compare them to the observed magnitudes.
-For each set of model and observed magnitudes we calculate a $\chi^2$ value and adopt the $M/L$ and SFR from model with the lowest $\chi^2$ as our best estimates.
+We simulate a suite of synthetic galaxy star-formation histories from which we synthesise model SEDs using stellar population models from \citet{Bruzual2003}  and a \citet{Chabrier2003} initial mass function (IMF).
+The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}.
+From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed magnitudes.
+For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for  key model parameters (mass-to-light ratio $M/L$ and specific star-formation rate sSFR).
 To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds.
@@
 
-\caption{Host galaxy properties for the 49 DES RET host galaxies with redshifts and host galaxy spectra. The full table is available online in the online version in a machine readable format.}
+\caption{Host galaxy properties for the 49 DES RET host galaxies with redshifts and host galaxy spectra. The table is available in the online version in a machine readable format.}
 \begin{threeparttable}
@@
 DES13X1hav &   $9.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.38}$ &  $-0.44 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.93}$ &   $-9.60 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.55}$ &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &                                                             - &                                                             - &                                                             - &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &   $8.20 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.36}$ \\
+DES13X3nyg &   $9.31 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.42}$ &   $0.05 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.73}$ &   $-9.27 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &  $8.46 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.12}$ &                                                             - &                                                             - &                                                             - &  $8.46 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.12}$ &   $8.18 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.07}$ \\
+DES13X3gmd &  $10.33 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.44}$ &   $0.74 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.86}$ &   $-9.59 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.42}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                              - \\
+DES13X2wvv &   $9.79 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.34}$ &   $0.19 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.25}$ &   $-9.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.91}$ &  $8.41 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &  $8.41 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.27}$ &   $8.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.16}$ \\
+DES14S2anq &   $9.41 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.23}$ &  $-0.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.54}$ &   $-9.75 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.32}$ &  $8.34 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.02}$ &  $8.16 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &  $8.34 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.35 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.02}$ &  $8.36 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &   $8.29 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ \\
+DES14X1bnh &  $11.71 _{\scriptscriptstyle 0.69} ^{\scriptscriptstyle 0.25}$ &   $1.53 _{\scriptscriptstyle 0.95} ^{\scriptscriptstyle 0.52}$ &  $-10.18 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                              - \\
+DES15S1fli &  $10.24 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.26}$ &   $1.54 _{\scriptscriptstyle 1.01} ^{\scriptscriptstyle 0.67}$ &   $-8.70 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.41}$ &  $8.79 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.05}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.05}$ &   $8.44 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.06}$ \\
+DES15S1fll &   $9.20 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.32}$ &  $-0.14 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.54}$ &   $-9.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.22}$ &  $8.34 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.32}$ &  $8.38 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.36}$ &  $8.32 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.16}$ &  $8.27 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.13}$ &  $8.59 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.57}$ &   $8.29 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.31}$ \\
+DES14X3pkl &   $9.60 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.26}$ &   $0.26 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.72}$ &   $-9.34 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.46}$ &  $8.37 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.13}$ &  $8.20 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &  $8.48 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.06}$ &                                                             - &                                                             - &   $8.52 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.07}$ \\
+DES13X3npb &  $11.02 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.18}$ &   $1.14 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 1.35}$ &   $-9.88 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 1.17}$ &  $8.98 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.05}$ &                                                             - &                                                             - &                                                             - &  $8.98 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.05}$ &   $8.65 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ \\
+DES15X2ead &   $9.92 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.20}$ &   $0.22 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.47}$ &   $-9.69 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.27}$ &  $8.47 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.13}$ &  $8.23 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.09}$ &  $8.48 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.52 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.08}$ &  $8.67 _{\scriptscriptstyle 0.66} ^{\scriptscriptstyle 0.33}$ &  $8.45 _{\scriptscriptstyle -0.00} ^{\scriptscriptstyle 0.16}$ \\
+DES14S2plb &  $10.36 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.25}$ &   $0.89 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.77}$ &   $-9.47 _{\scriptscriptstyle 0.40} ^{\scriptscriptstyle 0.52}$ &  $8.62 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.33}$ &  $8.59 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.60 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.63 _{\scriptscriptstyle 0.00} ^{\scriptscriptstyle 0.00}$ &  $8.96 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &   $8.64 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ \\
+DES14S2pli &  $10.27 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.34}$ &   $0.50 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.61}$ &   $-9.77 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.27}$ &  $8.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &                                                             - &  $8.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &   $8.52 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ \\
+DES14C3tnz &  $10.21 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.41}$ &   $0.78 _{\scriptscriptstyle 0.60} ^{\scriptscriptstyle 0.88}$ &   $-9.44 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.47}$ &  $8.68 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.68 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 0.26}$ &   $8.33 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ \\
+DES15X3mxf &   $9.93 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.32}$ &   $0.78 _{\scriptscriptstyle 1.18} ^{\scriptscriptstyle 0.90}$ &   $-9.15 _{\scriptscriptstyle 0.88} ^{\scriptscriptstyle 0.58}$ &  $8.57 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.11}$ &                                                             - &                                                             - &                                                             - &  $8.57 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.11}$ &   $8.24 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.09}$ \\
+DES15C3lpq &   $9.32 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.39}$ &   $0.86 _{\scriptscriptstyle 0.73} ^{\scriptscriptstyle 1.08}$ &   $-8.45 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.68}$ &  $8.59 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.59 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.26}$ &   $8.25 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.25}$ \\
+DES15C3nat &  $10.49 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.58}$ &   $1.14 _{\scriptscriptstyle 0.60} ^{\scriptscriptstyle 0.98}$ &   $-9.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.41}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                              - \\
+DES15C3mgq &   $8.41 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.29}$ &  $-1.12 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.55}$ &   $-9.53 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &  $8.33 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.25}$ &  $8.29 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.51}$ &  $8.38 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.17}$ &  $8.29 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.11}$ &  $8.37 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.46}$ &   $8.28 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.21}$ \\
+DES15E2nqh &   $9.28 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.28}$ &   $0.11 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.94}$ &   $-9.17 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.66}$ &  $8.50 _{\scriptscriptstyle 0.76} ^{\scriptscriptstyle 0.37}$ &                                                             - &                                                             - &                                                             - &  $8.50 _{\scriptscriptstyle 0.76} ^{\scriptscriptstyle 0.37}$ &   $8.20 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.32}$ \\
+DES15C3opk &   $9.89 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.22}$ &   $0.89 _{\scriptscriptstyle 1.20} ^{\scriptscriptstyle 0.67}$ &   $-9.01 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.45}$ &  $8.68 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &  $8.68 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.27}$ &   $8.33 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.29}$ \\
+DES15C3opp &   $9.15 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.32}$ &   $0.13 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.84}$ &   $-9.02 _{\scriptscriptstyle 0.57} ^{\scriptscriptstyle 0.52}$ &  $8.59 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.19}$ &                                                             - &                                                             - &                                                             - &  $8.59 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.19}$ &   $8.25 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.17}$ \\
+DES16E2pv  &   $9.57 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.43}$ &   $0.07 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.98}$ &   $-9.50 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.55}$ &  $8.53 _{\scriptscriptstyle 0.74} ^{\scriptscriptstyle 0.35}$ &                                                             - &                                                             - &                                                             - &  $8.53 _{\scriptscriptstyle 0.74} ^{\scriptscriptstyle 0.35}$ &   $8.21 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.32}$ \\
+DES16S1bbp &   $9.06 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &   $0.30 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.79}$ &   $-8.75 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.49}$ &  $8.26 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.08}$ &  $8.14 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.17}$ &  $8.26 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.30 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.19 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.20}$ &  $8.28 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle -0.01}$ \\
+DES16X3cxn &   $9.55 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.57}$ &  $-0.32 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 1.00}$ &   $-9.88 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.43}$ &  $8.53 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.25}$ &                                                             - &                                                             - &                                                             - &  $8.53 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.25}$ &   $8.21 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.21}$ \\
+DES16C1cbd &  $10.77 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.22}$ &  $-1.43 _{\scriptscriptstyle 1.94} ^{\scriptscriptstyle 1.48}$ &  $-12.20 _{\scriptscriptstyle 1.79} ^{\scriptscriptstyle 1.26}$ &  $8.72 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.11}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.11}$ &   $8.36 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.11}$ \\
+DES16X3ega &   $9.94 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.18}$ &   $0.30 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.26}$ &   $-9.64 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.08}$ &  $8.58 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ &  $8.43 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.17}$ &  $8.47 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &  $8.61 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.07}$ &  $8.77 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.06}$ &   $8.51 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.08}$ \\
+DES16X3erw &   $9.89 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &   $0.94 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.62}$ &   $-8.94 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.36}$ &  $8.72 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.09}$ &   $8.37 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.09}$ \\
+DES16C3gin &   $9.85 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &   $0.45 _{\scriptscriptstyle 0.68} ^{\scriptscriptstyle 1.00}$ &   $-9.41 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.68}$ &  $8.80 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.80 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.09}$ &   $8.44 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.10}$ \\
+DES16S1dxu &   $8.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.41}$ &  $-0.49 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 1.70}$ &   $-9.09 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.29}$ &  $8.27 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.19}$ &  $8.25 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.43}$ &  $8.22 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.12}$ &  $8.26 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.09}$ &  $8.37 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.20}$ &   $8.21 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.10}$ \\
+DES16X1eho &  $10.70 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.42}$ &   $0.01 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 1.33}$ &  $-10.69 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.91}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                              - \\
+DES17C3gop &   $9.90 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.58}$ &   $0.19 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.86}$ &   $-9.71 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ &  $8.61 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.34}$ &                                                             - &                                                             - &                                                             - &  $8.61 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.34}$ &   $8.27 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.34}$ \\
+DES17S2fee &  $11.20 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.22}$ &   $0.28 _{\scriptscriptstyle 1.91} ^{\scriptscriptstyle 0.70}$ &  $-10.92 _{\scriptscriptstyle 1.77} ^{\scriptscriptstyle 0.48}$ &  $8.59 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.21}$ &  $8.39 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.78 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &                                                             - &                                                             - &      $8.86 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle -}$ \\
+DES17X3dxu &  $10.49 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.22}$ &   $1.02 _{\scriptscriptstyle 0.69} ^{\scriptscriptstyle 0.63}$ &   $-9.47 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.40}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                              - \\
+DES17X3cds &   $9.36 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.31}$ &  $-0.18 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.83}$ &   $-9.53 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.52}$ &  $8.76 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.20}$ &                                                             - &                                                             - &                                                             - &  $8.76 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.20}$ &   $8.41 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.22}$ \\
+DES17X3hxi &   $8.60 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.00}$ &  $-0.37 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.10}$ &   $-8.96 _{\scriptscriptstyle 0.00} ^{\scriptscriptstyle 0.10}$ &  $8.55 _{\scriptscriptstyle 0.82} ^{\scriptscriptstyle 0.36}$ &                                                             - &                                                             - &                                                             - &  $8.55 _{\scriptscriptstyle 0.82} ^{\scriptscriptstyle 0.36}$ &   $8.22 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.34}$ \\
 DES13E2lpk &  $10.66 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.10}$ &   $0.46 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.45}$ &  $-10.20 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.35}$ &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &                                                             - &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &   $8.58 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\

### 2020-03-12 RET_Hosts_IR.tex

@@
 The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient.
-The spectra have a resolution of 1400-1700 and a wavelength range of 3700~\AA~-~8800~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
+The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
 Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
@@
 \caption{Baldwin-Phillips-Terlovich (BPT) diagram for RET hosts, showing that the emission lines are consistent with being generated by star formation rather than AGN activity.
-The three curves show the delimitation between star formation and AGN according to \citet{Kewley2013}.
+The three curves show the delimitation between star formation and AGN at $z =0, 0.5, 1$ according to \citet{Kewley2013}.
 \label{fig:bpt}}
@@
 To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds.
+The results are presented in Table \ref{tab:derived}.
 
@@
 
-Due to the low S/N of the spectra in this sample, we are constrained to a subset of these diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959 and 5007, \NII 6548 and 6583, and \SII 6717 and 6731.
-Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII and \SII are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta lines available, mandating the use of the R23 diagnostic.
-For hosts at $z<0.3$ we are able to use the \OIII /\NII (O3N2), \NII /\halpha (N2), and \SII /\NII (S2N2) line ratios.
+Due to the low S/N of the spectra in this sample, we are constrained to a subset of metallicity diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959/5007, \NII 6548/6583, and \SII 6717/6731.
+Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII~and \SII~are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta~lines available, mandating the use of the R23 diagnostic.
+For hosts at $z<0.3$ we are able to use the \OIII /\NII~(O3N2), \NII /\halpha~(N2), and \SII /\NII~(S2N2) line ratios.
 
-Due to the redshift range of our sample, and the limited wavelength coverage of the spectra ($3000-8000~\AA$), we are unable to use a single line ratio to estimate the oxygen abundances.
+Due to the redshift range of our sample, and the limited wavelength coverage of the spectra ($3000-8000$~\AA), we are unable to use a single line ratio to estimate the oxygen abundances.
 We thus determine a set of indicators for which to calculate abundances.
@@
 At abundances around $12 + \log \mathrm{(O/H)} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio.
-In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII / \OII ratio \citep{Kewley2008}.
-In the cases where \NII is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy mass to derive a crude metallicity estimate from the MZR of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic.
+In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII/\OII~ratio \citep{Kewley2008}.
+In the cases where \NII~is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy stellar mass to derive a crude metallicity estimate from the mass-metallicity relation (MZR) of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic.
 For $12 + \log \mathrm{(O/H)}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.
+While this is circular (in Section \ref{subsec:res_metallicity} we plot the MZR for RETs), it is a rough estimation.
+If we leave the branch choice for those with no \NII~to be random, we find that the results are consistent to within uncertainties
 
@@
 Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the scale of PP04 (O3N2) using the conversion from \citet{Kewley2008}.
-This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide for DES RET hosts where available.
+This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available.
 For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we calculate a weighted mean of the values after transforming them to the PP04 O3N2 scale.

### 2020-03-16 RET_Hosts_IR.tex
Updates from Overleaf

@@
 \newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
-\newcommand{\miika}[1]{\color{green}#1 \color{black}}
-
+\newcommand{\replychris}[1]{\color{magenta}#1 \color{black}}
+\newcommand{\replylluis}[1]{\color{green}#1 \color{black}}
 \newcommand{\comment}[1]{\textbf{[#1]}} %comments
@@
 \begin{abstract}
-Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a mysterious class of astrophysical event.
+Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a \replychris{distinct} class of astrophysical event.
 They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
@@
 In this paper, we investigate the host galaxies of the largest RET sample to date from the Dark Energy Survey (DES).
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 hosts, and metallicity for 42.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 hosts, and metallicit\replychris{ies} for 42.
 We find that RETs explode almost exclusively in star-forming galaxies and are thus likely associated with massive stars.
-Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFR, indicating a link to young stellar populations, similar to stripped-envelope SNe.
-RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SNe host galaxies.
+Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFR\replychris{s}, indicating a link to young stellar populations, similar to stripped-envelope SNe.
+RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies.
 There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.
@@
 There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
-On average, SESNe reside in galaxies with higher specific star-formation rate (sSFR) and younger stellar age indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II \citep{James2006,Kelly2008,Galbany2018}.
+On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs) and younger stellar age\replychris{s} indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II \citep{James2006,Kelly2008,Galbany2018}.
 More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
@@
 SLSN host galaxies also appear to be lower in metallicity than would be expected for their stellar mass, with a suppression of SLSN production at a value around half-solar \citep{Lunnan2014,Chen2016a,Perley2016c}.
-They also require particularly high sSFR, suggesting that they are explosions of very young, rapidly rotating massive stars.
+They also require a particularly high sSFR, suggesting that they are explosions of very young, rapidly rotating massive stars.
 
@@
 \citet{Drout2014} discovered a class of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
-\citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
+\replychris{\citet{Arcavi2016} discovered three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one declines rapidly like the PS1 sample.} \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
 A further sample of five objects has been discovered by the Hyper Suprime-Cam Subaru Strategic Program (SSP) Transient Survey \citep{Tampo2020}.
@@
 The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN) \citep{Ho2019}.
-There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN) \citep{Soker2019}
-Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf in a non-standard scenario, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
+There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN) \citep{Soker2019}; \replychris{or a wind-driven transient \citep{Ono2020}}.
+Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
 It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.
@@
 
-The order of the paper is as follows:
+The order of the paper is as follows: \replychris{in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}.
+The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).}
 Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$.
@@
 \includegraphics[width=0.5\textwidth]{figs/spec_gr_trise_r_GP5_new_colorscheme.pdf}
-\caption{Observer-frame $g-r$ colour and $r$-band rise-time, derived from Gaussian Processed fits to DES-SN photometry for spectroscopically confirmed SNe and \citetalias{Pursiainen2018} RETs.
-The location of the red box is designed to maximise the completeness and purity of RETs,
+\caption{Observer-frame $g-r$ colour \replychris{at maximum light} and \replychris{observer-frame} $r$-band rise-time, derived from Gaussian Processed fits to DES-SN photometry for spectroscopically confirmed SNe and \citetalias{Pursiainen2018} RETs.
+The location of the red box is designed to maximise the completeness and purity of RETs.
+\replychris{ The fractions in the legend refer to the number of each class of transient passing the cuts of Section \ref{subsec:new_method} compared to the total number of that class in DES-SN, while the number in parentheses refers to the number inside the red box defining RET parameter space.
+}
 \label{fig:selection}}
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
-\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES.
-The orange histogram represents the 97/106 DES RETs for which a host was detected.
-The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
-\label{fig:mag_dist}}
-\end{figure}
-
-\begin{figure}
 \includegraphics[width=0.5\textwidth]{figs/z_dist.png}
@@
 
-\section{Sample selection\label{sec:sample}}
-
+\section{Sample selection}
+\label{sec:sample}
 We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey.
@@
 We refer to the resulting sample as DES RETs.
-Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift.
+Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift \replychris{which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04).
+The full OzDES GRC will be available alongside the public data release detailed in \citet{Lidman2020}}.
 A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves.
@@
 
-The observed magnitude distribution of all DES RET hosts is displayed in Fig.
-\ref{fig:mag_dist}, while Fig.
+Fig.
 \ref{fig:z_dist} shows the distribution of redshifts amongst the 49 hosts for which such a measurement was possible.
@@
 
-\section{Host galaxy observations \label{sec:obs}}
+\section{Host galaxy observations}
+\label{sec:obs}
 \subsection{Photometry \label{subsec:phot}}
@@
 The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
-Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
-Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the General Redshift Catalogue nontheless.
+\replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
+\replychris{We also obtained redshifts for some transient hosts as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey (PI: A.
+Baker) \citep{Baker2020} (labelled NOAO in Table \ref{tab:obs}}.
+Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.
 Where the spectra from which those redshifts were derived are also public they are included in this analysis.
@@
 
-\section{Estimating host galaxy properties \label{sec:measure}}
-
+\section{Estimating host galaxy properties}
+\label{sec:measure}
 \subsection{SED fitting \label{subsec:sedfit}}
@@
 
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
-\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-\label{fig:sfr_cum}}
-\end{figure}
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
+%\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+%\label{fig:sfr_cum}}
+%\end{figure}
+
 \subsection{Estimating metallicities \label{subsec:calc_Z}}
@@
 \subsection{Star formation rate \label{subsec:res_sfr}}
-Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for CCSNe and for the field galaxies of SDSS.
-RETs and CCSNe both systematically avoid passive galaxies, suggesting that RETs may require the presence of star-formation and thus be linked to massive stars.
-
-In Fig.~\ref{fig:sfr_cum} we show the cumulative distributions of the star-formation rate in RETs, CCSNe, and SDSS galaxies.
-With the exception of three objects, all RETs occured in galaxies with $\textrm{SFR}>0.1 \msun$yr$^{-1}$, and the curve is shifted towards higher SFRs than that for CCSNe.
-This would imply that a higher SFR is required for RETs to occur - or can be thought of as a higher SFR threshold for the formation of a RET progenitor.
+Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for the comparison samples and for the field galaxies of SDSS.
+RETs follow CCSNe, LGRBs and SLSNe in systematically avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
+The local rapid transients Cow, Koala and SN2018gep are
 
@@
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.
-Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts.
+Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely starforming environments home to LGRBs or SLSNe.
 
-As for SFR, we show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}.
+We show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}.
 The RET hosts are clearly shifted to higher sSFRs than CCSNe.
@@
 central value, identical to mean for a skewness of 0) and `scale' (spread, identical to standard deviation for a skewness of 0)\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
-The results from the simultaneous fitting shows RET hosts to be shifted to higher sSFRs CCSNe.
+The results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
+The comparison shows RET hosts to be shifted to higher sSFRs CCSNe.
 In 100\% of the posterior samples the RETs were located at higher average sSFRs than SNe II, while the same was true 76\% of the time for RETs when comparing with SESNe.
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
+\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES.
+The orange histogram represents the 97/106 DES RETs for which a host was detected.
+The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
+\label{fig:mag_dist}}
+\end{figure}
+
 In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars.
@@
 Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies.
-The cumulative distributions of metallicity are displayed in \ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies.
+The cumulative distributions of metallicity are displayed in Fig.
+\ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies.
 The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe.
@@
 
-In Fig.~\ref{fig:mzr} we show the mass-metallicity relation (MZR) for the RET and comparison samples.
+In Fig.~\ref{fig:mzr} we show the MZR for the RET and comparison samples.
 The contours show the MZR for low-redshift ($\hat{z}=0.08$) star-forming galaixes from SDSS, adjusted to the PP04 O3N2 diagnostic.
@@
 The RET hosts lie systematically below the galaxy MZR fits as well as the bulk of the SDSS galaxies, meaning that for a given stellar mass they have a lower metallicity.
+They populate similar regions to SESNe, LGRBs and SLSNe but are clearly offset from the SNe II.
 
@@
 
-\section{Discussion \label{sec:disc}}
+\section{Discussion}
+\label{sec:disc}
 \begin{figure}
@@
 In order to test this possibility, we examined the RETs that do not have a host galaxy redshift.
-Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process.
+Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process, and is summarised in Fig.
+\ref{fig:mag_dist}.
 Of the 48 objects without a redshift, 40 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}.
 Of more significance is that only 34 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign.
-The other, `hostless', objects are either transients that are located remotely from a host that was detected, or are hosted by a galaxy that was not detected.
+The other, `hostless', objects are either transients that are located remotely from a galaxy that was detected, or are hosted by a galaxy that was not detected.
 Non-detected hosts are either intrinsically faint and thus low in mass, situated at high redshift, or both.
@@
 A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation.
-The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), (\citetalias{Drout2014,Pursiainen2018,Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
+The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014},\citetalias{Pursiainen2018},\citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
 At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohmaier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
@@
 At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those redshifts only the more massive galaxies are detected.
-This effect can be seen in the Fig.
-\ref{fig:ret_v_host} panel a, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in panel b.
+This effect can be seen in panel a) of Fig.
+\ref{fig:ret_v_host}, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in panel b.
 It is hoped that a complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) allowing the removal of these biases in order to reveal any underlying relationships.
@@
 SN2018kzr \citep{McBrien2019} is one of the most rapidly declining transients ever discovered, with spectral signatures similar to SNe Ic.
-While host galaxy properties are not derived, the authors of that paper refer to narrow emission from the host galaxy, along with an apparently small, blue, star-forming host.
+While host galaxy properties are not derived, the authors of that paper refer to narrow emission from the host galaxy, along with an apparently small, blue, star-forming host and is thus consistent with the DES RETs.
 
-\subsection{The passive host of DES16C1cbd \label{subsec:disc_cbd}}
-In Figs. \ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr} there is one clear outlier with very low SFR. The host of DES16C1cbd appears to be a passive galaxy
+%\subsection{The passive host of DES16C1cbd \label{subsec:disc_cbd}}
+%In Figs. \ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr} there is one clear outlier with very low SFR. The host of %DES16C1cbd appears to be a passive galaxy
 
-\phil{Adding more once I know about the SFR from [OII]}
 \section{Conclusions}
-
+\label{sec:conc}
 By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of this as-yet unexplained phenomenon.
+We conclude that RETs are stronly linked to massive stars, due to their apparent reliance on star formation.
+Their origin is likely from more massive stars than SNe II, as they require higher sSFR.
+RET hosts are lower in metallicity than SNe II hosts, suggesting some reliance on rotational energy or other metallicity-dependent effects.
+Of the RET analogues discovered in the local Universe, ZTF18abvkwla shares the most similar host galaxy characteristics with the DES RET population.
+SN2018gep appears in a galaxy too faint to have been detected by DES-SN at the redshift of most of the DES RETs, while the host of AT2018cow is much higher in metallicity.
 
@@
 
+\section{Bayesian Fits}
+\label{app:b}
 \end{table*}

### 2020-03-17 RET_Hosts_IR.tex
Updates from Overleaf

@@
 \newcommand{\hdelta}[0]{H$\delta$}
+\newcommand{\HII}[0]{$[\textnormal{\textsc{Hii}}]$}
 \newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
@@
 \begin{abstract}
-Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a \replychris{distinct} class of astrophysical event.
+Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a distinct class of astrophysical event.
 They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
@@
 In this paper, we investigate the host galaxies of the largest RET sample to date from the Dark Energy Survey (DES).
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 hosts, and metallicit\replychris{ies} for 42.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 hosts, and metallicities for 44.
 We find that RETs explode almost exclusively in star-forming galaxies and are thus likely associated with massive stars.
-Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFR\replychris{s}, indicating a link to young stellar populations, similar to stripped-envelope SNe.
+Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs, indicating a link to young stellar populations, similar to stripped-envelope SNe.
 RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies.
@@
 In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe).
-CCSNe can be split into observationally-determinded subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
-Conversely, SNe Ib and Ic do not show signatures of hydrogen and are thus referred to collectively as stripped-envelope SNe (SESNe).
+CCSNe can be split into observationally-determinded subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \replylluis{that disappear after a few weeks}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
+Conversely, SNe Ib and Ic do not show signatures of hydrogen and are thus referred to collectively as stripped-envelope SNe (SESNe) \replylluis{, having undergone a partial removal of their outer atmospheres}.
 The SN IIb subclass, which shows hydrogen only at early epochs, is also commonly grouped along with SESNe.
+\replylluis{SNe IIn, with the n standing for \textit{narrow}, display hydrogen lines with much lower velocities than standard SNe II, indicating their origin from the ejecta impacting on slow-moving circumstellar material (CSM)}.
 Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
@@
 There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
-On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs) and younger stellar age\replychris{s} indicating that their progenitors are more massive than the various sub-classes of hydrogen-rich SNe II \citep{James2006,Kelly2008,Galbany2018}.
+On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs; \citealt{James2006,Kelly2008}), \replylluis{while studies of the local environments tend to show SESNe to explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Galbany2018}}.
 More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
@@
 There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}.
-The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN) \citep{Ho2019}.
-There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN) \citep{Soker2019}; \replychris{or a wind-driven transient \citep{Ono2020}}.
+The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}.
+There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Ono2020}}.
 Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
@@
 The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years.
-The second reason is an update to the sample selection technique.
-By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.
+\replylluis{By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.} The second reason is an update to the sample selection technique, \replylluis{which adds a further 14 transients.}
 
@@
 To negate this issue, we use lightcurves interpolated using Gaussian  (GP) as presented in \citet{Pursiainen2019}.
-The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band.
-Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space (Fig.
-\ref{fig:selection}) and are thus easier to separate.
-We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
+The interpolated light curves have a 0.5 day cadence and every epoch \replychris{and band} has a flux value, and an associated uncertainty.
+Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$ \replylluis{vs.} $t_{\mathrm{rise; r}}$ parameter space (Fig.
+\ref{fig:selection}), \replychris{where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness.} We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
 The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig.
@@
 In order to reduce the contamination from active galactic nuclei (AGN), we use a basic convolutional neural network (CNN) classifier.
-We train the CNN on spectrosopically confirmed SNe of all types and on spectroscopically typed AGN, and use it to separate the sample into two photometric subtypes: AGN-like and SNe-like.
-The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are removed by the final manual vetting.
-The SNe passing the CNN classifier are subjected to the LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs.
+We train the CNN on spectroscopically confirmed SNe of all types and on spectroscopically typed AGN, and use it to separate the sample into two photometric subtypes: AGN-like and SNe-like.
+The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are removed by manual vetting.
+The SNe passing the CNN classifier are subjected to LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs.
 These objects are subject to a further set of cuts.
-We impose a cut based on a fit of the LC with the \texttt{PSNID} software (\citet{Sako2008}).
+We impose a cut based on a fit of the LC with the \texttt{PSNID} software \citep{Sako2008}.
 We use thresholds of \texttt{FITPROB}$<0.91$ and \texttt{PBAYES}$<0.82$ to remove highly-probably SNe Ia, which removes 46 objects from the RET parameter space.
@@
 We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
-
+\replylluis{A selection of the host galaxies can be seen in Fig.
+\ref{fig:mosaic}, centered on the location of the transient.
+The figure showcases the diversity of host galaxy morphologies and colours, while also displaying the limitations of ground-based observations of high-redshift, relatively small galaxies in terms of spatial resolution.}
 Fig.
@@
 The effect that the redshift selection function has on the results is discussed in Section \ref{subsec:disc_bias}.
-The observational properties of the 97 detected hosts are displayed in Table \ref{tab:obs}.
+The observational properties of the 9\replylluis{6} detected hosts are displayed in Table \ref{tab:obs}.
 We highlight objects that were not presented in \citetalias{Pursiainen2018}.
@@
 \citet{Stoll2013} and \citet{Drout2014} assume a \citet{Salpeter1955} IMF whereas all other samples considered (including those calculated in this work in Section \ref{subsec:sedfit}) are determined assuming a \citet{Chabrier2003} IMF.
-Stellar masses and star-formation rates derived using a Salpeter IMF are believed to be roughly $\sim 1.72$ times higher than those using a Chabrier IMF \citep{Speagle2014}, and we convert the Salpeter-derived values by this factor in order to compare them.
+Stellar masses and star-formation rates derived using a Salpeter IMF are roughly $\sim 1.72$ times higher than those using a Chabrier IMF \citep{Speagle2014}, and we convert the Salpeter-derived values by this factor in order to compare them.
 
@@
 For $12 + \log \mathrm{(O/H)}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.
-While this is circular (in Section \ref{subsec:res_metallicity} we plot the MZR for RETs), it is a rough estimation.
+\replychris{We note that this is a rough estimation}.
 If we leave the branch choice for those with no \NII~to be random, we find that the results are consistent to within uncertainties
@@
 
-Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming intensity compared to galaxies of the same mass.
+Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming intensity.
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.
@@
 For both samples, we use identical normal priors for the `loc' (location, i.e.
-central value, identical to mean for a skewness of 0) and `scale' (spread, identical to standard deviation for a skewness of 0)\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
+central value, identical to mean \replychris{for zero skewness}) and `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
 The results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
@@
 The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{+1.8}_{-0.98}$ compared to $-0.18^{+0.75}_{-0.76}$ for RET hosts).
-The strong high-sSFR tail shows SLSNe to derive from a different population to RETs.
+The strong high-sSFR tail shows SLSNe to \replychris{occur in a different galaxy }population to RETs.
 
@@
 While stressing that these associations are lose - rates are uncertain and host galaxy parameters span wide ranges for all transients - they are both linked to the respective transients' progenitor channels.
-Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars that also require some extreme properties such as rapid rotation, albeit not as much as progenitors as SLSNe or LGRBs.
+Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, \replychris{potentially stripped of their envelopes, and possibly sharing some of the extreme properties of} SLSNe or LGRBs.
 It could therefore be possible that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to a shocked photosphere, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
@@
 Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies.
-For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFR \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
+For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFR\replychris{s} \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
 In Fig.

### 2020-03-18 RET_Hosts_IR.tex

@@
 \label{sec:measure}
-\subsection{SED fitting \label{subsec:sedfit}}
+\subsection{Photometric stellar parameters \label{subsec:sedfit}}
 To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
@@
 The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}.
-From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed magnitudes.
-For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for  key model parameters (mass-to-light ratio $M/L$ and specific star-formation rate sSFR).
+From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed \replylluis{Kron} magnitudes \replylluis{from the deep photometric catalogue of \citet{Wiseman2020}}.
+For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR).
 To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds.
 The results are presented in Table \ref{tab:derived}.
+\replylluis{These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population characteristics.}
 
-\subsection{Spectral line fitting \label{subsec:linefit}}
+\subsection{Spectroscopic gas-phase parameters \label{subsec:linefit}}
 
@@
 We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}).
-Rather than using global galaxy photometry (i.e.
-using a Kron aperture), we use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
+We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
+\replylluis{This way the resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy.
+This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole.
+There are several reasons this may not be the case, such as metallicity and age gradients or structure such as bars and discs (see e.g.
+\citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}), and proceed with our analysis with this caveat acknowledged.}
 

### 2020-03-18 RET_Hosts_IR.tex

@@
 \newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
+\newcommand{\OI}[0]{$[\textnormal{\textsc{Oi}}]$}
 \newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
@@
 \midrule
-DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
-DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
-DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
-DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    \tnote{d} &          - &             - \\
-DES13S2wxf\tnote{e}     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
-DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
-DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    \tnote{c} &      OzDES &             - \\
-DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
-DES13X3gmd\tnote{e}     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
-DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
-DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    \tnote{d} &          - &             - \\
-DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
+DES13C3avkj    & 51.97076 & -27.52792 & 24.07937 & 0.04534 &    $^c$ &      OzDES &             - \\
+DES13X3gms     & 35.80095 &  -4.49384 & 23.02264 & 0.06436 & 0.64792 &      OzDES &       6.58333 \\
+DES13C1tgd     & 54.06436 & -27.63867 & 20.30968 & 0.05848 & 0.19647 &      OzDES &      10.16667 \\
+DES13C3abtt    & 52.62108 & -28.16151 & 21.50529 & 0.03508 &    $^d$ &          - &             - \\
+DES13S2wxf     & 41.61268 &  -0.02634 & 21.31219 & 0.03266 & 0.56985 &      OzDES &       5.41639 \\
+DES13X1hav     & 35.03245 &  -5.11022 & 23.63452 & 0.07752 & 0.58236 &      OzDES &       4.00000 \\
+DES13C3smn     & 51.97112 & -28.08362 & 25.30041 & 0.06023 &    $^c$ &      OzDES &             - \\
+DES13X3nyg     & 36.99228 &  -3.91327 & 23.38744 & 0.06173 & 0.71205 &      OzDES &      45.50000 \\
+DES13X3gmd     & 36.50409 &  -4.21949 & 22.90614 & 0.05419 & 0.78082 &      OzDES &      13.91667 \\
+DES13C3bcok    & 53.02711 & -28.62476 & 18.61674 & 0.02560 & 0.34577 &  LADUMA &               \\
+DES13X3afjd    & 37.00386 &  -4.58049 & 20.75298 & 0.05737 &    $^d$ &          - &             - \\
+DES13C1acmt    & 54.32925 & -26.83371 & 23.18742 & 0.04422 &    $^c$ &      OzDES &             - \\
+DES13X3kgm     & 36.50380 &  -4.86636 & 26.46803 & 0.18709 &    $^d$ &          - &             - \\
+DES13C3uig     & 52.94416 & -27.58544 & 22.17966 & 0.03116 & 0.67346 &       ACES &               \\
+DES13C3nxi     & 51.96356 & -28.35720 & 24.99276 & 0.05177 &    $^c$ &      OzDES &             - \\
+DES13C3asvu    & 52.83670 & -27.36071 & 22.46669 & 0.02874 &    $^d$ &          - &             - \\
+DES13X3pby     & 36.33330 &  -5.31408 & 23.82628 & 0.04671 &    $^c$ &      OzDES &             - \\
+DES13X3aakf    & 35.71205 &  -4.69915 & 25.47453 & 0.09478 &    $^c$ &      OzDES &             - \\
+DES13X2wvv     & 34.86526 &  -6.71603 & 21.89573 & 0.02567 & 0.47503 &      OzDES &       4.50000 \\
+DES13X2oyb     & 35.31056 &  -5.67893 & 22.91589 & 0.06115 &    $^c$ &      OzDES &             - \\
+DES13X3alnb    & 37.18496 &  -5.14232 & 25.04147 & 0.06167 &    $^c$ &      OzDES &             - \\
+DES15X3atd     & 35.84011 &  -4.29142 & 23.87686 & 0.05432 &    $^c$ &      OzDES &             - \\
+DES14S2anq     & 41.27776 &  -0.74529 & 17.57076 & 0.03648 & 0.05211 &      OzDES &       0.75000 \\
+DES14E2xsm     &  9.67624 & -43.58736 & 23.39163 & 0.04458 &    $^c$ &      OzDES &             - \\
+DES14X1bnh     & 33.74902 &  -4.79254 & 21.95260 & 0.03597 & 0.82982 &      OzDES &       3.50000 \\
+DES14E1aqi     &  8.73970 & -43.40182 & 25.61559 & 0.23708 &    $^d$ &          - &             - \\
+DES15S1fli     & 43.18790 &  -0.88620 & 20.98517 & 0.02950 & 0.44739 &      OzDES &       2.33333 \\
+DES14C3gzj     & 52.57168 & -28.14019 & 26.04181 & 0.10494 &    $^d$ &          - &             - \\
+DES14X3pko     & 36.90824 &  -3.69642 & 24.48291 & 0.06326 &    $^d$ &          - &             - \\
+DES15S1fll     & 42.78846 &  -0.19747 & 20.95918 & 0.03719 & 0.22647 &      OzDES &       0.66667 \\
+DES14C1jnd     & 54.35153 & -27.49300 & 24.33143 & 0.08524 &    $^c$ &      OzDES &             - \\
+DES14X3pkl     & 37.21103 &  -4.80741 & 22.40853 & 0.06026 & 0.29537 &      OzDES &       5.16667 \\
+DES13X3npb     & 36.64218 &  -4.13381 & 20.79328 & 0.05336 & 0.49542 &      OzDES &       5.16667 \\
+DES15X2ead     & 36.48913 &  -6.45118 & 20.08582 & 0.03290 & 0.23175 &      OzDES &       2.00000 \\
+DES15C3edw     & 52.55235 & -27.71022 & 22.69331 & 0.03227 &    $^d$ &          - &             - \\
+DES14S2plb     & 41.85667 &  -1.61811 & 18.38419 & 0.03463 & 0.11531 &      OzDES &       2.00000 \\
+DES14S2pli     & 41.22837 &  -1.09830 & 20.86839 & 0.03093 & 0.35478 &      OzDES &       3.41667 \\
+DES15X3kyt     & 36.27500 &  -5.41103 & 24.74520 & 0.07892 &    $^d$ &          - &             - \\
+DES14C3tvw     & 53.32230 & -27.90621 & 21.31841 & 0.02516 & 0.70390 &       ACES &               \\
+DES14C3tnz     & 52.86248 & -28.51318 & 22.26137 & 0.03386 & 0.70452 &      OzDES &       5.79361 \\
+DES15X3mxf     & 36.74009 &  -5.23991 & 22.43347 & 0.04552 & 0.43673 &      OzDES &       9.83333 \\
+DES15X3nlv     & 36.04464 &  -5.02735 & 25.26349 & 0.08375 &    $^d$ &          - &             - \\
+DES15C3mem     & 52.14216 & -29.05851 & 20.28975 & 0.04590 & 0.61618 &     PRIMUS &               \\
+DES15E2lmq     &  9.62005 & -43.98734 & 25.65868 & 0.18116 &    $^d$ &          - &             - \\
+DES15C3lpq     & 52.71204 & -28.61319 & 23.28579 & 0.03610 & 0.61365 &      OzDES &       6.16667 \\
+DES15C3lzm     & 52.17460 & -28.23186 & 20.47636 & 0.02573 & 0.32690 &      ATLAS &               \\
+DES15C3nat     & 52.88528 & -28.72370 & 23.39015 & 0.03154 & 0.83929 &      OzDES &      18.62222 \\
+DES15C3mgq     & 52.76901 & -28.20882 & 22.97470 & 0.03194 & 0.23031 &      OzDES &       8.16667 \\
+DES15E2nqh     &  9.73174 & -43.08707 & 23.29709 & 0.03941 & 0.51525 &      OzDES &       6.83333 \\
+DES15C3opk     & 51.66147 & -28.34737 & 23.05209 & 0.03270 & 0.56984 &      OzDES &      12.16667 \\
+DES15C3opp     & 51.73962 & -28.11496 & 23.25950 & 0.04223 & 0.44242 &      OzDES &      16.75000 \\
+DES15C3pbi     & 52.23620 & -28.00223 & 25.10028 & 0.05470 &    $^d$ &          - &             - \\
+DES16E2pv      &  9.20875 & -43.52782 & 23.00100 & 0.05043 & 0.72608 &      OzDES &       6.00000 \\
+DES16S1bbp     & 43.26389 &   0.37149 & 21.42883 & 0.04524 & 0.19018 &      OzDES &       3.33333 \\
+DES15X3oma     & 36.74617 &  -5.11040 & 24.94606 & 0.07447 &    $^d$ &          - &             - \\
+DES16C3bor     & 52.48232 & -28.04256 & 23.83923 & 0.03711 &    $^c$ &      OzDES &             - \\
+DES16C1bde     & 54.30149 & -26.75840 & 24.96313 & 0.09485 &    $^d$ &          - &             - \\
+DES16X3wt      & 36.23751 &  -5.54488 & 26.90234 & 0.28423 &    $^d$ &          - &             - \\
+DES16X3cxn     & 36.83044 &  -4.95100 & 23.05257 & 0.04442 & 0.58464 &      OzDES &      12.83333 \\
+DES16X2bke     & 36.00989 &  -7.27130 & 25.13096 & 0.16403 &    $^d$ &          - &             - \\
+DES16C1cbd     & 54.85826 & -27.67254 & 20.93909 & 0.03048 & 0.54108 &      OzDES &       7.20000 \\
+DES16C3cdd     & 52.42731 & -27.14317 & 24.27019 & 0.05040 &    $^d$ &          - &             - \\
+DES16E1bir     &  7.74444 & -42.97696 & 24.74236 & 0.07595 &    $^c$ &      OzDES &             - \\
+DES16C3auv     & 51.90215 & -27.59087 & 24.39158 & 0.05296 &    $^c$ &      OzDES &             - \\
+DES16C3axz     & 52.80904 & -28.66678 & 20.41796 & 0.03716 & 0.22673 &  LADUMA &               \\
+DES16X3ega     & 37.09820 &  -4.77643 & 19.53601 & 0.04874 & 0.25762 &       GAMA &       1.00000 \\
+DES16X3erw     & 36.20545 &  -4.51438 & 22.23157 & 0.02865 & 0.45885 &      OzDES &       2.00000 \\
+DES16X1ddm     & 33.82824 &  -4.36428 & 21.46049 & 0.04767 &    $^c$ &      OzDES &             - \\
+DES16X3ddi     & 35.43936 &  -4.68602 & 23.93720 & 0.04360 &    $^c$ &      OzDES &             - \\
+DES16C3gin     & 52.76276 & -28.29145 & 21.52696 & 0.03653 & 0.34745 &      OzDES &       3.33333 \\
+DES16S1dxu     & 42.68141 &  -0.71039 & 21.35662 & 0.03193 & 0.13528 &      OzDES &       1.33333 \\
+DES16X1eho     & 35.34537 &  -4.52566 & 22.28516 & 0.07277 & 0.80735 &      OzDES &       6.75000 \\
+DES17X3gmp     & 37.40191 &  -4.65060 & 24.44397 & 0.06946 &    $^d$ &          - &             - \\
+DES17X2dqk     & 35.46926 &  -7.10815 & 25.96184 & 0.19576 &    $^d$ &          - &             - \\
+DES17C3gop     & 53.53574 & -28.40024 & 22.74858 & 0.03107 & 0.69185 &      OzDES &       4.00000 \\
+DES17C3gen     & 52.93346 & -29.01119 & 22.79380 & 0.04204 &    $^c$ &      OzDES &             - \\
+DES17X3fhq     & 35.93682 &  -3.97690 & 24.70876 & 0.05177 &    $^d$ &          - &             - \\
+DES17S2fee     & 41.40953 &  -1.33278 & 18.16644 & 0.04681 & 0.23737 &      OzDES &       2.00000 \\
+DES17X1hjj     & 34.24036 &  -4.21180 & 24.07284 & 0.05854 &    $^c$ &      OzDES &             - \\
+DES17X1dge     & 34.80886 &  -5.40370 & 24.15755 & 0.10116 &    $^d$ &          - &             - \\
+DES17C1fes     & 54.23372 & -27.57015 & 24.42015 & 0.10382 &    $^c$ &      OzDES &             - \\
+DES17E1gsx     &  8.11588 & -42.76823 & 22.70982 & 0.04695 &    $^c$ &      OzDES &             - \\
+DES17X3dxu     & 36.55911 &  -3.84432 & 22.83789 & 0.03973 & 0.85565 &      OzDES &       7.50000 \\
+DES17S1emy     & 43.36298 &   0.41758 & 22.51310 & 0.05326 &    $^d$ &          - &             - \\
+DES17X2cvk     & 35.93444 &  -7.32167 & 21.60107 & 0.06456 &    $^d$ &          - &             - \\
+DES17X3cdp     & 37.28283 &  -4.30434 & 25.10651 & 0.08381 &    $^c$ &      OzDES &             - \\
+DES17X3cds     & 36.27737 &  -3.79891 & 22.45168 & 0.06098 & 0.49444 &      OzDES &       5.50000 \\
+DES17C3fwd     & 52.90461 & -27.46979 & 20.46182 & 0.02355 & 0.34561 &    LADUMA &               \\
+DES17S1hih     & 42.57627 &  -0.76193 & 24.94967 & 0.12010 &    $^d$ &          - &             - \\
+DES17C3fjt     & 51.46785 & -28.14106 & 28.04246 & 0.44157 &    $^d$ &          - &             - \\
+DES17X3hxi     & 35.79624 &  -4.51713 & 23.36715 & 0.03375 & 0.62457 &      OzDES &       2.00000 \\
+DES13E2lpk     & 10.09911 & -43.53903 & 20.49379 & 0.03567 & 0.47541 &      OzDES &       6.00000 \\
+DES15C2eal     & 54.06180 & -29.23000 & 22.99891 & 0.03276 & 0.22347 &      OzDES &      16.90833 \\
+DES16C2ggt     & 53.89079 & -29.22496 & 21.09210 & 0.03142 & 0.31057 &      OzDES &       2.66667 \\
+DES16C2grk     & 55.06853 & -29.28963 & 20.45434 & 0.03869 &    $^d$ &          - &             - \\
+DES17C2hno     & 53.72691 & -29.19742 & 22.69257 & 0.07398 & 0.59953 &      OzDES &       4.66667 \\
 \bottomrule
@@
 \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
-\replychris{We also obtained redshifts for some transient hosts as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey (PI: A.
-Baker) \citep{Baker2020} (labelled NOAO in Table \ref{tab:obs}}.
+\replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA\footnte{\url{http://www.laduma.uct.ac.za}}) survey  \citep{Baker2020}, three of which are present in our sample} .
 Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.
@@
 We fit the emission lines with Gaussian profiles.
-In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a 100~\AA~window around the central wavelength of the line.
+In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution \replychris{based on the variance spectrum}.
 We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
@@
 \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
+\replylluis{We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram.
+This is also the case for the \SII and \OI versions of the diagram, and we find no evidence AGN amongst the 12 hosts in those diagrams either.}
 
@@
 
-Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the results from the probability density functions (PDFs) of the various different diagnostics, resulting in a final `best' PDF.
-We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and display the results in Table \ref{tab:derived}.
-
 The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised.
-Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the scale of PP04 (O3N2) using the conversion from \citet{Kewley2008}.
+Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion from \citet{Kewley2008}.
 This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available.
-For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we calculate a weighted mean of the values after transforming them to the PP04 O3N2 scale.
+For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we transform them all to the PP04 O3N2 scale.
+Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the probability density functions (PDFs) of the various different diagnostics \replylluis{scaled to PP04 O3N2}, resulting in a final `best' PDF.
+We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and \replylluis{for DES RETs} display the results in Table \ref{tab:derived}.
 
@@
 \subsection{Star formation rate \label{subsec:res_sfr}}
-Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for the comparison samples and for the field galaxies of SDSS.
+Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies, \replychris{as determined from photometric SED fitting} along with that for the comparison samples and for the field galaxies of SDSS.
 RETs follow CCSNe, LGRBs and SLSNe in systematically avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
-The local rapid transients Cow, Koala and SN2018gep are
+The local rapid transients Cow, Koala and SN2018gep \replychris{are lower in mass than the majority of RETs.
+SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.}
 
-Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming intensity.
+Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming \replylluis{efficiency}.
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.
@@
 To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}.
-For each pair of samples, we model the PDFs as skewed normal distributions.
-For both samples, we use identical normal priors for the `loc' (location, i.e.
-central value, identical to mean \replychris{for zero skewness}) and `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.
-The results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
+For each pair of samples, we model the PDFs as skewed normal distributions \replylluis{described by the parameters `loc' (location, identical to mean \replychris{for zero skewness}), `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, and `skewness'.
+To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0.
+We note that the loc parameter describes the location of the distribution (its relative position on the x-axis) and is not a mean, median, or mode.
+A highly-skewed distribution may have a loc that lies above almost the entire sample.
+A worked example as well as} the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
+
 The comparison shows RET hosts to be shifted to higher sSFRs CCSNe.
 In 100\% of the posterior samples the RETs were located at higher average sSFRs than SNe II, while the same was true 76\% of the time for RETs when comparing with SESNe.
-
 RET host galaxies are significantly lower in sSFR than LGRBs.
@@
 \caption{The mass-metallicity relation (MZR) for RET host galaxies.
+\replylluis{Upward- and downward-pointing triangles reflect lower and upper limits respectively.
+The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.}
 \label{fig:mzr}}
@@
 \caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES.
-The orange histogram represents the 97/106 DES RETs for which a host was detected.
+The orange histogram represents the 96/106 DES RETs for which a host was detected.
 The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
@@
 The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe.
-RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
+\replylluis{The metallicity distribution of SESNe is, however, quite broad \citep[e.g.][]{Anderson2010}, with different subclasses showing different trends (with SNe Ic host environments exhibiting higher metallicity than Ib, and IIb much lower).} RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
 
@@
 The median CDFs of LGRBs and SLSNe show divergence from the RETs, particularly at low metallicity.
-As a result, the central locations of their fits are shifted compared to the RETs.
-In 67\% of samples, the RET sample had a higher central metallicity than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
+As a result, the \replychris{locs} of their fits are shifted compared to the RETs.
+In 67\% of samples, the RET sample had a higher \replychris{loc} than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
 While these effects are not as significant as with the RETs - SNe II comparison, there is mild evidence that RETs located in galaxies with higher metal content than LGRBs.
@@
 We use the MZR parameterisation \citet{Zahid2014} to show the best fit to the MZR for star-forming galaxies.
-The blue dashed line shows the fit to the low-z data, while the orange dashed line corresponds to the MZR at $z=0.45$, the mean redshift of the RET host sample.
+The blue dashed line shows the fit to the low-z data, while the green dashed line corresponds to the MZR at $z=0.45$, the mean redshift of the RET host sample.
 The RET hosts lie systematically below the galaxy MZR fits as well as the bulk of the SDSS galaxies, meaning that for a given stellar mass they have a lower metallicity.
@@
 The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs.
-Of 106 objects, under half (49/106) have secure host galaxy redshifts.
-Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and six were obtained by programmes for which we do not have access to the spectra.
-Of the remaining 42, it was possible to derive a metallicity for 37 host galaxies.
+Of 106 objects, under half \replylluis{(52/106)} have secure host galaxy redshifts.
+Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and four were obtained by programmes for which we do not have access to the spectra.
+Of the remaining 45, it was possible to derive a metallicity \replylluis{or at least a limmit} for 40 host galaxies, \replylluis{while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega}.
 The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible.
-This scenario is unlikely.
 For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g.
-\halpha, \hbeta, \OIII, and \OII), whose absolute luminosity is not strongly dependent on metallicity.
-It is likely that the redshifts were not obtained because of low SNR, caused by the galaxies being smaller and at higher redshift.
-We do not envisage a plausible scenario where those galaxies are systematically higher in metallicity.
+\halpha, \hbeta, \OIII, and \OII).
+\replylluis{It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift.
+However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a positive redshift detection compared to less enriched galaxies with the same mass and redshift.
+Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to eliminate this possible bias.}
 

### 2020-03-18 RET_Hosts_IR.tex
Updates from Overleaf

@@
 \citet{Drout2014} discovered a class of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
-\replychris{\citet{Arcavi2016} discovered three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one declines rapidly like the PS1 sample.} \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
+\replychris{\citet{Arcavi2016} discovered three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly like the PS1 sample.} \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
 A further sample of five objects has been discovered by the Hyper Suprime-Cam Subaru Strategic Program (SSP) Transient Survey \citep{Tampo2020}.
@@
 \citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses, SFRs, and metallicities.
-To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'') with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
+\replychris{We also compare with the host galaxy of SNLS04D4ec \citep{Arcavi2016}.} To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'') with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
 
@@
 \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
-\replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA\footnte{\url{http://www.laduma.uct.ac.za}}) survey  \citep{Baker2020}, three of which are present in our sample} .
+\replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA\footnote{\url{http://www.laduma.uct.ac.za}}) survey  \citep{Baker2020}, three of which are present in our sample} .
 Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.
@@
 By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of this as-yet unexplained phenomenon.
-We conclude that RETs are stronly linked to massive stars, due to their apparent reliance on star formation.
+We conclude that RETs are strongly linked to massive stars, due to their apparent reliance on star formation.
 Their origin is likely from more massive stars than SNe II, as they require higher sSFR.
@@
 SN2018gep appears in a galaxy too faint to have been detected by DES-SN at the redshift of most of the DES RETs, while the host of AT2018cow is much higher in metallicity.
+
+\replychris{While current surveys such as ZTF, GOTO, and BlackGEM are well equipped to find low-redshift RETs, a sample similar to that presented here will likely not be collected until LSST comes online.
+With several hundreds of objects, detailed studies of RETs and their hosts will be possible in a systematic and more complete manner as has been achieved with LGRBs and SLSNe.
+At that point, the conclusions of this paper will be able to be tested.}
 
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+\newpage
+\appendix
+\onecolumn
+\section{Spectral line fluxes}
+Table \ref{tab:fluxes} presents the line fluxes for all DES RET hosts for which spectra were available.
 
-\appendix
+\begin{table*}
 
-\section{Spectral line fluxes}
-\begin{table*}
 \caption{Emission line fluxes for DES RET host galaxies.
-Values are given in units of erg/cm/s/\AA, and have been corrected for Milky Way reddening using \citet{Schlegel1998}, assuming a \citet{Cardelli1989} with $R_V = 3.1$, but not for intrinsic host galaxy reddening.}
+Values are given in units of erg/cm/s/\AA, and have been corrected for Milky Way reddening using \citet{Schlegel1998}, assuming a \citet{Cardelli1989} with $R_V = 3.1$, but not for intrinsic host galaxy reddening.\label{tab:fluxes}}
 \setlength{\tabcolsep}{3pt}
@@
 \end{tabular}
+\end{table*}
 
-\section{Bayesian Fits}
+\newpage
+\section{Bayesian Fits - sSFR}
 \label{app:b}
-\end{table*}
 

### 2020-03-18 RET_Hosts_IR.tex
Updates from Overleaf

@@
 
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_histfit_ssfr_final.png}
+\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SESNe, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
+\caption{Blah
+\label{fig:param_diffs}}
+\end{figure*}
+To compare two distributions we follow the method outlined in \citet{Wiseman2020}.
+We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler Hamiltonian Monte Carlo algorithm via \texttt{pymc3}\footnote{https://docs.pymc.io/} to explore the posterior distribution.
+Fig.
+\ref{histfit} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared.
+Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness).
+We then compare the differences in these parameters, as seen in Fig.
+\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
+\phil{Note to Chris and Lluis: I also plot 'effect size' which is leftover from the original work in \citet{Kruschke2012} based on simple normal distributions.
+I don't like it for me skewed-normals as I haven't worked out how to fit skewness in (skewness is fairly degenerate with scale).
+So please ignore that panel as it will be removed tommorrow}
+
+\section{Bayesian Fits - Metallicity}
+\label{app:c}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-18 RET_Hosts_IR.tex

@@
 \includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
-\caption{Blah
+\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
 \label{fig:param_diffs}}
 \end{figure*}
-To compare two distributions we follow the method outlined in \citet{Wiseman2020}.
+\replychris{To compare two distributions we follow the method outlined in \citet{Wiseman2020}.
 We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler Hamiltonian Monte Carlo algorithm via \texttt{pymc3}\footnote{https://docs.pymc.io/} to explore the posterior distribution.
+We use a warm-up period of 5000 iterations and a fit period of 10000.
 Fig.
@@
 We then compare the differences in these parameters, as seen in Fig.
-\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
-\phil{Note to Chris and Lluis: I also plot 'effect size' which is leftover from the original work in \citet{Kruschke2012} based on simple normal distributions.
+\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.} \phil{Note to Chris and Lluis: I also plot 'effect size' which is leftover from the original work in \citet{Kruschke2012} based on simple normal distributions.
 I don't like it for me skewed-normals as I haven't worked out how to fit skewness in (skewness is fairly degenerate with scale).
@@
 \label{app:c}
+
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets}
+\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-19 RET_Hosts_IR.tex
Updates from Overleaf

@@
 \end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
+\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
+\label{fig:param_diffs}}
+\end{figure*}
+
 \replychris{To compare two distributions we follow the method outlined in \citet{Wiseman2020}.
-We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler Hamiltonian Monte Carlo algorithm via \texttt{pymc3}\footnote{https://docs.pymc.io/} to explore the posterior distribution.
-We use a warm-up period of 5000 iterations and a fit period of 10000.
+We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution.
+We use a warm-up period of $5\times10^3$ iterations and a fit period of $10^4$ iterations.
 Fig.
@@
 We then compare the differences in these parameters, as seen in Fig.
-\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.} \phil{Note to Chris and Lluis: I also plot 'effect size' which is leftover from the original work in \citet{Kruschke2012} based on simple normal distributions.
-I don't like it for me skewed-normals as I haven't worked out how to fit skewness in (skewness is fairly degenerate with scale).
-So please ignore that panel as it will be removed tommorrow}
+\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.}
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
+\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
+\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
+\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
 
@@
 \begin{figure*}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_histfit_OH_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_OH_final.png}
+\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_OH_final.png}
+\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
+\label{fig:histfit}}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_OH_final.png}
+\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SLSNe, accounting for uncertainties in each bin.
 \label{fig:histfit}}

### 2020-03-19 RET_Hosts_IR.tex

@@
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SESNe, accounting for uncertainties in each bin.
-\label{fig:histfit}}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
+\label{fig:histfit_s12_ssfr}}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{mc_figs/rets_s12}
 \caption{Histograms showing the differences between the fit parameters across the MCMC samples.
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
-\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
-\label{fig:param_diffs}}
+\includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
+\caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
+Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the skewness (alpha) for S12 is not well constrained due do the sharp cut off at $-9.5$ (see Fig.
+\ref{fig:histfit_s12_ssfr}); 3) the RETs scale vs alpha distribution is two-tailed due to alpha being centered close to 0; 4) there is a degeneracy to (3) between RETs loc and alpha for the same reason.
+\label{fig:corner}}
 \end{figure*}

### 2020-03-19 RET_Hosts_IR.tex
Updates from Overleaf

@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{mc_figs/rets_s12}
+\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
 \caption{Histograms showing the differences between the fit parameters across the MCMC samples.
@@
 \includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
-\caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
+\caption{\replychris{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
 Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the skewness (alpha) for S12 is not well constrained due do the sharp cut off at $-9.5$ (see Fig.
 \ref{fig:histfit_s12_ssfr}); 3) the RETs scale vs alpha distribution is two-tailed due to alpha being centered close to 0; 4) there is a degeneracy to (3) between RETs loc and alpha for the same reason.
+Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.}
 \label{fig:corner}}
@@
 Fig.
-\ref{histfit} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared.
+\ref{fig:histfit} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared.
 Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness).
@@
 \ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.}
-\begin{figure*}
+\twocolumn
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
@@
 \label{fig:histfit}}
-\end{figure*}
-\begin{figure*}
+\end{figure}
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
@@
 \label{fig:histfit}}
-\end{figure*}
-\begin{figure*}
+\end{figure}
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
@@
 \label{fig:histfit}}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_histfit_OH_final.png}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
 \label{fig:histfit}}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_OH_final.png}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
 \label{fig:histfit}}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_OH_final.png}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
 \label{fig:histfit}}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_OH_final.png}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SLSNe, accounting for uncertainties in each bin.
 \label{fig:histfit}}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-19 RET_Hosts_IR.tex

@@
 \caption{\replychris{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
-Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the skewness (alpha) for S12 is not well constrained due do the sharp cut off at $-9.5$ (see Fig.
-\ref{fig:histfit_s12_ssfr}); 3) the RETs scale vs alpha distribution is two-tailed due to alpha being centered close to 0; 4) there is a degeneracy to (3) between RETs loc and alpha for the same reason.
+Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the scale vs alpha and loc vs scale distributions are two-tailed due to alpha being centred close to 0; 3) there is a degeneracy between loc and alpha for the same reason.
 Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.}

### 2020-03-19 RET_Hosts_IR.tex

@@
 The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}.
-There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Ono2020}}.
+There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Uno2020}}.
 Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
@@
 \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
-\replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA\footnote{\url{http://www.laduma.uct.ac.za}}) survey  \citep{Baker2020}, three of which are present in our sample} .
+\replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey\footnote{\url{http://www.laduma.uct.ac.za}}, three of which are present in our sample} .
 Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.

### 2020-03-19 RET_Hosts_IR.tex
Updates from Overleaf

@@
 \newcommand{\replychris}[1]{\color{magenta}#1 \color{black}}
-\newcommand{\replylluis}[1]{\color{green}#1 \color{black}}
+\newcommand{\replylluis}[1]{\color{brown}#1 \color{black}}
 \newcommand{\comment}[1]{\textbf{[#1]}} %comments
@@
 There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
-On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs; \citealt{James2006,Kelly2008}), \replylluis{while studies of the local environments tend to show SESNe to explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Galbany2018}}.
+On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs; \citealt{James2006,Kelly2008}), \replylluis{while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Galbany2018}}.
 More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
@@
 The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).}
-Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$.
+Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$. Magnitudes are presented in the AB system \citep{Oke1983}.
 
@@
 \midrule
-DES13C3avkj    & 51.97076 & -27.52792 & 24.07937 & 0.04534 &    $^c$ &      OzDES &             - \\
-DES13X3gms     & 35.80095 &  -4.49384 & 23.02264 & 0.06436 & 0.64792 &      OzDES &       6.58333 \\
-DES13C1tgd     & 54.06436 & -27.63867 & 20.30968 & 0.05848 & 0.19647 &      OzDES &      10.16667 \\
-DES13C3abtt    & 52.62108 & -28.16151 & 21.50529 & 0.03508 &    $^d$ &          - &             - \\
-DES13S2wxf     & 41.61268 &  -0.02634 & 21.31219 & 0.03266 & 0.56985 &      OzDES &       5.41639 \\
-DES13X1hav     & 35.03245 &  -5.11022 & 23.63452 & 0.07752 & 0.58236 &      OzDES &       4.00000 \\
-DES13C3smn     & 51.97112 & -28.08362 & 25.30041 & 0.06023 &    $^c$ &      OzDES &             - \\
-DES13X3nyg     & 36.99228 &  -3.91327 & 23.38744 & 0.06173 & 0.71205 &      OzDES &      45.50000 \\
-DES13X3gmd     & 36.50409 &  -4.21949 & 22.90614 & 0.05419 & 0.78082 &      OzDES &      13.91667 \\
-DES13C3bcok    & 53.02711 & -28.62476 & 18.61674 & 0.02560 & 0.34577 &  LADUMA &               \\
-DES13X3afjd    & 37.00386 &  -4.58049 & 20.75298 & 0.05737 &    $^d$ &          - &             - \\
-DES13C1acmt    & 54.32925 & -26.83371 & 23.18742 & 0.04422 &    $^c$ &      OzDES &             - \\
-DES13X3kgm     & 36.50380 &  -4.86636 & 26.46803 & 0.18709 &    $^d$ &          - &             - \\
-DES13C3uig     & 52.94416 & -27.58544 & 22.17966 & 0.03116 & 0.67346 &       ACES &               \\
-DES13C3nxi     & 51.96356 & -28.35720 & 24.99276 & 0.05177 &    $^c$ &      OzDES &             - \\
-DES13C3asvu    & 52.83670 & -27.36071 & 22.46669 & 0.02874 &    $^d$ &          - &             - \\
-DES13X3pby     & 36.33330 &  -5.31408 & 23.82628 & 0.04671 &    $^c$ &      OzDES &             - \\
-DES13X3aakf    & 35.71205 &  -4.69915 & 25.47453 & 0.09478 &    $^c$ &      OzDES &             - \\
-DES13X2wvv     & 34.86526 &  -6.71603 & 21.89573 & 0.02567 & 0.47503 &      OzDES &       4.50000 \\
-DES13X2oyb     & 35.31056 &  -5.67893 & 22.91589 & 0.06115 &    $^c$ &      OzDES &             - \\
-DES13X3alnb    & 37.18496 &  -5.14232 & 25.04147 & 0.06167 &    $^c$ &      OzDES &             - \\
-DES15X3atd     & 35.84011 &  -4.29142 & 23.87686 & 0.05432 &    $^c$ &      OzDES &             - \\
-DES14S2anq     & 41.27776 &  -0.74529 & 17.57076 & 0.03648 & 0.05211 &      OzDES &       0.75000 \\
-DES14E2xsm     &  9.67624 & -43.58736 & 23.39163 & 0.04458 &    $^c$ &      OzDES &             - \\
-DES14X1bnh     & 33.74902 &  -4.79254 & 21.95260 & 0.03597 & 0.82982 &      OzDES &       3.50000 \\
-DES14E1aqi     &  8.73970 & -43.40182 & 25.61559 & 0.23708 &    $^d$ &          - &             - \\
-DES15S1fli     & 43.18790 &  -0.88620 & 20.98517 & 0.02950 & 0.44739 &      OzDES &       2.33333 \\
-DES14C3gzj     & 52.57168 & -28.14019 & 26.04181 & 0.10494 &    $^d$ &          - &             - \\
-DES14X3pko     & 36.90824 &  -3.69642 & 24.48291 & 0.06326 &    $^d$ &          - &             - \\
-DES15S1fll     & 42.78846 &  -0.19747 & 20.95918 & 0.03719 & 0.22647 &      OzDES &       0.66667 \\
-DES14C1jnd     & 54.35153 & -27.49300 & 24.33143 & 0.08524 &    $^c$ &      OzDES &             - \\
-DES14X3pkl     & 37.21103 &  -4.80741 & 22.40853 & 0.06026 & 0.29537 &      OzDES &       5.16667 \\
-DES13X3npb     & 36.64218 &  -4.13381 & 20.79328 & 0.05336 & 0.49542 &      OzDES &       5.16667 \\
-DES15X2ead     & 36.48913 &  -6.45118 & 20.08582 & 0.03290 & 0.23175 &      OzDES &       2.00000 \\
-DES15C3edw     & 52.55235 & -27.71022 & 22.69331 & 0.03227 &    $^d$ &          - &             - \\
-DES14S2plb     & 41.85667 &  -1.61811 & 18.38419 & 0.03463 & 0.11531 &      OzDES &       2.00000 \\
-DES14S2pli     & 41.22837 &  -1.09830 & 20.86839 & 0.03093 & 0.35478 &      OzDES &       3.41667 \\
-DES15X3kyt     & 36.27500 &  -5.41103 & 24.74520 & 0.07892 &    $^d$ &          - &             - \\
-DES14C3tvw     & 53.32230 & -27.90621 & 21.31841 & 0.02516 & 0.70390 &       ACES &               \\
-DES14C3tnz     & 52.86248 & -28.51318 & 22.26137 & 0.03386 & 0.70452 &      OzDES &       5.79361 \\
-DES15X3mxf     & 36.74009 &  -5.23991 & 22.43347 & 0.04552 & 0.43673 &      OzDES &       9.83333 \\
-DES15X3nlv     & 36.04464 &  -5.02735 & 25.26349 & 0.08375 &    $^d$ &          - &             - \\
-DES15C3mem     & 52.14216 & -29.05851 & 20.28975 & 0.04590 & 0.61618 &     PRIMUS &               \\
-DES15E2lmq     &  9.62005 & -43.98734 & 25.65868 & 0.18116 &    $^d$ &          - &             - \\
-DES15C3lpq     & 52.71204 & -28.61319 & 23.28579 & 0.03610 & 0.61365 &      OzDES &       6.16667 \\
-DES15C3lzm     & 52.17460 & -28.23186 & 20.47636 & 0.02573 & 0.32690 &      ATLAS &               \\
-DES15C3nat     & 52.88528 & -28.72370 & 23.39015 & 0.03154 & 0.83929 &      OzDES &      18.62222 \\
-DES15C3mgq     & 52.76901 & -28.20882 & 22.97470 & 0.03194 & 0.23031 &      OzDES &       8.16667 \\
-DES15E2nqh     &  9.73174 & -43.08707 & 23.29709 & 0.03941 & 0.51525 &      OzDES &       6.83333 \\
-DES15C3opk     & 51.66147 & -28.34737 & 23.05209 & 0.03270 & 0.56984 &      OzDES &      12.16667 \\
-DES15C3opp     & 51.73962 & -28.11496 & 23.25950 & 0.04223 & 0.44242 &      OzDES &      16.75000 \\
-DES15C3pbi     & 52.23620 & -28.00223 & 25.10028 & 0.05470 &    $^d$ &          - &             - \\
-DES16E2pv      &  9.20875 & -43.52782 & 23.00100 & 0.05043 & 0.72608 &      OzDES &       6.00000 \\
-DES16S1bbp     & 43.26389 &   0.37149 & 21.42883 & 0.04524 & 0.19018 &      OzDES &       3.33333 \\
-DES15X3oma     & 36.74617 &  -5.11040 & 24.94606 & 0.07447 &    $^d$ &          - &             - \\
-DES16C3bor     & 52.48232 & -28.04256 & 23.83923 & 0.03711 &    $^c$ &      OzDES &             - \\
-DES16C1bde     & 54.30149 & -26.75840 & 24.96313 & 0.09485 &    $^d$ &          - &             - \\
-DES16X3wt      & 36.23751 &  -5.54488 & 26.90234 & 0.28423 &    $^d$ &          - &             - \\
-DES16X3cxn     & 36.83044 &  -4.95100 & 23.05257 & 0.04442 & 0.58464 &      OzDES &      12.83333 \\
-DES16X2bke     & 36.00989 &  -7.27130 & 25.13096 & 0.16403 &    $^d$ &          - &             - \\
-DES16C1cbd     & 54.85826 & -27.67254 & 20.93909 & 0.03048 & 0.54108 &      OzDES &       7.20000 \\
-DES16C3cdd     & 52.42731 & -27.14317 & 24.27019 & 0.05040 &    $^d$ &          - &             - \\
-DES16E1bir     &  7.74444 & -42.97696 & 24.74236 & 0.07595 &    $^c$ &      OzDES &             - \\
-DES16C3auv     & 51.90215 & -27.59087 & 24.39158 & 0.05296 &    $^c$ &      OzDES &             - \\
-DES16C3axz     & 52.80904 & -28.66678 & 20.41796 & 0.03716 & 0.22673 &  LADUMA &               \\
-DES16X3ega     & 37.09820 &  -4.77643 & 19.53601 & 0.04874 & 0.25762 &       GAMA &       1.00000 \\
-DES16X3erw     & 36.20545 &  -4.51438 & 22.23157 & 0.02865 & 0.45885 &      OzDES &       2.00000 \\
-DES16X1ddm     & 33.82824 &  -4.36428 & 21.46049 & 0.04767 &    $^c$ &      OzDES &             - \\
-DES16X3ddi     & 35.43936 &  -4.68602 & 23.93720 & 0.04360 &    $^c$ &      OzDES &             - \\
-DES16C3gin     & 52.76276 & -28.29145 & 21.52696 & 0.03653 & 0.34745 &      OzDES &       3.33333 \\
-DES16S1dxu     & 42.68141 &  -0.71039 & 21.35662 & 0.03193 & 0.13528 &      OzDES &       1.33333 \\
-DES16X1eho     & 35.34537 &  -4.52566 & 22.28516 & 0.07277 & 0.80735 &      OzDES &       6.75000 \\
-DES17X3gmp     & 37.40191 &  -4.65060 & 24.44397 & 0.06946 &    $^d$ &          - &             - \\
-DES17X2dqk     & 35.46926 &  -7.10815 & 25.96184 & 0.19576 &    $^d$ &          - &             - \\
-DES17C3gop     & 53.53574 & -28.40024 & 22.74858 & 0.03107 & 0.69185 &      OzDES &       4.00000 \\
-DES17C3gen     & 52.93346 & -29.01119 & 22.79380 & 0.04204 &    $^c$ &      OzDES &             - \\
-DES17X3fhq     & 35.93682 &  -3.97690 & 24.70876 & 0.05177 &    $^d$ &          - &             - \\
-DES17S2fee     & 41.40953 &  -1.33278 & 18.16644 & 0.04681 & 0.23737 &      OzDES &       2.00000 \\
-DES17X1hjj     & 34.24036 &  -4.21180 & 24.07284 & 0.05854 &    $^c$ &      OzDES &             - \\
-DES17X1dge     & 34.80886 &  -5.40370 & 24.15755 & 0.10116 &    $^d$ &          - &             - \\
-DES17C1fes     & 54.23372 & -27.57015 & 24.42015 & 0.10382 &    $^c$ &      OzDES &             - \\
-DES17E1gsx     &  8.11588 & -42.76823 & 22.70982 & 0.04695 &    $^c$ &      OzDES &             - \\
-DES17X3dxu     & 36.55911 &  -3.84432 & 22.83789 & 0.03973 & 0.85565 &      OzDES &       7.50000 \\
-DES17S1emy     & 43.36298 &   0.41758 & 22.51310 & 0.05326 &    $^d$ &          - &             - \\
-DES17X2cvk     & 35.93444 &  -7.32167 & 21.60107 & 0.06456 &    $^d$ &          - &             - \\
-DES17X3cdp     & 37.28283 &  -4.30434 & 25.10651 & 0.08381 &    $^c$ &      OzDES &             - \\
-DES17X3cds     & 36.27737 &  -3.79891 & 22.45168 & 0.06098 & 0.49444 &      OzDES &       5.50000 \\
-DES17C3fwd     & 52.90461 & -27.46979 & 20.46182 & 0.02355 & 0.34561 &    LADUMA &               \\
-DES17S1hih     & 42.57627 &  -0.76193 & 24.94967 & 0.12010 &    $^d$ &          - &             - \\
-DES17C3fjt     & 51.46785 & -28.14106 & 28.04246 & 0.44157 &    $^d$ &          - &             - \\
-DES17X3hxi     & 35.79624 &  -4.51713 & 23.36715 & 0.03375 & 0.62457 &      OzDES &       2.00000 \\
-DES13E2lpk     & 10.09911 & -43.53903 & 20.49379 & 0.03567 & 0.47541 &      OzDES &       6.00000 \\
-DES15C2eal     & 54.06180 & -29.23000 & 22.99891 & 0.03276 & 0.22347 &      OzDES &      16.90833 \\
-DES16C2ggt     & 53.89079 & -29.22496 & 21.09210 & 0.03142 & 0.31057 &      OzDES &       2.66667 \\
-DES16C2grk     & 55.06853 & -29.28963 & 20.45434 & 0.03869 &    $^d$ &          - &             - \\
-DES17C2hno     & 53.72691 & -29.19742 & 22.69257 & 0.07398 & 0.59953 &      OzDES &       4.66667 \\
+DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    $^c$ &      OzDES &             - \\
+DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.58333 \\
+DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.16667 \\
+DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    $^d$ &          - &             - \\
+DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.56985 &      OzDES &       5.41639 \\
+DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.00000 \\
+DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    $^c$ &      OzDES &             - \\
+DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.50000 \\
+DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.91667 \\
+DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.34577 &  LADUMA &               \\
+DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    $^d$ &          - &             - \\
+DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    $^c$ &      OzDES &             - \\
+DES13X3kgm     & 36.50380 &  -4.86636 & $26.46 \pm 0.18$ &    $^d$ &          - &             - \\
+DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.67346 &       ACES &               \\
+DES13C3nxi     & 51.96356 & -28.35720 & $24.99 \pm 0.05$ &    $^c$ &      OzDES &             - \\
+DES13C3asvu    & 52.83670 & -27.36071 & $22.46 \pm 0.02$ &    $^d$ &          - &             - \\
+DES13X3pby     & 36.33330 &  -5.31408 & $23.82 \pm 0.04$ &    $^c$ &      OzDES &             - \\
+DES13X3aakf    & 35.71205 &  -4.69915 & $25.47 \pm 0.09$ &    $^c$ &      OzDES &             - \\
+DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.50000 \\
+DES13X2oyb     & 35.31056 &  -5.67893 & $22.91 \pm 0.06$ &    $^c$ &      OzDES &             - \\
+DES13X3alnb    & 37.18496 &  -5.14232 & $25.04 \pm 0.06$ &    $^c$ &      OzDES &             - \\
+DES15X3atd     & 35.84011 &  -4.29142 & $23.87 \pm 0.05$ &    $^c$ &      OzDES &             - \\
+DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75000 \\
+DES14E2xsm     &  9.67624 & -43.58736 & $23.39 \pm 0.04$ &    $^c$ &      OzDES &             - \\
+DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.50000 \\
+DES14E1aqi     &  8.73970 & -43.40182 & $25.61 \pm 0.23$ &    $^d$ &          - &             - \\
+DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.33333 \\
+DES14C3gzj     & 52.57168 & -28.14019 & $26.04 \pm 0.10$ &    $^d$ &          - &             - \\
+DES14X3pko     & 36.90824 &  -3.69642 & $24.48 \pm 0.06$ &    $^d$ &          - &             - \\
+DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.66667 \\
+DES14C1jnd     & 54.35153 & -27.49300 & $24.33 \pm 0.08$ &    $^c$ &      OzDES &             - \\
+DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.16667 \\
+DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.16667 \\
+DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.00000 \\
+DES15C3edw     & 52.55235 & -27.71022 & $22.69 \pm 0.03$ &    $^d$ &          - &             - \\
+DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.00000 \\
+DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.41667 \\
+DES15X3kyt     & 36.27500 &  -5.41103 & $24.74 \pm 0.07$ &    $^d$ &          - &             - \\
+DES14C3tvw     & 53.32230 & -27.90621 & $21.31 \pm 0.02$ & 0.70390 &       ACES &               \\
+DES14C3tnz     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.79361 \\
+DES15X3mxf     & 36.74009 &  -5.23991 & $22.43 \pm 0.04$ & 0.43673 &      OzDES &       9.83333 \\
+DES15X3nlv     & 36.04464 &  -5.02735 & $25.26 \pm 0.08$ &    $^d$ &          - &             - \\
+DES15C3mem     & 52.14216 & -29.05851 & $20.28 \pm 0.04$ & 0.61618 &     PRIMUS &               \\
+DES15E2lmq     &  9.62005 & -43.98734 & $25.65 \pm 0.18$ &    $^d$ &          - &             - \\
+DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.16667 \\
+DES15C3lzm     & 52.17460 & -28.23186 & $20.47 \pm 0.02$ & 0.32690 &      ATLAS &               \\
+DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.62222 \\
+DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.16667 \\
+DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.83333 \\
+DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.16667 \\
+
 \bottomrule
@@
 The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years.
-\replylluis{By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.} The second reason is an update to the sample selection technique, \replylluis{which adds a further 14 transients.}
+\replylluis{By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.} The second reason is an update to the sample selection technique, \replylluis{outlined in the following subsection, which adds a further 14 transients.}
 
@@
 We refer to the resulting sample as DES RETs.
-Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift \replychris{which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04).
+Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020} when using the Directional Light Radius method \citep{Sullivan2006} to associate hosts as per \citet{Wiseman2020}.
+Of these, 49 have a host galaxy spectroscopic redshift \replychris{which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04).
 The full OzDES GRC will be available alongside the public data release detailed in \citet{Lidman2020}}.
@@
 
+\subsection{Field Galaxies \label{subsubsec:sdss}}
+
+\phil{To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based off the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
+The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample.
+We do not correct for this, but take it into account when analysing our findings.
+}
 \section{Host galaxy observations}
@@
 \includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
-\caption{The SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\caption{The $M_*$ - SFR sequence of RET hosts, \phil{hosts of other transients, and SDSS field galaxies.
+Transient SFRs have not been corrected for redshift evolution.
+RET hosts lie slightly above the low-$z$ star-formation main sequence.}
 \label{fig:sfms_sfr}}
@@
 The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised.
-Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion from \citet{Kewley2008}.
+Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion factors given in \citet{Kewley2008}.
 This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available.
@@
 \includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
-\caption{The sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\caption{The sSFR of RET hosts and comparison samples, along with the SDSS field galaxies.
 \label{fig:sfms_ssfr}}
@@
 \includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
-\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample. Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
 \label{fig:ssfr_cum}}
@@
 RETs follow CCSNe, LGRBs and SLSNe in systematically avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
-The local rapid transients Cow, Koala and SN2018gep \replychris{are lower in mass than the majority of RETs.
-SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.}
+\phil{One object, DES16C1cbd, lies among passive galaxies.
+The spectrum of this object is red in colour, but does exhibit \OII emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar}.
+The individual rapid transients Cow, Koala and SN2018gep \replychris{are lower in mass than the majority of RETs.
+SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.
+SNLS04D4ec is consistent with the peak of the DES RET mass and SFR distributions.}
 
@@
 The comparison shows RET hosts to be shifted to higher sSFRs CCSNe.
-In 100\% of the posterior samples the RETs were located at higher average sSFRs than SNe II, while the same was true 76\% of the time for RETs when comparing with SESNe.
+In 98\% of the posterior samples the RET sSFR distribution loc was at a higher value than SNe II, while the same was true 95\% of the time for RETs when comparing with SESNe.
+\phil{The mean difference is 0.6 dex.
+To test whether some of this could be attributed to the difference in redshift between the samples we apply a crude redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}.
+Correcting all SFRs to $z=0$ would result in the CCSN SFRs droping by an average of 0.05 dex, while the RETs would drop 0.35 dex, i.e.
+a difference of 0.30 dex, or half of the observed difference.
+The remaining 0.3 dex is thus consistent with being an intrinsic difference.}
 RET host galaxies are significantly lower in sSFR than LGRBs.
 While the distributions are similar in shape, with a mean difference in scale of 0.28, the mean difference in loc is -1.64, with no overlap between the posterior distributions.
-The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{+1.8}_{-0.98}$ compared to $-0.18^{+0.75}_{-0.76}$ for RET hosts).
-The strong high-sSFR tail shows SLSNe to \replychris{occur in a different galaxy }population to RETs.
+The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{\scriptscriptstyle+1.8}_{\scriptscriptstyle-0.98}$ compared to $-0.18^{\scriptscriptstyle+0.75}_{\scriptscriptstyle-0.76}$ for RET hosts).
+The strong high-sSFR tail shows SLSNe \replychris{occur in a different galaxy} population to RETs.
 
@@
 \includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
-\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, compared to CCSNe and the low-z SDSS sample.
+\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, hosts of the comparison samples, and the SDSS sample.
+Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
 \label{fig:oh_cum}}
@@
 \includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
-\caption{The mass-metallicity relation (MZR) for RET host galaxies.
-\replylluis{Upward- and downward-pointing triangles reflect lower and upper limits respectively.
-The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.}
+\caption{The mass-metallicity relation (MZR) for RET host galaxies and comparison samples.
+\phil{Upward- and downward-pointing triangles reflect lower and upper limits respectively.
+The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.
+The dashed lines represent MZR parameterisations from \citet{Zahid2014}.}
 \label{fig:mzr}}
@@
 They populate similar regions to SESNe, LGRBs and SLSNe but are clearly offset from the SNe II.
+\phil{SN2018gep, the Koala, and SNLS04D4ec appear in line with the RETs, while the Cow lies quite distinctly above the MZR, and is even outside the bulk of the local field galaxies.}
 
@@
 The sample of DES RETs shows a preference for low-metallicity, strongly star-forming host environments.
-The PDF of their metallcities displays a strong similarity to the hosts of SNe Ibc, as well as LGRBs.
-There is a clear difference to the PDFs of SNe II, which follow SDSS field galaxies.
+The PDF of their metallcities displays a strong similarity to the hosts of SESNe, as well as LGRBs.
+There is a clear difference to the PDF of SNe II, which follow SDSS field galaxies.
 The preference for low-metallicity systems is not as strong as for LGRBs or SLSNe, but the highest metallicities found in all three samples are very similar at around solar metallicity.
@@
 Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, \replychris{potentially stripped of their envelopes, and possibly sharing some of the extreme properties of} SLSNe or LGRBs.
-It could therefore be possible that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to a shocked photosphere, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
+It could therefore be possible that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to \replychris{shock breakout and subsequent cooling}, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
 
@@
 
-\subsection{Comparison with local RETs \label{subsec:disc_lowz}}
+\subsection{Comparison with individual RETs \label{subsec:disc_lowz}}
 
@@
 We conclude that RETs are strongly linked to massive stars, due to their apparent reliance on star formation.
-Their origin is likely from more massive stars than SNe II, as they require higher sSFR.
+Their origin is likely from more massive stars than SNe II, and perhaps all SESNe, as they require higher galaxies with sSFR.
 RET hosts are lower in metallicity than SNe II hosts, suggesting some reliance on rotational energy or other metallicity-dependent effects.
-Of the RET analogues discovered in the local Universe, ZTF18abvkwla shares the most similar host galaxy characteristics with the DES RET population.
+Of the RET analogues discovered in modern large-area, high-cadence surveys, ZTF18abvkwla shares the most similar host galaxy characteristics with the DES RET population.
 SN2018gep appears in a galaxy too faint to have been detected by DES-SN at the redshift of most of the DES RETs, while the host of AT2018cow is much higher in metallicity.

### 2020-03-19 RET_Hosts_IR.tex

@@
 The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
-\replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
+\replychris{We use internal data release 7, a preliminary version of the public data release which is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
 \replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey\footnote{\url{http://www.laduma.uct.ac.za}}, three of which are present in our sample} .
@@
 This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole.
-There are several reasons this may not be the case, such as metallicity and age gradients or structure such as bars and discs (see e.g.
-\citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}), and proceed with our analysis with this caveat acknowledged.}
+There are several reasons this measurement may differ from one made at the SN explosion site, such as metallicity and age gradients or structure such as bars and discs (see e.g.
+\citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}).
+We proceed with our analysis with this caveat acknowledged.}
 
@@
 \caption{The $M_*$ - SFR sequence of RET hosts, \phil{hosts of other transients, and SDSS field galaxies.
-Transient SFRs have not been corrected for redshift evolution.
+SFRs have not been corrected for redshift evolution.
 RET hosts lie slightly above the low-$z$ star-formation main sequence.}
@@
 \replylluis{We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram.
-This is also the case for the \SII and \OI versions of the diagram, and we find no evidence AGN amongst the 12 hosts in those diagrams either.}
+This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence AGN amongst the 11 hosts in those diagrams either.}
 
@@
 \includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
-\caption{The sSFR of RET hosts and comparison samples, along with the SDSS field galaxies.
+\caption{The $M_*$ - sSFR sequence of RET hosts and comparison samples, along with the SDSS field galaxies.
 \label{fig:sfms_ssfr}}
@@
 To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}.
-For each pair of samples, we model the PDFs as skewed normal distributions \replylluis{described by the parameters `loc' (location, identical to mean \replychris{for zero skewness}), `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, and `skewness'.
+For each pair of samples, we model the PDFs as skewed normal distributions \replylluis{described by the parameters `loc' (location, identical to mean \replychris{for zero skewness}), `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'.
 To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0.
@@
 A highly-skewed distribution may have a loc that lies above almost the entire sample.
-A worked example as well as} the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
+\replychris{A worked example as well as} the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
+}
 

### 2020-03-19 RET_Hosts_IR.tex
Updates from Overleaf

@@
 We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
+Line fluxes are presented in Table \ref{tab:fluxes}.
 
@@
 
-We compare the metallicity distributions in the same way as the sSFRs.
+We compare the metallicity distributions in the same way as the sSFRs, with the distribution fits shown in Appendix \ref{app:c}.
 The RET host metallicity distribution shows a broad peak, leading to two families of skewed-Gaussians that fit it well, one with a low-valued centre  ($12 + \log \mathrm{(O/H)} \sim 8.1$) and a positive skew, and the other with a higher-valued centre ($12 + \log \mathrm{(O/H)} \sim 8.6$).
@@
 \label{app:c}
-
+In this section, we present the Bayesian fits to the metallicity distributions of RETs and the comparison samples.
 \begin{figure}

### 2020-03-23 RET_Hosts_IR.tex
Updates from Overleaf

@@
 There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}.
-The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}.
-There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Uno2020}}.
-Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
+The transient declined from its discovery, with constraints on the rise time of 1 day, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}.
+There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Uno2020}}.
+Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
 It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.
@@
 DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.58333 \\
-DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.16667 \\
+DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.6 \\
+DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.2 \\
 DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    $^d$ &          - &             - \\
-DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.56985 &      OzDES &       5.41639 \\
-DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.00000 \\
+DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.56985 &      OzDES &       5.4 \\
+DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.0 \\
 DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    $^c$ &      OzDES &             - \\
-DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.50000 \\
-DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.91667 \\
+DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.5 \\
+DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.9 \\
 DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.34577 &  LADUMA &               \\
@@
 DES13X3aakf    & 35.71205 &  -4.69915 & $25.47 \pm 0.09$ &    $^c$ &      OzDES &             - \\
-DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.50000 \\
+DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.5 \\
 DES13X2oyb     & 35.31056 &  -5.67893 & $22.91 \pm 0.06$ &    $^c$ &      OzDES &             - \\
@@
 DES15X3atd     & 35.84011 &  -4.29142 & $23.87 \pm 0.05$ &    $^c$ &      OzDES &             - \\
-DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75000 \\
+DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75 \\
 DES14E2xsm     &  9.67624 & -43.58736 & $23.39 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.50000 \\
+DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.5 \\
 DES14E1aqi     &  8.73970 & -43.40182 & $25.61 \pm 0.23$ &    $^d$ &          - &             - \\
-DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.33333 \\
+DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.3 \\
 DES14C3gzj     & 52.57168 & -28.14019 & $26.04 \pm 0.10$ &    $^d$ &          - &             - \\
 DES14X3pko     & 36.90824 &  -3.69642 & $24.48 \pm 0.06$ &    $^d$ &          - &             - \\
-DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.66667 \\
+DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.67 \\
 DES14C1jnd     & 54.35153 & -27.49300 & $24.33 \pm 0.08$ &    $^c$ &      OzDES &             - \\
-DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.16667 \\
-DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.16667 \\
-DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.00000 \\
+DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.2 \\
+DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.2 \\
+DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.0 \\
 DES15C3edw     & 52.55235 & -27.71022 & $22.69 \pm 0.03$ &    $^d$ &          - &             - \\
-DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.00000 \\
-DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.41667 \\
+DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.0 \\
+DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.4 \\
 DES15X3kyt     & 36.27500 &  -5.41103 & $24.74 \pm 0.07$ &    $^d$ &          - &             - \\
 DES14C3tvw     & 53.32230 & -27.90621 & $21.31 \pm 0.02$ & 0.70390 &       ACES &               \\
-DES14C3tnz     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.79361 \\
-DES15X3mxf     & 36.74009 &  -5.23991 & $22.43 \pm 0.04$ & 0.43673 &      OzDES &       9.83333 \\
+DES14C3tnz     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.8 \\
+DES15X3mxf     & 36.74009 &  -5.23991 & $22.43 \pm 0.04$ & 0.43673 &      OzDES &       9.8 \\
 DES15X3nlv     & 36.04464 &  -5.02735 & $25.26 \pm 0.08$ &    $^d$ &          - &             - \\
@@
 DES15E2lmq     &  9.62005 & -43.98734 & $25.65 \pm 0.18$ &    $^d$ &          - &             - \\
-DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.16667 \\
+DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.2 \\
 DES15C3lzm     & 52.17460 & -28.23186 & $20.47 \pm 0.02$ & 0.32690 &      ATLAS &               \\
-DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.62222 \\
-DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.16667 \\
-DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.83333 \\
-DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.16667 \\
+DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.6 \\
+DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.1 \\
+DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.8 \\
+DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.2 \\
 
@@
 The stamps have a size of 10\arcsec in each direction.
+\replylluis{DES17X1hjk is considered hostless.}
 \label{fig:mosaic}}
@@
 The results are presented in Table \ref{tab:derived}.
-\replylluis{These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population characteristics.}
+\replylluis{These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population.}
 
@@
 We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
-\replylluis{This way the resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy.
+\replylluis{The resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy.
 This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole.
@@
 \replychris{We note that this is a rough estimation}.
-If we leave the branch choice for those with no \NII~to be random, we find that the results are consistent to within uncertainties
+If we leave the branch choice for those with no \NII~to be random, we find that the results are consistent to within uncertainties.
 
@@
 RET host galaxies are significantly lower in sSFR than LGRBs.
-While the distributions are similar in shape, with a mean difference in scale of 0.28, the mean difference in loc is -1.64, with no overlap between the posterior distributions.
-The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{\scriptscriptstyle+1.8}_{\scriptscriptstyle-0.98}$ compared to $-0.18^{\scriptscriptstyle+0.75}_{\scriptscriptstyle-0.76}$ for RET hosts).
+While the distributions are similar in shape, with a mean difference in scale of 0.09, the mean difference in loc is -1.16, with no overlap between the posterior distributions.
+The sSFR distribution of SLSNe hosts is much broader than the RETs, with a scale of 1.12, twice that of the RETs.
+They are also shifted to higher sSFRs than RETs, with the loc of the distribution on average 0.76 dex greater than RETs.
 The strong high-sSFR tail shows SLSNe \replychris{occur in a different galaxy} population to RETs.
@@
 Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and four were obtained by programmes for which we do not have access to the spectra.
-Of the remaining 45, it was possible to derive a metallicity \replylluis{or at least a limmit} for 40 host galaxies, \replylluis{while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega}.
+Of the remaining 45, it was possible to derive a metallicity \replylluis{or at least a limit} for 40 host galaxies, \replylluis{while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega}.
 The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible.
@@
 \ref{fig:mag_dist}.
-Of the 48 objects without a redshift, 40 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}.
-Of more significance is that only 34 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign.
+Of the 57 objects without a redshift, 47 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}.
+Of more significance is that only 40 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign.
 The other, `hostless', objects are either transients that are located remotely from a galaxy that was detected, or are hosted by a galaxy that was not detected.
@@
 Neither are expected to be systematically higher in metallicity than the detected hosts.
-Similarly, a further 16 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found.
-The resulting redshift completeness of targetted objects is 70\% (82\% for objects brighter than $m_r = 24$~mag, which is in line with the average for OzDES as a whole \citep{Lidman2020}.
+Similarly, a further 22 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found.
+The resulting redshift completeness of targetted objects is 71\% (83\% for objects brighter than $m_r = 24$~mag), which is in line with the average for OzDES as a whole \citep{Lidman2020}.
 In Fig.
 \ref{fig:g-i} we show the observer-frame $r$-band magnitudes and $g-i$ colours for all RET hosts that were detected.
-The 40 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts.
+The 47 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts.
 This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.
@@
         All RETs & 106 \\
-        No redshift   & 48\\
-        Host in SN Deep & 40\\
-        Host in SVA1 & 34 \\
+        No redshift   & 57\\
+        Has host in SN Deep & 47\\
+        Has host in SVA1 & 40 \\
         Targetted by OzDES & 18 \\
@@
     \end{tabular}
-    \caption{Numbers of RETs passing various cuts relating to redshift targetting.}
+    \caption{Numbers of RETs passing various cuts relating to redshift targetting and completeness. Each row is a subset of the row above.}
     \label{tab:z_cuts}
@@
 By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of this as-yet unexplained phenomenon.
-We conclude that RETs are strongly linked to massive stars, due to their apparent reliance on star formation.
-Their origin is likely from more massive stars than SNe II, and perhaps all SESNe, as they require higher galaxies with sSFR.
-RET hosts are lower in metallicity than SNe II hosts, suggesting some reliance on rotational energy or other metallicity-dependent effects.
+We conclude that RETs are strongly linked to massive stars, due to their hosts all exhibiting signatures of star formation.
+They likely originate from stars more massive, on average, than than those that cause SNe II, and perhaps all SESNe, as they occur in galaxies with higher sSFR.
+RET hosts are significantly lower in metallicity than SN II hosts, and marginally lower than SESN hosts, suggesting some reliance on rotational energy or other metallicity-dependent effects.
 Of the RET analogues discovered in modern large-area, high-cadence surveys, ZTF18abvkwla shares the most similar host galaxy characteristics with the DES RET population.
@@
 
-\replychris{While current surveys such as ZTF, GOTO, and BlackGEM are well equipped to find low-redshift RETs, a sample similar to that presented here will likely not be collected until LSST comes online.
+\replychris{While current surveys such as ZTF \citep{Bellm2019}, GOTO \citep{Dyer2018}, and BlackGEM \citep{Bloemen2016} are well equipped to find low-redshift RETs, a sample similar to that presented here will likely not be collected until LSST comes online.
 With several hundreds of objects, detailed studies of RETs and their hosts will be possible in a systematic and more complete manner as has been achieved with LGRBs and SLSNe.
@@
 Fig.
-\ref{fig:histfit} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared.
+\ref{fig:histfit_s12_ssfr} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared.
 Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness).
@@
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
-\label{fig:histfit}}
+\label{fig:histfit_ssfr_s13}}
 \end{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
-\label{fig:histfit}}
+\label{fig:histfit_ssfr_k15}}
 \end{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
-\label{fig:histfit}}
+\label{fig:histfit_ssfr_p16}}
 \end{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
-\label{fig:histfit}}
+\label{fig:histfit_oh_s12}}
 \end{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
-\label{fig:histfit}}
+\label{fig:histfit_oh_s13}}
 \end{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
-\label{fig:histfit}}
+\label{fig:histfit_oh_k15}}
 \end{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SLSNe, accounting for uncertainties in each bin.
-\label{fig:histfit}}
+\label{fig:histfit_oh_p16}}
 \end{figure}

### 2020-04-09 RET_Hosts_SNWG.tex

--- 2020-03-23 RET_Hosts_IR.tex
@@
 \newcommand{\hdelta}[0]{H$\delta$}
+\newcommand{\hepsilon}[0]{H$\epsilon$}
 \newcommand{\HII}[0]{$[\textnormal{\textsc{Hii}}]$}
@@
 \defcitealias{Pursiainen2018}{P18}
+\defcitealias{Wiseman2020}{W20}
 \defcitealias{Pursiainen2020}{P20}
@@
 Their evolution on fast timescales has hindered high quality follow-up observations, such that their origin and explosion/emission mechanism remains unexplained.
-In this paper, we investigate the host galaxies of the largest RET sample to date from the Dark Energy Survey (DES).
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 hosts, and metallicities for 44.
-We find that RETs explode almost exclusively in star-forming galaxies and are thus likely associated with massive stars.
-Comparing RET hosts to samples of host galaxies of other explosive transient as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs, indicating a link to young stellar populations, similar to stripped-envelope SNe.
+In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 44.
+We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars.
+Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs, indicating a link to young stellar populations, similar to stripped-envelope SNe.
 RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies.
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+transients: supernovae -- galaxies: star formation -- galaxies: abundances -- galaxies: photometry 
 \end{keywords}
@@
 In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe).
-CCSNe can be split into observationally-determinded subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \replylluis{that disappear after a few weeks}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
-Conversely, SNe Ib and Ic do not show signatures of hydrogen and are thus referred to collectively as stripped-envelope SNe (SESNe) \replylluis{, having undergone a partial removal of their outer atmospheres}.
-The SN IIb subclass, which shows hydrogen only at early epochs, is also commonly grouped along with SESNe.
-\replylluis{SNe IIn, with the n standing for \textit{narrow}, display hydrogen lines with much lower velocities than standard SNe II, indicating their origin from the ejecta impacting on slow-moving circumstellar material (CSM)}.
+CCSNe can be split into observationally-determinded subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \citep{Minkowski1941}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
+Conversely, SNe Ib and Ic do not show signatures of hydrogen \citep[e.g.[]{Filippenko1997} and are thus referred to collectively as stripped-envelope SNe (SESNe), having undergone a partial removal of their outer atmospheres.
+The SN IIb subclass, which shows hydrogen only at early epochs that disappears after a few weeks \citep{Filippenko1988}, is also commonly grouped along with SESNe.
+SNe IIn, with the n standing for \textit{narrow}, which refers to the apparent width of the hydrogen emission lines when compared to standard SNe II \citep{Schlegel1990}, indicating their origin from the ejecta impacting on slow-moving circumstellar material (CSM).
 Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
@@
 There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
-On average, SESNe reside in galaxies with higher specific star-formation rate\replychris{s} (sSFRs; \citealt{James2006,Kelly2008}), \replylluis{while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Galbany2018}}.
+On average, SESNe reside in galaxies with higher specific star-formation rates (sSFRs; \citealt{James2006,Kelly2008}), while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Anderson2012,Galbany2018}.
 More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
@@
 Recently, inspection of high-cadence, large-area survey data sets have revealed yet more exotic transients that are less easy to explain with conventional models.
-\citet{Drout2014} discovered a class of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
-\replychris{\citet{Arcavi2016} discovered three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly like the PS1 sample.} \citet{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
+\citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
+\citet{Arcavi2016} reported three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly like the PS1 sample.
+\citet[hereafter P18]{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
 A further sample of five objects has been discovered by the Hyper Suprime-Cam Subaru Strategic Program (SSP) Transient Survey \citep{Tampo2020}.
@@
 
-There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}.
-The transient declined from its discovery, with constraints on the rise time of 1 day, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}.
-There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Uno2020}}.
+There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}.
+The transient declined from its discovery, with constraints on the rise time of 1 day, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}).
+There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Uno2020}.
 Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
@@
 In this paper, we present the first comprehensive study of the host galaxies of RETs.
-We make use of the final DES sample, which builds on \citet{Pursiainen2018} using the final year of data as well as more refined discovery techniques.
-Using the deep DES photometry from \citet{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
+We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} using the final year of data as well as more refined discovery techniques.
+Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
 For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.
 
-The order of the paper is as follows: \replychris{in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}.
-The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).}
-Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters H$0=70$ km~s$^{-1}$ and $\Omega_{\textrm{M}}=0.3$. Magnitudes are presented in the AB system \citep{Oke1983}.
+The order of the paper is as follows: in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}.
+The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).
+Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters $H_0=70$ km~s$^{-1}$ Mpc$^{-1}$ and $\Omega_{\textrm{M}}=0.3$.
+Magnitudes are presented in the AB system \citep{Oke1983}, and values (uncertainties) are quoted at the 50\textsuperscript{th} (16\textsuperscript{th} and 84\textsuperscript{th}, i.e.
+$1\sigma$) percentiles of their probability density function.
 
@@
 \includegraphics[width=0.5\textwidth]{figs/spec_gr_trise_r_GP5_new_colorscheme.pdf}
-\caption{Observer-frame $g-r$ colour \replychris{at maximum light} and \replychris{observer-frame} $r$-band rise-time, derived from Gaussian Processed fits to DES-SN photometry for spectroscopically confirmed SNe and \citetalias{Pursiainen2018} RETs.
+\caption{Observer-frame $g-r$ colour at maximum light and observer-frame $r$-band rise-time, derived from Gaussian Processed fits to DES-SN photometry for spectroscopically confirmed SNe and \citetalias{Pursiainen2018} RETs.
 The location of the red box is designed to maximise the completeness and purity of RETs.
-\replychris{ The fractions in the legend refer to the number of each class of transient passing the cuts of Section \ref{subsec:new_method} compared to the total number of that class in DES-SN, while the number in parentheses refers to the number inside the red box defining RET parameter space.
-}
+The fractions in the legend refer to the number of each class of transient passing the cuts of Section \ref{subsec:new_method} compared to the total number of that class in DES-SN, while the number in parentheses refers to the number inside the red box defining RET parameter space.
 \label{fig:selection}}
@@
 \begin{table*}
-\caption{Host galaxy information for the 49 RETs with a host galaxy redshift. A full-length, machine-readable version of this table is available in the online version of the manuscript.}
+\caption{Host galaxy information for the 106 RETs in the DES 5-year sample. A full-length, machine-readable version of this table is available in the online version of the manuscript.}
 
@@
 \midrule
+DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    $^c$ &      OzDES &             - \\
+DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.17 \\
+DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    $^d$ &          - &             - \\
+DES13C3asvu    & 52.83670 & -27.36071 & $22.46 \pm 0.02$ &    $^d$ &          - &             - \\
 DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.6 \\
-DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.2 \\
-DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    $^d$ &          - &             - \\
-DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.56985 &      OzDES &       5.4 \\
-DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.0 \\
+DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.34577 &  LADUMA &               \\
+DES13C3nxi     & 51.96356 & -28.35720 & $24.99 \pm 0.05$ &    $^c$ &      OzDES &             - \\
 DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    $^c$ &      OzDES &             - \\
-DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.5 \\
-DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.9 \\
-DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.34577 &  LADUMA &               \\
+DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.67346 &       ACES &               \\
+DES13E2lpk     & 10.09911 & -43.53903 & $20.49 \pm 0.03$ & 0.47541 &      OzDES &       6.00 \\
+DES13S2wxf\tnote{e}     & 41.61268 &  $-0.02 \pm 21.3$9 & 0.03266 & 0.56985 &      OzDES &       5.42 \\
+DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.00 \\
+DES13X2oyb     & 35.31056 &  -5.67893 & $22.91 \pm 0.06$ &    $^c$ &      OzDES &             - \\
+DES13X2wvv\tnote{e}     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.50 \\
+DES13X3aakf    & 35.71205 &  -4.69915 & $25.47 \pm 0.09$ &    $^c$ &      OzDES &             - \\
 DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    $^d$ &          - &             - \\
-DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    $^c$ &      OzDES &             - \\
+DES13X3alnb    & 37.18496 &  -5.14232 & $25.04 \pm 0.06$ &    $^c$ &      OzDES &             - \\
+DES13X3gmd\tnote{e}     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.92 \\
+DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.58 \\
 DES13X3kgm     & 36.50380 &  -4.86636 & $26.46 \pm 0.18$ &    $^d$ &          - &             - \\
-DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.67346 &       ACES &               \\
-DES13C3nxi     & 51.96356 & -28.35720 & $24.99 \pm 0.05$ &    $^c$ &      OzDES &             - \\
-DES13C3asvu    & 52.83670 & -27.36071 & $22.46 \pm 0.02$ &    $^d$ &          - &             - \\
+DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.17 \\
+DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.50 \\
 DES13X3pby     & 36.33330 &  -5.31408 & $23.82 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES13X3aakf    & 35.71205 &  -4.69915 & $25.47 \pm 0.09$ &    $^c$ &      OzDES &             - \\
-DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.5 \\
-DES13X2oyb     & 35.31056 &  -5.67893 & $22.91 \pm 0.06$ &    $^c$ &      OzDES &             - \\
-DES13X3alnb    & 37.18496 &  -5.14232 & $25.04 \pm 0.06$ &    $^c$ &      OzDES &             - \\
+DES14C1jnd     & 54.35153 & -27.49300 & $24.33 \pm 0.08$ &    $^c$ &      OzDES &             - \\
+DES14C3gzj\tnote{e}     & 52.57168 & -28.14019 & $26.04 \pm 0.10$ &    $^d$ &          - &             - \\
+DES14C3tnz\tnote{e}     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.79 \\
+DES14C3tvw     & 53.32230 & -27.90621 & $21.31 \pm 0.02$ & 0.70390 &       ACES &               \\
+DES14E1aqi\tnote{e}     &  8.73970 & -43.40182 & $25.61 \pm 0.23$ &    $^d$ &          - &             - \\
+DES14E2xsm     &  9.67624 & -43.58736 & $23.39 \pm 0.04$ &    $^c$ &      OzDES &             - \\
+DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75 \\
+DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.00 \\
+DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.42 \\
+DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.50 \\
+DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.17 \\
+DES14X3pko     & 36.90824 &  -3.69642 & $24.48 \pm 0.06$ &    $^d$ &          - &             - \\
+DES15C2eal     & 54.06180 & -29.23000 & $22.99 \pm 0.03$ & 0.22347 &      OzDES &      16.91 \\
+DES15C3edw     & 52.55235 & -27.71022 & $22.69 \pm 0.03$ &    $^d$ &          - &             - \\
+DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.17 \\
+DES15C3lzm     & 52.17460 & -28.23186 & $20.47 \pm 0.02$ & 0.32690 &      ATLAS &               \\
+DES15C3mem\tnote{e}     & 52.14216 & -29.05851 & $20.28 \pm 0.04$ & 0.61618 &     PRIMUS &               \\
+DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.17 \\
+DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.62 \\
+DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.17 \\
+DES15C3opp     & 51.73962 & -28.11496 & $23.25 \pm 0.04$ & 0.44242 &      OzDES &      16.75 \\
+DES15C3pbi     & 52.23620 & -28.00223 & $25.10 \pm 0.05$ &    $^d$ &          - &             - \\
+DES15E2lmq     &  9.62005 & -43.98734 & $25.65 \pm 0.18$ &    $^d$ &          - &             - \\
+DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.83 \\
+DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.33 \\
+DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.67 \\
+DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.00 \\
 DES15X3atd     & 35.84011 &  -4.29142 & $23.87 \pm 0.05$ &    $^c$ &      OzDES &             - \\
-DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75 \\
-DES14E2xsm     &  9.67624 & -43.58736 & $23.39 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.5 \\
-DES14E1aqi     &  8.73970 & -43.40182 & $25.61 \pm 0.23$ &    $^d$ &          - &             - \\
-DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.3 \\
-DES14C3gzj     & 52.57168 & -28.14019 & $26.04 \pm 0.10$ &    $^d$ &          - &             - \\
-DES14X3pko     & 36.90824 &  -3.69642 & $24.48 \pm 0.06$ &    $^d$ &          - &             - \\
-DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.67 \\
-DES14C1jnd     & 54.35153 & -27.49300 & $24.33 \pm 0.08$ &    $^c$ &      OzDES &             - \\
-DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.2 \\
-DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.2 \\
-DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.0 \\
-DES15C3edw     & 52.55235 & -27.71022 & $22.69 \pm 0.03$ &    $^d$ &          - &             - \\
-DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.0 \\
-DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.4 \\
 DES15X3kyt     & 36.27500 &  -5.41103 & $24.74 \pm 0.07$ &    $^d$ &          - &             - \\
-DES14C3tvw     & 53.32230 & -27.90621 & $21.31 \pm 0.02$ & 0.70390 &       ACES &               \\
-DES14C3tnz     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.8 \\
-DES15X3mxf     & 36.74009 &  -5.23991 & $22.43 \pm 0.04$ & 0.43673 &      OzDES &       9.8 \\
-DES15X3nlv     & 36.04464 &  -5.02735 & $25.26 \pm 0.08$ &    $^d$ &          - &             - \\
-DES15C3mem     & 52.14216 & -29.05851 & $20.28 \pm 0.04$ & 0.61618 &     PRIMUS &               \\
-DES15E2lmq     &  9.62005 & -43.98734 & $25.65 \pm 0.18$ &    $^d$ &          - &             - \\
-DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.2 \\
-DES15C3lzm     & 52.17460 & -28.23186 & $20.47 \pm 0.02$ & 0.32690 &      ATLAS &               \\
-DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.6 \\
-DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.1 \\
-DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.8 \\
-DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.2 \\
 
@@
 \begin{tablenotes}
-\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
+\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citetalias{Wiseman2020}, not corrected for Galactic foreground reddening.
 \item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
 \item[c] Host targetted by OzDES but no redshift measurement possible.
-\item[d] Host not targetted by OzDES
-\item[e] Found by updated search method (Section \ref{subsec:new_method})
-\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method 
+\item[d] Host not targetted by OzDES.
+\item[e] Found by updated search method (Section \ref{subsec:new_method}).
+\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method.
+\item[g] Redshift updated since to \citetalias{Pursiainen2018}.
 \end{tablenotes}
@@
 \includegraphics[width=0.7\textwidth]{figs/RET_Mosaic.png}
-\caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ band deep coadds from \citet{Wiseman2020}.
+\caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ band deep coadds from \citetalias{Wiseman2020}.
 The locations of the transients are indicated with cyan crosses.
 The stamps have a size of 10\arcsec in each direction.
-\replylluis{DES17X1hjk is considered hostless.}
+DES14E2bfx and DES17X1hjk are considered hostless.
 \label{fig:mosaic}}
@@
 The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years.
-\replylluis{By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.} The second reason is an update to the sample selection technique, \replylluis{outlined in the following subsection, which adds a further 14 transients.}
+By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.
+The second reason is an update to the sample selection technique, outlined in the following subsection, which adds a further 14 transients.
 
@@
 Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
-To negate this issue, we use lightcurves interpolated using Gaussian  (GP) as presented in \citet{Pursiainen2019}.
-The interpolated light curves have a 0.5 day cadence and every epoch \replychris{and band} has a flux value, and an associated uncertainty.
-Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$ \replylluis{vs.} $t_{\mathrm{rise; r}}$ parameter space (Fig.
-\ref{fig:selection}), \replychris{where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness.} We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
+To negate this issue, we use lightcurves interpolated using Gaussian  (GP) as presented in \citetalias{Pursiainen2018}.
+The interpolated light curves have a 0.5 day cadence and every epoch and band has a flux value, and an associated uncertainty.
+Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$ vs.
+$t_{\mathrm{rise; r}}$ parameter space (Fig.
+\ref{fig:selection}), where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness.
+We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
 The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig.
@@
 This removes 347 SNe, resulting in 546 objects remaining inside the parameter space.
-The final 564 transients have been visually inspected, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.
+The final 546 transients have been visually inspected, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.
 
@@
 We refer to the resulting sample as DES RETs.
-Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020} when using the Directional Light Radius method \citep{Sullivan2006} to associate hosts as per \citet{Wiseman2020}.
-Of these, 49 have a host galaxy spectroscopic redshift \replychris{which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04).
-The full OzDES GRC will be available alongside the public data release detailed in \citet{Lidman2020}}.
+Of the 106 objects in the sample, 96 have a host galaxy detected in deep host galaxy photometry of \citetalias{Wiseman2020} when using the Directional Light Radius method \citep{Sullivan2006} to associate hosts as per \citetalias{Wiseman2020}.
+Of these, 49 have a host galaxy spectroscopic redshift which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04).
+The full OzDES GRC will be available alongside the public data release detailed in \citet{Lidman2020}.
 A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves.
 We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
-\replylluis{A selection of the host galaxies can be seen in Fig.
-\ref{fig:mosaic}, centered on the location of the transient.
-The figure showcases the diversity of host galaxy morphologies and colours, while also displaying the limitations of ground-based observations of high-redshift, relatively small galaxies in terms of spatial resolution.}
+A selection of the host galaxies can be seen in Fig.
+\ref{fig:mosaic}, centred on the location of the transient.
+The figure showcases the diversity of host galaxy morphologies and colours, while also displaying the limitations of ground-based observations of high-redshift, relatively small galaxies in terms of spatial resolution.
 Fig.
@@
 The effect that the redshift selection function has on the results is discussed in Section \ref{subsec:disc_bias}.
-The observational properties of the 9\replylluis{6} detected hosts are displayed in Table \ref{tab:obs}.
+The observational properties of the 96 detected hosts are displayed in Table \ref{tab:obs}.
 We highlight objects that were not presented in \citetalias{Pursiainen2018}.
@@
 \citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses, SFRs, and metallicities.
-\replychris{We also compare with the host galaxy of SNLS04D4ec \citep{Arcavi2016}.} To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'') with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
+We also compare with the host galaxy of SNLS04D4ec \citep{Arcavi2016}.
+To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'') with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
 
@@
 
-\phil{To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based off the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
+To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based off the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
 The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample.
 We do not correct for this, but take it into account when analysing our findings.
-}
 \section{Host galaxy observations}
@@
 
-The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which is based upon deep coadds reaching $r$-band limiting magnitudes of 26.5.
+The host galaxy photometry for the sample of RETs is taken from the catalogue of \citetalias{Wiseman2020}, which is based upon deep coadds reaching $r$-band limiting magnitudes of 26.5.
 The coadds were created using data from all five seasons of DES-SN, but by excluding one season at a time in order for that coadd not to include contamination from the transients in that season.
@@
 The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient.
-The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
-\replychris{We use internal data release 7, a preliminary version of the public data release which is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
-\replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey\footnote{\url{http://www.laduma.uct.ac.za}}, three of which are present in our sample} .
+The spectra have a resolution of 1400-1700 and a wavelength range of $3700 -8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts.
+We use internal data release 7, a preliminary version of the public data release which is detailed in \citet{Lidman2020}.
+Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}.
+We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey\footnote{\url{http://www.laduma.uct.ac.za}}, three of which are present in our sample.
 Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.
+Surveys fulfilling this criteria include the Australia Telescope Large Area Survey (ATLAS;
+citealt{Mao2012}, the Arizona CDFS Environment Survey (ACES; \citealt{Cooper2012}), and the PRIsm MUlti-object Survey (PRIMUS; \citealt{Coil2011,Cool2013}).
 Where the spectra from which those redshifts were derived are also public they are included in this analysis.
 These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS.
-In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel.
+In total we analyse 45 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel.
 We stress that the emission lines are detected with a higher SNR than this.
@@
 \caption{The spectrum of DES16C2ggt, decomposed into its constituent components according to the \texttt{pPXF} fit.
+a) the best fit superimposed on the observed spectrum.
+b) the constituent parts of the decomposition: the stellar template including absorption features, and the nebular gas emission.
+The grey area shows the location of higher-order (\hepsilon onwards) Balmer lines.
 \label{fig:host_spec}}
@@
 The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}.
-From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed \replylluis{Kron} magnitudes \replylluis{from the deep photometric catalogue of \citet{Wiseman2020}}.
-For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR).
+From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed Kron magnitudes from the deep photometric catalogue of \citetalias{Wiseman2020}.
+For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these estimate a probability density function (PDF) for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR).
 To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds.
 The results are presented in Table \ref{tab:derived}.
-\replylluis{These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population.}
+These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population.
 
@@
 We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
-\replylluis{The resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy.
+The resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy.
 This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole.
@@
 \citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}).
-We proceed with our analysis with this caveat acknowledged.}
+We proceed with our analysis with this caveat acknowledged.
 
@@
 We fit the emission lines with Gaussian profiles.
-In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution \replychris{based on the variance spectrum}.
+In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution based on the variance spectrum.
 We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
@@
 \toprule
-Transient Name &$\log \left(M_*\right)$ &$\log \left(\mathrm{SFR}\right)$ &  $\log \left(\mathrm{sSFR}\right)$ &                                                           \multicolumn{6}{c}{$12+\log\left(\mathrm{O/H}\right)\tnote{a} $}\\
+Transient Name &$\log \left(M_*\right)$ &$\log \left(\mathrm{SFR}\right)$ &  $\log \left(\mathrm{sSFR}\right)$ &                                                           \multicolumn{6}{c}{$12+\log\left(\mathrm{O/H}\right) $}\\
 %\midrule
-{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(M_{\odot}\ \mathrm{yr}^{-1} M_{\odot}^{-1}\right)$& Best &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\
+{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(M_{\odot}\ \mathrm{yr}^{-1} M_{\odot}^{-1}\right)$& Best\tnote{a} &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\
 \midrule
@@
 \includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
-\caption{The $M_*$ - SFR sequence of RET hosts, \phil{hosts of other transients, and SDSS field galaxies.
+\caption{The $M_*$ - SFR sequence of RET hosts, hosts of other transients, and SDSS field galaxies (grey contours).
 SFRs have not been corrected for redshift evolution.
-RET hosts lie slightly above the low-$z$ star-formation main sequence.}
+RET hosts lie slightly above the low-$z$ star-formation main sequence, and systematically avoid passive galaxies (dense contours in the lower right).
 \label{fig:sfms_sfr}}
@@
 \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
-\replylluis{We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram.
-This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence AGN amongst the 11 hosts in those diagrams either.}
+We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram.
+This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence AGN amongst the 11 hosts in those diagrams either.
 
@@
 We thus determine a set of indicators for which to calculate abundances.
-For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII~is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}.
+For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII~is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016} (D16).
 For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04).
@@
 For $12 + \log \mathrm{(O/H)}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.
-\replychris{We note that this is a rough estimation}.
+We note that this is a rough estimation.
 If we leave the branch choice for those with no \NII~to be random, we find that the results are consistent to within uncertainties.
@@
 For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we transform them all to the PP04 O3N2 scale.
-Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the probability density functions (PDFs) of the various different diagnostics \replylluis{scaled to PP04 O3N2}, resulting in a final `best' PDF.
-We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and \replylluis{for DES RETs} display the results in Table \ref{tab:derived}.
+Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the PDFs of the various different diagnostics scaled to PP04 O3N2, resulting in a final `best' PDF.
+We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and for DES RETs display the results in Table \ref{tab:derived}.
 
@@
 \subsection{Star formation rate \label{subsec:res_sfr}}
-Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies, \replychris{as determined from photometric SED fitting} along with that for the comparison samples and for the field galaxies of SDSS.
+Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS.
 RETs follow CCSNe, LGRBs and SLSNe in systematically avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
-\phil{One object, DES16C1cbd, lies among passive galaxies.
-The spectrum of this object is red in colour, but does exhibit \OII emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar}.
-The individual rapid transients Cow, Koala and SN2018gep \replychris{are lower in mass than the majority of RETs.
+One object, DES16C1cbd, lies among passive galaxies.
+The spectrum of this object is red in colour, but does exhibit \OII emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar.
+The individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs.
 SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.
-SNLS04D4ec is consistent with the peak of the DES RET mass and SFR distributions.}
-
-Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming \replylluis{efficiency}.
+SNLS04D4ec is consistent with the peak of the DES RET mass and SFR distributions.
+
+Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming efficiency.
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.
@@
 The RET hosts are clearly shifted to higher sSFRs than CCSNe.
-To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}.
-For each pair of samples, we model the PDFs as skewed normal distributions \replylluis{described by the parameters `loc' (location, identical to mean \replychris{for zero skewness}), `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'.
+To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citetalias{Wiseman2020}.
+For each pair of samples, we model the PDFs as skewed normal distributions described by the parameters `loc' (location, identical to mean for zero skewness), `scale' (spread, identical to standard deviation for zero skewness)\footnote{See \citetalias{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'.
 To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0.
@@
 A highly-skewed distribution may have a loc that lies above almost the entire sample.
-\replychris{A worked example as well as} the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
-}
+A worked example as well as the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
 
@@
 In 98\% of the posterior samples the RET sSFR distribution loc was at a higher value than SNe II, while the same was true 95\% of the time for RETs when comparing with SESNe.
-\phil{The mean difference is 0.6 dex.
+The mean difference is 0.6 dex.
 To test whether some of this could be attributed to the difference in redshift between the samples we apply a crude redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}.
@@
 a difference of 0.30 dex, or half of the observed difference.
-The remaining 0.3 dex is thus consistent with being an intrinsic difference.}
+The remaining 0.3 dex is thus consistent with being an intrinsic difference.
 RET host galaxies are significantly lower in sSFR than LGRBs.
@@
 They are also shifted to higher sSFRs than RETs, with the loc of the distribution on average 0.76 dex greater than RETs.
-The strong high-sSFR tail shows SLSNe \replychris{occur in a different galaxy} population to RETs.
+The strong high-sSFR tail shows SLSNe occur in a different galaxy population to RETs.
 
@@
 \caption{The mass-metallicity relation (MZR) for RET host galaxies and comparison samples.
-\phil{Upward- and downward-pointing triangles reflect lower and upper limits respectively.
+Upward- and downward-pointing triangles reflect lower and upper limits respectively.
 The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.
-The dashed lines represent MZR parameterisations from \citet{Zahid2014}.}
+The dashed lines represent MZR parameterisations from \citet{Zahid2014}.
 \label{fig:mzr}}
@@
 The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe.
-\replylluis{The metallicity distribution of SESNe is, however, quite broad \citep[e.g.][]{Anderson2010}, with different subclasses showing different trends (with SNe Ic host environments exhibiting higher metallicity than Ib, and IIb much lower).} RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
+The metallicity distribution of SESNe is, however, quite broad \citep[e.g.][]{Anderson2010}, with different subclasses showing different trends (with SNe Ic host environments exhibiting higher metallicity than Ib, and IIb much lower).
+RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
 
@@
 The median CDFs of LGRBs and SLSNe show divergence from the RETs, particularly at low metallicity.
-As a result, the \replychris{locs} of their fits are shifted compared to the RETs.
-In 67\% of samples, the RET sample had a higher \replychris{loc} than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
+As a result, the locs of their fits are shifted compared to the RETs.
+In 67\% of samples, the RET sample had a higher loc than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
 While these effects are not as significant as with the RETs - SNe II comparison, there is mild evidence that RETs located in galaxies with higher metal content than LGRBs.
@@
 They populate similar regions to SESNe, LGRBs and SLSNe but are clearly offset from the SNe II.
-\phil{SN2018gep, the Koala, and SNLS04D4ec appear in line with the RETs, while the Cow lies quite distinctly above the MZR, and is even outside the bulk of the local field galaxies.}
+SN2018gep, the Koala, and SNLS04D4ec appear in line with the RETs, while the Cow lies quite distinctly above the MZR, and is even outside the bulk of the local field galaxies.
 
@@
 The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs.
-Of 106 objects, under half \replylluis{(52/106)} have secure host galaxy redshifts.
+Of 106 objects, under half (52/106) have secure host galaxy redshifts.
 Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and four were obtained by programmes for which we do not have access to the spectra.
-Of the remaining 45, it was possible to derive a metallicity \replylluis{or at least a limit} for 40 host galaxies, \replylluis{while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega}.
+Of the remaining 45, it was possible to derive a metallicity or at least a limit for 40 host galaxies, while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega.
 The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible.
@@
 \halpha, \hbeta, \OIII, and \OII).
-\replylluis{It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift.
+It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift.
 However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a positive redshift detection compared to less enriched galaxies with the same mass and redshift.
-Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to eliminate this possible bias.}
+Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to eliminate this possible bias.
 
@@
 \ref{fig:mag_dist}.
-Of the 57 objects without a redshift, 47 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}.
+Of the 57 objects without a redshift, 47 of them have host galaxies detected in the SN Deep coadds of \citetalias{Wiseman2020}.
 Of more significance is that only 40 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign.
@@
 These figures place the DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching their location in host galaxy parameter space.
-While stressing that these associations are lose - rates are uncertain and host galaxy parameters span wide ranges for all transients - they are both linked to the respective transients' progenitor channels.
-Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, \replychris{potentially stripped of their envelopes, and possibly sharing some of the extreme properties of} SLSNe or LGRBs.
-It could therefore be possible that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to \replychris{shock breakout and subsequent cooling}, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
+While stressing that these associations are loose - rates are uncertain and host galaxy parameters span wide ranges for all transients - they are both linked to the respective transients' progenitor channels.
+Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSNe or LGRBs.
+It could therefore be possible that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
 
@@
 Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies.
-For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFR\replychris{s} \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
+For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFRs \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
 In Fig.
-\ref{fig:ret_v_host} we show the RET peak magnitude (upper pannels) and decline rate parameterised as $t_{\mathrm{half}}$, the time taken for the LC to decline to half the peak brightness (lower panels) and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
+\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and decline rate parameterised as $t_{\mathrm{half}}$, the time taken for the LC to decline to half the peak brightness (lower panels) and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
 The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a simple blackbody SED.
@@
 The host of SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR.
-While the SN2018gep host is lower in stellar mass than any DES RET ($\log \left(M/M_{\odot}\right) =8.11$, galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}.
+While the SN2018gep host is lower in stellar mass than any DES RET $\left(\log \left(M/M_{\odot}\right) =8.11\right)$, galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}.
 The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}.
@@
 The host of the Koala is a low metallicity starburst more typical of LGRBs and SLSNe, and places this transient at the very extreme end of the DES RET host population.
-While we note that the \citet{Ho2020} study made multiple non-detections of radio emission from the DES RETs, these were taken at very late epochs ($\geq 1\mathrm{year}$), so the presence of jets in the early evolution is not ruled out.
+While we note that the \citet{Ho2020} study made multiple non-detections of radio emission from the DES RETs, these were taken at very late epochs ($\geq 1~\mathrm{year}$), so the presence of jets in the early evolution is not ruled out.
 Seen from the other point of view, we cannot rule out that the Koala comes from the same population of transients as the DES RETs.
@@
 
-\replychris{While current surveys such as ZTF \citep{Bellm2019}, GOTO \citep{Dyer2018}, and BlackGEM \citep{Bloemen2016} are well equipped to find low-redshift RETs, a sample similar to that presented here will likely not be collected until LSST comes online.
+While current surveys such as ZTF \citep{Bellm2019}, GOTO \citep{Dyer2018}, and BlackGEM \citep{Bloemen2016} are well equipped to find low-redshift RETs, a sample similar to that presented here will likely not be collected until LSST comes online.
 With several hundreds of objects, detailed studies of RETs and their hosts will be possible in a systematic and more complete manner as has been achieved with LGRBs and SLSNe.
-At that point, the conclusions of this paper will be able to be tested.}
+At that point, the conclusions of this paper will be able to be tested.
 
@@
 Table \ref{tab:fluxes} presents the line fluxes for all DES RET hosts for which spectra were available.
+Spectra are available from the public OzDES DR2 at \url{https://docs.datacentral.org.au/ozdes/overview/dr2/}.
 
@@
 \includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
-\caption{\replychris{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
+\caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
 Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the scale vs alpha and loc vs scale distributions are two-tailed due to alpha being centred close to 0; 3) there is a degeneracy between loc and alpha for the same reason.
-Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.}
+Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.
 \label{fig:corner}}
@@
 
-\replychris{To compare two distributions we follow the method outlined in \citet{Wiseman2020}.
+To compare two distributions we follow the method outlined in \citetalias{Wiseman2020}.
 We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution.
@@
 We then compare the differences in these parameters, as seen in Fig.
-\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.}
+\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
 \twocolumn

### 2020-04-09 RET_Hosts_SNWG.tex
Updates from Overleaf

@@
 CCSNe can be split into observationally-determinded subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \citep{Minkowski1941}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
-Conversely, SNe Ib and Ic do not show signatures of hydrogen \citep[e.g.[]{Filippenko1997} and are thus referred to collectively as stripped-envelope SNe (SESNe), having undergone a partial removal of their outer atmospheres.
+Conversely, SNe Ib and Ic do not show signatures of hydrogen \citep[e.g.][]{Filippenko1997} and are thus referred to collectively as stripped-envelope SNe (SESNe), having undergone a partial removal of their outer atmospheres.
 The SN IIb subclass, which shows hydrogen only at early epochs that disappears after a few weeks \citep{Filippenko1988}, is also commonly grouped along with SESNe.

### 2020-04-09 RET_Hosts_SNWG.tex
Updates from Overleaf

@@
 \includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
-\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
+\caption{Histograms showing the differences between the fit parameters across the MCMC samples for the comparison between RETs and SESNe. 
 \label{fig:param_diffs}}
@@
 We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution.
-We use a warm-up period of $5\times10^3$ iterations and a fit period of $10^4$ iterations.
+We utilise two chains, for a warm-up period of $5\times10^3$ iterations per chain and a fit period of $5\times10^3$ iterations per chain.
 Fig.

### 2020-04-09 RET_Hosts_SNWG.tex
Updates from Overleaf

@@
 DES13E2lpk     & 10.09911 & -43.53903 & $20.49 \pm 0.03$ & 0.47541 &      OzDES &       6.00 \\
-DES13S2wxf\tnote{e}     & 41.61268 &  $-0.02 \pm 21.3$9 & 0.03266 & 0.56985 &      OzDES &       5.42 \\
+DES13S2wxf\tnote{e}& 41.61268 & -0.02634&$21.39 \pm0.03$9& 0.56985 &      OzDES &       5.42 \\
 DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.00 \\
@@
 \begin{figure*}
-\includegraphics[width=0.7\textwidth]{figs/RET_Mosaic.png}
+\includegraphics[width=\linewidth]{figs/RET_Mosaic.png}
 \caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ band deep coadds from \citetalias{Wiseman2020}.
@@
 This number expands upon the 72 of \citetalias{Pursiainen2018}.
-The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years.
+The first reason for the increased sample size is the use of the 5th year of DES-SN, as \citetalias{Pursiainen2018} were only able to make use of the first four years.
 By imposing the \citetalias{Pursiainen2018} selection criteria on season 5, the sample is increased to 92 objects.
@@
 Here, a more sophisticated search method is presented.
-As only a fraction of transients in DES-SN have redshift information from host galaxy, the search must be done in the observer frame.
+As only a fraction of transients in DES-SN have redshift information from their host galaxies, the search must be done in the observer frame.
 The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution and blue colour at peak.
@@
 Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
-To negate this issue, we use lightcurves interpolated using Gaussian  (GP) as presented in \citetalias{Pursiainen2018}.
+To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citetalias{Pursiainen2018}.
 The interpolated light curves have a 0.5 day cadence and every epoch and band has a flux value, and an associated uncertainty.
@@
 Of these, 49 have a host galaxy spectroscopic redshift which we access through an internal release of the OzDES Global Redshift Catalog (GRC; v.2020\_01\_04).
-The full OzDES GRC will be available alongside the public data release detailed in \citet{Lidman2020}.
+The full OzDES redshift catalogue will be available alongside the public data release detailed in \citet{Lidman2020}.
 A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves.
@@
 
-To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based off the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
+To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based on the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
 The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample.
@@
 We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram.
-This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence AGN amongst the 11 hosts in those diagrams either.
+This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence of AGN amongst the 11 hosts in those diagrams either.
 
 Due to the low S/N of the spectra in this sample, we are constrained to a subset of metallicity diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959/5007, \NII 6548/6583, and \SII 6717/6731.
-Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII~and \SII~are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta~lines available, mandating the use of the R23 diagnostic.
+Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII~and \SII~are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta~lines available, mandating the use of the R23 diagnostic, which is based off the relative strengths of the \OII and \OIII lines.
 For hosts at $z<0.3$ we are able to use the \OIII /\NII~(O3N2), \NII /\halpha~(N2), and \SII /\NII~(S2N2) line ratios.
@@
 One object, DES16C1cbd, lies among passive galaxies.
-The spectrum of this object is red in colour, but does exhibit \OII emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar.
+The spectrum of this object is red in colour, but does exhibit \OII~emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar.
 The individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs.
@@
 
-Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming efficiency.
-It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies.
-Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely starforming environments home to LGRBs or SLSNe.
+Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
+It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR.
+Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments home to LGRBs or SLSNe.
 
@@
 To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citetalias{Wiseman2020}.
-For each pair of samples, we model the PDFs as skewed normal distributions described by the parameters `loc' (location, identical to mean for zero skewness), `scale' (spread, identical to standard deviation for zero skewness)\footnote{See \citetalias{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'.
+For each pair of samples, we model the PDFs as skewed normal distributions described by the parameters `loc' (location, identical to the mean for zero skewness), `scale' (spread, identical to the standard deviation for zero skewness)\footnote{See \citetalias{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'.
 To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0.
@@
 
-The comparison shows RET hosts to be shifted to higher sSFRs CCSNe.
+The comparison shows RET hosts to be shifted to higher sSFRs than CCSNe.
 In 98\% of the posterior samples the RET sSFR distribution loc was at a higher value than SNe II, while the same was true 95\% of the time for RETs when comparing with SESNe.
@@
 To test whether some of this could be attributed to the difference in redshift between the samples we apply a crude redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}.
-Correcting all SFRs to $z=0$ would result in the CCSN SFRs droping by an average of 0.05 dex, while the RETs would drop 0.35 dex, i.e.
+Correcting all SFRs to $z=0$ would result in the CCSN SFRs dropping by an average of 0.05 dex, while the RETs would decrease 0.35 dex, i.e.
 a difference of 0.30 dex, or half of the observed difference.
-The remaining 0.3 dex is thus consistent with being an intrinsic difference.
+The remaining 0.30 dex is thus consistent with being an intrinsic difference.
 RET host galaxies are significantly lower in sSFR than LGRBs.
@@
 In 67\% of samples, the RET sample had a higher loc than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
-While these effects are not as significant as with the RETs - SNe II comparison, there is mild evidence that RETs located in galaxies with higher metal content than LGRBs.
+While these effects are not as significant as with the RETs - SNe II comparison, there is mild evidence that RETs are located in galaxies with higher metal content than LGRBs.
 The effect is more pronounced for SLSNe, where the RETs have a higher metallicity for the distribution peak 92\% of the time.
@@
 
-Another possibility is that the hosts without a redshift are mostly non-starforming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}.
+Another possibility is that the hosts without a redshift are mostly non star-forming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}.
 In order to test this possibility, we examined the RETs that do not have a host galaxy redshift.
@@
 A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation.
-The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014},\citetalias{Pursiainen2018},\citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
+The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
 At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohmaier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
 These figures place the DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching their location in host galaxy parameter space.
-While stressing that these associations are loose - rates are uncertain and host galaxy parameters span wide ranges for all transients - they are both linked to the respective transients' progenitor channels.
+While stressing that these associations are loose – rates are uncertain and host galaxy parameters span wide ranges for all transients – they are both linked to the respective transients' progenitor channels.
 Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSNe or LGRBs.
@@
 While we note that the \citet{Ho2020} study made multiple non-detections of radio emission from the DES RETs, these were taken at very late epochs ($\geq 1~\mathrm{year}$), so the presence of jets in the early evolution is not ruled out.
-Seen from the other point of view, we cannot rule out that the Koala comes from the same population of transients as the DES RETs.
+Similarly, we cannot rule out that the Koala comes from the same population of transients as the DES RETs.
 
@@
 \label{sec:conc}
-By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of this as-yet unexplained phenomenon.
+By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of these as-yet unexplained phenomena.
 We conclude that RETs are strongly linked to massive stars, due to their hosts all exhibiting signatures of star formation.
@@
 We acknowledge support from STFC grant ST/R000506/1.
+MSm, MSu, and CPG acknowledge support from EU/FP7-ERC grant 615929.
+LG was funded by the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l{}odowska-Curie grant agreement No.
+839090.
+This work has been partially supported by the Spanish grant PGC2018-095317-B-C21 within the European Funds for Regional Development (FEDER).
 L.K.
 was supported by the Science and Technology Facilities Council (grant number ST/P006760/1) through the DISCnet Centre for Doctoral Training.
-M.S.
-and M.S.
-acknowledge support from EU/FP7-ERC grant 615929.
-L.G.
-was funded by the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l{}odowska-Curie grant agreement No.
-839090.
 
@@
 \caption{Emission line fluxes for DES RET host galaxies.
-Values are given in units of erg/cm/s/\AA, and have been corrected for Milky Way reddening using \citet{Schlegel1998}, assuming a \citet{Cardelli1989} with $R_V = 3.1$, but not for intrinsic host galaxy reddening.\label{tab:fluxes}}
+Values are given in units of erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$, and have been corrected for Milky Way reddening using \citet{Schlegel1998} assuming a \citet{Cardelli1989} reddening law with $R_V = 3.1$, but have not been corrected for intrinsic host galaxy reddening.\label{tab:fluxes}}
 \setlength{\tabcolsep}{3pt}
-\begin{tabular}{llllllllllll}
+\begin{tabular}{lccccccccccc}
 \toprule

### 2020-04-13 RET_Hosts_SNWG.tex

@@
 %\midrule
-{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(M_{\odot}\ \mathrm{yr}^{-1} M_{\odot}^{-1}\right)$& Best\tnote{a} &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\
+{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(\mathrm{yr}^{-1} \right)$& Best\tnote{a} &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\
 \midrule
@@
 Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the PDFs of the various different diagnostics scaled to PP04 O3N2, resulting in a final `best' PDF.
-We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and for DES RETs display the results in Table \ref{tab:derived}.
+We take $1\sigma$ uncertainties from the 16\textsuperscript{th} and 84\textsuperscript{th} percentiles of these PDFs, and for DES RETs display the results in Table \ref{tab:derived}.
 

### 2020-05-06 RET_Hosts_CWR.tex
Updates from Overleaf

--- 2020-04-13 RET_Hosts_SNWG.tex
@@
 Their evolution on fast timescales has hindered high quality follow-up observations, such that their origin and explosion/emission mechanism remains unexplained.
-In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey.
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 44.
+In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the first substantial analysis of RET host galaxies.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 37.
 We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars.
@@
  Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973}, were only unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
-Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
+Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, which themselves make up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
 The second exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g.
@@
 In this paper, we present the first comprehensive study of the host galaxies of RETs.
-We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} using the final year of data as well as more refined discovery techniques.
+We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} by adding the 5th and final year of DES-SN observations as well as more refined discovery techniques.
 Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
@@
 Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
-To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citetalias{Pursiainen2018}.
+To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citetalias{Pursiainen2020}.
 The interpolated light curves have a 0.5 day cadence and every epoch and band has a flux value, and an associated uncertainty.
@@
 \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
-We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram.
+We note than only 12 of the 45 RET host spectra have the necessary lines to plot a BPT diagram.
 This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence of AGN amongst the 11 hosts in those diagrams either.
@@
 In Fig.
-\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and decline rate parameterised as $t_{\mathrm{half}}$, the time taken for the LC to decline to half the peak brightness (lower panels) and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
+\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and lightcurve width parameterised as $t_{\mathrm{half}}$, the time the lightcurve is above half the peak brightness (lower panels), and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
 The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a simple blackbody SED.
@@
 \midrule
-DES13X3gms &  $43.3 \pm 27.7$ &   $10.9 \pm 7.9$ &    $32.9 \pm 7.9$ &               - &               - &               - &               - &   $2.0 \pm 7.6$ &   $17.0 \pm 7.1$ &    $6.3 \pm 9.5$ &                - \\
-DES13C1tgd &    $1.9 \pm 0.7$ &    $0.0 \pm 0.1$ &     $0.0 \pm 0.1$ &   $0.5 \pm 0.1$ &   $1.6 \pm 0.1$ &   $1.1 \pm 0.0$ &   $0.8 \pm 0.0$ &   $0.9 \pm 0.2$ &    $1.3 \pm 0.1$ &    $0.2 \pm 0.1$ &    $4.5 \pm 0.2$ \\
-DES13S2wxf &   $22.1 \pm 5.3$ &    $3.2 \pm 2.0$ &     $9.8 \pm 2.0$ &               - &               - &               - &               - &   $2.4 \pm 1.0$ &    $4.3 \pm 0.8$ &    $4.5 \pm 2.1$ &                - \\
-DES13X1hav &  $31.4 \pm 49.1$ &  $10.5 \pm 12.0$ &   $31.9 \pm 12.0$ &               - &               - &               - &               - &   $0.0 \pm 6.2$ &   $5.2 \pm 11.5$ &   $10.6 \pm 4.8$ &                - \\
-DES13X3nyg &   $15.1 \pm 1.6$ &    $3.2 \pm 0.4$ &     $9.8 \pm 0.4$ &               - &               - &               - &               - &   $0.5 \pm 0.4$ &    $0.0 \pm 0.6$ &    $3.3 \pm 0.4$ &                - \\
-DES13X3gmd &   $18.8 \pm 5.3$ &                - &                 - &               - &               - &               - &               - &   $1.9 \pm 3.8$ &    $2.3 \pm 2.7$ &    $7.0 \pm 8.3$ &                - \\
-DES13X2wvv &  $61.5 \pm 14.4$ &    $7.4 \pm 3.6$ &    $22.6 \pm 3.6$ &               - &               - &               - &               - &   $2.7 \pm 4.9$ &    $1.1 \pm 3.3$ &   $10.3 \pm 2.8$ &                - \\
-DES14S2anq &  $486.0 \pm 0.4$ &   $74.9 \pm 1.1$ &   $227.1 \pm 1.1$ &  $10.3 \pm 5.1$ &  $31.1 \pm 5.1$ &  $43.1 \pm 4.0$ &  $31.1 \pm 4.5$ &  $31.5 \pm 1.4$ &   $58.9 \pm 1.4$ &  $114.0 \pm 1.4$ &  $240.0 \pm 0.9$ \\
-DES14X1bnh &   $23.1 \pm 1.2$ &                - &                 - &               - &               - &               - &               - &   $0.4 \pm 0.4$ &    $3.1 \pm 0.5$ &                - &                - \\
-DES15S1fli &   $33.3 \pm 3.3$ &    $3.4 \pm 1.5$ &    $10.5 \pm 1.5$ &               - &               - &               - &               - &   $3.0 \pm 1.5$ &    $4.2 \pm 0.8$ &    $8.7 \pm 0.4$ &                - \\
-DES15S1fll &  $75.2 \pm 78.8$ &  $13.6 \pm 10.8$ &   $41.3 \pm 10.8$ &   $1.4 \pm 3.9$ &   $4.4 \pm 3.9$ &   $2.7 \pm 2.6$ &   $4.9 \pm 2.8$ &  $0.6 \pm 19.2$ &  $14.3 \pm 16.6$ &  $13.4 \pm 10.2$ &   $40.9 \pm 5.2$ \\
-DES14X3pkl &   $13.5 \pm 9.5$ &    $2.6 \pm 0.8$ &     $7.9 \pm 0.8$ &   $0.7 \pm 0.4$ &   $2.2 \pm 0.4$ &   $3.5 \pm 0.5$ &   $1.9 \pm 0.3$ &   $1.7 \pm 2.7$ &    $2.6 \pm 2.8$ &    $0.0 \pm 2.1$ &   $10.4 \pm 0.7$ \\
-DES13X3npb &   $14.6 \pm 4.1$ &    $1.4 \pm 0.2$ &     $4.2 \pm 0.2$ &               - &               - &               - &               - &   $2.3 \pm 0.2$ &    $4.0 \pm 0.2$ &    $5.7 \pm 0.2$ &                - \\
-DES15X2ead &   $9.7 \pm 10.0$ &    $0.8 \pm 0.8$ &     $2.3 \pm 0.8$ &   $0.8 \pm 0.4$ &   $2.5 \pm 0.4$ &   $3.5 \pm 0.3$ &   $2.2 \pm 0.6$ &   $2.9 \pm 2.5$ &    $1.3 \pm 1.7$ &    $2.3 \pm 0.8$ &   $11.5 \pm 0.3$ \\
-DES14S2plb &   $14.1 \pm 0.7$ &    $1.0 \pm 0.1$ &     $3.0 \pm 0.1$ &   $1.2 \pm 0.0$ &   $3.6 \pm 0.0$ &   $2.3 \pm 0.0$ &   $1.8 \pm 0.0$ &   $2.0 \pm 0.1$ &    $2.3 \pm 0.1$ &    $4.8 \pm 0.1$ &   $12.2 \pm 0.0$ \\
-DES14S2pli &   $13.7 \pm 0.9$ &    $0.6 \pm 0.1$ &     $1.7 \pm 0.1$ &               - &               - &               - &               - &   $0.0 \pm 0.4$ &    $1.6 \pm 0.3$ &    $3.5 \pm 0.1$ &                - \\
-DES14C3tnz &   $23.1 \pm 4.5$ &    $3.0 \pm 1.0$ &     $9.2 \pm 1.0$ &               - &               - &               - &               - &   $1.1 \pm 0.9$ &    $4.5 \pm 1.5$ &    $4.4 \pm 3.8$ &                - \\
-DES15X3mxf &   $29.5 \pm 3.4$ &    $1.7 \pm 0.5$ &     $5.2 \pm 0.5$ &               - &               - &               - &               - &   $1.1 \pm 2.8$ &    $4.0 \pm 1.2$ &    $5.0 \pm 0.5$ &                - \\
-DES15C3lpq &   $37.0 \pm 9.8$ &    $8.6 \pm 3.3$ &    $26.2 \pm 3.3$ &               - &               - &               - &               - &   $4.2 \pm 2.6$ &    $2.3 \pm 2.6$ &    $9.1 \pm 4.5$ &                - \\
-DES15C3nat &   $21.6 \pm 1.5$ &                - &                 - &               - &               - &               - &               - &   $1.5 \pm 0.6$ &    $4.2 \pm 1.4$ &                - &                - \\
-DES15C3mgq &  $17.0 \pm 20.8$ &    $6.3 \pm 2.4$ &    $19.1 \pm 2.4$ &   $0.4 \pm 1.3$ &   $1.3 \pm 1.3$ &   $1.2 \pm 0.7$ &   $0.0 \pm 3.6$ &   $1.8 \pm 5.1$ &    $1.7 \pm 4.0$ &    $6.2 \pm 2.9$ &   $10.6 \pm 0.8$ \\
-DES15E2nqh &  $34.7 \pm 22.4$ &    $9.3 \pm 3.6$ &    $28.2 \pm 3.6$ &               - &               - &               - &               - &   $2.4 \pm 4.3$ &    $4.8 \pm 5.2$ &    $7.7 \pm 5.1$ &                - \\
-DES15C3opk &   $10.5 \pm 6.5$ &    $5.0 \pm 3.1$ &    $15.1 \pm 3.1$ &               - &               - &               - &               - &   $0.7 \pm 1.2$ &    $1.8 \pm 0.9$ &    $2.9 \pm 3.7$ &                - \\
-DES15C3opp &   $15.5 \pm 3.3$ &    $1.7 \pm 0.6$ &     $5.2 \pm 0.6$ &               - &               - &               - &               - &   $0.7 \pm 2.1$ &    $2.9 \pm 1.5$ &    $3.1 \pm 0.7$ &                - \\
-DES16E2pv  &  $39.7 \pm 12.2$ &    $6.0 \pm 9.5$ &    $18.0 \pm 9.5$ &               - &               - &               - &               - &   $0.3 \pm 4.9$ &    $5.9 \pm 5.1$ &    $6.9 \pm 4.9$ &                - \\
-DES16S1bbp &  $37.2 \pm 13.0$ &    $7.5 \pm 1.7$ &    $22.9 \pm 1.7$ &   $0.7 \pm 0.4$ &   $2.1 \pm 0.4$ &   $2.8 \pm 1.3$ &   $2.0 \pm 0.4$ &   $2.9 \pm 2.7$ &    $6.0 \pm 1.9$ &   $12.2 \pm 2.3$ &   $24.2 \pm 0.8$ \\
-DES16X3cxn &   $23.5 \pm 5.6$ &    $1.6 \pm 2.6$ &     $4.9 \pm 2.6$ &               - &               - &               - &               - &   $0.0 \pm 2.2$ &    $0.7 \pm 1.4$ &    $4.0 \pm 1.0$ &                - \\
-DES16C1cbd &    $9.3 \pm 1.8$ &    $0.6 \pm 0.3$ &     $1.8 \pm 0.3$ &               - &               - &               - &               - &   $0.8 \pm 0.1$ &    $1.0 \pm 0.1$ &    $1.9 \pm 0.1$ &                - \\
-DES16X3ega &   $28.2 \pm 2.1$ &    $0.9 \pm 1.0$ &     $2.8 \pm 1.0$ &   $1.0 \pm 0.8$ &   $3.0 \pm 0.8$ &   $2.8 \pm 0.4$ &   $1.5 \pm 0.9$ &   $2.0 \pm 0.8$ &    $4.4 \pm 0.7$ &    $5.8 \pm 0.5$ &   $14.5 \pm 0.4$ \\
-DES16X3erw &   $31.6 \pm 4.0$ &    $2.9 \pm 1.6$ &     $8.8 \pm 1.6$ &               - &               - &               - &               - &   $3.4 \pm 1.7$ &    $2.1 \pm 1.5$ &    $7.2 \pm 0.7$ &                - \\
-DES16C3gin &   $17.1 \pm 2.8$ &    $1.5 \pm 0.4$ &     $4.4 \pm 0.4$ &               - &               - &               - &               - &   $1.6 \pm 1.1$ &    $0.0 \pm 1.2$ &    $4.3 \pm 0.6$ &   $10.1 \pm 0.5$ \\
-DES16S1dxu &  $96.3 \pm 33.0$ &   $16.4 \pm 8.4$ &    $49.5 \pm 8.4$ &   $0.8 \pm 2.5$ &   $2.4 \pm 2.5$ &   $1.2 \pm 3.6$ &   $3.7 \pm 1.8$ &   $5.5 \pm 6.9$ &    $9.1 \pm 4.8$ &   $22.8 \pm 3.9$ &   $39.2 \pm 1.2$ \\
-DES16X1eho &    $6.6 \pm 0.9$ &                - &                 - &               - &               - &               - &               - &   $0.0 \pm 0.3$ &    $1.2 \pm 0.6$ &    $1.4 \pm 0.8$ &                - \\
-DES17C3gop &  $21.1 \pm 17.3$ &    $2.5 \pm 2.4$ &     $7.6 \pm 2.4$ &               - &               - &               - &               - &   $2.7 \pm 2.4$ &    $5.3 \pm 3.2$ &    $4.8 \pm 1.4$ &                - \\
-DES17S2fee &    $0.1 \pm 0.2$ &    $0.0 \pm 0.0$ &     $0.0 \pm 0.0$ &   $0.1 \pm 0.0$ &   $0.2 \pm 0.0$ &   $0.0 \pm 0.0$ &   $0.3 \pm 0.0$ &   $0.0 \pm 0.0$ &    $0.1 \pm 0.0$ &    $0.0 \pm 0.0$ &    $0.4 \pm 0.0$ \\
-DES17X3dxu &   $22.1 \pm 2.8$ &                - &                 - &               - &               - &               - &               - &   $3.8 \pm 6.1$ &    $4.7 \pm 1.3$ &                - &                - \\
-DES17X3cds &    $9.4 \pm 6.5$ &    $2.0 \pm 1.1$ &     $6.1 \pm 1.1$ &               - &               - &               - &               - &   $0.0 \pm 0.9$ &    $0.6 \pm 0.7$ &    $3.1 \pm 0.7$ &                - \\
-DES17X3hxi &  $56.6 \pm 78.6$ &  $35.7 \pm 26.0$ &  $108.3 \pm 26.0$ &               - &               - &               - &               - &  $8.9 \pm 22.2$ &  $16.1 \pm 22.9$ &  $22.7 \pm 18.0$ &                - \\
-DES13E2lpk &   $11.3 \pm 0.7$ &    $0.5 \pm 0.1$ &     $1.5 \pm 0.1$ &               - &               - &               - &               - &   $0.7 \pm 0.2$ &    $1.3 \pm 0.1$ &    $3.3 \pm 0.1$ &                - \\
-DES15C2eal &  $28.1 \pm 17.9$ &    $2.1 \pm 2.3$ &     $6.5 \pm 2.3$ &   $0.5 \pm 1.6$ &   $1.5 \pm 1.6$ &   $3.0 \pm 0.7$ &   $4.3 \pm 0.8$ &   $0.0 \pm 4.4$ &    $4.0 \pm 3.7$ &    $4.1 \pm 3.2$ &   $17.6 \pm 2.0$ \\
-DES16C2ggt &   $21.0 \pm 1.0$ &    $2.3 \pm 0.3$ &     $6.9 \pm 0.3$ &   $1.1 \pm 0.2$ &   $3.3 \pm 0.2$ &   $3.5 \pm 0.1$ &   $2.2 \pm 0.1$ &   $0.7 \pm 0.3$ &    $2.7 \pm 0.5$ &    $7.4 \pm 0.2$ &   $14.2 \pm 0.1$ \\
-DES17C2hno &   $19.1 \pm 6.2$ &    $2.1 \pm 1.5$ &     $6.2 \pm 1.5$ &               - &               - &               - &               - &   $2.4 \pm 2.5$ &    $2.7 \pm 1.6$ &    $7.0 \pm 1.8$ &                - \\
+DES13X3gms  &   $1.2 \pm 14.8$ &  $0.3 \pm 1.8$ &   $0.9 \pm 1.8$ &              - &               - &              - &              - &  $0.0 \pm 1.9$ &  $15.1 \pm 2.0$ &   $0.7 \pm 1.5$ &               - \\
+DES13C1tgd  &    $1.6 \pm 1.5$ &  $0.0 \pm 0.5$ &   $0.0 \pm 0.5$ &  $0.7 \pm 0.6$ &   $2.2 \pm 0.6$ &  $1.5 \pm 0.3$ &  $1.0 \pm 0.4$ &  $0.4 \pm 0.5$ &   $1.1 \pm 0.5$ &   $0.3 \pm 0.5$ &   $5.8 \pm 0.8$ \\
+DES13S2wxf  &  $32.7 \pm 10.5$ &  $1.3 \pm 1.1$ &   $4.1 \pm 1.1$ &              - &               - &              - &              - &  $1.9 \pm 1.2$ &   $2.1 \pm 1.0$ &   $1.8 \pm 1.1$ &               - \\
+DES13X1hav  &    $3.0 \pm 1.2$ &  $1.0 \pm 0.6$ &   $3.0 \pm 0.6$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.5 \pm 0.5$ &   $0.9 \pm 0.3$ &               - \\
+DES13X3nyg  &    $2.6 \pm 0.6$ &  $0.1 \pm 0.4$ &   $0.3 \pm 0.4$ &              - &               - &              - &              - &  $0.1 \pm 0.2$ &   $0.0 \pm 0.2$ &   $0.1 \pm 0.1$ &               - \\
+DES13X3gmd  &    $2.7 \pm 0.7$ &              - &               - &              - &               - &              - &              - &  $0.1 \pm 0.4$ &   $0.3 \pm 0.4$ &   $1.3 \pm 1.0$ &               - \\
+DES13C3bcok &    $3.6 \pm 3.8$ &  $0.7 \pm 1.2$ &   $2.2 \pm 1.2$ &              - &               - &              - &              - &  $0.0 \pm 1.2$ &   $2.0 \pm 1.4$ &   $2.3 \pm 1.0$ &  $10.8 \pm 3.0$ \\
+DES13X2wvv  &   $16.4 \pm 2.7$ &  $2.9 \pm 1.4$ &   $8.8 \pm 1.4$ &              - &               - &              - &              - &  $1.1 \pm 1.3$ &   $0.6 \pm 1.2$ &   $4.3 \pm 1.1$ &               - \\
+DES14X1bnh  &    $8.3 \pm 0.8$ &              - &               - &              - &               - &              - &              - &  $0.1 \pm 0.3$ &   $1.0 \pm 0.3$ &               - &               - \\
+DES15S1fli  &   $15.0 \pm 1.6$ &  $1.3 \pm 1.0$ &   $3.9 \pm 1.0$ &              - &               - &              - &              - &  $1.4 \pm 0.8$ &   $2.2 \pm 0.6$ &   $4.3 \pm 0.5$ &               - \\
+DES15S1fll  &   $10.3 \pm 2.5$ &  $5.0 \pm 2.0$ &  $15.2 \pm 2.0$ &  $0.5 \pm 1.1$ &   $1.4 \pm 1.1$ &  $0.8 \pm 0.8$ &  $1.5 \pm 0.8$ &  $0.6 \pm 1.1$ &   $2.5 \pm 1.3$ &   $4.2 \pm 1.5$ &  $15.4 \pm 1.4$ \\
+DES14X3pkl  &    $2.5 \pm 1.2$ &  $0.8 \pm 0.4$ &   $2.3 \pm 0.4$ &  $0.2 \pm 0.2$ &   $0.5 \pm 0.2$ &  $0.8 \pm 0.2$ &  $0.4 \pm 0.2$ &  $0.4 \pm 0.5$ &   $0.6 \pm 0.6$ &   $0.0 \pm 0.7$ &   $2.3 \pm 0.3$ \\
+DES13X3npb  &   $15.9 \pm 6.6$ &  $0.8 \pm 0.8$ &   $2.4 \pm 0.8$ &              - &               - &              - &              - &  $2.0 \pm 0.7$ &   $2.6 \pm 0.4$ &   $3.3 \pm 0.8$ &               - \\
+DES15X2ead  &  $31.4 \pm 23.5$ &  $1.6 \pm 3.0$ &   $4.8 \pm 3.0$ &  $1.1 \pm 1.6$ &   $3.5 \pm 1.6$ &  $5.3 \pm 1.7$ &  $3.2 \pm 1.9$ &  $9.6 \pm 7.9$ &   $4.5 \pm 6.0$ &   $5.4 \pm 3.1$ &  $16.7 \pm 1.9$ \\
+DES14S2plb  &   $54.5 \pm 7.2$ &  $4.5 \pm 2.1$ &  $13.5 \pm 2.1$ &  $5.6 \pm 1.8$ &  $16.9 \pm 1.8$ &  $9.5 \pm 0.9$ &  $7.1 \pm 0.7$ &  $6.5 \pm 2.0$ &   $7.9 \pm 1.7$ &  $19.3 \pm 1.5$ &  $53.4 \pm 1.7$ \\
+DES14S2pli  &    $7.7 \pm 1.1$ &  $0.4 \pm 0.4$ &   $1.2 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.6$ &   $1.1 \pm 0.5$ &   $2.4 \pm 0.3$ &               - \\
+DES14C3tnz  &    $4.2 \pm 0.9$ &  $0.4 \pm 0.3$ &   $1.3 \pm 0.3$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.4 \pm 0.3$ &   $0.4 \pm 0.5$ &               - \\
+DES15X3mxf  &    $4.8 \pm 0.7$ &  $0.4 \pm 0.3$ &   $1.2 \pm 0.3$ &              - &               - &              - &              - &  $0.6 \pm 0.5$ &   $0.7 \pm 0.4$ &   $1.1 \pm 0.3$ &               - \\
+DES15C3lpq  &    $3.9 \pm 0.8$ &  $0.5 \pm 0.3$ &   $1.6 \pm 0.3$ &              - &               - &              - &              - &  $0.5 \pm 0.3$ &   $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &               - \\
+DES15C3nat  &    $3.9 \pm 0.6$ &              - &               - &              - &               - &              - &              - &  $0.2 \pm 0.1$ &   $0.2 \pm 0.1$ &               - &               - \\
+DES15C3mgq  &    $4.1 \pm 2.5$ &  $1.1 \pm 0.5$ &   $3.2 \pm 0.5$ &  $0.1 \pm 0.2$ &   $0.2 \pm 0.2$ &  $0.2 \pm 0.2$ &  $0.0 \pm 0.4$ &  $0.6 \pm 0.8$ &   $0.4 \pm 0.7$ &   $1.2 \pm 0.5$ &   $1.4 \pm 0.2$ \\
+DES15E2nqh  &    $0.7 \pm 1.0$ &  $0.9 \pm 0.5$ &   $2.8 \pm 0.5$ &              - &               - &              - &              - &  $0.4 \pm 0.4$ &   $0.9 \pm 0.5$ &   $0.8 \pm 0.5$ &               - \\
+DES15C3opk  &    $1.6 \pm 0.8$ &  $0.5 \pm 0.3$ &   $1.4 \pm 0.3$ &              - &               - &              - &              - &  $0.1 \pm 0.3$ &   $0.3 \pm 0.2$ &   $0.4 \pm 0.3$ &               - \\
+DES15C3opp  &    $2.5 \pm 0.7$ &  $0.2 \pm 0.2$ &   $0.5 \pm 0.2$ &              - &               - &              - &              - &  $0.2 \pm 0.4$ &   $0.5 \pm 0.3$ &   $0.4 \pm 0.1$ &               - \\
+DES16E2pv   &    $2.5 \pm 0.6$ &  $0.7 \pm 1.0$ &   $2.2 \pm 1.0$ &              - &               - &              - &              - &  $0.0 \pm 0.4$ &   $0.7 \pm 0.5$ &   $1.3 \pm 0.6$ &               - \\
+DES16S1bbp  &   $21.9 \pm 3.5$ &  $3.8 \pm 0.9$ &  $11.4 \pm 0.9$ &  $0.3 \pm 0.4$ &   $1.0 \pm 0.4$ &  $1.5 \pm 0.7$ &  $0.9 \pm 0.3$ &  $1.4 \pm 1.1$ &   $3.4 \pm 0.9$ &   $6.4 \pm 1.0$ &  $11.1 \pm 0.6$ \\
+DES16X3cxn  &    $2.3 \pm 0.5$ &  $0.3 \pm 0.4$ &   $0.9 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &               - \\
+DES16C1cbd  &    $4.4 \pm 1.8$ &  $0.4 \pm 0.8$ &   $1.2 \pm 0.8$ &              - &               - &              - &              - &  $0.4 \pm 0.4$ &   $0.4 \pm 0.4$ &   $1.1 \pm 0.4$ &               - \\
+DES16C3axz  &   $26.8 \pm 2.6$ &  $2.3 \pm 0.8$ &   $7.0 \pm 0.8$ &  $2.6 \pm 0.6$ &   $7.7 \pm 0.6$ &  $5.4 \pm 0.5$ &  $4.0 \pm 0.5$ &  $2.7 \pm 0.9$ &   $5.6 \pm 0.8$ &   $9.9 \pm 0.8$ &  $29.1 \pm 0.7$ \\
+DES16X3erw  &    $5.9 \pm 0.9$ &  $0.8 \pm 0.6$ &   $2.6 \pm 0.6$ &              - &               - &              - &              - &  $0.6 \pm 0.4$ &   $0.4 \pm 0.4$ &   $1.9 \pm 0.3$ &               - \\
+DES16C3gin  &    $5.8 \pm 1.2$ &  $0.5 \pm 0.4$ &   $1.6 \pm 0.4$ &              - &               - &              - &              - &  $0.5 \pm 0.6$ &   $0.0 \pm 0.6$ &   $1.6 \pm 0.4$ &   $2.5 \pm 0.4$ \\
+DES16S1dxu  &   $29.2 \pm 3.6$ &  $6.4 \pm 1.9$ &  $19.5 \pm 1.9$ &  $0.4 \pm 1.0$ &   $1.2 \pm 1.0$ &  $0.5 \pm 1.0$ &  $1.4 \pm 0.7$ &  $1.7 \pm 1.1$ &   $2.9 \pm 0.9$ &   $8.6 \pm 1.1$ &  $16.5 \pm 0.8$ \\
+DES16X1eho  &    $2.5 \pm 0.9$ &              - &               - &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.2 \pm 0.4$ &   $0.7 \pm 0.5$ &               - \\
+DES17C3gop  &    $2.0 \pm 0.8$ &  $0.2 \pm 0.3$ &   $0.6 \pm 0.3$ &              - &               - &              - &              - &  $0.2 \pm 0.3$ &   $0.6 \pm 0.4$ &   $0.5 \pm 0.2$ &               - \\
+DES17S2fee  &    $0.8 \pm 5.1$ &  $0.0 \pm 1.2$ &   $0.0 \pm 1.2$ &  $0.4 \pm 1.0$ &   $1.2 \pm 1.0$ &  $0.4 \pm 1.1$ &  $1.4 \pm 1.0$ &  $0.0 \pm 1.2$ &   $0.6 \pm 1.2$ &   $0.0 \pm 1.0$ &   $2.3 \pm 0.7$ \\
+DES17X3dxu  &    $3.1 \pm 0.5$ &              - &               - &              - &               - &              - &              - &  $0.7 \pm 0.5$ &   $0.7 \pm 0.2$ &               - &               - \\
+DES17X3cds  &    $3.3 \pm 1.8$ &  $0.4 \pm 0.4$ &   $1.4 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.4$ &   $0.3 \pm 0.3$ &   $0.8 \pm 0.3$ &               - \\
+DES17C3fwd  &   $14.7 \pm 1.5$ &  $2.0 \pm 0.6$ &   $6.2 \pm 0.6$ &  $0.3 \pm 0.6$ &   $0.8 \pm 0.6$ &              - &              - &  $1.1 \pm 0.7$ &   $0.5 \pm 0.7$ &   $3.8 \pm 0.5$ &   $6.2 \pm 1.5$ \\
+DES17X3hxi  &    $5.4 \pm 1.8$ &  $2.3 \pm 0.9$ &   $7.1 \pm 0.9$ &              - &               - &              - &              - &  $1.0 \pm 0.7$ &   $1.6 \pm 0.7$ &   $1.6 \pm 0.5$ &               - \\
+DES13E2lpk  &    $8.9 \pm 1.5$ &  $0.4 \pm 0.5$ &   $1.2 \pm 0.5$ &              - &               - &              - &              - &  $0.4 \pm 0.6$ &   $0.8 \pm 0.5$ &   $2.4 \pm 0.4$ &               - \\
+DES15C2eal  &    $1.9 \pm 0.6$ &  $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &  $0.1 \pm 0.2$ &   $0.2 \pm 0.2$ &  $0.4 \pm 0.2$ &  $0.5 \pm 0.2$ &  $0.0 \pm 0.2$ &   $0.3 \pm 0.2$ &   $0.4 \pm 0.3$ &   $2.1 \pm 0.3$ \\
+DES16C2ggt  &   $11.8 \pm 1.2$ &  $1.1 \pm 0.4$ &   $3.2 \pm 0.4$ &  $0.4 \pm 0.4$ &   $1.4 \pm 0.4$ &  $1.7 \pm 0.3$ &  $1.1 \pm 0.3$ &  $0.4 \pm 0.5$ &   $1.5 \pm 0.6$ &   $3.4 \pm 0.4$ &   $6.9 \pm 0.5$ \\
+DES17C2hno  &    $3.7 \pm 1.1$ &  $0.2 \pm 0.2$ &   $0.7 \pm 0.2$ &              - &               - &              - &              - &  $0.4 \pm 0.5$ &   $0.6 \pm 0.4$ &   $0.9 \pm 0.2$ &               - \\
 \bottomrule
@@
 Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the scale vs alpha and loc vs scale distributions are two-tailed due to alpha being centred close to 0; 3) there is a degeneracy between loc and alpha for the same reason.
+Loc and scale have units of yr$^{-1}$, while alpha is dimensionless.
 Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.

### 2020-05-07 author_list_07_May.tex
Creating author list

% Author list file generated with: mkauthlist.py 0+unknown 
% mkauthlist.py -a order.csv -j mnras -sb author_list_07_May.csv author_list_07_May.tex

\author[DES Collaboration]{
\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Pursiainen,$^{1}$
M.~Childress,$^{1}$
E.~Swann,$^{2}$
M.~Smith,$^{1}$
L.~Galbany,$^{3}$
C.~Lidman,$^{4}$
T.~M.~Davis,$^{5}$
A.~M\"oller,$^{6}$
B.~P.~Thomas,$^{7,2}$
C.~Frohmaier,$^{2}$
R.~J.~Foley,$^{8}$
S.~R.~Hinton,$^{5}$
L.~Kelsey,$^{1}$
G.~F.~Lewis,$^{9}$
M.~Sako,$^{10}$
D.~Scolnic,$^{11}$
M.~Sullivan,$^{1}$
M.~Vincenzi,$^{2}$
B.~E.~Tucker,$^{4}$
C.~P.~Guti\'errez,$^{1}$
T.~M.~C.~Abbott,$^{12}$
M.~Aguena,$^{13,14}$
S.~Allam,$^{15}$
J.~Annis,$^{15}$
E.~Bertin,$^{16,17}$
S.~Bhargava,$^{18}$
D.~Brooks,$^{19}$
D.~L.~Burke,$^{20,21}$
A.~Carnero~Rosell,$^{7}$
D.~Carollo,$^{7,22}$
M.~Carrasco~Kind,$^{23,24}$
J.~Carretero,$^{25}$
M.~Costanzi,$^{26,27}$
L.~N.~da Costa,$^{14,28}$
H.~T.~Diehl,$^{15}$
P.~Doel,$^{19}$
S.~Everett,$^{8}$
J.~Frieman,$^{15,29}$
J.~Garc\'ia-Bellido,$^{30}$
E.~Gaztanaga,$^{31,32}$
K.~Glazebrook,$^{33}$
D.~Gruen,$^{34,20,21}$
R.~A.~Gruendl,$^{23,24}$
J.~Gschwend,$^{14,28}$
G.~Gutierrez,$^{15}$
K.~Honscheid,$^{35,36}$
D.~J.~James,$^{37}$
K.~Kuehn,$^{38,39}$
N.~Kuropatkin,$^{15}$
M.~Lima,$^{13,14}$
M.~A.~G.~Maia,$^{14,28}$
J.~L.~Marshall,$^{40}$
P.~Martini,$^{35,41}$
F.~Menanteau,$^{23,24}$
R.~Miquel,$^{42,25}$
A.~Palmese,$^{15,29}$
F.~Paz-Chinch\'{o}n,$^{43,24}$
A.~A.~Plazas,$^{44}$
A.~K.~Romer,$^{18}$
E.~Sanchez,$^{45}$
M.~Schubnell,$^{46}$
S.~Serrano,$^{31,32}$
I.~Sevilla-Noarbe,$^{45}$
N.~E.~Sommer,$^{4}$
E.~Suchyta,$^{47}$
M.~E.~C.~Swanson,$^{24}$
G.~Tarle,$^{46}$
D.~L.~Tucker,$^{15}$
T.~N.~Varga,$^{48,49}$
and A.~R.~Walker$^{12}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
%\scriptsize
$^{1}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK\\
$^{2}$ Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK\\
$^{3}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{4}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia\\
$^{5}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{6}$ Universit\{'e} Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
$^{7}$ \\
$^{8}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
$^{9}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{10}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
$^{11}$ Department of Physics, Duke University Durham, NC 27708, USA\\
$^{12}$ Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory, Casilla 603, La Serena, Chile\\
$^{13}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
$^{14}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
$^{15}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
$^{16}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
$^{17}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
$^{18}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
$^{19}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
$^{20}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
$^{21}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{22}$ INAF, Astrophysical Observatory of Turin, I-10025 Pino Torinese, Italy\\
$^{23}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
$^{24}$ National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
$^{25}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
$^{26}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
$^{27}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
$^{28}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
$^{29}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
$^{30}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
$^{31}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
$^{32}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
$^{33}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
$^{34}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
$^{35}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
$^{36}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
$^{37}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{38}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
$^{39}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
$^{40}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
$^{41}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
$^{42}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
$^{43}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{44}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
$^{45}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{46}$ Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA\\
$^{47}$ Computer Science and Mathematics Division, Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
$^{48}$ Max Planck Institute for Extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany\\
$^{49}$ Universit\"ats-Sternwarte, Fakult\"at f\"ur Physik, Ludwig-Maximilians Universit\"at M\"unchen, Scheinerstr. 1, 81679 M\"unchen, Germany\\
}
}

### 2020-05-07 author_list_07_May.tex
With Rick

@@
 % Author list file generated with: mkauthlist.py 0+unknown 
-% mkauthlist.py -a order.csv -j mnras -sb author_list_07_May.csv author_list_07_May.tex
+% mkauthlist.py -f -a order.csv -j mnras -sb author_list_07_May.csv author_list_07_May.tex
 
@@
 T.~M.~Davis,$^{5}$
+C.~P.~Guti\'errez,$^{1}$
 A.~M\"oller,$^{6}$
-B.~P.~Thomas,$^{7,2}$
+B.~P.~Thomas,$^{2}$
 C.~Frohmaier,$^{2}$
-R.~J.~Foley,$^{8}$
+R.~J.~Foley,$^{7}$
 S.~R.~Hinton,$^{5}$
 L.~Kelsey,$^{1}$
-G.~F.~Lewis,$^{9}$
-M.~Sako,$^{10}$
-D.~Scolnic,$^{11}$
+R.~Kessler,$^{8,9}$
+G.~F.~Lewis,$^{10}$
+M.~Sako,$^{11}$
+D.~Scolnic,$^{12}$
 M.~Sullivan,$^{1}$
 M.~Vincenzi,$^{2}$
-B.~E.~Tucker,$^{4}$
-C.~P.~Guti\'errez,$^{1}$
-T.~M.~C.~Abbott,$^{12}$
-M.~Aguena,$^{13,14}$
-S.~Allam,$^{15}$
-J.~Annis,$^{15}$
-E.~Bertin,$^{16,17}$
-S.~Bhargava,$^{18}$
-D.~Brooks,$^{19}$
-D.~L.~Burke,$^{20,21}$
-A.~Carnero~Rosell,$^{7}$
-D.~Carollo,$^{7,22}$
-M.~Carrasco~Kind,$^{23,24}$
-J.~Carretero,$^{25}$
-M.~Costanzi,$^{26,27}$
-L.~N.~da Costa,$^{14,28}$
-H.~T.~Diehl,$^{15}$
-P.~Doel,$^{19}$
-S.~Everett,$^{8}$
-J.~Frieman,$^{15,29}$
-J.~Garc\'ia-Bellido,$^{30}$
-E.~Gaztanaga,$^{31,32}$
-K.~Glazebrook,$^{33}$
-D.~Gruen,$^{34,20,21}$
-R.~A.~Gruendl,$^{23,24}$
-J.~Gschwend,$^{14,28}$
-G.~Gutierrez,$^{15}$
-K.~Honscheid,$^{35,36}$
-D.~J.~James,$^{37}$
-K.~Kuehn,$^{38,39}$
-N.~Kuropatkin,$^{15}$
-M.~Lima,$^{13,14}$
-M.~A.~G.~Maia,$^{14,28}$
-J.~L.~Marshall,$^{40}$
-P.~Martini,$^{35,41}$
-F.~Menanteau,$^{23,24}$
-R.~Miquel,$^{42,25}$
-A.~Palmese,$^{15,29}$
-F.~Paz-Chinch\'{o}n,$^{43,24}$
-A.~A.~Plazas,$^{44}$
-A.~K.~Romer,$^{18}$
-E.~Sanchez,$^{45}$
+T.~M.~C.~Abbott,$^{13}$
+M.~Aguena,$^{14,15}$
+S.~Allam,$^{16}$
+J.~Annis,$^{16}$
+E.~Bertin,$^{17,18}$
+S.~Bhargava,$^{19}$
+D.~Brooks,$^{20}$
+D.~L.~Burke,$^{21,22}$
+A.~Carnero~Rosell,$^{23}$
+D.~Carollo,$^{24}$
+M.~Carrasco~Kind,$^{25,26}$
+J.~Carretero,$^{27}$
+M.~Costanzi,$^{28,29}$
+L.~N.~da Costa,$^{15,30}$
+H.~T.~Diehl,$^{16}$
+P.~Doel,$^{20}$
+S.~Everett,$^{7}$
+J.~Frieman,$^{16,9}$
+J.~Garc\'ia-Bellido,$^{31}$
+E.~Gaztanaga,$^{32,33}$
+K.~Glazebrook,$^{34}$
+D.~Gruen,$^{35,21,22}$
+R.~A.~Gruendl,$^{25,26}$
+J.~Gschwend,$^{15,30}$
+G.~Gutierrez,$^{16}$
+K.~Honscheid,$^{36,37}$
+D.~J.~James,$^{38}$
+K.~Kuehn,$^{39,40}$
+N.~Kuropatkin,$^{16}$
+M.~Lima,$^{14,15}$
+M.~A.~G.~Maia,$^{15,30}$
+J.~L.~Marshall,$^{41}$
+P.~Martini,$^{36,42}$
+F.~Menanteau,$^{25,26}$
+R.~Miquel,$^{43,27}$
+A.~Palmese,$^{16,9}$
+F.~Paz-Chinch\'{o}n,$^{44,26}$
+A.~A.~Plazas,$^{45}$
+A.~K.~Romer,$^{19}$
+E.~Sanchez,$^{23}$
 M.~Schubnell,$^{46}$
-S.~Serrano,$^{31,32}$
-I.~Sevilla-Noarbe,$^{45}$
+S.~Serrano,$^{32,33}$
+I.~Sevilla-Noarbe,$^{23}$
 N.~E.~Sommer,$^{4}$
 E.~Suchyta,$^{47}$
-M.~E.~C.~Swanson,$^{24}$
+M.~E.~C.~Swanson,$^{26}$
 G.~Tarle,$^{46}$
-D.~L.~Tucker,$^{15}$
+B.~E.~Tucker,$^{4}$
+D.~L.~Tucker,$^{16}$
 T.~N.~Varga,$^{48,49}$
-and A.~R.~Walker$^{12}$
+and A.~R.~Walker$^{13}$
 \begin{center} (DES Collaboration) \end{center}
@@
 $^{5}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
-$^{6}$ Universit\{'e} Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
-$^{7}$ \\
-$^{8}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
-$^{9}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
-$^{10}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
-$^{11}$ Department of Physics, Duke University Durham, NC 27708, USA\\
-$^{12}$ Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory, Casilla 603, La Serena, Chile\\
-$^{13}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
-$^{14}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
-$^{15}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
-$^{16}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
-$^{17}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
-$^{18}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
-$^{19}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
-$^{20}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
-$^{21}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
-$^{22}$ INAF, Astrophysical Observatory of Turin, I-10025 Pino Torinese, Italy\\
-$^{23}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
-$^{24}$ National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
-$^{25}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
-$^{26}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
-$^{27}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
-$^{28}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
-$^{29}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
-$^{30}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
-$^{31}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
-$^{32}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
-$^{33}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
-$^{34}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
-$^{35}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
-$^{36}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
-$^{37}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{38}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
-$^{39}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
-$^{40}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
-$^{41}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
-$^{42}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
-$^{43}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{44}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
-$^{45}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
+$^{6}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
+$^{7}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
+$^{8}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
+$^{9}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
+$^{10}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
+$^{11}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
+$^{12}$ Department of Physics, Duke University Durham, NC 27708, USA\\
+$^{13}$ Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory, Casilla 603, La Serena, Chile\\
+$^{14}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
+$^{15}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
+$^{16}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
+$^{17}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
+$^{18}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
+$^{19}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
+$^{20}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
+$^{21}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
+$^{22}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
+$^{23}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
+$^{24}$ INAF, Astrophysical Observatory of Turin, I-10025 Pino Torinese, Italy\\
+$^{25}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
+$^{26}$ National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
+$^{27}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
+$^{28}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
+$^{29}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
+$^{30}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
+$^{31}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
+$^{32}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
+$^{33}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
+$^{34}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
+$^{35}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
+$^{36}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
+$^{37}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
+$^{38}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{39}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
+$^{40}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
+$^{41}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
+$^{42}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
+$^{43}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
+$^{44}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{45}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
 $^{46}$ Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA\\

### 2020-05-07 RET_Hosts_CWR.tex
Updates from Overleaf

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[P. Wiseman et al.]{
-P. Wiseman$^1$\thanks{E-mail: p.s.wiseman@soton.ac.uk (PW)},
- %M. Pursiainen$^1$,
- %M. J. Childress$^1$,
- %M. Smith$^1$,
- %E. Swann$^2$,
- and Other Authors$^{1,2,3}$,
-\newauthor
-(The DES Collaboration)
+\author[DES Collaboration]{
+\parbox{\textwidth}{
+\Large
+P.~Wiseman,$^{1}$
+M.~Pursiainen,$^{1}$
+M.~Childress,$^{1}$
+E.~Swann,$^{2}$
+M.~Smith,$^{1}$
+L.~Galbany,$^{3}$
+C.~Lidman,$^{4}$
+T.~M.~Davis,$^{5}$
+A.~M\"oller,$^{6}$
+B.~P.~Thomas,$^{7,2}$
+C.~Frohmaier,$^{2}$
+R.~J.~Foley,$^{8}$
+S.~R.~Hinton,$^{5}$
+L.~Kelsey,$^{1}$
+G.~F.~Lewis,$^{9}$
+M.~Sako,$^{10}$
+D.~Scolnic,$^{11}$
+M.~Sullivan,$^{1}$
+M.~Vincenzi,$^{2}$
+B.~E.~Tucker,$^{4}$
+C.~P.~Guti\'errez,$^{1}$
+T.~M.~C.~Abbott,$^{12}$
+M.~Aguena,$^{13,14}$
+S.~Allam,$^{15}$
+J.~Annis,$^{15}$
+E.~Bertin,$^{16,17}$
+S.~Bhargava,$^{18}$
+D.~Brooks,$^{19}$
+D.~L.~Burke,$^{20,21}$
+A.~Carnero~Rosell,$^{7}$
+D.~Carollo,$^{7,22}$
+M.~Carrasco~Kind,$^{23,24}$
+J.~Carretero,$^{25}$
+M.~Costanzi,$^{26,27}$
+L.~N.~da Costa,$^{14,28}$
+H.~T.~Diehl,$^{15}$
+P.~Doel,$^{19}$
+S.~Everett,$^{8}$
+J.~Frieman,$^{15,29}$
+J.~Garc\'ia-Bellido,$^{30}$
+E.~Gaztanaga,$^{31,32}$
+K.~Glazebrook,$^{33}$
+D.~Gruen,$^{34,20,21}$
+R.~A.~Gruendl,$^{23,24}$
+J.~Gschwend,$^{14,28}$
+G.~Gutierrez,$^{15}$
+K.~Honscheid,$^{35,36}$
+D.~J.~James,$^{37}$
+K.~Kuehn,$^{38,39}$
+N.~Kuropatkin,$^{15}$
+M.~Lima,$^{13,14}$
+M.~A.~G.~Maia,$^{14,28}$
+J.~L.~Marshall,$^{40}$
+P.~Martini,$^{35,41}$
+F.~Menanteau,$^{23,24}$
+R.~Miquel,$^{42,25}$
+A.~Palmese,$^{15,29}$
+F.~Paz-Chinch\'{o}n,$^{43,24}$
+A.~A.~Plazas,$^{44}$
+A.~K.~Romer,$^{18}$
+E.~Sanchez,$^{45}$
+M.~Schubnell,$^{46}$
+S.~Serrano,$^{31,32}$
+I.~Sevilla-Noarbe,$^{45}$
+N.~E.~Sommer,$^{4}$
+E.~Suchyta,$^{47}$
+M.~E.~C.~Swanson,$^{24}$
+G.~Tarle,$^{46}$
+D.~L.~Tucker,$^{15}$
+T.~N.~Varga,$^{48,49}$
+and A.~R.~Walker$^{12}$
+\begin{center} (DES Collaboration) \end{center}
+}
+\vspace{0.4cm}
 \\
-% List of institutions
-$^{1}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK\\
-$^{2}$Other Institutions\\
-%$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+\parbox{\textwidth}{Affiliations are listed at the end of the paper}
 }
-
 % These dates will be filled out by the publisher
@@
 Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
-To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citetalias{Pursiainen2020}.
+To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citet{Pursiainen2020}.
 The interpolated light curves have a 0.5 day cadence and every epoch and band has a flux value, and an associated uncertainty.
@@
 We also compare with the host galaxy of SNLS04D4ec \citep{Arcavi2016}.
-To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'') with host galaxy photometric measurements from \citet{Perley2019} and metallicity (\citealt{Pettini2004} O3N2) from \citet{Morokuma-Matsui2019}, SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
+To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'').
+The host galaxy of AT2018cow has been studied with photometric measurements \citep{Perley2019} as well as with an integral field spectrograph \citep{Lyman2020}, with consistent results.
+For our comparison, we use the galaxy-averaged stellar mass and SFR from \citet{Lyman2020} and the metallicity from the host nucleus as reported by both \citet{Morokuma-Matsui2019} and \citet{Lyman2020} as it best represents the method of obtaining spectra for our RET sample.
+We further compare to SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
 
@@
 There have been several suggestions that AT2018cow is indeed an analogue of the high-z RETs.
-The host galaxy of AT2018cow appears to be moderately star forming and lies very close to the centre of the SFMS (Figs.
+The host galaxy of AT2018cow appears to be moderately star forming and lies very close to the centre of the SFMS (\citealt{Lyman2020}; Figs.
 \ref{fig:sfms_sfr},\ref{fig:sfms_ssfr}), along with many of the DES RET hosts.
-However, the host lies significantly above the fiducial MZR in Fig.
-\ref{fig:mzr}, suggesting that it has an abnormally high metallicity for its stellar mass.
-This is in contrast to the DES RET hosts, which are systematically less enriched for a given stellar mass.
+However, the host lies somewhat above the fiducial MZR in Fig.
+\ref{fig:mzr}, suggesting that it has an unusually high metallicity for its stellar mass.
+While consistent with SNe II, this is in contrast to the DES RET hosts which are systematically less enriched for a given stellar mass.
 
@@
 Of the RET analogues discovered in modern large-area, high-cadence surveys, ZTF18abvkwla shares the most similar host galaxy characteristics with the DES RET population.
-SN2018gep appears in a galaxy too faint to have been detected by DES-SN at the redshift of most of the DES RETs, while the host of AT2018cow is much higher in metallicity.
+SN2018gep appears in a galaxy too faint to have been detected by DES-SN at the redshift of most of the DES RETs, while the host of AT2018cow is higher in metallicity.
 
@@
 With several hundreds of objects, detailed studies of RETs and their hosts will be possible in a systematic and more complete manner as has been achieved with LGRBs and SLSNe.
-At that point, the conclusions of this paper will be able to be tested.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\onecolumn
+\input{affiliations.tex}
 

### 2020-05-07 affiliations.tex

\parbox{\textwidth}{
%\scriptsize
$^{1}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK\\
$^{2}$ Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK\\
$^{3}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{4}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia\\
$^{5}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{6}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
$^{7}$ \\
$^{8}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
$^{9}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{10}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
$^{11}$ Department of Physics, Duke University Durham, NC 27708, USA\\
$^{12}$ Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory, Casilla 603, La Serena, Chile\\
$^{13}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
$^{14}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
$^{15}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
$^{16}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
$^{17}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
$^{18}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
$^{19}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
$^{20}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
$^{21}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{22}$ INAF, Astrophysical Observatory of Turin, I-10025 Pino Torinese, Italy\\
$^{23}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
$^{24}$ National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
$^{25}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
$^{26}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
$^{27}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
$^{28}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
$^{29}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
$^{30}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
$^{31}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
$^{32}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
$^{33}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
$^{34}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
$^{35}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
$^{36}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
$^{37}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{38}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
$^{39}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
$^{40}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
$^{41}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
$^{42}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
$^{43}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{44}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
$^{45}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{46}$ Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA\\
$^{47}$ Computer Science and Mathematics Division, Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
$^{48}$ Max Planck Institute for Extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany\\
$^{49}$ Universit\"ats-Sternwarte, Fakult\"at f\"ur Physik, Ludwig-Maximilians Universit\"at M\"unchen, Scheinerstr. 1, 81679 M\"unchen, Germany\\
}

### 2020-05-07 affiliations.tex
Updates from Overleaf

@@
 $^{6}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
-$^{7}$ \\
-$^{8}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
-$^{9}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
-$^{10}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
-$^{11}$ Department of Physics, Duke University Durham, NC 27708, USA\\
-$^{12}$ Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory, Casilla 603, La Serena, Chile\\
-$^{13}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
-$^{14}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
-$^{15}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
-$^{16}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
-$^{17}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
-$^{18}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
-$^{19}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
-$^{20}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
-$^{21}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
-$^{22}$ INAF, Astrophysical Observatory of Turin, I-10025 Pino Torinese, Italy\\
-$^{23}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
-$^{24}$ National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
-$^{25}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
-$^{26}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
-$^{27}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
-$^{28}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
-$^{29}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
-$^{30}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
-$^{31}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
-$^{32}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
-$^{33}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
-$^{34}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
-$^{35}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
-$^{36}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
-$^{37}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{38}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
-$^{39}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
-$^{40}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
-$^{41}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
-$^{42}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
-$^{43}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{44}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
-$^{45}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
+$^{7}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
+$^{8}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
+$^{9}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
+$^{10}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
+$^{11}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
+$^{12}$ Department of Physics, Duke University Durham, NC 27708, USA\\
+$^{13}$ Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory, Casilla 603, La Serena, Chile\\
+$^{14}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
+$^{15}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
+$^{16}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
+$^{17}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
+$^{18}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
+$^{19}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
+$^{20}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
+$^{21}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
+$^{22}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
+$^{23}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
+$^{24}$ INAF, Astrophysical Observatory of Turin, I-10025 Pino Torinese, Italy\\
+$^{25}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
+$^{26}$ National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
+$^{27}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
+$^{28}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
+$^{29}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
+$^{30}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
+$^{31}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
+$^{32}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
+$^{33}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
+$^{34}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
+$^{35}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
+$^{36}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
+$^{37}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
+$^{38}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{39}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
+$^{40}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
+$^{41}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
+$^{42}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
+$^{43}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
+$^{44}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{45}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
 $^{46}$ Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA\\

### 2020-05-14 RET_Hosts_CWR.tex
Updates from Overleaf

@@
 \newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
-\newcommand{\replychris}[1]{\color{magenta}#1 \color{black}}
+\newcommand{\replyrick}[1]{\color{magenta}#1 \color{black}}
 \newcommand{\replylluis}[1]{\color{brown}#1 \color{black}}
@@
 Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a distinct class of astrophysical event.
-They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
-Their evolution on fast timescales has hindered high quality follow-up observations, such that their origin and explosion/emission mechanism remains unexplained.
+They are characterised by lightcurves that decline much faster than common classes supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
+Their evolution on fast timescales has hindered high quality follow-up observations, and thus their origin and explosion/emission mechanism remains unexplained.
 In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the first substantial analysis of RET host galaxies.
@@
 The SN IIb subclass, which shows hydrogen only at early epochs that disappears after a few weeks \citep{Filippenko1988}, is also commonly grouped along with SESNe.
-SNe IIn, with the n standing for \textit{narrow}, which refers to the apparent width of the hydrogen emission lines when compared to standard SNe II \citep{Schlegel1990}, indicating their origin from the ejecta impacting on slow-moving circumstellar material (CSM).
+\replyrick{SNe IIn display much narrower hydrogen emission lines when compared to standard SNe II \citep{Schlegel1990}.
+The narrow emission originates from the ejecta impacting on slow-moving circumstellar material (CSM)}.
 Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
 
- Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973}, were only unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
+ Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973}, were unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}.
 Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, which themselves make up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
-The second exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g.
+\replyrick{Another} exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g.
 \citealt{Quimby2011, Gal-Yam2012}).
-Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citep{Li2011}.
+Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than \replyrick{typical} CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, \replyrick{which overlaps with} the bright end of the CCSN luminosity function \citep{Li2011}.
 The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly formed, rapidly rotating magnetar.
 
- Along with observations of the transients themselves, host galaxies are frequently-used laboratories from which strong inferences about the progenitor stars and explosion mechanisms can be made.
+ Along with observations of the transients themselves, \replyrick{studies of} host galaxies are frequently \replyrick{used to make strong inferences about the progenitor stars and explosion mechanisms}.
 CCSNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars.
@@
 Theory predicts that the production of a LGRB should only be possible in stars with a metallicity of $Z/Z_{\sun}\leq 0.3$ \citep{Woosley1993}  in order for the likely Wolf-Rayet or blue supergiant progenitors not to lose their outer atmospheres through metal-driven winds, thus conserving sufficient angular momentum to power the black-hole-driven jet or rapidly rotating magnetar.
-Many LGRB host galaxy studies have indeed revealed a metallicity threshold to be observed between 0.5 and 1 times the solar value \citep[e.g.][]{Stanek2006,Modjaz2008,Kruehler2015,Perley2016b,Japelj2016,Vergani2017}, although this is not a rigid cut.
-SLSN host galaxies also appear to be lower in metallicity than would be expected for their stellar mass, with a suppression of SLSN production at a value around half-solar \citep{Lunnan2014,Chen2016a,Perley2016c}.
-They also require a particularly high sSFR, suggesting that they are explosions of very young, rapidly rotating massive stars.
-
-Recently, inspection of high-cadence, large-area survey data sets have revealed yet more exotic transients that are less easy to explain with conventional models.
+Many LGRB host galaxy studies have indeed revealed a metallicity threshold between 0.5 and 1 times the solar value \citep[e.g.][]{Stanek2006,Modjaz2008,Kruehler2015,Perley2016b,Japelj2016,Vergani2017}, although this is not a rigid \replyrick{threshold}.
+SLSN host galaxies also appear to be lower in metallicity than would be expected for their stellar mass, with a suppression of SLSN production \replyrick{above a value of about} half-solar \citep{Lunnan2014,Chen2016a,Perley2016c}.
+\replyrick{Like LGRBs, SLSNe} also require a particularly high sSFR, suggesting that they are explosions of very young, rapidly rotating massive stars.
+
+Recently, inspection of high-cadence, large-area survey data sets have revealed more exotic transients that are \replyrick{difficult} to explain with conventional models.
 \citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
@@
 RETs typically rise to peak brightness in less than 10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
-The photometric measurements of the PS1 and DES RETs seem to be well described by simple expanding blackbodies, although a handful show declining photospheric radii from the outset.
+The photometric measurements of the PS1 and DES RETs seem to be well described by expanding blackbodies, although a handful show declining photospheric radii from the \replyrick{first detection}.
 Due to the rapid nature of their lightcurves and location at high-redshift, spectral coverage is sparse and signal-to-noise ratio (SNR) is low, such that there has not yet been a conclusive detection of absorption or emission features from the transients and thus the physical mechanism responsible for their rapid evolution remains unexplained.
 
-There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}.
-The transient declined from its discovery, with constraints on the rise time of 1 day, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}).
+There are a limited number of events detected in the local Universe whose properties appear consistent with the RETs seen at cosmological distances in the PS1 and DES samples, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}.
+The transient declined from its discovery, with constraints on the rise time of 1 day, and \replyrick{from X-rays through to radio wavelengths} did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}) .
 There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Uno2020}.
-Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
-It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.
+Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the \replyrick{accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger}, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
+It is currently unclear whether these transients represent the local analogues of the DES and PS\replyrick{1} RETs.
 
 In this paper, we present the first comprehensive study of the host galaxies of RETs.
-We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} by adding the 5th and final year of DES-SN observations as well as more refined discovery techniques.
-Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
+We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} by adding the 5th and final \replyrick{season} of DES-SN observations as well as more refined \replyrick{selection} techniques.
+Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties \replyrick{and} compare them to \replyrick{samples of host galaxies of} CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
 For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.
@@
 However, as the search was simplistic and relied heavily on visual inspection of the available data (etc.
-images, light curves, host galaxy information), it is impossible to be sure how complete the sample is.
-For instance, due to the large redshift range within the sample it is entirely possible that distant events could have been missed due to time dilation.
+images, light curves, host galaxy information), it is impossible to \replyrick{quantify the completeness of the sample}.
+For instance, due to the large redshift range within the sample it is entirely possible that distant events \replyrick{with longer rise times could have been missed due to time dilation stretching their lightcurves, while faster events and low redshift may evolve on timescales quicker than the survey cadence}.
 Here, a more sophisticated search method is presented.
-As only a fraction of transients in DES-SN have redshift information from their host galaxies, the search must be done in the observer frame.
-The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution and blue colour at peak.
-Even though both of these quantities depend on the redshift of the transient, they still seem to distinguish the the fast events from traditional SN types.
-
-To assess the unique photometric properties of RETs, we take the sample of 72 from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES, along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
+As only a fraction of transients in DES-SN have redshift information from their host galaxies, \replyrick{we perform the search} in the observer frame.
+The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution (rise to peak in $\lesssim15$ days) and blue colour at peak ($g-r \lesssim 0.5$).
+Even though both of these quantities depend on the redshift of the transient, they still effectively distinguish the the fast events from traditional SN types.
+We thus attempt to select a sample based on observed rise times and colours at peak brightness.
+
+\subsubsection{Gaussian processed lightcurves}
+Using observed photometric data points directly to infer rise time and colour has several problems that can be improved.
+For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights in the `deep' fields, thus making it impossible to measure the peak colour accurately.
+Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a lightcurve model.
+To negate this issue, we use interpolate the lightcurves of all DES-SN candidates using Gaussian Processes (GP) as presented in \citet{Pursiainen2020}.
+The interpolated lightcurves have a 0.5 day cadence and every epoch and band has a flux value and an associated uncertainty.
+
+\subsubsection{Photometric definition of RETs \label{subsubsec:trise_gr}}
+To make an improved selection of RETs we use a parameter space described by observed $g-r$ colour and the time taken to rise from non-detection to peak $r$-band magnitude in the observer frame.
+Using rise times and colours from GP lightcurves, we populate this parameter space with the sample of 72 RETs from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES.\replyrick{ We add spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe observed by DES in order to verify that they are rejected by the search method}.
+We keep objects passing the following criteria and disregard those that fail:
 \begin{enumerate}
-\item The transient was only detected in one DES-SN observing season.
-\item Maximum observed brightness in both $g$- and $r$-bands was brighter than 24 mag (in the eight `shallow' DES-SN fields) or 25 mag (in the two `deep' fields).
-\item $g$- and $r$-band observations used for the colour had to be taken within 2 days of each other in the observer frame.
+\item The transient was detected in \replyrick{only} one DES-SN observing season.
+\item Maximum observed brightness in both $g$- and $r$-bands was brighter than 24 mag (in the eight `shallow' DES-SN fields) or 25 mag (in the two `deep' fields), as in \citetalias{Pursiainen2018}.
+%\item $g$- and $r$-band observations used for the colour had to be taken within 2 days of each other in the observer frame.
 \end{enumerate}
 
-Of objects passing these cuts, the RETs cluster at shorter timescales and bluer colours than other SNe, even in the observer frame.
-However, using photometric data points directly has several problems that can be improved.
-For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights, thus making it impossible to measure the peak colour in a number of cases.
-Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range.
-To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citet{Pursiainen2020}.
-The interpolated light curves have a 0.5 day cadence and every epoch and band has a flux value, and an associated uncertainty.
-Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$ vs.
+ SNe Ia and RETs populate two distinct regions of $g-r$ vs.
 $t_{\mathrm{rise; r}}$ parameter space (Fig.
 \ref{fig:selection}), where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness.
+RETs appear bluer and faster than the typical SNe.
 We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
-The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig.
-\ref{fig:selection}.
-
-We process all $\sim 30,000$ DES-SN transient candidates with GP.
-In order to reduce the contamination from active galactic nuclei (AGN), we use a basic convolutional neural network (CNN) classifier.
-We train the CNN on spectroscopically confirmed SNe of all types and on spectroscopically typed AGN, and use it to separate the sample into two photometric subtypes: AGN-like and SNe-like.
-The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are removed by manual vetting.
-The SNe passing the CNN classifier are subjected to LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs.
-These objects are subject to a further set of cuts.
-We impose a cut based on a fit of the LC with the \texttt{PSNID} software \citep{Sako2008}.
-We use thresholds of \texttt{FITPROB}$<0.91$ and \texttt{PBAYES}$<0.82$ to remove highly-probably SNe Ia, which removes 46 objects from the RET parameter space.
+The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, \replyrick{corresponding to the red box in Fig.
+\ref{fig:selection}}.
+
+\subsubsection{Removal of active galactic nuclei \label{subsubsec:cnn}}
+
+In order to apply selection criterion i) from Section \ref{subsubsec:trise_gr} it is necessary to distinguish between DES-SN candidates that are truly multi-season events (typcially active galactic nuclei; AGN) and those that are single-season events with spurious detections in other seasons.
+To detect and filter out AGN we use a basic convolutional neural network (CNN) classifier.
+We train the CNN on spectroscopically confirmed SNe of all types as well as the 92 RETs identified using the \citetalias{Pursiainen2018} method (181 objects) and on spectroscopically typed AGN (182 objects), and use it to separate the sample into two photometric subtypes: AGN-like and SNe-like.
+The classifier returns SNe-like objects with an accuracy of 0.992 on the test set (391 SNe and 79 AGN).
+No SNe were classified as AGN-like.
+The remaining AGN classified as SNe-like are removed by manual vetting later in the process.
+
+\subsubsection{Final DES RET sample}
+The GP lightcurves of all DES-SN candidates are classified as AGN-like or SNe-like by the CNN, and are then subject to the lightcurve quality cuts i) and ii) (Section \ref{subsubsec:trise_gr}), resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined \replyrick{for} RETs.
+These objects are subject to a further set of cuts \replyrick{in order to remove remaining contaminants}.
+We impose a cut based on a fit of the lightcurve with the \texttt{PSNID} software \citep{Sako2008}.
+\replyrick{\texttt{PSNID} returns a normalised goodness of fit to different SN templates, along with a probability of it being a SN Ia given that it is a SN.
+To remove highly-probably SNe Ia, we use thresholds of $<0.91$ and $<0.82$ respectively to the above algorithms,} which removes 46 objects from the RET parameter space.
 In order to further remove longer-lived SNe, the decline time to half of the peak brightness must be $<24$ days.
 This removes 347 SNe, resulting in 546 objects remaining inside the parameter space.
-The final 546 transients have been visually inspected, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.
+The final 546 transients have been visually inspected by MP, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.
 
@@
 We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
-A selection of the host galaxies can be seen in Fig.
+A selection of the host galaxies \replyrick{is shown} in Fig.
 \ref{fig:mosaic}, centred on the location of the transient.
@@
 To compare with CCSNe, we draw on the untargetted sample of 47 SNe II from the Palomar Transient Factory (PTF; \citealt{Stoll2013}), which is likely complete in terms of hosts (all SNe have an associated host).
-While this sample lies at much lower redshift than the DES RETs (a maximum of 0.18 and mean of 0.05), redshift evolution is easier to account for than unknown incompleteness.
+While this sample lies at much lower redshift than the DES RETs (a maximum of 0.18 and mean of 0.05), redshift evolution is easier to account for \replyrick{in a less biased way than correcting for }unknown incompleteness.
 We add to this the compilation of 56 untargeted SESNe from \citet{Sanders2012}, with a maximum redshift of 0.26 and a mean of 0.05.
 Since \citet{Sanders2012} do not report host galaxy magnitudes, stellar masses or SFRs, we cross-match the SN positions with the the Sloan Digital Sky Survey (SDSS; \citealt{York2000}) Data Release 16 (DR16; \citealt{Ahumada2019}) and perform our own SED fit using the method outlined in Section \ref{subsec:sedfit}.
-We are able to do this for 38 objects, with the others lying outside of the SDSS footprint.
+We are able to do this \replyrick{SED fit} for 38 objects, with the others lying outside of the SDSS footprint.
 
@@
 The three curves show the delimitation between star formation and AGN at $z =0, 0.5, 1$ according to \citet{Kewley2013}.
+\replyrick{The redshift of the RETs is indicated by the colourbar on the right.}
 \label{fig:bpt}}
@@
 SFRs have not been corrected for redshift evolution.
-RET hosts lie slightly above the low-$z$ star-formation main sequence, and systematically avoid passive galaxies (dense contours in the lower right).
+RET hosts lie slightly above the low-$z$ star-formation main sequence \replyrick{upper half of the SDSS contours}, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
 \label{fig:sfms_sfr}}
@@
 \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
-We note than only 12 of the 45 RET host spectra have the necessary lines to plot a BPT diagram.
-This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence of AGN amongst the 11 hosts in those diagrams either.
+Only 12 of the 45 RET host spectra have the necessary lines to plot an \NII BPT diagram.
+This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence of AGN amongst the 12 hosts in those diagrams either.
 
 Due to the low S/N of the spectra in this sample, we are constrained to a subset of metallicity diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959/5007, \NII 6548/6583, and \SII 6717/6731.
-Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII~and \SII~are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta~lines available, mandating the use of the R23 diagnostic, which is based off the relative strengths of the \OII and \OIII lines.
+Furthermore, for each host galaxy only a subset of these lines \replyrick{is} detected - for example, \halpha, \NII~and \SII~are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta~lines available \replyrick{and thus the} R23 diagnostic, which is based off the relative strengths of the \OII and \OIII lines.
 For hosts at $z<0.3$ we are able to use the \OIII /\NII~(O3N2), \NII /\halpha~(N2), and \SII /\NII~(S2N2) line ratios.
@@
 Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS.
-RETs follow CCSNe, LGRBs and SLSNe in systematically avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
-One object, DES16C1cbd, lies among passive galaxies.
+RETs follow CCSNe, LGRBs and SLSNe in avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
+One object (DES16C1cbd) lies among passive galaxies.
 The spectrum of this object is red in colour, but does exhibit \OII~emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar.
-The individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs.
+The \replyrick{hosts of} individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs.
 SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.
@@
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR.
-Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments home to LGRBs or SLSNe.
+Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments \replyrick{of} LGRBs or SLSNe.
 
@@
 The mean difference is 0.6 dex.
-To test whether some of this could be attributed to the difference in redshift between the samples we apply a crude redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}.
-Correcting all SFRs to $z=0$ would result in the CCSN SFRs dropping by an average of 0.05 dex, while the RETs would decrease 0.35 dex, i.e.
+To test whether some of this could be attributed to the difference in redshift between the samples we apply \replyrick{an approximate} redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}.
+\replyrick{Transforming all host SFRs to their values at $z=0$} would result in the CCSN SFRs dropping by an average of 0.05 dex, while the RETs would decrease 0.35 dex, i.e.
 a difference of 0.30 dex, or half of the observed difference.
@@
 A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity.
-Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies.
+Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies.
 The cumulative distributions of metallicity are displayed in Fig.
@@
 It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift.
-However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a positive redshift detection compared to less enriched galaxies with the same mass and redshift.
-Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to eliminate this possible bias.
+However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a redshift detection compared to less enriched galaxies with the same mass and redshift.
+Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to \replyrick{reduce} this possible bias.
 
 Another possibility is that the hosts without a redshift are mostly non star-forming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}.
-In order to test this possibility, we examined the RETs that do not have a host galaxy redshift.
+To test this possibility, we examined the RETs that do not have a host galaxy redshift.
 Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process, and is summarised in Fig.
@@
 Similarly, a further 22 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found.
-The resulting redshift completeness of targetted objects is 71\% (83\% for objects brighter than $m_r = 24$~mag), which is in line with the average for OzDES as a whole \citep{Lidman2020}.
+The resulting redshift completeness of targetted objects is 71\% (83\% for objects brighter than $m_r = 24$~mag), which is in line with the average for OzDES \citep{Lidman2020}.
 In Fig.
@@
 The preference for low-metallicity systems is not as strong as for LGRBs or SLSNe, but the highest metallicities found in all three samples are very similar at around solar metallicity.
-This result is further suggestive of a stripped-envelope, massive-star origin for RETs.
+This result is suggestive of a stripped-envelope, massive-star origin for RETs.
 The population of RET hosts lies, on average, between CCSNe and LGRBs/SLSNe in terms of both star formation and metallicity.
-A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation.
-The rough rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
+A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation \replyrick{$-$ on average, rarer events occur in more extreme environments}.
+The \replyrick{approximate} rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
 At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohmaier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
-These figures place the DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching their location in host galaxy parameter space.
-While stressing that these associations are loose – rates are uncertain and host galaxy parameters span wide ranges for all transients – they are both linked to the respective transients' progenitor channels.
+These figures place the \replyrick{rate of} DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching \replyrick{the location of RET hosts in the various host galaxy parameter spaces presented in Section \ref{sec:analysis}}.
+While stressing rates are uncertain and host galaxy parameters span wide ranges for all transients, they are both linked to the respective transients' progenitor channels.
 Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSNe or LGRBs.
-It could therefore be possible that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
+\replyrick{This hypothesis also suggests} that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
 
@@
 Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies.
-For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFRs \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
+For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFRs \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSN \replyrick{lightcurves} that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
 In Fig.
-\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and lightcurve width parameterised as $t_{\mathrm{half}}$, the time the lightcurve is above half the peak brightness (lower panels), and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
-The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a simple blackbody SED.
+\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and lightcurve width parameterised as $t_{\mathrm{half}}$, the time the lightcurve is above half the peak brightness (lower panels), and \replyrick{their correlation with} host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
+The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a blackbody SED.
 There is no correlation between decline rate and either stellar mass or sSFR, while there are hints of a trend between peak magnitude and both mass and sSFR.
@@
 Assuming that these points are not outliers, the trends are still likely driven by selection effects.
-At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those redshifts only the more massive galaxies are detected.
-This effect can be seen in panel a) of Fig.
-\ref{fig:ret_v_host}, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in panel b.
-It is hoped that a complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) allowing the removal of these biases in order to reveal any underlying relationships.
+At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those \replyrick{high} redshifts only the more massive galaxies are detected.
+This effect can be seen in Fig.
+\ref{fig:ret_v_host}a, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in \replyrick{Fig.
+\ref{fig:ret_v_host}b}.
+It is hoped that a \replyrick{more} complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) in order to reveal any underlying relationships.
 
@@
 The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Fox2019,Mohan2020} due to its rapid evolution and blue colour.
-AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018} , developing to something entirely different later on \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.
+AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018} , developing to something entirely different \replyrick{at later epochs} \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.
 There have been several suggestions that AT2018cow is indeed an analogue of the high-z RETs.
-The host galaxy of AT2018cow appears to be moderately star forming and lies very close to the centre of the SFMS (\citealt{Lyman2020}; Figs.
+The host galaxy of AT2018cow \replyrick{is} to be moderately star forming and lies very close to the centre of the SFMS (\citealt{Lyman2020}; Figs.
 \ref{fig:sfms_sfr},\ref{fig:sfms_ssfr}), along with many of the DES RET hosts.

### 2020-05-14 RET_Hosts_CWR.tex
Updates from Overleaf

@@
 
+\subsection{The DES supernova programme \label{subsec:desdata}}
+
+\replyrick{The Dark Energy Survey (DES) makes use of the Dark Energy Camera (DECam; \citealt{Flaugher2015}) to survey $5000\deg^2$ of the southern sky between 2013 and 2019.
+The supernova programme (DES-SN), designed primarily to perform cosmology with type Ia SNe \citep{Bernstein2012}, consisted of five 6-month seasons of approximately 7 day cadence \citep{DAndrea2018}} in ten single pointings, known as the SN fields.
+Of these fields, two were observed with longer exposure times and are referred to as deep fields; the remaining eight are labelled shallow.
+Transient detection was performed by difference imaging using a custom pipeline \citep{Kessler2015}.
+Transient candidates were vetted via machine-learning techniques \citep{Goldstein2015}, leading to $\sim 30,000$ viable supernova candidates over the full five seasons.
+A full description of the search for rapid transients in DES can be found in \citetalias{Pursiainen2018}.
+
 \subsection{Improvements to the search method \label{subsec:new_method}}
@@
 
-To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based on the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
+To show how RETs compare to the galaxy population as a whole, we use \replyrick{a sample of $\sim800,000$ measurements from the} MPA-JHU catalogues of stellar masses (based on the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
 The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample.
@@
 
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
-\caption{The $M_*$ - SFR sequence of RET hosts, hosts of other transients, and SDSS field galaxies (grey contours).
-SFRs have not been corrected for redshift evolution.
-RET hosts lie slightly above the low-$z$ star-formation main sequence \replyrick{upper half of the SDSS contours}, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
-\label{fig:sfms_sfr}}
-\end{figure}
-
-%\begin{figure}
-%\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
-%\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
-%\label{fig:sfr_cum}}
-%\end{figure}
-
 \subsection{Estimating metallicities \label{subsec:calc_Z}}
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
-\caption{The $M_*$ - sSFR sequence of RET hosts and comparison samples, along with the SDSS field galaxies.
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_RETs.png}
+\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, and SDSS field galaxies (grey contours).
+SFRs have not been corrected for redshift evolution.
+RET hosts lie slightly above the low-$z$ star-formation main sequence \replyrick{upper half of the SDSS contours}, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
+\label{fig:sfms_sfr}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_Other.png}
+\caption{Same as Fig. \ref{fig:sfms_sfr}, but comparing RET hosts with hosts of SESNe, LGRBs and SLSNe, and SDSS field galaxies (grey contours).
+\label{fig:sfms_sfr_other}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_RETs.png}
+\caption{The $M_* -$ sSFR sequence of RET hosts as well as local rapid transients and SNe II, along with the SDSS field galaxies.
 \label{fig:sfms_ssfr}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_other.png}
+\caption{Same as Fig. \ref{fig:sfms_ssfr} but comparing RET hosts with hosts of SESN, LGRB, and SLSN hosts, along with the SDSS field galaxies.
+\label{fig:sfms_ssfr_other}}
 \end{figure}
@@
 \subsection{Star formation rate \label{subsec:res_sfr}}
-Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS.
+Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, \replyrick{split in two for clarity,} show the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS.
 RETs follow CCSNe, LGRBs and SLSNe in avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
@@
 
-Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
+Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR.

### 2020-05-15 RET_Hosts_CWR.tex

@@
 \replyrick{The Dark Energy Survey (DES) makes use of the Dark Energy Camera (DECam; \citealt{Flaugher2015}) to survey $5000\deg^2$ of the southern sky between 2013 and 2019.
-The supernova programme (DES-SN), designed primarily to perform cosmology with type Ia SNe \citep{Bernstein2012}, consisted of five 6-month seasons of approximately 7 day cadence \citep{DAndrea2018}} in ten single pointings, known as the SN fields.
+The supernova programme (DES-SN), designed primarily to detect type Ia SNe (SNe Ia) for cosmological measurements \citep{Bernstein2012}, consisted of five 6-month seasons of approximately 7 day cadence \citep{DAndrea2018}} in ten single pointings, known as the SN fields which cover a total area of $\sim27 \deg^2$.
 Of these fields, two were observed with longer exposure times and are referred to as deep fields; the remaining eight are labelled shallow.
@@
 
-In order to apply selection criterion i) from Section \ref{subsubsec:trise_gr} it is necessary to distinguish between DES-SN candidates that are truly multi-season events (typcially active galactic nuclei; AGN) and those that are single-season events with spurious detections in other seasons.
+In order to apply selection criterion i) from Section \ref{subsubsec:trise_gr} it is necessary to distinguish between DES-SN candidates that are truly multi-season events (typically active galactic nuclei; AGN) and those that are single-season events with spurious detections in other seasons.
 To detect and filter out AGN we use a basic convolutional neural network (CNN) classifier.
@@
 This removes 347 SNe, resulting in 546 objects remaining inside the parameter space.
-The final 546 transients have been visually inspected by MP, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.
+The final 546 transients have been visually inspected, with the majority rejected for \replyrick{clearly} being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing a longer timescale decline.
 
@@
 
+\begin{table}
+    \centering
+    \caption{\replyrick{Summary statistics for the samples compared in this work.
+Here we show the mean and standard deviation of the stellar mass, sSFR, and oxygen abundance, but note that the values for these parameters are not necessarily normally distributed for each sample.} }
+    \begin{tabular}{lccc}
+    \toprule
+   Sample & $\langle\log \left(M_*\right)\rangle$ &  $\langle\log \left(\mathrm{sSFR}\right)\rangle$ &$\langle12+\log\left(\mathrm{O/H}\right) \rangle$\\
+   \midrule
+   {} & $\left( M_{\odot}\right)$ & $\left(\mathrm{yr}^{-1} \right)$& \\
+   \midrule
+   DES RETs &$9.9 \pm 0.8$ & $-9.6 \pm 0.6 $ &$ 8.4 \pm 0.2$ \\
+    PS1 RETs &$9.0 \pm 0.8$ & $-9.2 \pm 0.8 $ &$ 8.5 \pm 0.2$ \\
+    SNe II &$9.8 \pm 0.8$ & $-9.8 \pm 0.7 $ &$ 8.6 \pm 0.2$ \\
+    SESNe &$9.5 \pm 0.9$ & $-10.2 \pm 1.0 $ &$ 8.4 \pm 0.2$ \\
+    LGRBs &$9.2 \pm 0.6$ & $-8.9 \pm 0.8 $ &$ 8.4 \pm 0.2$ \\
+    SLSNe &$8.5 \pm 0.9$ & $-8.7 \pm 0.9 $ &$ 8.3 \pm 0.2$ \\
+\bottomrule
+    \end{tabular}
+
+    \label{tab:summary}
+\end{table}
+
 \begin{figure}
@@
 \label{sec:analysis} % used for referring to this section from elsewhere
+\replyrick{A summary of the masses, sSFRs and metallicities for the hosts of DES RETs and various comparison samples is presented in Table \ref{tab:summary}.
+In the following sections, we compare the host galaxy properties of RETs to each sample in detail.
+}
 
@@
 This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.
+\replyrick{We thus believe that the results presented from the subset of hosts with measured redshifts are at the very least representative of the star-forming nature of the population of RET hosts}.
 

### 2020-05-16 author_list_16_May.tex
Final edits

--- 2020-05-07 author_list_07_May.tex
@@
 % Author list file generated with: mkauthlist.py 0+unknown 
-% mkauthlist.py -f -a order.csv -j mnras -sb author_list_07_May.csv author_list_07_May.tex
+% mkauthlist.py -f -a DES-RET-Hosts/order.csv -s -j mnras DES-RET-Hosts/author_list_16_May.csv DES-RET-Hosts/author_list_16_May.tex
 
@@
 S.~Everett,$^{7}$
+P.~Fosalba,$^{31,32}$
 J.~Frieman,$^{16,9}$
-J.~Garc\'ia-Bellido,$^{31}$
-E.~Gaztanaga,$^{32,33}$
+J.~Garc\'ia-Bellido,$^{33}$
+E.~Gaztanaga,$^{31,32}$
 K.~Glazebrook,$^{34}$
@@
 G.~Gutierrez,$^{16}$
+D.~L.~Hollowood,$^{7}$
 K.~Honscheid,$^{36,37}$
@@
 E.~Sanchez,$^{23}$
+V.~Scarpine,$^{16}$
 M.~Schubnell,$^{46}$
-S.~Serrano,$^{32,33}$
+S.~Serrano,$^{31,32}$
 I.~Sevilla-Noarbe,$^{23}$
@@
 $^{30}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
-$^{31}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
-$^{32}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
-$^{33}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
+$^{31}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
+$^{32}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
+$^{33}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
 $^{34}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\

### 2020-05-16 DES_RET_Hosts_submit.tex

--- 2020-05-15 RET_Hosts_CWR.tex
@@
 \usepackage{lineno}
-\linenumbers
+%\linenumbers
 % MNRAS is set in Times font. If you don't have this installed (most LaTeX
@@
 \usepackage[dvipsnames]{xcolor}
-\usepackage{subcaption}
+\usepackage{caption}
+%\usepackage{subcaption}
 \usepackage{multicol}
-\usepackage{wrapfig}
+%\usepackage{wrapfig}
 \usepackage{ctable}
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[DES Collaboration]{
+\author[P. S. Wiseman]{
 \parbox{\textwidth}{
@@
 Their evolution on fast timescales has hindered high quality follow-up observations, and thus their origin and explosion/emission mechanism remains unexplained.
-In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the first substantial analysis of RET host galaxies.
+In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the most comprehensive analysis of RET host galaxies.
 Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 37.
@@
 In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe).
-CCSNe can be split into observationally-determinded subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \citep{Minkowski1941}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
+CCSNe can be split into observationally-determined subclasses based on their lightcurve and spectral evolution: SNe II display hydrogen features in their spectra \citep{Minkowski1941}, and are thought to occur in stars that retain a large fraction of their hydrogen envelope.
 Conversely, SNe Ib and Ic do not show signatures of hydrogen \citep[e.g.][]{Filippenko1997} and are thus referred to collectively as stripped-envelope SNe (SESNe), having undergone a partial removal of their outer atmospheres.
 The SN IIb subclass, which shows hydrogen only at early epochs that disappears after a few weeks \citep{Filippenko1988}, is also commonly grouped along with SESNe.
-\replyrick{SNe IIn display much narrower hydrogen emission lines when compared to standard SNe II \citep{Schlegel1990}.
-The narrow emission originates from the ejecta impacting on slow-moving circumstellar material (CSM)}.
+SNe IIn display much narrower hydrogen emission lines when compared to standard SNe II \citep{Schlegel1990}.
+The narrow emission originates from the ejecta impacting on slow-moving circumstellar material (CSM).
 Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
@@
 Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, which themselves make up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.
-\replyrick{Another} exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g.
+Another exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g.
 \citealt{Quimby2011, Gal-Yam2012}).
-Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than \replyrick{typical} CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, \replyrick{which overlaps with} the bright end of the CCSN luminosity function \citep{Li2011}.
+Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than typical CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, which overlaps with the bright end of the CCSN luminosity function \citep{Li2011}.
 The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly formed, rapidly rotating magnetar.
 
- Along with observations of the transients themselves, \replyrick{studies of} host galaxies are frequently \replyrick{used to make strong inferences about the progenitor stars and explosion mechanisms}.
+ Along with observations of the transients themselves, studies of host galaxies are frequently used to make strong inferences about the progenitor stars and explosion mechanisms.
 CCSNe are confined almost exclusively to galaxies hosting recent or ongoing star formation, due to their origin from massive stars.
@@
 On average, SESNe reside in galaxies with higher specific star-formation rates (sSFRs; \citealt{James2006,Kelly2008}), while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Anderson2012,Galbany2018}.
-More extreme events tend to occur in galaxies low in mass and high in sSFR, with both GRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
+More extreme events tend to occur in galaxies low in mass and high in sSFR, with both LGRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
 
@@
 Theory predicts that the production of a LGRB should only be possible in stars with a metallicity of $Z/Z_{\sun}\leq 0.3$ \citep{Woosley1993}  in order for the likely Wolf-Rayet or blue supergiant progenitors not to lose their outer atmospheres through metal-driven winds, thus conserving sufficient angular momentum to power the black-hole-driven jet or rapidly rotating magnetar.
-Many LGRB host galaxy studies have indeed revealed a metallicity threshold between 0.5 and 1 times the solar value \citep[e.g.][]{Stanek2006,Modjaz2008,Kruehler2015,Perley2016b,Japelj2016,Vergani2017}, although this is not a rigid \replyrick{threshold}.
-SLSN host galaxies also appear to be lower in metallicity than would be expected for their stellar mass, with a suppression of SLSN production \replyrick{above a value of about} half-solar \citep{Lunnan2014,Chen2016a,Perley2016c}.
-\replyrick{Like LGRBs, SLSNe} also require a particularly high sSFR, suggesting that they are explosions of very young, rapidly rotating massive stars.
-
-Recently, inspection of high-cadence, large-area survey data sets have revealed more exotic transients that are \replyrick{difficult} to explain with conventional models.
+Many LGRB host galaxy studies have indeed revealed a metallicity threshold between 0.5 and 1 times the solar value \citep[e.g.][]{Stanek2006,Modjaz2008,Kruehler2015,Perley2016b,Japelj2016,Vergani2017}, although this is not a rigid threshold.
+SLSN host galaxies also appear to be lower in metallicity than would be expected for their stellar mass, with a suppression of SLSN production above a value of about half-solar \citep{Lunnan2014,Chen2016a,Perley2016c}.
+Like LGRBs, SLSNe also require a particularly high sSFR, suggesting that they are explosions of very young, rapidly rotating massive stars.
+
+Recently, inspection of high-cadence, large-area survey data sets have revealed more exotic transients that are difficult to explain with conventional models.
 \citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
@@
 RETs typically rise to peak brightness in less than 10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
-The photometric measurements of the PS1 and DES RETs seem to be well described by expanding blackbodies, although a handful show declining photospheric radii from the \replyrick{first detection}.
+The photometric measurements of the PS1 and DES RETs seem to be well described by expanding blackbodies, although a handful show declining photospheric radii from the first detection.
 Due to the rapid nature of their lightcurves and location at high-redshift, spectral coverage is sparse and signal-to-noise ratio (SNR) is low, such that there has not yet been a conclusive detection of absorption or emission features from the transients and thus the physical mechanism responsible for their rapid evolution remains unexplained.
@@
 There are a limited number of events detected in the local Universe whose properties appear consistent with the RETs seen at cosmological distances in the PS1 and DES samples, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}.
-The transient declined from its discovery, with constraints on the rise time of 1 day, and \replyrick{from X-rays through to radio wavelengths} did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}) .
+The transient declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}) .
 There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Uno2020}.
-Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the \replyrick{accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger}, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
-It is currently unclear whether these transients represent the local analogues of the DES and PS\replyrick{1} RETs.
+Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
+It is currently unclear whether these transients represent the local analogues of the DES and PS1 RETs.
 
 In this paper, we present the first comprehensive study of the host galaxies of RETs.
-We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} by adding the 5th and final \replyrick{season} of DES-SN observations as well as more refined \replyrick{selection} techniques.
-Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties \replyrick{and} compare them to \replyrick{samples of host galaxies of} CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
+We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} by adding the 5th and final season of DES-SN observations as well as more refined selection techniques.
+Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties and compare them to samples of host galaxies of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
 For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.
@@
 
-\replyrick{The Dark Energy Survey (DES) makes use of the Dark Energy Camera (DECam; \citealt{Flaugher2015}) to survey $5000\deg^2$ of the southern sky between 2013 and 2019.
-The supernova programme (DES-SN), designed primarily to detect type Ia SNe (SNe Ia) for cosmological measurements \citep{Bernstein2012}, consisted of five 6-month seasons of approximately 7 day cadence \citep{DAndrea2018}} in ten single pointings, known as the SN fields which cover a total area of $\sim27 \deg^2$.
-Of these fields, two were observed with longer exposure times and are referred to as deep fields; the remaining eight are labelled shallow.
+The Dark Energy Survey (DES) makes use of the Dark Energy Camera (DECam; \citealt{Flaugher2015}) to survey $5000\deg^2$ of the southern sky between 2013 and 2019.
+The supernova programme (DES-SN), designed primarily to detect type Ia SNe (SNe Ia) for cosmological measurements \citep{Bernstein2012}, consisted of five 6-month seasons of approximately 7 day cadence in ten single pointings, known as the SN fields which cover a total area of $\sim27 \deg^2$.
+Of these fields, two were observed with longer exposure times and are referred to as deep fields with remaining eight known as shallow fields; the resulting approximate single-visit depths are 23.5 mag (shallow) and 24.5 mag (deep) in the DES $r$-band.
 Transient detection was performed by difference imaging using a custom pipeline \citep{Kessler2015}.
 Transient candidates were vetted via machine-learning techniques \citep{Goldstein2015}, leading to $\sim 30,000$ viable supernova candidates over the full five seasons.
+DES-SN included an extensive spectroscopic follow-up program to identify transients and measure spectroscopic redshifts of host galaxies \citep{DAndrea2018}.
 A full description of the search for rapid transients in DES can be found in \citetalias{Pursiainen2018}.
@@
 However, as the search was simplistic and relied heavily on visual inspection of the available data (etc.
-images, light curves, host galaxy information), it is impossible to \replyrick{quantify the completeness of the sample}.
-For instance, due to the large redshift range within the sample it is entirely possible that distant events \replyrick{with longer rise times could have been missed due to time dilation stretching their lightcurves, while faster events and low redshift may evolve on timescales quicker than the survey cadence}.
+images, light curves, host galaxy information), it is impossible to quantify the completeness of the sample.
+For instance, due to the large redshift range within the sample it is entirely possible that distant events with longer rise times could have been missed due to time dilation stretching their lightcurves, while faster events and low redshift may evolve on timescales quicker than the survey cadence.
 Here, a more sophisticated search method is presented.
-As only a fraction of transients in DES-SN have redshift information from their host galaxies, \replyrick{we perform the search} in the observer frame.
+As only a fraction of transients in DES-SN have redshift information from their host galaxies, we perform the search in the observer frame.
 The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution (rise to peak in $\lesssim15$ days) and blue colour at peak ($g-r \lesssim 0.5$).
@@
 Using observed photometric data points directly to infer rise time and colour has several problems that can be improved.
-For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights in the `deep' fields, thus making it impossible to measure the peak colour accurately.
-Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a lightcurve model.
-To negate this issue, we use interpolate the lightcurves of all DES-SN candidates using Gaussian Processes (GP) as presented in \citet{Pursiainen2020}.
+For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights in the `deep' fields, thus adding larger uncertainty in the peak colour estimate.
+We do not have a light curve model for RETs, and therefore  measuring a 10-15 day rise time is difficult with a one week  cadence.
+Rather than fitting with a physically motivated model, we instead interpolate the lightcurves of all DES-SN candidates using Gaussian Processes (GP) as presented in \citet{Pursiainen2020}.
 The interpolated lightcurves have a 0.5 day cadence and every epoch and band has a flux value and an associated uncertainty.
@@
 To make an improved selection of RETs we use a parameter space described by observed $g-r$ colour and the time taken to rise from non-detection to peak $r$-band magnitude in the observer frame.
-Using rise times and colours from GP lightcurves, we populate this parameter space with the sample of 72 RETs from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES.\replyrick{ We add spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe observed by DES in order to verify that they are rejected by the search method}.
-We keep objects passing the following criteria and disregard those that fail:
+Using rise times and colours from GP lightcurves, we populate this parameter space with the sample of 72 RETs from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES.
+We add spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe observed by DES in order to verify that they are rejected by the search method.
+We keep objects passing the following selection requirements (cuts):
 \begin{enumerate}
-\item The transient was detected in \replyrick{only} one DES-SN observing season.
+\item The transient was detected in only one DES-SN observing season.
 \item Maximum observed brightness in both $g$- and $r$-bands was brighter than 24 mag (in the eight `shallow' DES-SN fields) or 25 mag (in the two `deep' fields), as in \citetalias{Pursiainen2018}.
@@
  SNe Ia and RETs populate two distinct regions of $g-r$ vs.
-$t_{\mathrm{rise; r}}$ parameter space (Fig.
-\ref{fig:selection}), where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness.
+$t_{\mathrm{rise; r}}$ parameter space (Fig.~\ref{fig:selection}), where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness.
 RETs appear bluer and faster than the typical SNe.
 We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness).
-The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, \replyrick{corresponding to the red box in Fig.
-\ref{fig:selection}}.
+The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, corresponding to the red box in Fig.~\ref{fig:selection}.
 
@@
 To detect and filter out AGN we use a basic convolutional neural network (CNN) classifier.
-We train the CNN on spectroscopically confirmed SNe of all types as well as the 92 RETs identified using the \citetalias{Pursiainen2018} method (181 objects) and on spectroscopically typed AGN (182 objects), and use it to separate the sample into two photometric subtypes: AGN-like and SNe-like.
+We train the CNN on spectroscopically confirmed SNe of all types as well as the 92 RETs identified using the \citetalias{Pursiainen2018} method (181 objects) and on spectroscopically typed AGN (182 objects), and use it to separate the sample into two photometric subtypes: AGN-like and SN-like.
 The classifier returns SNe-like objects with an accuracy of 0.992 on the test set (391 SNe and 79 AGN).
@@
 The remaining AGN classified as SNe-like are removed by manual vetting later in the process.
+The CNN does not separate the SN-like objects into RETs and other SN subtypes: this is done in the subsequent processing step.
 
 \subsubsection{Final DES RET sample}
-The GP lightcurves of all DES-SN candidates are classified as AGN-like or SNe-like by the CNN, and are then subject to the lightcurve quality cuts i) and ii) (Section \ref{subsubsec:trise_gr}), resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined \replyrick{for} RETs.
-These objects are subject to a further set of cuts \replyrick{in order to remove remaining contaminants}.
-We impose a cut based on a fit of the lightcurve with the \texttt{PSNID} software \citep{Sako2008}.
-\replyrick{\texttt{PSNID} returns a normalised goodness of fit to different SN templates, along with a probability of it being a SN Ia given that it is a SN.
-To remove highly-probably SNe Ia, we use thresholds of $<0.91$ and $<0.82$ respectively to the above algorithms,} which removes 46 objects from the RET parameter space.
+The GP lightcurves of all DES-SN candidates are classified as AGN-like or SNe-like by the CNN, and are then subject to the lightcurve quality cuts i) and ii) (Section \ref{subsubsec:trise_gr}), resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined for RETs.
+These objects are subject to a further set of cuts in order to remove remaining contaminants.
+We impose a cut based on a SN classifier (\texttt{PSNID}; \citealt{Sako2008}), that returns a normalised goodness of fit to different SN Ia and CCSN templates, along with a Bayesian probability of it being a SN Ia.
+To remove highly-probable SNe Ia, we use threshold probabilities of P(Ia)$<0.91$ and P(Ia; Bayes)$<0.82$ respectively to the above algorithms, which removes 46 objects from the RET parameter space.
 In order to further remove longer-lived SNe, the decline time to half of the peak brightness must be $<24$ days.
 This removes 347 SNe, resulting in 546 objects remaining inside the parameter space.
-The final 546 transients have been visually inspected, with the majority rejected for \replyrick{clearly} being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing a longer timescale decline.
+The final 546 transients have been visually inspected, with the majority rejected for clearly being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing a longer timescale decline.
 
@@
 We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
-A selection of the host galaxies \replyrick{is shown} in Fig.
-\ref{fig:mosaic}, centred on the location of the transient.
+A selection of the host galaxies is shown in Fig.~\ref{fig:mosaic}, centred on the location of the transient.
 The figure showcases the diversity of host galaxy morphologies and colours, while also displaying the limitations of ground-based observations of high-redshift, relatively small galaxies in terms of spatial resolution.
-Fig.
-\ref{fig:z_dist} shows the distribution of redshifts amongst the 49 hosts for which such a measurement was possible.
+Fig.~\ref{fig:z_dist} shows the distribution of redshifts amongst the 49 hosts for which such a measurement was possible.
 The effect that the redshift selection function has on the results is discussed in Section \ref{subsec:disc_bias}.
@@
 To compare with CCSNe, we draw on the untargetted sample of 47 SNe II from the Palomar Transient Factory (PTF; \citealt{Stoll2013}), which is likely complete in terms of hosts (all SNe have an associated host).
-While this sample lies at much lower redshift than the DES RETs (a maximum of 0.18 and mean of 0.05), redshift evolution is easier to account for \replyrick{in a less biased way than correcting for }unknown incompleteness.
+While this sample lies at much lower redshift than the DES RETs (a maximum of 0.18 and mean of 0.05), redshift evolution is easier to account for in a less biased way than correcting for unknown incompleteness.
 We add to this the compilation of 56 untargeted SESNe from \citet{Sanders2012}, with a maximum redshift of 0.26 and a mean of 0.05.
 Since \citet{Sanders2012} do not report host galaxy magnitudes, stellar masses or SFRs, we cross-match the SN positions with the the Sloan Digital Sky Survey (SDSS; \citealt{York2000}) Data Release 16 (DR16; \citealt{Ahumada2019}) and perform our own SED fit using the method outlined in Section \ref{subsec:sedfit}.
-We are able to do this \replyrick{SED fit} for 38 objects, with the others lying outside of the SDSS footprint.
+We are able to do this SED fit for 38 objects, with the others lying outside of the SDSS footprint.
 
@@
 
-To show how RETs compare to the galaxy population as a whole, we use \replyrick{a sample of $\sim800,000$ measurements from the} MPA-JHU catalogues of stellar masses (based on the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
+To show how RETs compare to the galaxy population as a whole, we use a sample of $\sim800,000$ measurements from the MPA-JHU catalogues of stellar masses (based on the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}).
 The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample.
@@
 The three curves show the delimitation between star formation and AGN at $z =0, 0.5, 1$ according to \citet{Kewley2013}.
-\replyrick{The redshift of the RETs is indicated by the colourbar on the right.}
+The redshift of each RET is indicated by the colourbar on the right.
 \label{fig:bpt}}
@@
 By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines.
-An example of this procedure is shown in Fig.
-\ref{fig:host_spec}.
+An example of this procedure is shown in Fig.~\ref{fig:host_spec}.
 We fit the emission lines with Gaussian profiles.
@@
 \midrule
-DES13X3gms &   $9.41 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.27}$ &  $-0.06 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.78}$ &   $-9.47 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.52}$ &  $8.55 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.37}$ &                                                             - &                                                             - &                                                             - &  $8.55 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.37}$ &   $8.22 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.35}$ \\
-DES13C1tgd &  $10.24 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &   $0.10 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.38}$ &  $-10.14 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &  $8.64 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.06}$ &  $8.59 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &  $8.68 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &   $8.75 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
-DES13S2wxf &   $9.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.06}$ &   $0.29 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.10}$ &   $-9.57 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.58 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &  $8.58 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.27}$ &   $8.25 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.25}$ \\
-DES13X1hav &   $9.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.38}$ &  $-0.44 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.93}$ &   $-9.60 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.55}$ &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &                                                             - &                                                             - &                                                             - &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &   $8.20 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.36}$ \\
-DES13X3nyg &   $9.31 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.42}$ &   $0.05 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.73}$ &   $-9.27 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &  $8.46 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.12}$ &                                                             - &                                                             - &                                                             - &  $8.46 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.12}$ &   $8.18 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.07}$ \\
+DES13C1tgd  &  $10.24 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &   $0.10 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.38}$ &  $-10.14 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &  $8.67 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.18}$ &  $8.62 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.18}$ &  $8.72 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.16}$ &                                                             - &                                                             - &     $8.80 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle -}$ \\
+DES13C3bcok &  $11.57 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.11}$ &   $1.20 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.49}$ &  $-10.37 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.38}$ &  $8.99 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.08}$ &                                                             - &                                                             - &                                                             - &  $8.99 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.08}$ &  $8.66 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.10}$ \\
+DES13C3uig  &  $10.28 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.23}$ &   $0.59 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.40}$ &   $-9.68 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.16}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
+DES13E2lpk  &  $10.66 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.10}$ &   $0.46 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.45}$ &  $-10.20 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.35}$ &  $8.89 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.89 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.09}$ &  $8.54 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.11}$ \\
+DES13S2wxf  &   $9.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.06}$ &   $0.29 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.10}$ &   $-9.57 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $7.62 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 0.62}$ &                                                             - &                                                             - &                                                             - &  $7.62 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 0.62}$ &                                                             - \\
+DES13X1hav  &   $9.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.38}$ &  $-0.44 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.93}$ &   $-9.60 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.55}$ &  $8.62 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.24}$ &                                                             - &                                                             - &                                                             - &  $8.62 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.24}$ &  $8.28 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.24}$ \\
+DES13X2wvv  &   $9.79 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.34}$ &   $0.19 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.25}$ &   $-9.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.91}$ &  $8.68 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &                                                             - &  $8.68 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.15}$ &  $8.33 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.16}$ \\
 DES13X3gmd  &  $10.33 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.44}$ &   $0.74 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.86}$ &   $-9.59 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.42}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES13X2wvv &   $9.79 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.34}$ &   $0.19 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.25}$ &   $-9.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.91}$ &  $8.41 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &  $8.41 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.27}$ &   $8.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.16}$ \\
-DES14S2anq &   $9.41 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.23}$ &  $-0.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.54}$ &   $-9.75 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.32}$ &  $8.34 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.02}$ &  $8.16 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &  $8.34 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.35 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.02}$ &  $8.36 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &   $8.29 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ \\
+DES13X3gms  &   $9.41 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.27}$ &  $-0.06 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.78}$ &   $-9.47 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.52}$ &  $8.51 _{\scriptscriptstyle 0.96} ^{\scriptscriptstyle 0.50}$ &                                                             - &                                                             - &                                                             - &  $8.51 _{\scriptscriptstyle 0.96} ^{\scriptscriptstyle 0.50}$ &  $8.21 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.48}$ \\
+DES13X3npb  &  $11.02 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.18}$ &   $1.14 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 1.35}$ &   $-9.88 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 1.17}$ &  $8.72 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.23}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.23}$ &  $8.37 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.26}$ \\
+DES13X3nyg  &   $9.31 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.42}$ &   $0.05 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.73}$ &   $-9.27 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &  $7.69 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.61}$ &                                                             - &                                                             - &                                                             - &  $7.69 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.61}$ &                                                             - \\
+DES14C3tnz  &  $10.21 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.41}$ &   $0.78 _{\scriptscriptstyle 0.60} ^{\scriptscriptstyle 0.88}$ &   $-9.44 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.47}$ &  $8.38 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.42}$ &                                                             - &                                                             - &                                                             - &  $8.38 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.42}$ &  $8.15 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.29}$ \\
+DES14C3tvw  &  $11.09 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &   $1.02 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.39}$ &  $-10.07 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.29}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
+DES14S2anq  &   $9.41 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.23}$ &  $-0.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.54}$ &   $-9.75 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.32}$ &  $8.34 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.02}$ &  $8.16 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &  $8.34 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.35 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &  $8.36 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.29 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ \\
+DES14S2plb  &  $10.36 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.25}$ &   $0.89 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.77}$ &   $-9.47 _{\scriptscriptstyle 0.40} ^{\scriptscriptstyle 0.52}$ &  $8.65 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.29}$ &  $8.65 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.06}$ &  $8.63 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.62 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &  $8.95 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.04}$ &  $8.64 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.04}$ \\
+DES14S2pli  &  $10.27 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.34}$ &   $0.50 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.61}$ &   $-9.77 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.27}$ &  $8.95 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &                                                             - &                                                             - &                                                             - &  $8.95 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &  $8.61 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.07}$ \\
 DES14X1bnh  &  $11.71 _{\scriptscriptstyle 0.69} ^{\scriptscriptstyle 0.25}$ &   $1.53 _{\scriptscriptstyle 0.95} ^{\scriptscriptstyle 0.52}$ &  $-10.18 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES15S1fli &  $10.24 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.26}$ &   $1.54 _{\scriptscriptstyle 1.01} ^{\scriptscriptstyle 0.67}$ &   $-8.70 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.41}$ &  $8.79 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.05}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.05}$ &   $8.44 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.06}$ \\
-DES15S1fll &   $9.20 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.32}$ &  $-0.14 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.54}$ &   $-9.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.22}$ &  $8.34 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.32}$ &  $8.38 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.36}$ &  $8.32 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.16}$ &  $8.27 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.13}$ &  $8.59 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.57}$ &   $8.29 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.31}$ \\
-DES14X3pkl &   $9.60 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.26}$ &   $0.26 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.72}$ &   $-9.34 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.46}$ &  $8.37 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.13}$ &  $8.20 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &  $8.48 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.06}$ &                                                             - &                                                             - &   $8.52 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.07}$ \\
-DES13X3npb &  $11.02 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.18}$ &   $1.14 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 1.35}$ &   $-9.88 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 1.17}$ &  $8.98 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.05}$ &                                                             - &                                                             - &                                                             - &  $8.98 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.05}$ &   $8.65 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ \\
-DES15X2ead &   $9.92 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.20}$ &   $0.22 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.47}$ &   $-9.69 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.27}$ &  $8.47 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.13}$ &  $8.23 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.09}$ &  $8.48 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.52 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.08}$ &  $8.67 _{\scriptscriptstyle 0.66} ^{\scriptscriptstyle 0.33}$ &  $8.45 _{\scriptscriptstyle -0.00} ^{\scriptscriptstyle 0.16}$ \\
-DES14S2plb &  $10.36 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.25}$ &   $0.89 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.77}$ &   $-9.47 _{\scriptscriptstyle 0.40} ^{\scriptscriptstyle 0.52}$ &  $8.62 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.33}$ &  $8.59 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.60 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.63 _{\scriptscriptstyle 0.00} ^{\scriptscriptstyle 0.00}$ &  $8.96 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &   $8.64 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ \\
-DES14S2pli &  $10.27 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.34}$ &   $0.50 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.61}$ &   $-9.77 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.27}$ &  $8.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &                                                             - &  $8.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &   $8.52 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ \\
-DES14C3tnz &  $10.21 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.41}$ &   $0.78 _{\scriptscriptstyle 0.60} ^{\scriptscriptstyle 0.88}$ &   $-9.44 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.47}$ &  $8.68 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.68 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 0.26}$ &   $8.33 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ \\
-DES15X3mxf &   $9.93 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.32}$ &   $0.78 _{\scriptscriptstyle 1.18} ^{\scriptscriptstyle 0.90}$ &   $-9.15 _{\scriptscriptstyle 0.88} ^{\scriptscriptstyle 0.58}$ &  $8.57 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.11}$ &                                                             - &                                                             - &                                                             - &  $8.57 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.11}$ &   $8.24 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.09}$ \\
-DES15C3lpq &   $9.32 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.39}$ &   $0.86 _{\scriptscriptstyle 0.73} ^{\scriptscriptstyle 1.08}$ &   $-8.45 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.68}$ &  $8.59 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.59 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.26}$ &   $8.25 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.25}$ \\
+DES14X3pkl  &   $9.60 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.26}$ &   $0.26 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.72}$ &   $-9.34 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.46}$ &  $8.38 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.20}$ &  $8.22 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.23}$ &  $8.48 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &  $8.52 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ \\
+DES15C2eal  &   $8.42 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.18}$ &  $-1.29 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.33}$ &   $-9.72 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.15}$ &  $8.30 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.25}$ &  $8.04 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.32}$ &  $8.32 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.19}$ &  $8.34 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.15}$ &  $8.39 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.50}$ &  $8.28 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.25}$ \\
+DES15C3lpq  &   $9.32 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.39}$ &   $0.86 _{\scriptscriptstyle 0.73} ^{\scriptscriptstyle 1.08}$ &   $-8.45 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.68}$ &  $8.30 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.33}$ &                                                             - &                                                             - &                                                             - &  $8.30 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.33}$ &  $8.15 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.14}$ \\
+DES15C3lzm  &  $10.06 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.28}$ &   $1.08 _{\scriptscriptstyle 0.68} ^{\scriptscriptstyle 0.75}$ &   $-8.98 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.47}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
+DES15C3mem  &  $10.76 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.37}$ &   $1.04 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.64}$ &   $-9.72 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
+DES15C3mgq  &   $8.41 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.29}$ &  $-1.12 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.55}$ &   $-9.53 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &  $8.37 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.29}$ &  $8.45 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.48}$ &  $8.43 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.24}$ &  $8.34 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.11}$ &  $8.34 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.39}$ &  $8.32 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.20}$ \\
 DES15C3nat  &  $10.49 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.58}$ &   $1.14 _{\scriptscriptstyle 0.60} ^{\scriptscriptstyle 0.98}$ &   $-9.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.41}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES15C3mgq &   $8.41 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.29}$ &  $-1.12 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.55}$ &   $-9.53 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &  $8.33 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.25}$ &  $8.29 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.51}$ &  $8.38 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.17}$ &  $8.29 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.11}$ &  $8.37 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.46}$ &   $8.28 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.21}$ \\
-DES15E2nqh &   $9.28 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.28}$ &   $0.11 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.94}$ &   $-9.17 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.66}$ &  $8.50 _{\scriptscriptstyle 0.76} ^{\scriptscriptstyle 0.37}$ &                                                             - &                                                             - &                                                             - &  $8.50 _{\scriptscriptstyle 0.76} ^{\scriptscriptstyle 0.37}$ &   $8.20 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.32}$ \\
-DES15C3opk &   $9.89 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.22}$ &   $0.89 _{\scriptscriptstyle 1.20} ^{\scriptscriptstyle 0.67}$ &   $-9.01 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.45}$ &  $8.68 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &  $8.68 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.27}$ &   $8.33 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.29}$ \\
-DES15C3opp &   $9.15 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.32}$ &   $0.13 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.84}$ &   $-9.02 _{\scriptscriptstyle 0.57} ^{\scriptscriptstyle 0.52}$ &  $8.59 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.19}$ &                                                             - &                                                             - &                                                             - &  $8.59 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.19}$ &   $8.25 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.17}$ \\
-DES16E2pv  &   $9.57 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.43}$ &   $0.07 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.98}$ &   $-9.50 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.55}$ &  $8.53 _{\scriptscriptstyle 0.74} ^{\scriptscriptstyle 0.35}$ &                                                             - &                                                             - &                                                             - &  $8.53 _{\scriptscriptstyle 0.74} ^{\scriptscriptstyle 0.35}$ &   $8.21 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.32}$ \\
-DES16S1bbp &   $9.06 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &   $0.30 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.79}$ &   $-8.75 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.49}$ &  $8.26 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.08}$ &  $8.14 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.17}$ &  $8.26 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.30 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.19 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.20}$ &  $8.28 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle -0.01}$ \\
-DES16X3cxn &   $9.55 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.57}$ &  $-0.32 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 1.00}$ &   $-9.88 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.43}$ &  $8.53 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.25}$ &                                                             - &                                                             - &                                                             - &  $8.53 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.25}$ &   $8.21 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.21}$ \\
-DES16C1cbd &  $10.77 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.22}$ &  $-1.43 _{\scriptscriptstyle 1.94} ^{\scriptscriptstyle 1.48}$ &  $-12.20 _{\scriptscriptstyle 1.79} ^{\scriptscriptstyle 1.26}$ &  $8.72 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.11}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.11}$ &   $8.36 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.11}$ \\
-DES16X3ega &   $9.94 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.18}$ &   $0.30 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.26}$ &   $-9.64 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.08}$ &  $8.58 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ &  $8.43 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.17}$ &  $8.47 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &  $8.61 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.07}$ &  $8.77 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.06}$ &   $8.51 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.08}$ \\
-DES16X3erw &   $9.89 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &   $0.94 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.62}$ &   $-8.94 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.36}$ &  $8.72 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.09}$ &   $8.37 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.09}$ \\
-DES16C3gin &   $9.85 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &   $0.45 _{\scriptscriptstyle 0.68} ^{\scriptscriptstyle 1.00}$ &   $-9.41 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.68}$ &  $8.80 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.80 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.09}$ &   $8.44 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.10}$ \\
-DES16S1dxu &   $8.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.41}$ &  $-0.49 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 1.70}$ &   $-9.09 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.29}$ &  $8.27 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.19}$ &  $8.25 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.43}$ &  $8.22 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.12}$ &  $8.26 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.09}$ &  $8.37 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.20}$ &   $8.21 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.10}$ \\
+DES15C3opk  &   $9.89 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.22}$ &   $0.89 _{\scriptscriptstyle 1.20} ^{\scriptscriptstyle 0.67}$ &   $-9.01 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.45}$ &  $8.57 _{\scriptscriptstyle 0.80} ^{\scriptscriptstyle 0.33}$ &                                                             - &                                                             - &                                                             - &  $8.57 _{\scriptscriptstyle 0.80} ^{\scriptscriptstyle 0.33}$ &  $8.24 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.31}$ \\
+DES15C3opp  &   $9.15 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.32}$ &   $0.13 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.84}$ &   $-9.02 _{\scriptscriptstyle 0.57} ^{\scriptscriptstyle 0.52}$ &  $8.45 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.32}$ &                                                             - &                                                             - &                                                             - &  $8.45 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.32}$ &  $8.17 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.24}$ \\
+DES15E2nqh  &   $9.28 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.28}$ &   $0.11 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.94}$ &   $-9.17 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.66}$ &  $8.83 _{\scriptscriptstyle 0.52} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &                                                             - &  $8.83 _{\scriptscriptstyle 0.52} ^{\scriptscriptstyle 0.15}$ &  $8.48 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.17}$ \\
+DES15S1fli  &  $10.24 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.26}$ &   $1.54 _{\scriptscriptstyle 1.01} ^{\scriptscriptstyle 0.67}$ &   $-8.70 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.41}$ &  $8.86 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &                                                             - &                                                             - &                                                             - &  $8.86 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &  $8.52 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.07}$ \\
+DES15S1fll  &   $9.20 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.32}$ &  $-0.14 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.54}$ &   $-9.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.22}$ &  $8.26 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.23}$ &  $8.37 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.36}$ &  $8.28 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.13}$ &  $8.22 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.10}$ &  $8.26 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.34}$ &  $8.22 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.12}$ \\
+DES15X2ead  &   $9.92 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.20}$ &   $0.22 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.47}$ &   $-9.69 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.27}$ &  $8.45 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.23}$ &  $8.22 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.25}$ &  $8.47 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.15}$ &  $8.52 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.14}$ &  $8.61 _{\scriptscriptstyle 0.77} ^{\scriptscriptstyle 0.38}$ &  $8.43 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.24}$ \\
+DES15X3mxf  &   $9.93 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.32}$ &   $0.78 _{\scriptscriptstyle 1.18} ^{\scriptscriptstyle 0.90}$ &   $-9.15 _{\scriptscriptstyle 0.88} ^{\scriptscriptstyle 0.58}$ &  $8.72 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.15}$ &  $8.36 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.16}$ \\
+DES16C1cbd  &  $10.77 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.22}$ &  $-1.43 _{\scriptscriptstyle 1.94} ^{\scriptscriptstyle 1.48}$ &  $-12.20 _{\scriptscriptstyle 1.79} ^{\scriptscriptstyle 1.26}$ &  $8.79 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.20}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.20}$ &  $8.44 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.22}$ \\
+DES16C2ggt  &   $9.86 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.36}$ &   $0.13 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.94}$ &   $-9.73 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.59}$ &  $8.50 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.33}$ &  $8.28 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.17}$ &  $8.45 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.10}$ &  $8.51 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.05}$ &  $8.85 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.06}$ &  $8.50 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ \\
+DES16C3axz  &   $9.85 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.33}$ &   $0.20 _{\scriptscriptstyle 0.56} ^{\scriptscriptstyle 0.78}$ &   $-9.65 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.44}$ &  $8.59 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.37}$ &  $8.53 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.56 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &  $8.59 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &  $8.97 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.03}$ &  $8.61 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
+DES16C3gin  &   $9.85 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &   $0.45 _{\scriptscriptstyle 0.68} ^{\scriptscriptstyle 1.00}$ &   $-9.41 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.68}$ &  $8.84 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.12}$ &                                                             - &                                                             - &                                                             - &  $8.84 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.12}$ &  $8.49 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.14}$ \\
+DES16E2pv   &   $9.57 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.43}$ &   $0.07 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.98}$ &   $-9.50 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.55}$ &  $8.93 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.11}$ &                                                             - &                                                             - &                                                             - &  $8.93 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.11}$ &  $8.59 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.13}$ \\
+DES16S1bbp  &   $9.06 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &   $0.30 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.79}$ &   $-8.75 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.49}$ &  $8.25 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.10}$ &  $8.11 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.25}$ &  $8.25 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.07}$ &  $8.31 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.05}$ &  $8.24 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.13}$ &  $8.24 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.04}$ \\
+DES16S1dxu  &   $8.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.41}$ &  $-0.49 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 1.70}$ &   $-9.09 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.29}$ &  $8.26 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.12}$ &  $8.33 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.38}$ &  $8.24 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.11}$ &  $8.27 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.07}$ &  $8.27 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.10}$ &  $8.22 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.07}$ \\
 DES16X1eho  &  $10.70 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.42}$ &   $0.01 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 1.33}$ &  $-10.69 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.91}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES17C3gop &   $9.90 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.58}$ &   $0.19 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.86}$ &   $-9.71 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ &  $8.61 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.34}$ &                                                             - &                                                             - &                                                             - &  $8.61 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.34}$ &   $8.27 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.34}$ \\
-DES17S2fee &  $11.20 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.22}$ &   $0.28 _{\scriptscriptstyle 1.91} ^{\scriptscriptstyle 0.70}$ &  $-10.92 _{\scriptscriptstyle 1.77} ^{\scriptscriptstyle 0.48}$ &  $8.59 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.21}$ &  $8.39 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.78 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &                                                             - &                                                             - &      $8.86 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle -}$ \\
+DES16X3cxn  &   $9.55 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.57}$ &  $-0.32 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 1.00}$ &   $-9.88 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.43}$ &  $8.79 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.16}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.16}$ &  $8.43 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.18}$ \\
+DES16X3ega  &   $9.94 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.18}$ &   $0.30 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.26}$ &   $-9.64 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.08}$ &  $8.58 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ &  $8.44 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.17}$ &  $8.47 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &  $8.61 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.07}$ &  $8.77 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &  $8.51 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.08}$ \\
+DES16X3erw  &   $9.89 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &   $0.94 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.62}$ &   $-8.94 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.36}$ &  $8.84 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.84 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.09}$ &  $8.49 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.10}$ \\
+DES17C2hno  &   $9.56 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.16}$ &  $-0.02 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.33}$ &   $-9.58 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.17}$ &  $8.78 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.17}$ &                                                             - &                                                             - &                                                             - &  $8.78 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.17}$ &  $8.43 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.19}$ \\
+DES17C3fwd  &  $10.07 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.23}$ &   $0.84 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.50}$ &   $-9.22 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.27}$ &  $8.34 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.12}$ &                                                             - &  $8.35 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.18}$ &  $8.38 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.08}$ &  $8.29 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.11}$ &  $8.30 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.10}$ \\
+DES17C3gop  &   $9.90 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.58}$ &   $0.19 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.86}$ &   $-9.71 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ &  $8.79 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.21}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.21}$ &  $8.43 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.24}$ \\
+DES17S2fee  &  $11.20 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.22}$ &   $0.28 _{\scriptscriptstyle 1.91} ^{\scriptscriptstyle 0.70}$ &  $-10.92 _{\scriptscriptstyle 1.77} ^{\scriptscriptstyle 0.48}$ &  $8.75 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.52}$ &  $8.55 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.42}$ &  $8.95 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.47}$ &                                                             - &                                                             - &                                                             - \\
+DES17X3cds  &   $9.36 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.31}$ &  $-0.18 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.83}$ &   $-9.53 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.52}$ &  $8.69 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.69 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.26}$ &  $8.33 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ \\
 DES17X3dxu  &  $10.49 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.22}$ &   $1.02 _{\scriptscriptstyle 0.69} ^{\scriptscriptstyle 0.63}$ &   $-9.47 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.40}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES17X3cds &   $9.36 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.31}$ &  $-0.18 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.83}$ &   $-9.53 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.52}$ &  $8.76 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.20}$ &                                                             - &                                                             - &                                                             - &  $8.76 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.20}$ &   $8.41 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.22}$ \\
-DES17X3hxi &   $8.60 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.00}$ &  $-0.37 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.10}$ &   $-8.96 _{\scriptscriptstyle 0.00} ^{\scriptscriptstyle 0.10}$ &  $8.55 _{\scriptscriptstyle 0.82} ^{\scriptscriptstyle 0.36}$ &                                                             - &                                                             - &                                                             - &  $8.55 _{\scriptscriptstyle 0.82} ^{\scriptscriptstyle 0.36}$ &   $8.22 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.34}$ \\
-DES13E2lpk &  $10.66 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.10}$ &   $0.46 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.45}$ &  $-10.20 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.35}$ &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &                                                             - &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &   $8.58 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
-DES15C2eal &   $8.42 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.18}$ &  $-1.29 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.33}$ &   $-9.72 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.15}$ &  $8.29 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.25}$ &  $7.97 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.29}$ &  $8.29 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.15}$ &  $8.34 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.15}$ &  $8.52 _{\scriptscriptstyle 0.49} ^{\scriptscriptstyle 0.57}$ &   $8.28 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.30}$ \\
-DES16C2ggt &   $9.86 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.36}$ &   $0.13 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.94}$ &   $-9.73 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.59}$ &  $8.53 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.39}$ &  $8.37 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.51 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &  $8.54 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.93 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &   $8.56 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ \\
-DES17C2hno &   $9.56 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.16}$ &  $-0.02 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.33}$ &   $-9.58 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.17}$ &  $8.94 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.94 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.09}$ &   $8.60 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.11}$ \\
+DES17X3hxi  &   $8.60 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.00}$ &  $-0.37 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.10}$ &   $-8.96 _{\scriptscriptstyle 0.00} ^{\scriptscriptstyle 0.10}$ &  $8.45 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.45 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.26}$ &  $8.18 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ \\
 
@@
 Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation.
-Using the Baldwin-Phillips-Terlevich diagram (Fig.
-\ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
+Using the Baldwin-Phillips-Terlevich diagram (Fig.~\ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.
 Only 12 of the 45 RET host spectra have the necessary lines to plot an \NII BPT diagram.
@@
 Due to the low S/N of the spectra in this sample, we are constrained to a subset of metallicity diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959/5007, \NII 6548/6583, and \SII 6717/6731.
-Furthermore, for each host galaxy only a subset of these lines \replyrick{is} detected - for example, \halpha, \NII~and \SII~are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta~lines available \replyrick{and thus the} R23 diagnostic, which is based off the relative strengths of the \OII and \OIII lines.
+Furthermore, for each host galaxy only a subset of these lines is detected - for example, \halpha, \NII~and \SII~are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta~lines available and thus the R23 diagnostic, which is based off the relative strengths of the \OII and \OIII lines.
 For hosts at $z<0.3$ we are able to use the \OIII /\NII~(O3N2), \NII /\halpha~(N2), and \SII /\NII~(S2N2) line ratios.
@@
 We take $1\sigma$ uncertainties from the 16\textsuperscript{th} and 84\textsuperscript{th} percentiles of these PDFs, and for DES RETs display the results in Table \ref{tab:derived}.
+\begin{figure}
+
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_RETs.png}
+\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, and SDSS field galaxies (grey contours).
+SFRs have not been corrected for redshift evolution.
+RET hosts lie slightly above the low-$z$ star-formation main sequence upper half of the SDSS contours, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
+\label{fig:sfms_sfr}}
+\end{figure}
+
+\section{Analysis}
+\label{sec:analysis} % used for referring to this section from elsewhere
+A summary of the masses, sSFRs and metallicities for the hosts of DES RETs and various comparison samples is presented in Table \ref{tab:summary}.
+In the following sections, we compare the host galaxy properties of RETs to each sample in detail.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_Other.png}
+\caption{Same as Fig.~\ref{fig:sfms_sfr}, but comparing RET hosts with hosts of SESNe, LGRBs and SLSNe, and SDSS field galaxies (grey contours).
+\label{fig:sfms_sfr_other}}
+\end{figure}
+
+\subsection{Star formation rate \label{subsec:res_sfr}}
+Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, split in two for clarity, show the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS.
+RETs follow CCSNe, LGRBs and SLSNe in avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
+One object (DES16C1cbd) lies among passive galaxies.
+The spectrum of this object is red in colour, but does exhibit \OII~emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar.
+The hosts of individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs.
+SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.
+SNLS04D4ec is consistent with the peak of the DES RET mass and SFR distributions.
+
+Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
+It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR.
+Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments of LGRBs or SLSNe.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_RETs.png}
+\caption{The $M_* -$ sSFR sequence of RET hosts as well as local rapid transients and SNe II, along with the SDSS field galaxies.
+\label{fig:sfms_ssfr}}
+\end{figure}
+
+We show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}.
+The RET hosts are clearly shifted to higher sSFRs than CCSNe.
+To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citetalias{Wiseman2020}.
+For each pair of samples, we model the PDFs as skewed normal distributions described by the parameters `loc' (location, identical to the mean for zero skewness), `scale' (spread, identical to the standard deviation for zero skewness)\footnote{See \citetalias{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'.
+To impose priors on loc and scale, we combine the two samples and use normal priors centred on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centred on 0.
+We note that the loc parameter describes the location of the distribution (its relative position on the x-axis) and is not a mean, median, or mode.
+A highly-skewed distribution may have a loc that lies above almost the entire sample.
+A worked example as well as the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
+
+The comparison shows RET hosts to be shifted to higher sSFRs than CCSNe.
+In 98\% of the posterior samples the RET sSFR distribution loc was at a higher value than SNe II, while the same was true 95\% of the time for RETs when comparing with SESNe.
+The mean difference is 0.6 dex.
+To test whether some of this could be attributed to the difference in redshift between the samples we apply an approximate redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}.
+Transforming all host SFRs to their values at $z=0$ would result in the CCSN SFRs dropping by an average of 0.05 dex, while the RETs would decrease 0.35 dex, i.e.
+a difference of 0.30 dex, or half of the observed difference.
+The remaining 0.30 dex is thus consistent with being an intrinsic difference.
+RET host galaxies are significantly lower in sSFR than LGRBs.
+While the distributions are similar in shape, with a mean difference in scale of 0.09, the mean difference in loc is -1.16, with no overlap between the posterior distributions.
+The sSFR distribution of SLSNe hosts is much broader than the RETs, with a scale of 1.12, twice that of the RETs.
+They are also shifted to higher sSFRs than RETs, with the loc of the distribution on average 0.76 dex greater than RETs.
+The strong high-sSFR tail shows SLSNe occur in a different galaxy population to RETs.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_other.png}
+\caption{Same as Fig.~\ref{fig:sfms_ssfr} but comparing RET hosts with hosts of SESN, LGRB, and SLSN hosts, along with the SDSS field galaxies.
+\label{fig:sfms_ssfr_other}}
+\end{figure}
+
+\subsection{Metallicity \label{subsec:res_metallicity}}
+
+In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars.
+A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity.
+Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies.
+The cumulative distributions of metallicity are displayed in Fig.~\ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies.
+The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe.
+The metallicity distribution of SESNe is, however, quite broad \citep[e.g.][]{Anderson2010}, with different subclasses showing different trends (with SNe Ic host environments exhibiting higher metallicity than Ib, and IIb much lower).
+RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
+
+We compare the metallicity distributions in the same way as the sSFRs, with the distribution fits shown in Appendix \ref{app:c}.
+The RET host metallicity distribution shows a broad peak, leading to two families of skewed-Gaussians that fit it well, one with a low-valued centre  ($12 + \log \mathrm{(O/H)} \sim 8.1$) and a positive skew, and the other with a higher-valued centre ($12 + \log \mathrm{(O/H)} \sim 8.6$).
+Comparing the DES RETs to the \citet{Stoll2013} SNe II shows the latter to be centred around 8.8, with the centre being greater than the RETs in 94\% of samples.
+We determine that the RET host metallicities are derived from a different population to the SNe II.
+On the other hand, simultaneous fits with SESNe show very similar distributions, including a smaller higher-metallicity peak, such that they are indistinguishable statistically.
+
+The median CDFs of LGRBs and SLSNe show divergence from the RETs, particularly at low metallicity.
+As a result, the locs of their fits are shifted compared to the RETs.
+In 67\% of samples, the RET sample had a higher loc than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
+While these effects are not as significant as with the RETs - SNe II comparison, there is mild evidence that RETs are located in galaxies with higher metal content than LGRBs.
+The effect is more pronounced for SLSNe, where the RETs have a higher metallicity for the distribution peak 92\% of the time.
+The SLSN distribution is also more strongly skewed, with 89\% of the posterior distribution being more strongly skewed than the RETs.
+There is thus mild-to-strong evidence that RETs occur in more metal-rich environments than SLSNe.
+
+In Fig.~\ref{fig:mzr} we show the MZR for the RET and comparison samples.
+The contours show the MZR for low-redshift ($\hat{z}=0.08$) star-forming galaixes from SDSS, adjusted to the PP04 O3N2 diagnostic.
+We use the MZR parameterisation \citet{Zahid2014} to show the best fit to the MZR for star-forming galaxies.
+The blue dashed line shows the fit to the low-z data, while the green dashed line corresponds to the MZR at $z=0.45$, the mean redshift of the RET host sample.
+The RET hosts lie systematically below the galaxy MZR fits as well as the bulk of the SDSS galaxies, meaning that for a given stellar mass they have a lower metallicity.
+They populate similar regions to SESNe, LGRBs and SLSNe but are clearly offset from the SNe II.
+SN2018gep, the Koala, and SNLS04D4ec appear in line with the RETs, while the Cow lies quite distinctly above the MZR, and is even outside the bulk of the local field galaxies.
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
+\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample. Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
+\label{fig:ssfr_cum}}
+\end{figure}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
+\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, hosts of the comparison samples, and the SDSS sample.
+Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
+\label{fig:oh_cum}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
+\caption{The mass-metallicity relation (MZR) for RET host galaxies and comparison samples.
+Upward- and downward-pointing triangles reflect lower and upper limits respectively.
+The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.
+The dashed lines represent MZR parameterisations from \citet{Zahid2014}.
+\label{fig:mzr}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
+\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES.
+The orange histogram represents the 96/106 DES RETs for which a host was detected.
+The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
+\label{fig:mag_dist}}
+\end{figure}
 
@@
     \centering
-    \caption{\replyrick{Summary statistics for the samples compared in this work.
-Here we show the mean and standard deviation of the stellar mass, sSFR, and oxygen abundance, but note that the values for these parameters are not necessarily normally distributed for each sample.} }
+    \caption{Summary statistics for the samples compared in this work.
+Here we show the mean and standard deviation of the stellar mass, sSFR, and oxygen abundance, but note that the values for these parameters are not necessarily normally distributed for each sample.
+}
     \begin{tabular}{lccc}
@@
 \end{table}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_RETs.png}
-\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, and SDSS field galaxies (grey contours).
-SFRs have not been corrected for redshift evolution.
-RET hosts lie slightly above the low-$z$ star-formation main sequence \replyrick{upper half of the SDSS contours}, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
-\label{fig:sfms_sfr}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_Other.png}
-\caption{Same as Fig. \ref{fig:sfms_sfr}, but comparing RET hosts with hosts of SESNe, LGRBs and SLSNe, and SDSS field galaxies (grey contours).
-\label{fig:sfms_sfr_other}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_RETs.png}
-\caption{The $M_* -$ sSFR sequence of RET hosts as well as local rapid transients and SNe II, along with the SDSS field galaxies.
-\label{fig:sfms_ssfr}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_other.png}
-\caption{Same as Fig. \ref{fig:sfms_ssfr} but comparing RET hosts with hosts of SESN, LGRB, and SLSN hosts, along with the SDSS field galaxies.
-\label{fig:sfms_ssfr_other}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
-\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample. Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
-\label{fig:ssfr_cum}}
-\end{figure}
-
-\section{Analysis}
-\label{sec:analysis} % used for referring to this section from elsewhere
-\replyrick{A summary of the masses, sSFRs and metallicities for the hosts of DES RETs and various comparison samples is presented in Table \ref{tab:summary}.
-In the following sections, we compare the host galaxy properties of RETs to each sample in detail.
-}
-
-\subsection{Star formation rate \label{subsec:res_sfr}}
-Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, \replyrick{split in two for clarity,} show the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS.
-RETs follow CCSNe, LGRBs and SLSNe in avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
-One object (DES16C1cbd) lies among passive galaxies.
-The spectrum of this object is red in colour, but does exhibit \OII~emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar.
-The \replyrick{hosts of} individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs.
-SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.
-SNLS04D4ec is consistent with the peak of the DES RET mass and SFR distributions.
-
-Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
-It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR.
-Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments \replyrick{of} LGRBs or SLSNe.
-
-We show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}.
-The RET hosts are clearly shifted to higher sSFRs than CCSNe.
-To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citetalias{Wiseman2020}.
-For each pair of samples, we model the PDFs as skewed normal distributions described by the parameters `loc' (location, identical to the mean for zero skewness), `scale' (spread, identical to the standard deviation for zero skewness)\footnote{See \citetalias{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'.
-To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0.
-We note that the loc parameter describes the location of the distribution (its relative position on the x-axis) and is not a mean, median, or mode.
-A highly-skewed distribution may have a loc that lies above almost the entire sample.
-A worked example as well as the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.
-
-The comparison shows RET hosts to be shifted to higher sSFRs than CCSNe.
-In 98\% of the posterior samples the RET sSFR distribution loc was at a higher value than SNe II, while the same was true 95\% of the time for RETs when comparing with SESNe.
-The mean difference is 0.6 dex.
-To test whether some of this could be attributed to the difference in redshift between the samples we apply \replyrick{an approximate} redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}.
-\replyrick{Transforming all host SFRs to their values at $z=0$} would result in the CCSN SFRs dropping by an average of 0.05 dex, while the RETs would decrease 0.35 dex, i.e.
-a difference of 0.30 dex, or half of the observed difference.
-The remaining 0.30 dex is thus consistent with being an intrinsic difference.
-RET host galaxies are significantly lower in sSFR than LGRBs.
-While the distributions are similar in shape, with a mean difference in scale of 0.09, the mean difference in loc is -1.16, with no overlap between the posterior distributions.
-The sSFR distribution of SLSNe hosts is much broader than the RETs, with a scale of 1.12, twice that of the RETs.
-They are also shifted to higher sSFRs than RETs, with the loc of the distribution on average 0.76 dex greater than RETs.
-The strong high-sSFR tail shows SLSNe occur in a different galaxy population to RETs.
-
-\subsection{Metallicity \label{subsec:res_metallicity}}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
-\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, hosts of the comparison samples, and the SDSS sample.
-Uncertainties have been estimated via a bootstrap Monte-Carlo technique and include limits.
-\label{fig:oh_cum}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
-\caption{The mass-metallicity relation (MZR) for RET host galaxies and comparison samples.
-Upward- and downward-pointing triangles reflect lower and upper limits respectively.
-The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.
-The dashed lines represent MZR parameterisations from \citet{Zahid2014}.
-\label{fig:mzr}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
-\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES.
-The orange histogram represents the 96/106 DES RETs for which a host was detected.
-The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
-\label{fig:mag_dist}}
-\end{figure}
-
-In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars.
-A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity.
-Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies.
-The cumulative distributions of metallicity are displayed in Fig.
-\ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies.
-The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe.
-The metallicity distribution of SESNe is, however, quite broad \citep[e.g.][]{Anderson2010}, with different subclasses showing different trends (with SNe Ic host environments exhibiting higher metallicity than Ib, and IIb much lower).
-RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
-
-We compare the metallicity distributions in the same way as the sSFRs, with the distribution fits shown in Appendix \ref{app:c}.
-The RET host metallicity distribution shows a broad peak, leading to two families of skewed-Gaussians that fit it well, one with a low-valued centre  ($12 + \log \mathrm{(O/H)} \sim 8.1$) and a positive skew, and the other with a higher-valued centre ($12 + \log \mathrm{(O/H)} \sim 8.6$).
-Comparing the DES RETs to the \citet{Stoll2013} SNe II shows the latter to be centred around 8.8, with the centre being greater than the RETs in 94\% of samples.
-We determine that the RET host metallicities are derived from a different population to the SNe II.
-On the other hand, simultaneous fits with SESNe show very similar distributions, including a smaller higher-metallicity peak, such that they are indistinguishable statistically.
-
-The median CDFs of LGRBs and SLSNe show divergence from the RETs, particularly at low metallicity.
-As a result, the locs of their fits are shifted compared to the RETs.
-In 67\% of samples, the RET sample had a higher loc than the LGRBS, with RETs also showing a broader distribution 67\% of the time.
-While these effects are not as significant as with the RETs - SNe II comparison, there is mild evidence that RETs are located in galaxies with higher metal content than LGRBs.
-The effect is more pronounced for SLSNe, where the RETs have a higher metallicity for the distribution peak 92\% of the time.
-The SLSN distribution is also more strongly skewed, with 89\% of the posterior distribution being more strongly skewed than the RETs.
-There is thus mild-to-strong evidence that RETs occur in more metal-rich environments than SLSNe.
-
-In Fig.~\ref{fig:mzr} we show the MZR for the RET and comparison samples.
-The contours show the MZR for low-redshift ($\hat{z}=0.08$) star-forming galaixes from SDSS, adjusted to the PP04 O3N2 diagnostic.
-We use the MZR parameterisation \citet{Zahid2014} to show the best fit to the MZR for star-forming galaxies.
-The blue dashed line shows the fit to the low-z data, while the green dashed line corresponds to the MZR at $z=0.45$, the mean redshift of the RET host sample.
-The RET hosts lie systematically below the galaxy MZR fits as well as the bulk of the SDSS galaxies, meaning that for a given stellar mass they have a lower metallicity.
-They populate similar regions to SESNe, LGRBs and SLSNe but are clearly offset from the SNe II.
-SN2018gep, the Koala, and SNLS04D4ec appear in line with the RETs, while the Cow lies quite distinctly above the MZR, and is even outside the bulk of the local field galaxies.
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/mag_v_colour.png}
-\caption{The colour-magnitude distribution of RET hosts with (cyan) and without (orange) redshifts. There is an excess of objects with blue colours that do not have redshift measurements.
-\label{fig:g-i}}
-\end{figure}
-
 \section{Discussion}
-\label{sec:disc}
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/RET_vs_host.png}
-\caption{RET lightcurve properties as a function of host galaxy measurements.
-\label{fig:ret_v_host}}
-\end{figure}
+
 \subsection{Selection Biases \label{subsec:disc_bias}}
@@
 However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a redshift detection compared to less enriched galaxies with the same mass and redshift.
-Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to \replyrick{reduce} this possible bias.
+Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to reduce this possible bias.
 
@@
 To test this possibility, we examined the RETs that do not have a host galaxy redshift.
-Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process, and is summarised in Fig.
-\ref{fig:mag_dist}.
+Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process, and is summarised in Fig.~\ref{fig:mag_dist}.
 Of the 57 objects without a redshift, 47 of them have host galaxies detected in the SN Deep coadds of \citetalias{Wiseman2020}.
-Of more significance is that only 40 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign.
+Of more significance is that only 40 have host galaxies in the SVA1 catalogues which were used for targeting during the OzDES campaign.
 The other, `hostless', objects are either transients that are located remotely from a galaxy that was detected, or are hosted by a galaxy that was not detected.
@@
 Neither are expected to be systematically higher in metallicity than the detected hosts.
-Similarly, a further 22 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found.
-The resulting redshift completeness of targetted objects is 71\% (83\% for objects brighter than $m_r = 24$~mag), which is in line with the average for OzDES \citep{Lidman2020}.
-In Fig.
-\ref{fig:g-i} we show the observer-frame $r$-band magnitudes and $g-i$ colours for all RET hosts that were detected.
+Similarly, a further 22 hosts were detected but not targeted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found.
+The resulting redshift completeness of targeted objects is 71\% (83\% for objects brighter than $m_r = 24$~mag), which is in line with the average for OzDES \citep{Lidman2020}.
+In Fig.~\ref{fig:g-i} we show the observer-frame $r$-band magnitudes and $g-i$ colours for all RET hosts that were detected.
 The 47 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts.
 This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.
-\replyrick{We thus believe that the results presented from the subset of hosts with measured redshifts are at the very least representative of the star-forming nature of the population of RET hosts}.
+We thus conclude that the results presented from the subset of hosts with measured redshifts are at the very least representative of the star-forming nature of the population of RET hosts.
 
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/mag_v_colour.png}
+\caption{The colour-magnitude distribution of RET hosts with (cyan) and without (orange) redshifts. There is an excess of objects with blue colours that do not have redshift measurements.
+\label{fig:g-i}}
+\end{figure}
+
 \subsection{Origin of RETs \label{subsec:disc_origin}}
@@
 The sample of DES RETs shows a preference for low-metallicity, strongly star-forming host environments.
-The PDF of their metallcities displays a strong similarity to the hosts of SESNe, as well as LGRBs.
+The PDF of their metallicities displays a strong similarity to the hosts of SESNe, as well as LGRBs.
 There is a clear difference to the PDF of SNe II, which follow SDSS field galaxies.
@@
 The population of RET hosts lies, on average, between CCSNe and LGRBs/SLSNe in terms of both star formation and metallicity.
-A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation \replyrick{$-$ on average, rarer events occur in more extreme environments}.
-The \replyrick{approximate} rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
+A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation $-$ on average, rarer events occur in more extreme environments.
+The approximate rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
 At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohmaier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
-These figures place the \replyrick{rate of} DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching \replyrick{the location of RET hosts in the various host galaxy parameter spaces presented in Section \ref{sec:analysis}}.
+These figures place the rate of DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching the location of RET hosts in the various host galaxy parameter spaces presented in Section \ref{sec:analysis}.
 While stressing rates are uncertain and host galaxy parameters span wide ranges for all transients, they are both linked to the respective transients' progenitor channels.
 Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSNe or LGRBs.
-\replyrick{This hypothesis also suggests} that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
+This hypothesis also suggests that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
 
@@
 Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies.
-For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFRs \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSN \replyrick{lightcurves} that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
-In Fig.
-\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and lightcurve width parameterised as $t_{\mathrm{half}}$, the time the lightcurve is above half the peak brightness (lower panels), and \replyrick{their correlation with} host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
+For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFRs \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSN lightcurves that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}.
+In Fig.~\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and lightcurve width parameterised as $t_{\mathrm{half}}$, the time the lightcurve is above half the peak brightness (lower panels), and their correlation with host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
 The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a blackbody SED.
@@
 Assuming that these points are not outliers, the trends are still likely driven by selection effects.
-At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those \replyrick{high} redshifts only the more massive galaxies are detected.
-This effect can be seen in Fig.
-\ref{fig:ret_v_host}a, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in \replyrick{Fig.
-\ref{fig:ret_v_host}b}.
-It is hoped that a \replyrick{more} complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) in order to reveal any underlying relationships.
+At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those high redshifts only the more massive galaxies are detected.
+This effect can be seen in Fig.~\ref{fig:ret_v_host}a, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in Fig.~\ref{fig:ret_v_host}b.
+It is hoped that a more complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) in order to reveal any underlying relationships.
+
+\label{sec:disc}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/RET_vs_host.png}
+\caption{RET lightcurve properties as a function of host galaxy measurements.
+\label{fig:ret_v_host}}
+\end{figure}
 
@@
 The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Fox2019,Mohan2020} due to its rapid evolution and blue colour.
-AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018} , developing to something entirely different \replyrick{at later epochs} \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.
+AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018}, developing to something entirely different at later epochs \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.
 There have been several suggestions that AT2018cow is indeed an analogue of the high-z RETs.
-The host galaxy of AT2018cow \replyrick{is} to be moderately star forming and lies very close to the centre of the SFMS (\citealt{Lyman2020}; Figs.
+The host galaxy of AT2018cow is to be moderately star forming and lies very close to the centre of the SFMS (\citealt{Lyman2020}; Figs.
 \ref{fig:sfms_sfr},\ref{fig:sfms_ssfr}), along with many of the DES RET hosts.
-However, the host lies somewhat above the fiducial MZR in Fig.
-\ref{fig:mzr}, suggesting that it has an unusually high metallicity for its stellar mass.
+However, the host lies somewhat above the fiducial MZR in Fig.~\ref{fig:mzr}, suggesting that it has an unusually high metallicity for its stellar mass.
 While consistent with SNe II, this is in contrast to the DES RET hosts which are systematically less enriched for a given stellar mass.
@@
 
-To compare two distributions we follow the method outlined in \citetalias{Wiseman2020}.
+To evaluate the likelihood that two independent distributions are from the same parent population we follow the method outlined in \citetalias{Wiseman2020}.
 We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution.
 We utilise two chains, for a warm-up period of $5\times10^3$ iterations per chain and a fit period of $5\times10^3$ iterations per chain.
-Fig.
-\ref{fig:histfit_s12_ssfr} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared.
+Fig.~\ref{fig:histfit_s12_ssfr} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared.
 Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness).
-We then compare the differences in these parameters, as seen in Fig.
-\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
+We then compare the differences in these parameters, as seen in Fig.~\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
 \twocolumn

### 2020-07-20 DES_RET_Hosts_replyref.tex

--- 2020-05-16 DES_RET_Hosts_submit.tex
@@
 \usepackage{threeparttable}
-\makeatletter
-%\newlength{\abovecaptionskip}%
-%\setlength{\abovecaptionskip}{10\p@}
-\makeatother
+
 \usepackage{booktabs}
@@
 \newcommand{\mike}[1]{\color{cyan}#1 \color{black}}
-\newcommand{\replyrick}[1]{\color{magenta}#1 \color{black}}
+\newcommand{\replyref}[1]{\color{magenta}#1 \color{black}}
 \newcommand{\replylluis}[1]{\color{brown}#1 \color{black}}
@@
 \newcommand{\msun}[0]{M_{\odot}}
+\usepackage{etoolbox}
+%\makeatletter
+%\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
+%  \errmessage{\noexpand\@combinedblfloats could not be %patched}%
+%}%
+%\makeatother
 
@@
 %\makeatletter
-%\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
+%\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outpu%tbox}{}{%
 %  \errmessage{\noexpand\@combinedblfloats could not be patched}%
@@
 %\makeatother
-%
+
 %\defcitealias{Smith2019}{S19}
@@
 % Keep the title short and informative.
-\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
+%\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
+\title[RET host galaxies in DES]{The Host Galaxies of 106 Rapidly Evolving Transients discovered by the Dark Energy Survey}
 % The list of authors, and the short list which is used in the headers.
@@
 \begin{abstract}
-Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a distinct class of astrophysical event.
-They are characterised by lightcurves that decline much faster than common classes supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1.
+Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a recently-discovered group of astrophysical events that display rapid luminosity evolution.
+RETs typically rise to peak in less than 10 days and fade within 30, a timescale unlikely to be compatible with the decay of Nickel-56 that drives conventional SNe.
+Their peak luminosity spans a range of $-15 <M_g<-22.5$, with some events observed at redshifts greater than 1.
 Their evolution on fast timescales has hindered high quality follow-up observations, and thus their origin and explosion/emission mechanism remains unexplained.
 In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the most comprehensive analysis of RET host galaxies.
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 37.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities ([O/H]) for 37.
 We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars.
-Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs, indicating a link to young stellar populations, similar to stripped-envelope SNe.
-RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies.
+Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs ($\langle\log \left(\mathrm{sSFR}\right)\rangle \sim -9.6$ ), indicating a link to young stellar populations, similar to stripped-envelope SNe.
+RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies $\langle12+\log\left(\mathrm{O/H}\right) \rangle \sim 9.4$.
 There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.
@@
 The narrow emission originates from the ejecta impacting on slow-moving circumstellar material (CSM).
-Since the turn of the century, observations of CCSNe, whose lightcurves are primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
+Since the turn of the century, observations of CCSNe, whose lightcurves are \replyref{thought to be} primarily powered by the radioactive decay of freshly synthesised Ni-56, have been supplemented by rarer, more exotic transient classes.
 
@@
 There are correlations between the expected progenitor mass of different sub-classes of CCSNe and host galaxy properties.
-On average, SESNe reside in galaxies with higher specific star-formation rates (sSFRs; \citealt{James2006,Kelly2008}), while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Anderson2012,Galbany2018}.
-More extreme events tend to occur in galaxies low in mass and high in sSFR, with both LGRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
+On average, SESNe reside in galaxies with higher specific star-formation rates (sSFRs; \citealt{James2006,Kelly2008}) \replyref{than SNe II}, while studies of the local environments tend to show that SESNe explode closer to \HII~regions than SNe II, indicating that the progenitors are younger and more massive than the various sub-classes of hydrogen-rich SNe II  \citep[e.g.][]{Anderson2012,Galbany2018}.
+More extreme events tend to occur in galaxies low in mass \replyref{($\leq10^{10} M_{\odot}$) and high in sSFR ($\geq 10^{-9.5}$ yr$^{-1}$)}, with both LGRBs \citep[e.g.][]{Fruchter2006,LeFloch2006,Levesque2010,Kruehler2015,Vergani2015,Perley2016b,Palmerio2019,Taggart2019} and to an even greater degree SLSNe \citep[e.g.][]{Neill2011,Lunnan2014,Leloudas2015,Angus2016,Schulze2018,Taggart2019} exhibiting this association.
 
@@
 \citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
-\citet{Arcavi2016} reported three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly like the PS1 sample.
+\citet{Arcavi2016} reported three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly.
 \citet[hereafter P18]{Pursiainen2018} expanded the known number of RETs to beyond 80 with their sample from the Dark Energy Survey (DES), spanning a redshift range of $\sim 0$ to $>1$.
 A further sample of five objects has been discovered by the Hyper Suprime-Cam Subaru Strategic Program (SSP) Transient Survey \citep{Tampo2020}.
-RETs typically rise to peak brightness in less than 10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
+\replyref{Although the search and selection criteria vary between the above samples, the objects} typically rise to peak brightness in less than 10 days, and decline to 10\% of their peak brightness within 30 days, much faster than typical SNe.
 The photometric measurements of the PS1 and DES RETs seem to be well described by expanding blackbodies, although a handful show declining photospheric radii from the first detection.
@@
 The transient declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}) .
-There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Uno2020}.
-Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.
-It is currently unclear whether these transients represent the local analogues of the DES and PS1 RETs.
+There are many diverse explanations for the power source of AT2018cow \replyref{proposed} in the literature, including: \replyref{engine-driven stellar explosions \citep{Ho2019,Margutti2019,Mohan2020}}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Piro2020,Uno2020}.
+Other nearby rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} which is a rapidly-declining, nearby SN Ic-BL, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.
+At higher redshift there is one RET -- ZTF18abvkwla \citep{Ho2020}.}
 
@@
 The order of the paper is as follows: in Section \ref{sec:sample} we introduce the full DES RET sample and describe the host galaxy observations in Section \ref{sec:obs}.
-The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:disc}) and conclusion (Section \ref{sec:conc}).
+The analysis methods and results are described in Sections \ref{sec:measure} and \ref{sec:analysis} respectively, before a discussion (Section \ref{sec:discussion}) and conclusion (Section \ref{sec:conc}).
 Where applicable, we adopt a spatially flat $\Lambda$CDM cosmology with the parameters $H_0=70$ km~s$^{-1}$ Mpc$^{-1}$ and $\Omega_{\textrm{M}}=0.3$.
@@
 
-Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
+Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
 It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR.
@@
 \end{table}
-\section{Discussion}
-
+
+\section{Discussion }
+\label{sec:discussion}
 \subsection{Selection Biases \label{subsec:disc_bias}}

### 2020-07-22 DES_RET_Hosts_replyref.tex
Updates from Overleaf

@@
 RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies $\langle12+\log\left(\mathrm{O/H}\right) \rangle \sim 9.4$.
-There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.
+There are no clear relationships between \replyref{mass or SFR} of the host galaxies and the peak magnitudes or decline rates of the transients themselves.
 
@@
 Recently, inspection of high-cadence, large-area survey data sets have revealed more exotic transients that are difficult to explain with conventional models.
-\citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1).
+\citet{Drout2014} presented a sample of rapidly evolving transients (RETs; also termed `Fast Blue Optical Transients' - FBOTs or `Fast Evolving Luminous Transients' - FELTs) in the Pan-STARRS survey (PS1), \replyref{defined as having time above half-brightness ($t_{\mathrm{half}}) \leq12$d}.
 \citet{Arcavi2016} reported three rapidly rising, highly luminous objects in the Supernova Legacy Survey (SNLS) and one in the Palomar Transient Factory (PTF), of which one (SNLS04D4ec) declines rapidly.
@@
 
-There are a limited number of events detected in the local Universe whose properties appear consistent with the RETs seen at cosmological distances in the PS1 and DES samples, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}.
-The transient declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}) .
-There are many diverse explanations for the power source of AT2018cow \replyref{proposed} in the literature, including: \replyref{engine-driven stellar explosions \citep{Ho2019,Margutti2019,Mohan2020}}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Piro2020,Uno2020}.
-Other nearby rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} which is a rapidly-declining, nearby SN Ic-BL, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.
-At higher redshift there is one RET -- ZTF18abvkwla \citep{Ho2020}.}
+There are a small number of other objects in the literature that would pass the DES RET criteria, including SNLS04D4ec \citep{Arcavi2016} at $z\sim0.59$, ZTF18abvkwla \replyref{whose rapid evolution has been attributed to shock interaction, while radio emission can be explained by a collimated jet \citep{Ho2020} at $z\sim0.27$, and the rapidly-evolving SN Ic-BL-like iPTF16asu \citep{Whitesides2017} at $z\sim0.19$.}
+
+There are also a limited number of events detected in the local Universe whose properties appear consistent with the RETs seen at cosmological distances in the PS1 and DES samples, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Margutti2019,Perley2019}.
+\replyref{AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Fox2019,Mohan2020} due to its rapid evolution and blue colour.
+AT2018cow declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}).
+It displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018}, developing to something entirely different at later epochs \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.} There are many diverse explanations for the power source of AT2018cow \replyref{proposed} in the literature, including: \replyref{engine-driven stellar explosions \citep{Ho2019,Margutti2019,Mohan2020}}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Piro2020,Uno2020}.
+Other nearby \replyref{($z<0.1$)} rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} \replyref{which is a rapidly-declining, spectroscopically classified, nearby SN Ic-BL with a rapid rise to peak}, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.}
 
@@
 Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties and compare them to samples of host galaxies of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients.
-For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.
 
@@
 {} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time \tnote{b} \\
-Transient name &  (J2000  & (J2000)  &  (AB)    &         &         &   (hours)         &               \\
+Transient name &  (\replyref{deg }J2000)  & (\replyref{deg} J2000)  &  (AB)    &         &         &   (hours)         &               \\
 \midrule
@@
 \label{sec:sample}
-We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey.
+\replyref{Our sample of RETs comprises 106 events} discovered in the 5-year DES-SN transient survey.
 This number expands upon the 72 of \citetalias{Pursiainen2018}.
@@
 The supernova programme (DES-SN), designed primarily to detect type Ia SNe (SNe Ia) for cosmological measurements \citep{Bernstein2012}, consisted of five 6-month seasons of approximately 7 day cadence in ten single pointings, known as the SN fields which cover a total area of $\sim27 \deg^2$.
-Of these fields, two were observed with longer exposure times and are referred to as deep fields with remaining eight known as shallow fields; the resulting approximate single-visit depths are 23.5 mag (shallow) and 24.5 mag (deep) in the DES $r$-band.
+Of these fields, two were observed with longer exposure times and are referred to as deep fields with \replyref{the} remaining eight known as shallow fields; the resulting approximate single-visit depths are 23.5 mag (shallow) and 24.5 mag (deep) in the DES $r$-band.
 Transient detection was performed by difference imaging using a custom pipeline \citep{Kessler2015}.
@@
 images, light curves, host galaxy information), it is impossible to quantify the completeness of the sample.
-For instance, due to the large redshift range within the sample it is entirely possible that distant events with longer rise times could have been missed due to time dilation stretching their lightcurves, while faster events and low redshift may evolve on timescales quicker than the survey cadence.
+For instance, due to the large redshift range within the sample it is entirely possible that distant events with longer rise times could have been missed due to time dilation stretching their lightcurves, while faster events \replyref{at} low redshift may evolve on timescales quicker than the survey cadence.
 Here, a more sophisticated search method is presented.
 As only a fraction of transients in DES-SN have redshift information from their host galaxies, we perform the search in the observer frame.
-The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution (rise to peak in $\lesssim15$ days) and blue colour at peak ($g-r \lesssim 0.5$).
-Even though both of these quantities depend on the redshift of the transient, they still effectively distinguish the the fast events from traditional SN types.
-We thus attempt to select a sample based on observed rise times and colours at peak brightness.
+The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution \replyref{($t_{\mathrm{half}}\leq12$d)} and blue colour at peak ($g-r \lesssim 0.5$).
+Even though both of these quantities depend on the redshift of the transient \replyref{(timescales, for example, are dilated by a factor of 2 at $z=1$)}, they still effectively distinguish the fast events from traditional SN types.
+\replyref{Here, we} attempt to select a sample based on observed rise times and colours at peak brightness.
 
@@
 To make an improved selection of RETs we use a parameter space described by observed $g-r$ colour and the time taken to rise from non-detection to peak $r$-band magnitude in the observer frame.
-Using rise times and colours from GP lightcurves, we populate this parameter space with the sample of 72 RETs from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES.
+\replyref{While limiting magnitudes are variable, the uncertainty this introduces onto the rise time is minimal compared to that caused by the fact that the rise time is shorter than the cadence of the survey (i.e.
+$<7$ d) for many RETs, such that the first detection is the peak.} Using rise times and colours from GP lightcurves, we populate this parameter space with the sample of 72 RETs from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES.
 We add spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe observed by DES in order to verify that they are rejected by the search method.
@@
 
+\replyref{Light curves are not corrected for Galactic extinction, but this is negligible at $\mathrm{E}(B-V)<<0.1$ in the DES-SN fields.}
+
  SNe Ia and RETs populate two distinct regions of $g-r$ vs.
@@
 To detect and filter out AGN we use a basic convolutional neural network (CNN) classifier.
+\replyref{The CNN uses features of the GP light curves in a set of layers in order to ``learn" the difference between SN and AGN lightcurves.
+We implement two 1-dimensional feature layers: the first searches for evolution over 2-day timescales in all four filters, while the second deals with long-term evolution on 20-day timescales.
+We include a dropout layer after each filter layer to prevent over-fitting, and a max-pooling layer to increase speed.
+At the end, a softmax layer outputs a probability that the individual transient is SN-like, for which we use 50\% as the threshold}.
 We train the CNN on spectroscopically confirmed SNe of all types as well as the 92 RETs identified using the \citetalias{Pursiainen2018} method (181 objects) and on spectroscopically typed AGN (182 objects), and use it to separate the sample into two photometric subtypes: AGN-like and SN-like.
@@
 These objects are subject to a further set of cuts in order to remove remaining contaminants.
-We impose a cut based on a SN classifier (\texttt{PSNID}; \citealt{Sako2008}), that returns a normalised goodness of fit to different SN Ia and CCSN templates, along with a Bayesian probability of it being a SN Ia.
+We impose a cut based on a SN \replyref{light curve} classifier (\texttt{PSNID}; \citealt{Sako2008}), that returns a normalised goodness of fit to different SN Ia and CCSN templates, along with a Bayesian probability of it being a SN Ia.
 To remove highly-probable SNe Ia, we use threshold probabilities of P(Ia)$<0.91$ and P(Ia; Bayes)$<0.82$ respectively to the above algorithms, which removes 46 objects from the RET parameter space.
@@
 We highlight objects that were not presented in \citetalias{Pursiainen2018}.
-We also highlight a small subset of objects for which the redshift has taken on a new value than that presented in \citetalias{Pursiainen2018} due to further OzDES observations leading to a more accurate determination.
+We also highlight a small subset of objects for which \replyref{further OzDES observations have led to a more accurate redshift than that presented in  \citetalias{Pursiainen2018}.}
 
@@
 \citet{Drout2014} present host galaxies of 10 RETs discovered in the Pan-STARRS survey, with measurements of stellar masses, SFRs, and metallicities.
-We also compare with the host galaxy of SNLS04D4ec \citep{Arcavi2016}.
-To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'').
+We also compare with the host galaxy of SNLS04D4ec \citep{Arcavi2016} \replyref{, ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}, and iPTF16asu \citep{Whitesides2017}.} To this we add the low-redshift transient AT2018cow (nicknamed ``The Cow'').
 The host galaxy of AT2018cow has been studied with photometric measurements \citep{Perley2019} as well as with an integral field spectrograph \citep{Lyman2020}, with consistent results.
 For our comparison, we use the galaxy-averaged stellar mass and SFR from \citet{Lyman2020} and the metallicity from the host nucleus as reported by both \citet{Morokuma-Matsui2019} and \citet{Lyman2020} as it best represents the method of obtaining spectra for our RET sample.
-We further compare to SN2018gep with data from  \citet{Ho2019}, and ZTF18abvkwla (nicknamed ``The Koala'') from \citet{Ho2020}.
+We further compare to low-redshift SN2018gep with data from \citet{Ho2019a} \replyref{and CSS161010 with data from \citet{Coppejans2020}.}
 
 \subsubsection{SNe and GRBs \label{subsubsec:compare_CCSNe}}
-
+\replyref{It is likely that the progenitor and explosion scenario of the DES RET sample is heterogeneous in origin and may include some known classes of transient, and as such we choose various samples of host galaxies from the literature to compare the DES RET hosts to.}
 In compiling a set of comparison samples, we aim for the least biased selections possible.
@@
 While in practice the second and third of these criteria are difficult to achieve, particularly with the fainter CCSNe, we are able to choose comparison samples from untargetted surveys to mitigate initial selection biases.
+\replyref{We choose large enough samples that a significant statistical comparison can be drawn, and thus do not split the major groups of SNe into sub-types.}
 
@@
 We add to this the compilation of 56 untargeted SESNe from \citet{Sanders2012}, with a maximum redshift of 0.26 and a mean of 0.05.
-Since \citet{Sanders2012} do not report host galaxy magnitudes, stellar masses or SFRs, we cross-match the SN positions with the the Sloan Digital Sky Survey (SDSS; \citealt{York2000}) Data Release 16 (DR16; \citealt{Ahumada2019}) and perform our own SED fit using the method outlined in Section \ref{subsec:sedfit}.
+Since \citet{Sanders2012} do not report host galaxy magnitudes, stellar masses or SFRs, we cross-match the SN positions with the Sloan Digital Sky Survey (SDSS; \citealt{York2000}) Data Release 16 (DR16; \citealt{Ahumada2019}) and perform our own SED fit using the method outlined in Section \ref{subsec:sedfit}.
 We are able to do this SED fit for 38 objects, with the others lying outside of the SDSS footprint.
@@
 We do not correct for this, but take it into account when analysing our findings.
+\replyref{The magnitude-limited nature of the SDSS redshift catalogue means that it is biased against low-mass galaxies, and metallicity estimates requiring strong lines to pass SNR thresholds mean that they too will be biased.
+Many works exploring extreme transients such as LGRBs, GRB-SNe, and SLSNe, use a complete, volume limited sample of field galaxies such as the Local Volume Legacy Survey (LVL) sample as a comparison \citep[e.g.][]{Chen2017,Modjaz2019,Taggart2019}.
+However the spectroscopic follow-up of DES RETs was performed as part of the magnitude-limited OzDES survey (Section \ref{subsec:spec}), which has similar selection biases and incompleteness effects to SDSS, albeit shifted to a higher redshift.
+In comparison, the many dwarf galaxies in LVL would not be detected in DES photometry, or get a redshift measurement from OzDES, and thus such a comparison sample is not representative of the way the DES RET host sample was observed.}
+
 \section{Host galaxy observations}
@@
 \citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}).
+\replyref{We note that for the majority of DES RET host galaxies, particularly at higher redshift, the fibre covers a large proportion of the galaxy profile, and that the uncertainties on our derived metallicities (Section \ref{subsec:res_metallicity}) are typically of order 0.2 dex, which is much larger than the 11\% offset found in SDSS galaxies in \citet{Iglesias-Paramo2016}}.
 We proceed with our analysis with this caveat acknowledged.
@@
 A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation $-$ on average, rarer events occur in more extreme environments.
-The approximate rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$), \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Tampo2020}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
+The approximate rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$; \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Coppejans2020}, \citealt{Ho2020}, \citealt{Tampo2020} \replyref{although the definition of RET varies in the above calculations}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
 At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohmaier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
@@
 While stressing rates are uncertain and host galaxy parameters span wide ranges for all transients, they are both linked to the respective transients' progenitor channels.
-Based upon both indicators, it is reasonable to infer that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSNe or LGRBs.
-This hypothesis also suggests that RETs are an intermediate and/or precursory step, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling, but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form.
+\replyref{While it is likely that RETs are a heterogeneous population comprising several progenitor scenarios, it is reasonable to infer from the rates and the host properties} that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSN or LGRB \replyref{progenitors such as rapid rotation and low metallicity}.
+This hypothesis \replyref{can be extended to posit} that \replyref{some} RETs \replyref{signify} an intermediate and/or precursory step \replyref{in the late stages of evolution of a massive star that is close to forming a SLSN or LGRB, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling driving the RET light curve (\citetalias{Pursiainen2018}), but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form, hence the lack of longer-term light curves.
+}
 
@@
 In Fig.~\ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and lightcurve width parameterised as $t_{\mathrm{half}}$, the time the lightcurve is above half the peak brightness (lower panels), and their correlation with host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
-The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a blackbody SED.
+The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a blackbody SED \replyref{as per \citetalias{Pursiainen2018}}.
 There is no correlation between decline rate and either stellar mass or sSFR, while there are hints of a trend between peak magnitude and both mass and sSFR.
@@
 
-The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Fox2019,Mohan2020} due to its rapid evolution and blue colour.
-AT2018cow displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018}, developing to something entirely different at later epochs \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.
  There have been several suggestions that AT2018cow is indeed an analogue of the high-z RETs.
@@
 
-Other local rapid transients include SN2018gep \citep{Ho2019}, a spectroscopically classified SN Ic-bl with a rapid rise.
-The host of SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR.
-While the SN2018gep host is lower in stellar mass than any DES RET $\left(\log \left(M/M_{\odot}\right) =8.11\right)$, galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}.
+The host of \replyref{the rapidly evolving SN Ic-BL} SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR.
+While the SN2018gep \replyref{and CSS16100 hosts are} lower in stellar mass than any DES RET ($\log \left(M/M_{\odot}\right) =8.11$ \replyref{and $7.3$, respectively),} galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}.
 The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}.
-
-The rapidly evolving lightcurve of ZTF18abvkwla (``the Koala'') has been attributed to shock interaction, while radio emission can be explained by a collimated jet.
+\replyref{The host of the other SN Ic-BL we compare to, iPTF16asu, is slightly more massive, but otherwise consistent with SN2018gep.}
+
 The host of the Koala is a low metallicity starburst more typical of LGRBs and SLSNe, and places this transient at the very extreme end of the DES RET host population.

### 2020-07-23 referee_response_1.tex
Updates from Overleaf

\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{color}

\hoffset = -1.0in
\voffset = -1.0in
\textwidth = 6.5in
\textheight = 9.0in

\begin{document}
\title{Response to the referee's comments}
\date{}
\maketitle
\section*{Title}
When I first read the title, I wondered whether it was the host galaxies that were detected in the Dark Energy Survey, or whether it was the rapidly evolving transients detected in DES, or both. My understanding after reading the paper is that it is both, and actually the selection of a large number of RETs in DES data is an important aspect of the analysis. I suggest changing the title to make this clear. One example could be “The Host Galaxies of N Rapidly Evolving Transients Discovered by the Dark Energy Survey,” or “The Host Galaxy Properties of N Rapidly Evolving Transients Discovered by the Dark Energy Survey.”

\vskip0.1cm
{\bf RESPONSE: } Thanks, the title has been changed to ``The Host Galaxies of 106 Rapidly Evolving Transients discovered bythe Dark Energy Survey"

\section*{Abstract}
\begin{enumerate}

\item I think the first sentence is misleading, that RETs/FBOTs are “a distinct class of astrophysical event.”
In fact, from the very few events we have studied in detail in the local universe, there is clearly heterogeneity: 18cow shares almost nothing in common with 18gep aside from a fast-evolving and luminous optical light curve. The PS1 objects in Drout+14 span an enormous range in luminosity, and could easily include known classes of SNe, such as Type Ibn and Type II SNe. I would say that RETs/ FBOTs seem to be distinct from “ordinary,” well-understood classes of supernovae, but still have considerable diversity in and among themselves.

\item I also think the second sentence is misleading, that RETs are characterized by light curves that decline much faster than common classes of supernovae and can be seen to redshifts greater than 1. Again, there is considerable heterogeneity in what has been called a RET/FBOT in the literature. In Drout +14, the distinction was that the peak of the light curve could not be powered by nickel decay — but a number of events had decline rates that could easily be explained by nickel decay (see Section 8.1). In SN2018gep, the rise and decline rate would have passed the Drout+14 criteria, but the decline was consistent with a Type Ic-BL SN. 18cow, of course, did decline much more quickly than typical SNe. Regarding the “can be seen to redshifts greater than 1,” this is only true of the very luminous RETs. The sample in Drout+14 spanned an enormous range of peak luminosity. I would remove this sentence, and instead make the point that the main distinguishing feature of an RET is that the *peak* of the light curve is unlikely to be powered by the radioactive decay of Ni-56 — and that the light curve is single peaked, unlike the many double peaked SNe that are known. In general, I think that it is typically the *rise* time that distinguishes RETs, rather than the decline timescale. Perhaps give numbers for the range of right times, decline times, and peak luminosities that are observed for these events?

\vskip0.1cm
{\bf RESPONSE: } These two points have been addressed together, by streamlining the introductory part of the abstract to the following: ``\textit{RETs typically rise to peak in less than 10 days and fade within 30, a timescale unlikely to be compatible with the decay of Nickel-56 that drives conventional SNe. Their peak luminosity spans a range of $-15<M_g<-22.5$, with some events observed at redshifts greater than 1.}"

\item There should be an “of” between “common classes” and “supernovae”
\vskip0.1cm
{\bf RESPONSE: } Changed to ``conventional supernovae"

\item I would state the exact definition of a DES RET somewhere in the abstract
\vskip0.1cm
{\bf RESPONSE: } There is no exact definition of a DES RET that does not take up a full section, as per Section 2.2. Instead we have added the typical rise and decline times.

\item In the abstract, perhaps state what is meant by “metallicity” ([O/H], etc)?
\vskip0.1cm
{\bf RESPONSE: } Added

\item “We find that RETs prefer galaxies with high specific SFRs” — state the number or range
\vskip0.1cm
{\bf RESPONSE: } Added the mean

\item “appear to show a lack of chemical enrichment” — state the number or range
\vskip0.1cm
{\bf RESPONSE: } Added the mean

\item “no clear relationships between properties of the host galaxies” — what properties?
\vskip0.1cm
{\bf RESPONSE: } Added mass and sSFR

\end{enumerate}

\section*{Introduction}
\begin{enumerate}

\item “CCSNe, whose lightcurves are primarily powered by” — I would say “are thought to be primarily powered by”
\vskip0.1cm
{\bf RESPONSE: } Changed

\item “On average, SESNe reside in galaxies with higher specific star-formation rates” — than hydrogen- rich SNe, you mean?
\vskip0.1cm
{\bf RESPONSE: } Yes, changed.

\item “More extreme events tend to occur in galaxies low in mass and high in sSFR” — again, please give some numbers for a reader who is not familiar with typical values
\vskip0.1cm
{\bf RESPONSE: } Added values

\item In the paragraph starting “Recently, inspection of high-cadence, large-area survey data” I think you should emphasize that different papers presenting “samples” have used different search criteria from one another. As stated in the abstract, I disagree with the statement that “one...declines rapidly like the PS1 sample,” because a number of the events in the PS1 sample did not decline particularly rapidly. As far as I understand, the PS1 and DES samples did not use the same search criteria.
\vskip0.1cm
{\bf RESPONSE: } Added a sentence stating \textit{although the search and selection criteria vary between the above samples}

\item “There are many diverse explanations for the power source of AT2018cow touted in the literature.” I suggest finding a different word to replace “tout,” such as “proposed.”
\vskip0.1cm
{\bf RESPONSE: } Changed

\item “including: magnetars” — I would instead say engine-driven stellar explosion, which could include magnetars but also accreting black holes. For this hypothesis, please cite Ho et al. 2019 and Margutti et al. 2019, who both proposed that 18cow was an engine-driven stellar explosion based on the X-ray and radio behavior.

\vskip0.1cm
{\bf RESPONSE: } Changed to engine-driven stellar explosions and added the references

\item You describe them later, but I would introduce SN2018gep (Ho+2019) in this section as well, and perhaps also mention the Koala (Ho+2020) and CSS+161010 (Coppejans+2020).
\vskip0.1cm
{\bf RESPONSE: } Added

\item “wind-driven transient” — please cite Piro \& Lu (2020), who made a similar proposal
\vskip0.1cm
{\bf RESPONSE: } Added

\item “It is currently unclear whether these transients represent the local analogues” — delete “the.” Also, I think it would be more useful to state whether these transients truly fit the search criteria used in the PS1 and DES searches. If you placed these transients at the redshift of the DES searches, would they pass the search criteria?
\vskip0.1cm
{\bf RESPONSE: } Have clarified that these objects would fit the criteria out to high redshifts.

\item “For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1” — this sentence is a bit unclear. You mean that you are applying a luminosity cut? What is the motivation for that?

\vskip0.1cm
{\bf RESPONSE: } Have removed this sentence

\item “before a discussion (Section 6.3) — perhaps you meant to say Section 6?
\vskip0.1cm
{\bf RESPONSE: } Changed, thanks

\item There should be a comma after “i.e.”
\vskip0.1cm
{\bf RESPONSE: } As far as we are aware, in British English i.e. comes without a comma (it seems this way on the MNRAS style guide as well).

\end{enumerate}
\section*{Sample Selection}

\begin{enumerate}
    \item “We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey.” sounds a bit strange — perhaps “We derive our sample of host-galaxy properties from,” or “Our sample comprises 106 RETs discovered in”

    \vskip0.1cm
{\bf RESPONSE: }
Changed to \textit{Our sample of RETs comprises 106 events discovered in }.

\item I want to make sure the authors are aware of Modjaz+ (2019) which presents an untargeted sample of the kinds of explosions relevant for RETs: Ic-BL SNe and Ic SNe from PTF, and 10 GRB-SNe. Perhaps this could be a useful comparison?
\vskip0.1cm
{\bf RESPONSE: } We have added the SNe Ic-BL as a comparison sample, due to both iPTF16asu and SN2018gep showing Ic-BL-like spectra.

\item “with remaining eight known as” — should be “with the remaining eight known as”

\vskip0.1cm
{\bf RESPONSE: } Changed

\item “while faster events and low redshift” — you mean “faster events at low redshift”?

\vskip0.1cm
{\bf RESPONSE: } Yes, changed

\item “The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution (rise to peak <15d) and blue colour at peak” — this is not consistent with what you said earlier, which is that the distinguishing feature is the fast *decline* rather than rise
\vskip0.1cm
{\bf RESPONSE: } We see how this was confusing, and have changed this sentence as well as the earlier one to imply that the key feature is the overall fast light curve evolution, rather than the rise or decline in particular

\item When you say “rise to peak” please quantify what this means — time from estimated explosion to peak? time from half-peak to peak in flux space? etc. Otherwise it is difficult to compare to other surveys.

\vskip0.1cm
{\bf RESPONSE: } We now state clearly $t_\mathrm{half}$.

\item “Even though both of these quantities depend on the redshift of the transient” — perhaps give the reader a sense for by how much these quantities can vary over the redshifts considered in the paper

\vskip0.1cm
{\bf RESPONSE: } Added

\item “the time taken to rise from non-detection to peak” — but doesn’t the magnitude of the non-detection vary with observing conditions, and over time? It seems like it would be difficult for someone using another survey dataset to reproduce your search criteria.

\vskip0.1cm
{\bf RESPONSE: } While this is true, in DES the limiting magnitudes were relatively stable. The relatively slow cadence of 7 days is much more of a limiting factor on constraining the rise time.

\item In this section, it’s not clear to me whether you’re using extinction-corrected colors or not. It seems like that would be important to take into consideration, and to mention in 2.2.2
\vskip0.1cm
{\bf RESPONSE: } Added a sentence clarifying that we are not using extinction-corrected magnitudes for classification, but that the extinction in the DES-SN fields is negligible.

\item Section 2.2.3 is very brief. For a reader who is not familiar with CNNs, perhaps provide a bit of context for this choice, the basic choices you had to make in setting up the model, possible drawbacks, and how the validation was done (a leave-one-out test...?)

\vskip0.1cm
{\bf RESPONSE: } We have added some detail regarding the CNN to this section.

\item “We impose a cut based on a SN classifier” — you mean a SN light-curve classifier?

\vskip0.1cm
{\bf RESPONSE: } Changed

\item  “The decline time to half of the peak brightness” — why not use a criterion like this for the rise time as well? You should be able to set a limit on the rise time based on the non-detection, even if you can’t measure it exactly

\vskip0.1cm
{\bf RESPONSE: } We do - this is the selection based on the red box in Fig. 1.

\item “or showing a longer timescale decline” — but if so, how did it pass the criterion of the decline being < 24 days?

\vskip0.1cm
{\bf RESPONSE: } Some objects (many of which are AGN) decline to half of peak within 24d but are clearly detected for much longer

\item  “for which the redshift has taken on a new value than that presented in P18 due to...more accurate determination” — this seems unnecessarily wordy. I would simply say, “for which further OzDES observations have led to a more accurate redshift than that presented in P18.”

\vskip0.1cm
{\bf RESPONSE: } Changed, thanks

\item[] Table 1: Perhaps add “decimal degrees” to the RA and Dec columns?
\vskip0.1cm
{\bf RESPONSE: } Added `deg' 
\item[] Figure 2: Please indicate the orientation (i.e. a compass showing N/S, E/W). I also suggest putting a scale bar on the figure rather than just stating it in the caption. Consider labeling the relevant boxes with the host redshift as well.

{\bf RESPONSE: } Added all of the above.

\end{enumerate}
\section*{Section 2.3}
\begin{enumerate}
    \item “there is no other large sample of RETs with which to compare host galaxy properties.” Do the properties of the DES RET sample overlap with known classes of supernovae? For example, Type Ibn supernovae, which rise quite quickly to high peak luminosity (M ~ -19.5)? It might be useful to acknowledge that there are probably subclasses represented in the DES sample, which arise from a variety of progenitor channels.

    \vskip0.1cm
    {\bf RESPONSE: } Added a sentence to the beginning of 2.3.2: \textit{It is likely that the progenitor and explosion scenario of the DES RET sample is heterogeneous in origin and may include some known classes of transient, and as such we choose samples of host galaxies of various transients from the literature to compare the DES RET hosts to}.

\item The reference to SN2018gep here, Ho et al. (2019), is actually to the AT2018cow paper. Please add the correct SN2018gep reference, which is a separate paper, i.e. will end up being Ho et al. 2019a \& Ho et al. 2019b.
\vskip0.1cm
 {\bf RESPONSE: } Changed

 \item “with the the” — extra “the”
 \vskip0.1cm
 {\bf RESPONSE: } Removed

 \item I might suggest adding iPTF16asu to your list of comparison objects. It was similar to SN2018gep. The reference is Whitesides+ 2017
 \vskip0.1cm
 {\bf RESPONSE: } We have added iPTF16asu to the comparison objects

\end{enumerate}

\section*{Section 2.4}

\begin{enumerate}
    \item I was a bit surprised by the choice of SDSS as a comparison sample of field galaxies. My understanding is that SDSS galaxies suffer from a number of biases -- they will be highly incomplete for dwarfs and biased towards massive galaxies, and the metallicity measurements are very biased (since they have enough S/N in the critical lines for the measurement, and the strengths of those lines is metallicity-dependent.) Since RETs are likely related to GRBs and SLSNe in terms of their stellar evolutionary pathways, it seems important to have a control sample that is inclusive of low-mass galaxies (see the discussion in Section 4.2 in Modjaz+2019, which presents a sample of Ic and Ic-BL hosts from PTF). Why do the authors not use a volume-complete sample of local galaxies instead or as well, as was done in e.g. Modjaz+2019? Either way, I think the authors need to spend more time motivating their choice of field galaxy sample, and discussing possible drawbacks and biases.
   \vskip0.1cm
 {\bf RESPONSE: } We agree that SDSS is not an ideal comparison sample due to the biases pointed out by the referee. We note, however, that the DES host galaxy photometry is similarly incomplete, albeit down to lower mass/higher redshift than SDSS. Furthermore, the majority of the hosts were followed up with OzDES with a magnitude-based selection and limit. We therefore expect similar biases in the DES RET hosts as seen in SDSS. 
 We acknowledge the use of comparing to LVL and have included that in the figures, but this is mainly for illustrative purposes, since the bulk of low mass LVL galaxies would not be seen in DES-SN at the redshifts of the RET sample.

\end{enumerate}

\section*{Section 4.2}
1) “There are several reasons this measurement may differ from one made at the SN explosion site” — could the authors give a quantitative sense for by how much this could differ?
   \vskip0.1cm
 {\bf RESPONSE: } We have added a section describing how these difference are negligible compared to the uncertainty caused by low SNR.

\section*{Section 5}
1) Again, I might suggest including iPTF16asu (Whitesides+2017)
 \vskip0.1cm
 {\bf RESPONSE: }Done

 \section*{Section 5.2}

 1)  “we compare the chemical state of RET host galaxies with...star-forming field galaxies.” As I stated
above, SDSS metallicities are very biased. I think the authors need to discuss this, or possibly use an additional comparison sample.
\vskip0.1cm
 {\bf RESPONSE: } Done, as discussed previously

 \section*{Section 6.2}
 \begin{enumerate}
     \item Ho et al. (2020) (ZTF18abvkwla) and Coppejans (2020) (CSS161010) also performed rate estimates of RETs, so these should be referenced
    \vskip0.1cm
 {\bf RESPONSE: }  Added
 \item As stated in the point above, I think that for a rate estimate it is important to be clear how these different papers define RET...Drout+14 spans a large luminosity distribution, for example
\vskip0.1cm
 {\bf RESPONSE: } Added this caveat

 \item “possibly sharing some of the extreme properties of SLSNe or LGRBs” — what kinds of extreme properties?
 \vskip0.1cm
 {\bf RESPONSE: } Added \textit{Such as rapid rotation and low metallicity}.

 \item “are an intermediary and/or precursory step” — intermediate and/or precursory step in terms of what parameters? I’m not sure what this means. For example, 18cow is clearly very different from an LGRB-type event — H and He emission lines were observed in the optical spectra, whereas no H or He has ever been observed in a Ic-BL SNe.

  \vskip0.1cm
 {\bf RESPONSE: } Clarified to now state: \textit{ his hypothesis can be extended to posit that some RETs represent an intermediate and/or precursory step in the late stages of evolution of a massive star that is close to forming a SLSN or LGRB, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling driving the RET light curve(P18), but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form, hence the lack of longer-term light curves.}

 \end{enumerate}

 \section*{Section 6.3}
 \begin{enumerate}
 \item “have been k-corrected assuming a blackbody SED” — doesn’t there have to be some temperature assumed for this?

  \vskip0.1cm
 {\bf RESPONSE: } We fit a blackbody to the data to measure a temperature and radius, which are then used to k-correct the observed magnitudes. We have added a reference to P18 where this procedure is described.

 \item Some of the detailed descriptions of individual objects here (18cow, 18gep) seem like they would
belong earlier in the paper, when these objects are mentioned for the first time
\vskip0.1cm
 {\bf RESPONSE: } Moved, thanks

 \item “we cannot rule out that the Koala comes from the same population of transients as the DES RETs” Would the light curve of the Koala (and 18gep, and 18kzr) have passed the criteria of the DES RET search, and if so out to what redshift? I think a more quantitative statement here would be useful
 \vskip0.1cm
 {\bf RESPONSE: } Yes, they would have passed out to high ($z\sim1$) redshifts. We have added a comment on this into the introduction

\end{enumerate}
\end{document}

### 2020-07-23 DES_RET_Hosts_replyref.tex
Updates from Overleaf

@@
 
-There are a small number of other objects in the literature that would pass the DES RET criteria, including SNLS04D4ec \citep{Arcavi2016} at $z\sim0.59$, ZTF18abvkwla \replyref{whose rapid evolution has been attributed to shock interaction, while radio emission can be explained by a collimated jet \citep{Ho2020} at $z\sim0.27$, and the rapidly-evolving SN Ic-BL-like iPTF16asu \citep{Whitesides2017} at $z\sim0.19$.}
+There are a small number of other objects in the literature that would pass the DES RET criteria, including SNLS04D4ec \citep{Arcavi2016} at $z\sim0.59$, ZTF18abvkwla \replyref{whose rapid evolution has been attributed to shock interaction, while radio emission can be explained by a collimated jet \citep{Ho2020} at $z\sim0.27$, and the rapidly-evolving SN Ic-BL-like iPTF16asu \citep{Whitesides2017} at $z\sim0.19$.
+}
 
@@
 It displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018}, developing to something entirely different at later epochs \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.} There are many diverse explanations for the power source of AT2018cow \replyref{proposed} in the literature, including: \replyref{engine-driven stellar explosions \citep{Ho2019,Margutti2019,Mohan2020}}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Piro2020,Uno2020}.
-Other nearby \replyref{($z<0.1$)} rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} \replyref{which is a rapidly-declining, spectroscopically classified, nearby SN Ic-BL with a rapid rise to peak}, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.}
+Other nearby \replyref{($z<0.1$)} rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} \replyref{which is a rapidly-declining, spectroscopically classified, nearby SN Ic-BL with a rapid rise to peak}, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.} \replyref{These objects evolved rapidly enough to have passed the DES RET criteria (Section \ref{subsec:new_method}) even at $z\sim1$ where they would appear slower, although they (or their host galaxies) may not necessarily have been bright enough to be detected.}
 
@@
 DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.34577 &  LADUMA &               \\
-DES13C3nxi     & 51.96356 & -28.35720 & $24.99 \pm 0.05$ &    $^c$ &      OzDES &             - \\
-DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    $^c$ &      OzDES &             - \\
-DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.67346 &       ACES &               \\
-DES13E2lpk     & 10.09911 & -43.53903 & $20.49 \pm 0.03$ & 0.47541 &      OzDES &       6.00 \\
-DES13S2wxf\tnote{e}& 41.61268 & -0.02634&$21.39 \pm0.03$9& 0.56985 &      OzDES &       5.42 \\
-DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.00 \\
-DES13X2oyb     & 35.31056 &  -5.67893 & $22.91 \pm 0.06$ &    $^c$ &      OzDES &             - \\
-DES13X2wvv\tnote{e}     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.50 \\
-DES13X3aakf    & 35.71205 &  -4.69915 & $25.47 \pm 0.09$ &    $^c$ &      OzDES &             - \\
-DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    $^d$ &          - &             - \\
-DES13X3alnb    & 37.18496 &  -5.14232 & $25.04 \pm 0.06$ &    $^c$ &      OzDES &             - \\
-DES13X3gmd\tnote{e}     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.92 \\
-DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.58 \\
-DES13X3kgm     & 36.50380 &  -4.86636 & $26.46 \pm 0.18$ &    $^d$ &          - &             - \\
-DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.17 \\
-DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.50 \\
-DES13X3pby     & 36.33330 &  -5.31408 & $23.82 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES14C1jnd     & 54.35153 & -27.49300 & $24.33 \pm 0.08$ &    $^c$ &      OzDES &             - \\
-DES14C3gzj\tnote{e}     & 52.57168 & -28.14019 & $26.04 \pm 0.10$ &    $^d$ &          - &             - \\
-DES14C3tnz\tnote{e}     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.79 \\
-DES14C3tvw     & 53.32230 & -27.90621 & $21.31 \pm 0.02$ & 0.70390 &       ACES &               \\
-DES14E1aqi\tnote{e}     &  8.73970 & -43.40182 & $25.61 \pm 0.23$ &    $^d$ &          - &             - \\
-DES14E2xsm     &  9.67624 & -43.58736 & $23.39 \pm 0.04$ &    $^c$ &      OzDES &             - \\
-DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75 \\
-DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.00 \\
-DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.42 \\
-DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.50 \\
-DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.17 \\
-DES14X3pko     & 36.90824 &  -3.69642 & $24.48 \pm 0.06$ &    $^d$ &          - &             - \\
-DES15C2eal     & 54.06180 & -29.23000 & $22.99 \pm 0.03$ & 0.22347 &      OzDES &      16.91 \\
-DES15C3edw     & 52.55235 & -27.71022 & $22.69 \pm 0.03$ &    $^d$ &          - &             - \\
-DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.17 \\
-DES15C3lzm     & 52.17460 & -28.23186 & $20.47 \pm 0.02$ & 0.32690 &      ATLAS &               \\
-DES15C3mem\tnote{e}     & 52.14216 & -29.05851 & $20.28 \pm 0.04$ & 0.61618 &     PRIMUS &               \\
-DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.17 \\
-DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.62 \\
-DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.17 \\
-DES15C3opp     & 51.73962 & -28.11496 & $23.25 \pm 0.04$ & 0.44242 &      OzDES &      16.75 \\
-DES15C3pbi     & 52.23620 & -28.00223 & $25.10 \pm 0.05$ &    $^d$ &          - &             - \\
-DES15E2lmq     &  9.62005 & -43.98734 & $25.65 \pm 0.18$ &    $^d$ &          - &             - \\
-DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.83 \\
-DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.33 \\
-DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.67 \\
-DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.00 \\
-DES15X3atd     & 35.84011 &  -4.29142 & $23.87 \pm 0.05$ &    $^c$ &      OzDES &             - \\
-DES15X3kyt     & 36.27500 &  -5.41103 & $24.74 \pm 0.07$ &    $^d$ &          - &             - \\
 
@@
 \item[d] Host not targetted by OzDES.
-\item[e] Found by updated search method (Section \ref{subsec:new_method}).
-\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method.
-\item[g] Redshift updated since to \citetalias{Pursiainen2018}.
 \end{tablenotes}
@@
 The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution \replyref{($t_{\mathrm{half}}\leq12$d)} and blue colour at peak ($g-r \lesssim 0.5$).
-Even though both of these quantities depend on the redshift of the transient \replyref{(timescales, for example, are dilated by a factor of 2 at $z=1$)}, they still effectively distinguish the fast events from traditional SN types.
+Even though both of these quantities depend on the redshift of the transient \replyref{(timescales, for example, are dilated by a factor of 2 at $z=1$ while higher-redshift objects may appear bluer, since the hot and bright UV is shifted into the observed bands)}, they still effectively distinguish the fast events from traditional SN types.
 \replyref{Here, we} attempt to select a sample based on observed rise times and colours at peak brightness.
@@
 \subsubsection{SNe and GRBs \label{subsubsec:compare_CCSNe}}
-\replyref{It is likely that the progenitor and explosion scenario of the DES RET sample is heterogeneous in origin and may include some known classes of transient, and as such we choose various samples of host galaxies from the literature to compare the DES RET hosts to.}
+\replyref{It is likely that the progenitor and explosion scenario of the DES RET sample is heterogeneous in origin and may include some known classes of transient, and as such we choose samples of host galaxies of various transients from the literature to compare the DES RET hosts to.}
 In compiling a set of comparison samples, we aim for the least biased selections possible.
@@
 While in practice the second and third of these criteria are difficult to achieve, particularly with the fainter CCSNe, we are able to choose comparison samples from untargetted surveys to mitigate initial selection biases.
-\replyref{We choose large enough samples that a significant statistical comparison can be drawn, and thus do not split the major groups of SNe into sub-types.}
+\replyref{We choose large enough samples that a significant statistical comparison can be drawn, and thus do not split the major groups of SNe into sub-types, with the exception of SNe Ic-BL whose signature has been identified in two of the literature RETs introduced above.}
 
@@
 We are able to do this SED fit for 38 objects, with the others lying outside of the SDSS footprint.
+
+\replyref{The individually reported rapid transients SN2018gep and iPTF16asu displayed spectra resembling SN Ic-BL.
+We thus compare the DES RET hosts to the sample of 14 nearby (mean redshift 0.07) SN Ic-BL hosts from \citet{Modjaz2019}.}
 
@@
 However the spectroscopic follow-up of DES RETs was performed as part of the magnitude-limited OzDES survey (Section \ref{subsec:spec}), which has similar selection biases and incompleteness effects to SDSS, albeit shifted to a higher redshift.
-In comparison, the many dwarf galaxies in LVL would not be detected in DES photometry, or get a redshift measurement from OzDES, and thus such a comparison sample is not representative of the way the DES RET host sample was observed.}
+In comparison, the many dwarf galaxies in LVL would not be detected in DES photometry, or get a redshift measurement from OzDES, and thus such a comparison sample is not representative of the way the DES RET host sample was observed.
+For completeness and illustrative purposes only, we display both the SDSS and LVL comparison samples.}
 
@@
 
-\caption{Host galaxy properties for the 49 DES RET host galaxies with redshifts and host galaxy spectra. The table is available in the online version in a machine readable format.}
+\caption{Host galaxy properties for the 49 DES RET host galaxies with redshifts and host galaxy spectra. The full table is available in the online version in a machine readable format.}
 \begin{threeparttable}
@@
 DES13S2wxf  &   $9.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.06}$ &   $0.29 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.10}$ &   $-9.57 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $7.62 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 0.62}$ &                                                             - &                                                             - &                                                             - &  $7.62 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 0.62}$ &                                                             - \\
-DES13X1hav  &   $9.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.38}$ &  $-0.44 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.93}$ &   $-9.60 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.55}$ &  $8.62 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.24}$ &                                                             - &                                                             - &                                                             - &  $8.62 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.24}$ &  $8.28 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.24}$ \\
-DES13X2wvv  &   $9.79 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.34}$ &   $0.19 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.25}$ &   $-9.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.91}$ &  $8.68 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &                                                             - &  $8.68 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.15}$ &  $8.33 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.16}$ \\
-DES13X3gmd  &  $10.33 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.44}$ &   $0.74 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.86}$ &   $-9.59 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.42}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES13X3gms  &   $9.41 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.27}$ &  $-0.06 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.78}$ &   $-9.47 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.52}$ &  $8.51 _{\scriptscriptstyle 0.96} ^{\scriptscriptstyle 0.50}$ &                                                             - &                                                             - &                                                             - &  $8.51 _{\scriptscriptstyle 0.96} ^{\scriptscriptstyle 0.50}$ &  $8.21 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.48}$ \\
-DES13X3npb  &  $11.02 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.18}$ &   $1.14 _{\scriptscriptstyle 0.70} ^{\scriptscriptstyle 1.35}$ &   $-9.88 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 1.17}$ &  $8.72 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.23}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.23}$ &  $8.37 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.26}$ \\
-DES13X3nyg  &   $9.31 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.42}$ &   $0.05 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.73}$ &   $-9.27 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &  $7.69 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.61}$ &                                                             - &                                                             - &                                                             - &  $7.69 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.61}$ &                                                             - \\
-DES14C3tnz  &  $10.21 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.41}$ &   $0.78 _{\scriptscriptstyle 0.60} ^{\scriptscriptstyle 0.88}$ &   $-9.44 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.47}$ &  $8.38 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.42}$ &                                                             - &                                                             - &                                                             - &  $8.38 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.42}$ &  $8.15 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.29}$ \\
-DES14C3tvw  &  $11.09 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &   $1.02 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.39}$ &  $-10.07 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.29}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES14S2anq  &   $9.41 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.23}$ &  $-0.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.54}$ &   $-9.75 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.32}$ &  $8.34 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.02}$ &  $8.16 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.09}$ &  $8.34 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.35 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &  $8.36 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.29 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ \\
-DES14S2plb  &  $10.36 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.25}$ &   $0.89 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.77}$ &   $-9.47 _{\scriptscriptstyle 0.40} ^{\scriptscriptstyle 0.52}$ &  $8.65 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.29}$ &  $8.65 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.06}$ &  $8.63 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.62 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &  $8.95 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.04}$ &  $8.64 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.04}$ \\
-DES14S2pli  &  $10.27 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.34}$ &   $0.50 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.61}$ &   $-9.77 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.27}$ &  $8.95 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &                                                             - &                                                             - &                                                             - &  $8.95 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &  $8.61 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.07}$ \\
-DES14X1bnh  &  $11.71 _{\scriptscriptstyle 0.69} ^{\scriptscriptstyle 0.25}$ &   $1.53 _{\scriptscriptstyle 0.95} ^{\scriptscriptstyle 0.52}$ &  $-10.18 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES14X3pkl  &   $9.60 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.26}$ &   $0.26 _{\scriptscriptstyle 0.85} ^{\scriptscriptstyle 0.72}$ &   $-9.34 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.46}$ &  $8.38 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.20}$ &  $8.22 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.23}$ &  $8.48 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &  $8.52 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ \\
-DES15C2eal  &   $8.42 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.18}$ &  $-1.29 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.33}$ &   $-9.72 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.15}$ &  $8.30 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.25}$ &  $8.04 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.32}$ &  $8.32 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.19}$ &  $8.34 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.15}$ &  $8.39 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.50}$ &  $8.28 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.25}$ \\
-DES15C3lpq  &   $9.32 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.39}$ &   $0.86 _{\scriptscriptstyle 0.73} ^{\scriptscriptstyle 1.08}$ &   $-8.45 _{\scriptscriptstyle 0.53} ^{\scriptscriptstyle 0.68}$ &  $8.30 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.33}$ &                                                             - &                                                             - &                                                             - &  $8.30 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.33}$ &  $8.15 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.14}$ \\
-DES15C3lzm  &  $10.06 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.28}$ &   $1.08 _{\scriptscriptstyle 0.68} ^{\scriptscriptstyle 0.75}$ &   $-8.98 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.47}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES15C3mem  &  $10.76 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.37}$ &   $1.04 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.64}$ &   $-9.72 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES15C3mgq  &   $8.41 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.29}$ &  $-1.12 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.55}$ &   $-9.53 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &  $8.37 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.29}$ &  $8.45 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 0.48}$ &  $8.43 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.24}$ &  $8.34 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.11}$ &  $8.34 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.39}$ &  $8.32 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.20}$ \\
-DES15C3nat  &  $10.49 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.58}$ &   $1.14 _{\scriptscriptstyle 0.60} ^{\scriptscriptstyle 0.98}$ &   $-9.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.41}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES15C3opk  &   $9.89 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.22}$ &   $0.89 _{\scriptscriptstyle 1.20} ^{\scriptscriptstyle 0.67}$ &   $-9.01 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.45}$ &  $8.57 _{\scriptscriptstyle 0.80} ^{\scriptscriptstyle 0.33}$ &                                                             - &                                                             - &                                                             - &  $8.57 _{\scriptscriptstyle 0.80} ^{\scriptscriptstyle 0.33}$ &  $8.24 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.31}$ \\
-DES15C3opp  &   $9.15 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.32}$ &   $0.13 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.84}$ &   $-9.02 _{\scriptscriptstyle 0.57} ^{\scriptscriptstyle 0.52}$ &  $8.45 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.32}$ &                                                             - &                                                             - &                                                             - &  $8.45 _{\scriptscriptstyle 0.59} ^{\scriptscriptstyle 0.32}$ &  $8.17 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.24}$ \\
-DES15E2nqh  &   $9.28 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.28}$ &   $0.11 _{\scriptscriptstyle 0.72} ^{\scriptscriptstyle 0.94}$ &   $-9.17 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.66}$ &  $8.83 _{\scriptscriptstyle 0.52} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &                                                             - &  $8.83 _{\scriptscriptstyle 0.52} ^{\scriptscriptstyle 0.15}$ &  $8.48 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.17}$ \\
-DES15S1fli  &  $10.24 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.26}$ &   $1.54 _{\scriptscriptstyle 1.01} ^{\scriptscriptstyle 0.67}$ &   $-8.70 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.41}$ &  $8.86 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &                                                             - &                                                             - &                                                             - &  $8.86 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &  $8.52 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.07}$ \\
-DES15S1fll  &   $9.20 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.32}$ &  $-0.14 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.54}$ &   $-9.34 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 0.22}$ &  $8.26 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.23}$ &  $8.37 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.36}$ &  $8.28 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.13}$ &  $8.22 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.10}$ &  $8.26 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.34}$ &  $8.22 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.12}$ \\
-DES15X2ead  &   $9.92 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.20}$ &   $0.22 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.47}$ &   $-9.69 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.27}$ &  $8.45 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.23}$ &  $8.22 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.25}$ &  $8.47 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.15}$ &  $8.52 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.14}$ &  $8.61 _{\scriptscriptstyle 0.77} ^{\scriptscriptstyle 0.38}$ &  $8.43 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.24}$ \\
-DES15X3mxf  &   $9.93 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.32}$ &   $0.78 _{\scriptscriptstyle 1.18} ^{\scriptscriptstyle 0.90}$ &   $-9.15 _{\scriptscriptstyle 0.88} ^{\scriptscriptstyle 0.58}$ &  $8.72 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.15}$ &                                                             - &                                                             - &                                                             - &  $8.72 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.15}$ &  $8.36 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.16}$ \\
-DES16C1cbd  &  $10.77 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.22}$ &  $-1.43 _{\scriptscriptstyle 1.94} ^{\scriptscriptstyle 1.48}$ &  $-12.20 _{\scriptscriptstyle 1.79} ^{\scriptscriptstyle 1.26}$ &  $8.79 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.20}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.20}$ &  $8.44 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.22}$ \\
-DES16C2ggt  &   $9.86 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.36}$ &   $0.13 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.94}$ &   $-9.73 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.59}$ &  $8.50 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.33}$ &  $8.28 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.17}$ &  $8.45 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.10}$ &  $8.51 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.05}$ &  $8.85 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.06}$ &  $8.50 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ \\
-DES16C3axz  &   $9.85 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.33}$ &   $0.20 _{\scriptscriptstyle 0.56} ^{\scriptscriptstyle 0.78}$ &   $-9.65 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.44}$ &  $8.59 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.37}$ &  $8.53 _{\scriptscriptstyle 0.05} ^{\scriptscriptstyle 0.05}$ &  $8.56 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &  $8.59 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &  $8.97 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.03}$ &  $8.61 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
-DES16C3gin  &   $9.85 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.32}$ &   $0.45 _{\scriptscriptstyle 0.68} ^{\scriptscriptstyle 1.00}$ &   $-9.41 _{\scriptscriptstyle 0.41} ^{\scriptscriptstyle 0.68}$ &  $8.84 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.12}$ &                                                             - &                                                             - &                                                             - &  $8.84 _{\scriptscriptstyle 0.23} ^{\scriptscriptstyle 0.12}$ &  $8.49 _{\scriptscriptstyle 0.22} ^{\scriptscriptstyle 0.14}$ \\
-DES16E2pv   &   $9.57 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.43}$ &   $0.07 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.98}$ &   $-9.50 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.55}$ &  $8.93 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.11}$ &                                                             - &                                                             - &                                                             - &  $8.93 _{\scriptscriptstyle 0.34} ^{\scriptscriptstyle 0.11}$ &  $8.59 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.13}$ \\
-DES16S1bbp  &   $9.06 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &   $0.30 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.79}$ &   $-8.75 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.49}$ &  $8.25 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.10}$ &  $8.11 _{\scriptscriptstyle 0.33} ^{\scriptscriptstyle 0.25}$ &  $8.25 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.07}$ &  $8.31 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.05}$ &  $8.24 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.13}$ &  $8.24 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.04}$ \\
-DES16S1dxu  &   $8.60 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.41}$ &  $-0.49 _{\scriptscriptstyle 0.71} ^{\scriptscriptstyle 1.70}$ &   $-9.09 _{\scriptscriptstyle 0.43} ^{\scriptscriptstyle 1.29}$ &  $8.26 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.12}$ &  $8.33 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.38}$ &  $8.24 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.11}$ &  $8.27 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.07}$ &  $8.27 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.10}$ &  $8.22 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.07}$ \\
-DES16X1eho  &  $10.70 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.42}$ &   $0.01 _{\scriptscriptstyle 0.50} ^{\scriptscriptstyle 1.33}$ &  $-10.69 _{\scriptscriptstyle 0.26} ^{\scriptscriptstyle 0.91}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES16X3cxn  &   $9.55 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.57}$ &  $-0.32 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 1.00}$ &   $-9.88 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.43}$ &  $8.79 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.16}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.16}$ &  $8.43 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.18}$ \\
-DES16X3ega  &   $9.94 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.18}$ &   $0.30 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.26}$ &   $-9.64 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.08}$ &  $8.58 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ &  $8.44 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.17}$ &  $8.47 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &  $8.61 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.07}$ &  $8.77 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.06}$ &  $8.51 _{\scriptscriptstyle 0.08} ^{\scriptscriptstyle 0.08}$ \\
-DES16X3erw  &   $9.89 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.26}$ &   $0.94 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.62}$ &   $-8.94 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.36}$ &  $8.84 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.84 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.09}$ &  $8.49 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.10}$ \\
-DES17C2hno  &   $9.56 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.16}$ &  $-0.02 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.33}$ &   $-9.58 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.17}$ &  $8.78 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.17}$ &                                                             - &                                                             - &                                                             - &  $8.78 _{\scriptscriptstyle 0.31} ^{\scriptscriptstyle 0.17}$ &  $8.43 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.19}$ \\
-DES17C3fwd  &  $10.07 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.23}$ &   $0.84 _{\scriptscriptstyle 0.78} ^{\scriptscriptstyle 0.50}$ &   $-9.22 _{\scriptscriptstyle 0.64} ^{\scriptscriptstyle 0.27}$ &  $8.34 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.12}$ &                                                             - &  $8.35 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.18}$ &  $8.38 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.08}$ &  $8.29 _{\scriptscriptstyle 0.10} ^{\scriptscriptstyle 0.11}$ &  $8.30 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.10}$ \\
-DES17C3gop  &   $9.90 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.58}$ &   $0.19 _{\scriptscriptstyle 0.38} ^{\scriptscriptstyle 0.86}$ &   $-9.71 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ &  $8.79 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.21}$ &                                                             - &                                                             - &                                                             - &  $8.79 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.21}$ &  $8.43 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.24}$ \\
-DES17S2fee  &  $11.20 _{\scriptscriptstyle 0.14} ^{\scriptscriptstyle 0.22}$ &   $0.28 _{\scriptscriptstyle 1.91} ^{\scriptscriptstyle 0.70}$ &  $-10.92 _{\scriptscriptstyle 1.77} ^{\scriptscriptstyle 0.48}$ &  $8.75 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.52}$ &  $8.55 _{\scriptscriptstyle 0.48} ^{\scriptscriptstyle 0.42}$ &  $8.95 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.47}$ &                                                             - &                                                             - &                                                             - \\
-DES17X3cds  &   $9.36 _{\scriptscriptstyle 0.12} ^{\scriptscriptstyle 0.31}$ &  $-0.18 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.83}$ &   $-9.53 _{\scriptscriptstyle 0.13} ^{\scriptscriptstyle 0.52}$ &  $8.69 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.69 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.26}$ &  $8.33 _{\scriptscriptstyle 0.28} ^{\scriptscriptstyle 0.28}$ \\
-DES17X3dxu  &  $10.49 _{\scriptscriptstyle 0.32} ^{\scriptscriptstyle 0.22}$ &   $1.02 _{\scriptscriptstyle 0.69} ^{\scriptscriptstyle 0.63}$ &   $-9.47 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.40}$ &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - &                                                             - \\
-DES17X3hxi  &   $8.60 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.00}$ &  $-0.37 _{\scriptscriptstyle 0.11} ^{\scriptscriptstyle 0.10}$ &   $-8.96 _{\scriptscriptstyle 0.00} ^{\scriptscriptstyle 0.10}$ &  $8.45 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.26}$ &                                                             - &                                                             - &                                                             - &  $8.45 _{\scriptscriptstyle 0.45} ^{\scriptscriptstyle 0.26}$ &  $8.18 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.18}$ \\
-
 \bottomrule
@@
 \includegraphics[width=0.5\textwidth]{figs/SFR_Mike_RETs.png}
-\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, and SDSS field galaxies (grey contours).
+\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, as well as SDSS field galaxies (grey contours) and \replyref{LVL galaxies (grey circles)}.
 SFRs have not been corrected for redshift evolution.
@@
 \includegraphics[width=0.5\textwidth]{figs/SFR_Mike_Other.png}
-\caption{Same as Fig.~\ref{fig:sfms_sfr}, but comparing RET hosts with hosts of SESNe, LGRBs and SLSNe, and SDSS field galaxies (grey contours).
+\caption{Same as Fig.~\ref{fig:sfms_sfr}, but comparing RET hosts with hosts of \replyref{SNe Ic-BL}, LGRBs and SLSNe, as well as SDSS field galaxies (grey contours) and \replyref{LVL galaxies (grey circles)}.
 \label{fig:sfms_sfr_other}}
@@
 \subsection{Star formation rate \label{subsec:res_sfr}}
-Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, split in two for clarity, show the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS.
+Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, split in two for clarity, show the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS \replyref{and the LVL sample}.
 RETs follow CCSNe, LGRBs and SLSNe in avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars.
@@
 Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency.
-It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR.
+It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR, \replyref{as well as the limited number of LVL galaxies that are as massive as the RET hosts}.
 Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments of LGRBs or SLSNe.
+\replyref{In contrast, the RET sSFR distribution appears well aligned with that of SNe Ic-BL.
+While the sSFR histograms for RETs and SNe Ic-BL appear similar to that for the LVL sample, it is clear that the transient hosts lie at higher mass, where the LVL sSFRs are lower.
+The incompleteness of the DES RET host sample at low mass prohibits a direct comparison with the majority of the LVL galaxies.}
 
@@
 \includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_RETs.png}
-\caption{The $M_* -$ sSFR sequence of RET hosts as well as local rapid transients and SNe II, along with the SDSS field galaxies.
+\caption{The $M_* -$ sSFR sequence of RET hosts as well as local rapid transients and SNe II, along with the SDSS field galaxies \replyref{and LVL galaxies}.
 \label{fig:sfms_ssfr}}
@@
 \includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_other.png}
-\caption{Same as Fig.~\ref{fig:sfms_ssfr} but comparing RET hosts with hosts of SESN, LGRB, and SLSN hosts, along with the SDSS field galaxies.
+\caption{Same as Fig.~\ref{fig:sfms_ssfr} but comparing RET hosts with hosts of SESN, LGRB, and SLSN hosts, along with the SDSS field galaxies \replyref{and LVL galaxies}.
 \label{fig:sfms_ssfr_other}}
@@
 We determine that the RET host metallicities are derived from a different population to the SNe II.
-On the other hand, simultaneous fits with SESNe show very similar distributions, including a smaller higher-metallicity peak, such that they are indistinguishable statistically.
+On the other hand, simultaneous fits with SESNe \replyref{and SNe Ic-BL} show very similar distributions, including a smaller higher-metallicity peak, such that they are indistinguishable statistically.
 
@@
 \replyref{While it is likely that RETs are a heterogeneous population comprising several progenitor scenarios, it is reasonable to infer from the rates and the host properties} that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSN or LGRB \replyref{progenitors such as rapid rotation and low metallicity}.
-This hypothesis \replyref{can be extended to posit} that \replyref{some} RETs \replyref{signify} an intermediate and/or precursory step \replyref{in the late stages of evolution of a massive star that is close to forming a SLSN or LGRB, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling driving the RET light curve (\citetalias{Pursiainen2018}), but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form, hence the lack of longer-term light curves.
+This hypothesis \replyref{can be extended to posit} that \replyref{some} RETs \replyref{represent} an intermediate and/or precursory step \replyref{in the late stages of evolution of a massive star that is close to forming a SLSN or LGRB, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling driving the RET light curve (\citetalias{Pursiainen2018}), but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form, hence the lack of longer-term light curves.
 }
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\newpage
 \appendix
-\onecolumn
+%\onecolumn
 \section{Spectral line fluxes}
@@
 \caption{Emission line fluxes for DES RET host galaxies.
-Values are given in units of erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$, and have been corrected for Milky Way reddening using \citet{Schlegel1998} assuming a \citet{Cardelli1989} reddening law with $R_V = 3.1$, but have not been corrected for intrinsic host galaxy reddening.\label{tab:fluxes}}
+Values are given in units of erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$, and have been corrected for Milky Way reddening using \citet{Schlegel1998} assuming a \citet{Cardelli1989} reddening law with $R_V = 3.1$, but have not been corrected for intrinsic host galaxy reddening.\label{tab:fluxes}.
+\replyref{A full length, machine readable version of this table is available in the online version.}}
 \setlength{\tabcolsep}{3pt}
@@
 DES13X1hav  &    $3.0 \pm 1.2$ &  $1.0 \pm 0.6$ &   $3.0 \pm 0.6$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.5 \pm 0.5$ &   $0.9 \pm 0.3$ &               - \\
-DES13X3nyg  &    $2.6 \pm 0.6$ &  $0.1 \pm 0.4$ &   $0.3 \pm 0.4$ &              - &               - &              - &              - &  $0.1 \pm 0.2$ &   $0.0 \pm 0.2$ &   $0.1 \pm 0.1$ &               - \\
-DES13X3gmd  &    $2.7 \pm 0.7$ &              - &               - &              - &               - &              - &              - &  $0.1 \pm 0.4$ &   $0.3 \pm 0.4$ &   $1.3 \pm 1.0$ &               - \\
-DES13C3bcok &    $3.6 \pm 3.8$ &  $0.7 \pm 1.2$ &   $2.2 \pm 1.2$ &              - &               - &              - &              - &  $0.0 \pm 1.2$ &   $2.0 \pm 1.4$ &   $2.3 \pm 1.0$ &  $10.8 \pm 3.0$ \\
-DES13X2wvv  &   $16.4 \pm 2.7$ &  $2.9 \pm 1.4$ &   $8.8 \pm 1.4$ &              - &               - &              - &              - &  $1.1 \pm 1.3$ &   $0.6 \pm 1.2$ &   $4.3 \pm 1.1$ &               - \\
-DES14X1bnh  &    $8.3 \pm 0.8$ &              - &               - &              - &               - &              - &              - &  $0.1 \pm 0.3$ &   $1.0 \pm 0.3$ &               - &               - \\
-DES15S1fli  &   $15.0 \pm 1.6$ &  $1.3 \pm 1.0$ &   $3.9 \pm 1.0$ &              - &               - &              - &              - &  $1.4 \pm 0.8$ &   $2.2 \pm 0.6$ &   $4.3 \pm 0.5$ &               - \\
-DES15S1fll  &   $10.3 \pm 2.5$ &  $5.0 \pm 2.0$ &  $15.2 \pm 2.0$ &  $0.5 \pm 1.1$ &   $1.4 \pm 1.1$ &  $0.8 \pm 0.8$ &  $1.5 \pm 0.8$ &  $0.6 \pm 1.1$ &   $2.5 \pm 1.3$ &   $4.2 \pm 1.5$ &  $15.4 \pm 1.4$ \\
-DES14X3pkl  &    $2.5 \pm 1.2$ &  $0.8 \pm 0.4$ &   $2.3 \pm 0.4$ &  $0.2 \pm 0.2$ &   $0.5 \pm 0.2$ &  $0.8 \pm 0.2$ &  $0.4 \pm 0.2$ &  $0.4 \pm 0.5$ &   $0.6 \pm 0.6$ &   $0.0 \pm 0.7$ &   $2.3 \pm 0.3$ \\
-DES13X3npb  &   $15.9 \pm 6.6$ &  $0.8 \pm 0.8$ &   $2.4 \pm 0.8$ &              - &               - &              - &              - &  $2.0 \pm 0.7$ &   $2.6 \pm 0.4$ &   $3.3 \pm 0.8$ &               - \\
-DES15X2ead  &  $31.4 \pm 23.5$ &  $1.6 \pm 3.0$ &   $4.8 \pm 3.0$ &  $1.1 \pm 1.6$ &   $3.5 \pm 1.6$ &  $5.3 \pm 1.7$ &  $3.2 \pm 1.9$ &  $9.6 \pm 7.9$ &   $4.5 \pm 6.0$ &   $5.4 \pm 3.1$ &  $16.7 \pm 1.9$ \\
-DES14S2plb  &   $54.5 \pm 7.2$ &  $4.5 \pm 2.1$ &  $13.5 \pm 2.1$ &  $5.6 \pm 1.8$ &  $16.9 \pm 1.8$ &  $9.5 \pm 0.9$ &  $7.1 \pm 0.7$ &  $6.5 \pm 2.0$ &   $7.9 \pm 1.7$ &  $19.3 \pm 1.5$ &  $53.4 \pm 1.7$ \\
-DES14S2pli  &    $7.7 \pm 1.1$ &  $0.4 \pm 0.4$ &   $1.2 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.6$ &   $1.1 \pm 0.5$ &   $2.4 \pm 0.3$ &               - \\
-DES14C3tnz  &    $4.2 \pm 0.9$ &  $0.4 \pm 0.3$ &   $1.3 \pm 0.3$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.4 \pm 0.3$ &   $0.4 \pm 0.5$ &               - \\
-DES15X3mxf  &    $4.8 \pm 0.7$ &  $0.4 \pm 0.3$ &   $1.2 \pm 0.3$ &              - &               - &              - &              - &  $0.6 \pm 0.5$ &   $0.7 \pm 0.4$ &   $1.1 \pm 0.3$ &               - \\
-DES15C3lpq  &    $3.9 \pm 0.8$ &  $0.5 \pm 0.3$ &   $1.6 \pm 0.3$ &              - &               - &              - &              - &  $0.5 \pm 0.3$ &   $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &               - \\
-DES15C3nat  &    $3.9 \pm 0.6$ &              - &               - &              - &               - &              - &              - &  $0.2 \pm 0.1$ &   $0.2 \pm 0.1$ &               - &               - \\
-DES15C3mgq  &    $4.1 \pm 2.5$ &  $1.1 \pm 0.5$ &   $3.2 \pm 0.5$ &  $0.1 \pm 0.2$ &   $0.2 \pm 0.2$ &  $0.2 \pm 0.2$ &  $0.0 \pm 0.4$ &  $0.6 \pm 0.8$ &   $0.4 \pm 0.7$ &   $1.2 \pm 0.5$ &   $1.4 \pm 0.2$ \\
-DES15E2nqh  &    $0.7 \pm 1.0$ &  $0.9 \pm 0.5$ &   $2.8 \pm 0.5$ &              - &               - &              - &              - &  $0.4 \pm 0.4$ &   $0.9 \pm 0.5$ &   $0.8 \pm 0.5$ &               - \\
-DES15C3opk  &    $1.6 \pm 0.8$ &  $0.5 \pm 0.3$ &   $1.4 \pm 0.3$ &              - &               - &              - &              - &  $0.1 \pm 0.3$ &   $0.3 \pm 0.2$ &   $0.4 \pm 0.3$ &               - \\
-DES15C3opp  &    $2.5 \pm 0.7$ &  $0.2 \pm 0.2$ &   $0.5 \pm 0.2$ &              - &               - &              - &              - &  $0.2 \pm 0.4$ &   $0.5 \pm 0.3$ &   $0.4 \pm 0.1$ &               - \\
-DES16E2pv   &    $2.5 \pm 0.6$ &  $0.7 \pm 1.0$ &   $2.2 \pm 1.0$ &              - &               - &              - &              - &  $0.0 \pm 0.4$ &   $0.7 \pm 0.5$ &   $1.3 \pm 0.6$ &               - \\
-DES16S1bbp  &   $21.9 \pm 3.5$ &  $3.8 \pm 0.9$ &  $11.4 \pm 0.9$ &  $0.3 \pm 0.4$ &   $1.0 \pm 0.4$ &  $1.5 \pm 0.7$ &  $0.9 \pm 0.3$ &  $1.4 \pm 1.1$ &   $3.4 \pm 0.9$ &   $6.4 \pm 1.0$ &  $11.1 \pm 0.6$ \\
-DES16X3cxn  &    $2.3 \pm 0.5$ &  $0.3 \pm 0.4$ &   $0.9 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &               - \\
-DES16C1cbd  &    $4.4 \pm 1.8$ &  $0.4 \pm 0.8$ &   $1.2 \pm 0.8$ &              - &               - &              - &              - &  $0.4 \pm 0.4$ &   $0.4 \pm 0.4$ &   $1.1 \pm 0.4$ &               - \\
-DES16C3axz  &   $26.8 \pm 2.6$ &  $2.3 \pm 0.8$ &   $7.0 \pm 0.8$ &  $2.6 \pm 0.6$ &   $7.7 \pm 0.6$ &  $5.4 \pm 0.5$ &  $4.0 \pm 0.5$ &  $2.7 \pm 0.9$ &   $5.6 \pm 0.8$ &   $9.9 \pm 0.8$ &  $29.1 \pm 0.7$ \\
-DES16X3erw  &    $5.9 \pm 0.9$ &  $0.8 \pm 0.6$ &   $2.6 \pm 0.6$ &              - &               - &              - &              - &  $0.6 \pm 0.4$ &   $0.4 \pm 0.4$ &   $1.9 \pm 0.3$ &               - \\
-DES16C3gin  &    $5.8 \pm 1.2$ &  $0.5 \pm 0.4$ &   $1.6 \pm 0.4$ &              - &               - &              - &              - &  $0.5 \pm 0.6$ &   $0.0 \pm 0.6$ &   $1.6 \pm 0.4$ &   $2.5 \pm 0.4$ \\
-DES16S1dxu  &   $29.2 \pm 3.6$ &  $6.4 \pm 1.9$ &  $19.5 \pm 1.9$ &  $0.4 \pm 1.0$ &   $1.2 \pm 1.0$ &  $0.5 \pm 1.0$ &  $1.4 \pm 0.7$ &  $1.7 \pm 1.1$ &   $2.9 \pm 0.9$ &   $8.6 \pm 1.1$ &  $16.5 \pm 0.8$ \\
-DES16X1eho  &    $2.5 \pm 0.9$ &              - &               - &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.2 \pm 0.4$ &   $0.7 \pm 0.5$ &               - \\
-DES17C3gop  &    $2.0 \pm 0.8$ &  $0.2 \pm 0.3$ &   $0.6 \pm 0.3$ &              - &               - &              - &              - &  $0.2 \pm 0.3$ &   $0.6 \pm 0.4$ &   $0.5 \pm 0.2$ &               - \\
-DES17S2fee  &    $0.8 \pm 5.1$ &  $0.0 \pm 1.2$ &   $0.0 \pm 1.2$ &  $0.4 \pm 1.0$ &   $1.2 \pm 1.0$ &  $0.4 \pm 1.1$ &  $1.4 \pm 1.0$ &  $0.0 \pm 1.2$ &   $0.6 \pm 1.2$ &   $0.0 \pm 1.0$ &   $2.3 \pm 0.7$ \\
-DES17X3dxu  &    $3.1 \pm 0.5$ &              - &               - &              - &               - &              - &              - &  $0.7 \pm 0.5$ &   $0.7 \pm 0.2$ &               - &               - \\
-DES17X3cds  &    $3.3 \pm 1.8$ &  $0.4 \pm 0.4$ &   $1.4 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.4$ &   $0.3 \pm 0.3$ &   $0.8 \pm 0.3$ &               - \\
-DES17C3fwd  &   $14.7 \pm 1.5$ &  $2.0 \pm 0.6$ &   $6.2 \pm 0.6$ &  $0.3 \pm 0.6$ &   $0.8 \pm 0.6$ &              - &              - &  $1.1 \pm 0.7$ &   $0.5 \pm 0.7$ &   $3.8 \pm 0.5$ &   $6.2 \pm 1.5$ \\
-DES17X3hxi  &    $5.4 \pm 1.8$ &  $2.3 \pm 0.9$ &   $7.1 \pm 0.9$ &              - &               - &              - &              - &  $1.0 \pm 0.7$ &   $1.6 \pm 0.7$ &   $1.6 \pm 0.5$ &               - \\
-DES13E2lpk  &    $8.9 \pm 1.5$ &  $0.4 \pm 0.5$ &   $1.2 \pm 0.5$ &              - &               - &              - &              - &  $0.4 \pm 0.6$ &   $0.8 \pm 0.5$ &   $2.4 \pm 0.4$ &               - \\
-DES15C2eal  &    $1.9 \pm 0.6$ &  $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &  $0.1 \pm 0.2$ &   $0.2 \pm 0.2$ &  $0.4 \pm 0.2$ &  $0.5 \pm 0.2$ &  $0.0 \pm 0.2$ &   $0.3 \pm 0.2$ &   $0.4 \pm 0.3$ &   $2.1 \pm 0.3$ \\
-DES16C2ggt  &   $11.8 \pm 1.2$ &  $1.1 \pm 0.4$ &   $3.2 \pm 0.4$ &  $0.4 \pm 0.4$ &   $1.4 \pm 0.4$ &  $1.7 \pm 0.3$ &  $1.1 \pm 0.3$ &  $0.4 \pm 0.5$ &   $1.5 \pm 0.6$ &   $3.4 \pm 0.4$ &   $6.9 \pm 0.5$ \\
-DES17C2hno  &    $3.7 \pm 1.1$ &  $0.2 \pm 0.2$ &   $0.7 \pm 0.2$ &              - &               - &              - &              - &  $0.4 \pm 0.5$ &   $0.6 \pm 0.4$ &   $0.9 \pm 0.2$ &               - \\
+
 \bottomrule
@@
 
-\newpage
+%\newpage
 \section{Bayesian Fits - sSFR}
@@
 \begin{figure*}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_histfit_ssfr_final.png}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_s12_histfit_ssfr_final.png}
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SESNe, accounting for uncertainties in each bin.
@@
 
-\begin{figure*}
-\includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
+\begin{figure}
+\includegraphics[width=0.6\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
 \caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
@@
 \label{fig:corner}}
-\end{figure*}
+\end{figure}
 
@@
 We then compare the differences in these parameters, as seen in Fig.~\ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
-\twocolumn
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
+%\twocolumn
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_m19_histfit_ssfr_final.png}
+\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe Ic-BL, accounting for uncertainties in each bin.
+\label{fig:histfit_ssfr_s13}}
+\end{figure}
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_OH_histfit_final.png}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_s12_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
@@
 \end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_OH_histfit_final.png}
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_m19_OH_histfit_final.png}
+\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe Ic-BL, accounting for uncertainties in each bin.
+\label{fig:histfit_ssfr_k15}}
+\end{figure}
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_k15_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_OH_histfit_final.png}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_p16_OH_histfit_final.png}
 \caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SLSNe, accounting for uncertainties in each bin.

### 2020-07-24 DES_RET_Hosts_replyref.tex
Updates from Overleaf

@@
 It displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018}, developing to something entirely different at later epochs \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.} There are many diverse explanations for the power source of AT2018cow \replyref{proposed} in the literature, including: \replyref{engine-driven stellar explosions \citep{Ho2019,Margutti2019,Mohan2020}}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Piro2020,Uno2020}.
-Other nearby \replyref{($z<0.1$)} rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star merger, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} \replyref{which is a rapidly-declining, spectroscopically classified, nearby SN Ic-BL with a rapid rise to peak}, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.} \replyref{These objects evolved rapidly enough to have passed the DES RET criteria (Section \ref{subsec:new_method}) even at $z\sim1$ where they would appear slower, although they (or their host galaxies) may not necessarily have been bright enough to be detected.}
+Other nearby \replyref{($z<0.1$)} rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star\replyref{black hole} merger \citep{Gillanders2020}, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} \replyref{which is a rapidly-declining, spectroscopically classified, nearby SN Ic-BL with a rapid rise to peak}, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.} \replyref{These objects evolved rapidly enough to have passed the DES RET criteria (Section \ref{subsec:new_method}) even at $z\sim1$ where they would appear slower, although they (or their host galaxies) may not necessarily have been bright enough to be detected.}
 
@@
 To estimate parameters from the OzDES host galaxy spectra requires several processing steps.
-We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}).
+We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in Swann et al., \textit{in prep}).
 We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
@@
 The remaining 0.30 dex is thus consistent with being an intrinsic difference.
+\replyref{The locs of the DES RETs and SNe Ic-BL differ by 0.51 dex, although this corresponds to a large difference in skewness of -3.4 -- that is, SNe Ic-BL sSFRs peak at lower values than DES RETs, but in general show a similar distribution.
+Given ths small number of SNe Ic-BL hosts considered, it is not possible to say that the DES RETs and SNe Ic-BL originate in hosts with significantly different sSFR distributions.}
 RET host galaxies are significantly lower in sSFR than LGRBs.
@@
 We determine that the RET host metallicities are derived from a different population to the SNe II.
-On the other hand, simultaneous fits with SESNe \replyref{and SNe Ic-BL} show very similar distributions, including a smaller higher-metallicity peak, such that they are indistinguishable statistically.
+On the other hand, simultaneous fits with SESNe show very similar distributions, including a smaller higher-metallicity peak, such that they are indistinguishable statistically.
+\replyref{The SNe Ic-BL host metallicity distribution is not well described by any skewed Gaussian, with a broad peak similar to the DES RETs.
+Despite this, 85\% of realisations suggest that the SNe Ic-BL lie at higher metallicities than DES RETs.}
 
@@
 A loose correlation exists between the luminosity and rarity of events, and the host galaxy conditions required for their formation $-$ on average, rarer events occur in more extreme environments.
-The approximate rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$; \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Coppejans2020}, \citealt{Ho2020}, \citealt{Tampo2020} \replyref{although the definition of RET varies in the above calculations}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe \citep{Kelly2012,Frohmaier2020}.
-At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017,Frohmaier2020}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
+The approximate rate of RETs ($\geq 10^{-6} \mathrm{Mpc}^{-3} \mathrm{yr}^{-1}$; \citealt{Drout2014}, \citetalias{Pursiainen2018}, \citealt{Coppejans2020}, \citealt{Ho2020}, \citealt{Tampo2020} \replyref{although the definition of RET varies in the above calculations}) is $\sim1\%$ of the CCSN rate \citep{Li2011,Horiuchi2011,Strolger2015}, which itself is divided into the more common SNe II and sub-dominant SESNe (\citealt{Kelly2012}, Frohmaier et al., \textit{in prep}.
+At $\sim1\%$ of the CCSN rate, RETs are more common than SLSNe ($\sim0.01 - 0.05\%$ of CCSNe; \citealt{McCrum2015,Prajs2017}, Frohmaier et al., \textit{in prep}) and LGRBs (intrinsically $\sim0.08\%$ when accounting for beaming; \citealt{Graham2016}).
 These figures place the rate of DES RETs between extreme objects (SLSNe, LGRBs) and more common SNe (SNe II, SESNe) in terms of rate, matching the location of RET hosts in the various host galaxy parameter spaces presented in Section \ref{sec:analysis}.
@@
 
-SN2018kzr \citep{McBrien2019} is one of the most rapidly declining transients ever discovered, with spectral signatures similar to SNe Ic.
+SN2018kzr \citep{McBrien2019,Gillanders2020} is one of the most rapidly declining transients ever discovered, with spectral signatures similar to SNe Ic.
 While host galaxy properties are not derived, the authors of that paper refer to narrow emission from the host galaxy, along with an apparently small, blue, star-forming host and is thus consistent with the DES RETs.
@@
 \section*{Acknowledgements}
+
+We thank the anonymous referee, whose input has significantly enhanced the quality of this work, particularly for giving up their time to review the work during a unprecedented time of global crisis.
+We thank Maryam Modjaz and Dan Perley for providing
 

### 2020-07-31 referee_response_1.tex

@@
 \vskip0.1cm
-{\bf RESPONSE: } There is no exact definition of a DES RET that does not take up a full section, as per Section 2.2. Instead we have added the typical rise and decline times.
+{\bf RESPONSE: } We appreciate the desire to properly define RET in the abstract; however there is no exact definition of a DES RET that does not take up a full section, as per Section 2.2.
+Instead we have added the typical rise and decline times.
 
@@
 \vskip0.1cm
-{\bf RESPONSE: } Added
+{\bf RESPONSE: } We have added ([O/H])
 
@@
 
+\item Perhaps include a final sentence looking to the future? What is the next step?
+\vskip0.1cm
+{\bf RESPONSE: } Such a sentence was originally in the abstract, but was cut due to the MNRAS abstract word limit. We provide an outlook to future work at the end of the paper.
 \end{enumerate}
@@
 \vskip0.1cm
-{\bf RESPONSE: } Changed
+{\bf RESPONSE: } Changed, thanks!
 
@@
     \vskip0.1cm
-    {\bf RESPONSE: } Added a sentence to the beginning of 2.3.2: \textit{It is likely that the progenitor and explosion scenario of the DES RET sample is heterogeneous in origin and may include some known classes of transient, and as such we choose samples of host galaxies of various transients from the literature to compare the DES RET hosts to}.
+    {\bf RESPONSE: } We have added a sentence to the beginning of 2.3.2: \textit{It is likely that the progenitor and explosion scenario of the DES RET sample is heterogeneous in origin and may include some known classes of transient, and as such we choose samples of host galaxies of various transients from the literature to compare the DES RET hosts to}.
 
@@
 \vskip0.1cm
- {\bf RESPONSE: } Changed
+ {\bf RESPONSE: } Thanks! Changed.
 
@@
  \vskip0.1cm
- {\bf RESPONSE: } Removed
+ {\bf RESPONSE: } Thanks, removed
 
@@
  \vskip0.1cm
- {\bf RESPONSE: } We have added iPTF16asu to the comparison objects
+ {\bf RESPONSE: } Thanks for pointing this out. We have added iPTF16asu to the comparison objects.
 
@@
 We therefore expect similar biases in the DES RET hosts as seen in SDSS.
- We acknowledge the use of comparing to LVL and have included that in the figures, but this is mainly for illustrative purposes, since the bulk of low mass LVL galaxies would not be seen in DES-SN at the redshifts of the RET sample.
+ We acknowledge the use of comparing to the Local Volume Legacy Survey galaxies and have included that in the figures, but this is mainly for illustrative purposes, since the bulk of low mass LVL galaxies would not be seen in DES-SN at the redshifts of the RET sample.
 
@@
    \vskip0.1cm
- {\bf RESPONSE: } We have added a section describing how these difference are negligible compared to the uncertainty caused by low SNR.
+ {\bf RESPONSE: } We have added a sentence describing how these difference are negligible compared to the uncertainty caused by low SNR.
 
@@
  \vskip0.1cm
- {\bf RESPONSE: }Done
+ {\bf RESPONSE: } Done, see above
 
@@
     \vskip0.1cm
- {\bf RESPONSE: }  Added
+ {\bf RESPONSE: }  We have added these references
  \item As stated in the point above, I think that for a rate estimate it is important to be clear how these different papers define RET...Drout+14 spans a large luminosity distribution, for example
 \vskip0.1cm
- {\bf RESPONSE: } Added this caveat
+ {\bf RESPONSE: } We have added this caveat
 

### 2020-07-31 DES_RET_Hosts_replyref.tex

@@
 \begin{abstract}
-Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a recently-discovered group of astrophysical events that display rapid luminosity evolution.
+Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), \replyref{are a recently-discovered group of astrophysical events that display rapid luminosity evolution.
 RETs typically rise to peak in less than 10 days and fade within 30, a timescale unlikely to be compatible with the decay of Nickel-56 that drives conventional SNe.
-Their peak luminosity spans a range of $-15 <M_g<-22.5$, with some events observed at redshifts greater than 1.
-Their evolution on fast timescales has hindered high quality follow-up observations, and thus their origin and explosion/emission mechanism remains unexplained.
-In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the most comprehensive analysis of RET host galaxies.
-Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities ([O/H]) for 37.
+Their peak luminosity spans a range of $-15 <M_g<-22.5$, with some events observed at redshifts greater than 1.} Their evolution on fast timescales has hindered high quality follow-up observations, and thus their origin and explosion/emission mechanism remains unexplained.
+In this paper we \replyref{present} the largest sample of RETs to date, comprising 106 objects \replyref{discovered by} the Dark Energy Survey, and perform the most comprehensive analysis of RET host galaxies.
+Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities \replyref{([O/H])} for 37.
 We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars.
-Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs ($\langle\log \left(\mathrm{sSFR}\right)\rangle \sim -9.6$ ), indicating a link to young stellar populations, similar to stripped-envelope SNe.
-RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies $\langle12+\log\left(\mathrm{O/H}\right) \rangle \sim 9.4$.
+Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs \replyref{($\langle\log \left(\mathrm{sSFR}\right)\rangle \sim -9.6$ ),} indicating a link to young stellar populations, similar to stripped-envelope SNe.
+RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies \replyref{($\langle12+\log\left(\mathrm{O/H}\right) \rangle \sim 9.4$)}.
 There are no clear relationships between \replyref{mass or SFR} of the host galaxies and the peak magnitudes or decline rates of the transients themselves.
@@
 %%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
+\replyref{}
 \section{Introduction}
@@
 
-There are a small number of other objects in the literature that would pass the DES RET criteria, including SNLS04D4ec \citep{Arcavi2016} at $z\sim0.59$, ZTF18abvkwla \replyref{whose rapid evolution has been attributed to shock interaction, while radio emission can be explained by a collimated jet \citep{Ho2020} at $z\sim0.27$, and the rapidly-evolving SN Ic-BL-like iPTF16asu \citep{Whitesides2017} at $z\sim0.19$.
+There are a small number of other objects in the literature that would pass the DES RET criteria, including SNLS04D4ec \citep{Arcavi2016} at $z\sim0.59$, \replyref{the radio-bright} ZTF18abvkwla \replyref{ at $z=0.27$.
+whose rapid evolution and radio brightness have been attributed to a shock and a collimated jet, respectively \citep{Ho2020}, and the rapidly-evolving SN Ic-BL-like iPTF16asu \citep{Whitesides2017} at $z\sim0.19$.
 }
@@
 \replyref{AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Fox2019,Mohan2020} due to its rapid evolution and blue colour.
-AT2018cow declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}).
+The brightness of AT2018cow declined from its discovery, with constraints on the rise time of 1 day, and from X-rays through to radio wavelengths did not resemble any known SN, GRB afterglow, or kilonova (KN; \citealt{Ho2019}).
 It displayed a contracting photosphere as well as evidence for central-engine power alongside an unusual spectrum that showed similarities to broad-lined SNe Ic (SN Ic-bl) at early stages \citep[e.g.][]{Xu2018,Izzo2018}, developing to something entirely different at later epochs \citep{Perley2019} with hints of similarities to interacting SNe Ibn \citep{Fox2019}.} There are many diverse explanations for the power source of AT2018cow \replyref{proposed} in the literature, including: \replyref{engine-driven stellar explosions \citep{Ho2019,Margutti2019,Mohan2020}}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova (CEJSN; \citealt{Soker2019}); or a wind-driven transient \citep{Piro2020,Uno2020}.
-Other nearby \replyref{($z<0.1$)} rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star\replyref{black hole} merger \citep{Gillanders2020}, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} \replyref{which is a rapidly-declining, spectroscopically classified, nearby SN Ic-BL with a rapid rise to peak}, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.} \replyref{These objects evolved rapidly enough to have passed the DES RET criteria (Section \ref{subsec:new_method}) even at $z\sim1$ where they would appear slower, although they (or their host galaxies) may not necessarily have been bright enough to be detected.}
+Other nearby \replyref{($z<0.1$)} rapid transients \replyref{that would pass the DES search criteria} include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the accretion-induced collapse of a white dwarf or a white dwarf-neutron star/\replyref{black hole} merger \citep{Gillanders2020}, KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material, \replyref{SN2018gep \citep{Ho2019a} \replyref{which is a rapidly-declining, spectroscopically classified, nearby SN Ic-BL with a rapid rise to peak}, and the H-rich, relativistic CSS161010 \citep{Coppejans2020}.} \replyref{These objects evolved rapidly enough to have passed the DES RET criteria (Section \ref{subsec:new_method}) even at $z\sim1$ where they would appear slower, although they (or their host galaxies) may not necessarily have been bright enough to be detected.}
 
@@
 Even though both of these quantities depend on the redshift of the transient \replyref{(timescales, for example, are dilated by a factor of 2 at $z=1$ while higher-redshift objects may appear bluer, since the hot and bright UV is shifted into the observed bands)}, they still effectively distinguish the fast events from traditional SN types.
-\replyref{Here, we} attempt to select a sample based on observed rise times and colours at peak brightness.
+\replyref{Here, we} select a sample based on observed rise times and colours at peak brightness.
 
@@
 We train the CNN on spectroscopically confirmed SNe of all types as well as the 92 RETs identified using the \citetalias{Pursiainen2018} method (181 objects) and on spectroscopically typed AGN (182 objects), and use it to separate the sample into two photometric subtypes: AGN-like and SN-like.
-The classifier returns SNe-like objects with an accuracy of 0.992 on the test set (391 SNe and 79 AGN).
+The classifier returns SNe-like objects with an accuracy of 0.992 on the test set (\replyref{ the remaining 391 DES SNe and 79 AGN that were spectroscopically classified at the time of testing}).
 No SNe were classified as AGN-like.
 The remaining AGN classified as SNe-like are removed by manual vetting later in the process.
-The CNN does not separate the SN-like objects into RETs and other SN subtypes: this is done in the subsequent processing step.
+\replyref{While this performance is very encouraging, it should be noted that the training and validation being performed on spectroscopically typed objects, which are in general high SNR, means its performance on fainter/lower-SNR objects is not well known.}  The CNN does not separate the SN-like objects into RETs and other SN subtypes: this is done in the subsequent processing step.
 
@@
 In comparison, the many dwarf galaxies in LVL would not be detected in DES photometry, or get a redshift measurement from OzDES, and thus such a comparison sample is not representative of the way the DES RET host sample was observed.
-For completeness and illustrative purposes only, we display both the SDSS and LVL comparison samples.}
+For completeness and illustrative purposes only, we display both the SDSS and LVL (data from D.
+Perley, priv.
+communication) comparison samples.}
 
@@
 \end{figure}
-
-\section{Estimating host galaxy properties}
-\label{sec:measure}
-\subsection{Photometric stellar parameters \label{subsec:sedfit}}
-To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
-We simulate a suite of synthetic galaxy star-formation histories from which we synthesise model SEDs using stellar population models from \citet{Bruzual2003}  and a \citet{Chabrier2003} initial mass function (IMF).
-The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}.
-From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed Kron magnitudes from the deep photometric catalogue of \citetalias{Wiseman2020}.
-For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these estimate a probability density function (PDF) for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR).
-To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds.
-The results are presented in Table \ref{tab:derived}.
-These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population.
-
-\subsection{Spectroscopic gas-phase parameters \label{subsec:linefit}}
-
-To estimate parameters from the OzDES host galaxy spectra requires several processing steps.
-We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in Swann et al., \textit{in prep}).
-We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
-The resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy.
-This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole.
-There are several reasons this measurement may differ from one made at the SN explosion site, such as metallicity and age gradients or structure such as bars and discs (see e.g.
-\citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}).
-\replyref{We note that for the majority of DES RET host galaxies, particularly at higher redshift, the fibre covers a large proportion of the galaxy profile, and that the uncertainties on our derived metallicities (Section \ref{subsec:res_metallicity}) are typically of order 0.2 dex, which is much larger than the 11\% offset found in SDSS galaxies in \citet{Iglesias-Paramo2016}}.
-We proceed with our analysis with this caveat acknowledged.
-
-In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}.
-By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines.
-An example of this procedure is shown in Fig.~\ref{fig:host_spec}.
-We fit the emission lines with Gaussian profiles.
-In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution based on the variance spectrum.
-We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
-Line fluxes are presented in Table \ref{tab:fluxes}.
-
 \begin{table*}
@@
 
+\section{Estimating host galaxy properties}
+\label{sec:measure}
+\subsection{Photometric stellar parameters \label{subsec:sedfit}}
+To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.
+We simulate a suite of synthetic galaxy star-formation histories from which we synthesise model SEDs using stellar population models from \citet{Bruzual2003}  and a \citet{Chabrier2003} initial mass function (IMF).
+The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}.
+From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed Kron magnitudes from the deep photometric catalogue of \citetalias{Wiseman2020}.
+For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these estimate a probability density function (PDF) for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR).
+To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds.
+The results are presented in Table \ref{tab:derived}.
+These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population.
+
+\subsection{Spectroscopic gas-phase parameters \label{subsec:linefit}}
+
+To estimate parameters from the OzDES host galaxy spectra requires several processing steps.
+We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in Swann et al., \textit{in prep}).
+We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.
+The resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy.
+This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole.
+There are several reasons this measurement may differ from one made at the SN explosion site, such as metallicity and age gradients or structure such as bars and discs (see e.g.
+\citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}).
+\replyref{We note that for the majority of DES RET host galaxies, particularly at higher redshift, the fibre covers a large proportion of the galaxy profile, and that the uncertainties on our derived metallicities (Section \ref{subsec:res_metallicity}) are typically of order 0.2 dex, which is much larger than the 11\% offset found in SDSS galaxies in \citet{Iglesias-Paramo2016}}.
+We proceed with our analysis with this caveat acknowledged.
+
+In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}.
+By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines.
+An example of this procedure is shown in Fig.~\ref{fig:host_spec}.
+We fit the emission lines with Gaussian profiles.
+In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution based on the variance spectrum.
+We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.
+Line fluxes are presented in Table \ref{tab:fluxes}.
+
 \subsection{Estimating metallicities \label{subsec:calc_Z}}
@@
 For hosts at $z<0.3$ we are able to use the \OIII /\NII~(O3N2), \NII /\halpha~(N2), and \SII /\NII~(S2N2) line ratios.
-
+\begin{figure}
+
+\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_RETs.png}
+\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, as well as SDSS field galaxies (grey contours) and \replyref{LVL galaxies (grey circles)}.
+SFRs have not been corrected for redshift evolution.
+RET hosts lie slightly above the low-$z$ star-formation main sequence upper half of the SDSS contours, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
+\label{fig:sfms_sfr}}
+\end{figure}
 Due to the redshift range of our sample, and the limited wavelength coverage of the spectra ($3000-8000$~\AA), we are unable to use a single line ratio to estimate the oxygen abundances.
@@
 We take $1\sigma$ uncertainties from the 16\textsuperscript{th} and 84\textsuperscript{th} percentiles of these PDFs, and for DES RETs display the results in Table \ref{tab:derived}.
-\begin{figure}
-
-\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_RETs.png}
-\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, as well as SDSS field galaxies (grey contours) and \replyref{LVL galaxies (grey circles)}.
-SFRs have not been corrected for redshift evolution.
-RET hosts lie slightly above the low-$z$ star-formation main sequence upper half of the SDSS contours, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
-\label{fig:sfms_sfr}}
-\end{figure}
 
@@
 SESNe &$9.5 \pm 0.9$ & $-10.2 \pm 1.0 $ &$ 8.4 \pm 0.2$ \\
+SNe Ic-BL &$8.8 \pm 0.5$ & $-9.2 \pm 0.6 $ &$ 8.3 \pm 0.1$ \\
 LGRBs &$9.2 \pm 0.6$ & $-8.9 \pm 0.8 $ &$ 8.4 \pm 0.2$ \\
@@
 \replyref{While it is likely that RETs are a heterogeneous population comprising several progenitor scenarios, it is reasonable to infer from the rates and the host properties} that RETs are linked to very massive stars, potentially stripped of their envelopes, and possibly sharing some of the extreme properties of SLSN or LGRB \replyref{progenitors such as rapid rotation and low metallicity}.
-This hypothesis \replyref{can be extended to posit} that \replyref{some} RETs \replyref{represent} an intermediate and/or precursory step \replyref{in the late stages of evolution of a massive star that is close to forming a SLSN or LGRB, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling driving the RET light curve (\citetalias{Pursiainen2018}), but conditions are not highly tuned enough for a LGRB or SLSN and the respective central engine does not form, hence the lack of longer-term light curves.
+This hypothesis \replyref{can be extended to posit} that \replyref{some} RETs \replyref{represent} an intermediate and/or precursory step \replyref{in the late stages of evolution of a massive star that is close to forming a SLSN or LGRB, whereby the initial collapse of the star occurs leading to shock breakout and subsequent cooling driving the RET light curve (\citetalias{Pursiainen2018}), but the progenitor is sufficiently different to the progenitors of LGRBs and SLSNe such that the central engine either does not form or has properties that differ from the central engines of LGRBs or SLSNe, hence the lack of longer-term light curves.
 }
@@
 
-We thank the anonymous referee, whose input has significantly enhanced the quality of this work, particularly for giving up their time to review the work during a unprecedented time of global crisis.
-We thank Maryam Modjaz and Dan Perley for providing
+We thank the anonymous referee, whose input has significantly enhanced the quality of this work, particularly for dedicating their time to review the work during unprecedented times of global crisis.
+We thank Maryam Modjaz and Dan Perley for providing the LVL compilation data.
 
@@
 
+\section*{Data availability}
+The data underlying this article are available in the article and in its online supplementary material.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{app:b}
-
-\begin{figure*}
-\includegraphics[width=0.45\textwidth]{mc_figs/rets_s12_histfit_ssfr_final.png}
-\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SESNe, accounting for uncertainties in each bin.
-\label{fig:histfit_s12_ssfr}}
-\end{figure*}
-
 \begin{figure*}
@@
 \end{figure*}
-
-\begin{figure}
-\includegraphics[width=0.6\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
-\caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
-Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the scale vs alpha and loc vs scale distributions are two-tailed due to alpha being centred close to 0; 3) there is a degeneracy between loc and alpha for the same reason.
-Loc and scale have units of yr$^{-1}$, while alpha is dimensionless.
-Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.
-\label{fig:corner}}
-\end{figure}
 
@@
 %\twocolumn
+
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_s12_histfit_ssfr_final.png}
+\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SESNe, accounting for uncertainties in each bin.
+\label{fig:histfit_s12_ssfr}}
+\end{figure}
+
 \begin{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe Ic-BL, accounting for uncertainties in each bin.
-\label{fig:histfit_ssfr_s13}}
+\label{fig:histfit_ssfr_m19}}
 \end{figure}
@@
 \end{figure}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
+\caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs.
+Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the scale vs alpha and loc vs scale distributions are two-tailed due to alpha being centred close to 0; 3) there is a degeneracy between loc and alpha for the same reason.
+Loc and scale have units of yr$^{-1}$, while alpha is dimensionless.
+Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.
+\label{fig:corner}}
+\end{figure}
 
@@
 In this section, we present the Bayesian fits to the metallicity distributions of RETs and the comparison samples.
+
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
+\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
+\label{fig:histfit_oh_s13}}
+\end{figure}
 \begin{figure}
@@
 \end{figure}
-
-\begin{figure}
-\includegraphics[width=0.45\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
-\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
-\label{fig:histfit_oh_s13}}
-\end{figure}
 \begin{figure}
@@
 \caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe Ic-BL, accounting for uncertainties in each bin.
-\label{fig:histfit_ssfr_k15}}
+\label{fig:histfit_oh_m19}}
 \end{figure}
@@
 \end{figure}
-
 \begin{figure}

### 2020-08-13 DES_RET_Hosts_replyref2.tex
Updates from Overleaf

--- 2020-07-31 DES_RET_Hosts_replyref.tex
@@
 %\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
-\title[RET host galaxies in DES]{The Host Galaxies of 106 Rapidly Evolving Transients discovered by the Dark Energy Survey}
+\title[RET host galaxies in DES]{The Host Galaxies of 106 Rapidly Evolving Transients Discovered by the Dark Energy Survey}
 % The list of authors, and the short list which is used in the headers.
@@
 While the SN2018gep \replyref{and CSS16100 hosts are} lower in stellar mass than any DES RET ($\log \left(M/M_{\odot}\right) =8.11$ \replyref{and $7.3$, respectively),} galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}.
-The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}.
+The conclusion of \citet{Ho2019a} that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}.
 \replyref{The host of the other SN Ic-BL we compare to, iPTF16asu, is slightly more massive, but otherwise consistent with SN2018gep.}
